### 2019-06-07 01_health_data.Rmd
Created health outcomes dataset

---
title: "Health Data"
author: "Greg Macfarlane"
date: "6/6/2019"
output: html_document
---

```{r setup}
library(leaflet)
library(tidyverse)
library(tidycensus)
library(RSocrata)
library(sf)
options(tigris_use_cache=TRUE)
```

In this document we collect the health and socioeconomic data necessary for the
project from the American Community Survey and the Centers for Disease Control.

## American Community Survey
We will use the `tidycensus` package from Kyle Walker to get the datatables in 
our analysis region, which is the five boroughs of New York City.

```{r region}
# The study area includes the five boroughs of New York City
counties <- c("081", "047", "061", "005", "085")
names(counties) <- c("Queens", "Brooklyn", "Manhattan", "Bronx", "Staten Island")
```

We need to get lots of variables from the American Community Survey 5-year data.
This vector defines the variable names as well as the table/cell in the Census
API that each variable is drawn from. The comments help to identify which
table name and population type they come from.
```{r acsvariables}
variables <- c(
  "population" = "B25008_001", # TOTAL POPULATION IN OCCUPIED HOUSING UNITS BY TENURE
  "housing_units" = "B25001_001", # HOUSING UNITS
  "households" = "B19001_001", #HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2017 INFLATION-ADJUSTED DOLLARS)
  # Employment status
  "men_fulltime" = "B23022_004",
  # Estimate!!Total!!Male!!Worked in the past 12 months!!Usually worked 35 or more hours per week
  "women_fulltime" = "B23022_028",
  #Estimate!!Total!!Female!!Worked in the past 12 months!!Usually worked 35 or more hours per week
  # LIVING ARRANGEMENTS OF ADULTS 18 YEARS AND OVER BY AGE
  # everyone who
  "adults" = "B09021_001",
  "lives_alone" = "B09021_002",
  "child_of_hhr" = "B09021_005",
  "other_rel" = "B09021_006",
  "other_nonrel" = "B09021_007",
  # EDUCATIONAL ATTAINMENT BY EMPLOYMENT STATUS FOR THE POPULATION 25 TO 64 YEARS
  "college" = "B23006_016",
  # RACE
  "black" = "B02001_003",
  "asian" = "B02001_005",
  "pacific" = "B02001_006",
  "nativeam" = "B02001_004",
  # HISPANIC OR LATINO ORIGIN BY SPECIFIC ORIGIN
  # The number of hispanic individuals needs to be drawn from a different table.
  "hispanic" = "B03001_003",
  #MEDIAN HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2017 INFLATION-ADJUSTED DOLLARS)
  "income" = "B19013_001",
  #HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2017 INFLATION-ADJUSTED DOLLARS)
  "inc_0010" = "B19001_002",  "inc_1015" = "B19001_003", "inc_1520" = "B19001_004",
  "inc_2025" = "B19001_005", "inc_2530" = "B19001_006", "inc_3035" = "B19001_007",
  "inc_125"  = "B19001_015", "inc_150"  = "B19001_016", "inc_200"  = "B19001_017",
  #AGE BY RATIO OF INCOME TO POVERTY LEVEL IN THE PAST 12 MONTHS.
  # we really only need the numbers of individuals in each age group, and the groups
  # are more coarse here than in the sex by age table.
  "age_0005" = "B17024_002", "age_0611" = "B17024_015", "age_1217" = "B17024_028",
  "age_1824" = "B17024_041", "age_2534" = "B17024_054",
  "age_3544" = "B17024_067", "age_4554" = "B17024_080", "age_5564" = "B17024_093",
  "age_6574" = "B17024_106",
  "age_75up" = "B17024_119"
)
```

Now that we've defined the necessary variables and geographic scope, we can pull
the data from the API. Because the data coming from census are counts, we need 
to transform the numbers into percents of the relevant population denominator.

```{r acs}
acs <- get_acs(geography = "tract", variables = variables, year = 2017,
               state = "NY", county = counties, geometry = TRUE) %>%
  select(-moe) %>%
  spread(variable, estimate) %>%
  filter(adults > 0) %>%
  mutate(area = as.numeric(st_area(geometry) * 1e-6)) %>%
  # area is in m^2, change to km^2
  transmute(
    geoid = GEOID,
    county_fips = substr(GEOID, 3, 5),
    borough = case_when(
      county_fips == "081" ~ "Queens",
      county_fips == "047" ~ "Brooklyn",
      county_fips == "061" ~ "Manhattan",
      county_fips == "005" ~ "Bronx",
      county_fips == "085" ~ "Staten Island",
      TRUE ~ as.character(NA)
    ),
    population, households, housing_units, adults,
    density = households / area,
    income,
    # many of the variables come in raw counts, but we want to consider
    # them as shares of a relevant denominator.
    lowincome    = 100 * (inc_0010 + inc_1015 + inc_1520 + inc_2530 +
                            inc_3035) / households,
    highincome   = 100 * (inc_125 + inc_150 + inc_200) / households,
    fulltime     = 100 * (men_fulltime + women_fulltime) / adults,
    college      = 100 * college / adults,
    single       = 100 * (lives_alone + child_of_hhr + other_rel +
                            other_nonrel) / adults,
    youth        = 100 * (age_0005 + age_0611 + age_1217) / population,
    young_adults = 100 * (age_1824 + age_2534) / population,
    seniors      = 100 * (age_6574 + age_75up) / population,
    black        = 100 * black / population,
    asian        = 100 * asian / population,
    hispanic     = 100 * hispanic / population,
    other        = 100 * (nativeam + pacific) / population
  )
```

## 500 Cities
The Centers for Disease Control and Prevention makes small-area estimates on
key health indicators available through its 500 Cities data program (CDC5002016).
The indicators are multilevel aggregations and imputations of BRFSS responses
(Wang2018, Wang2017), and have been recently used to study the tract-level
link between gentrification and urban health (Gibbons2018). We use two
indicators as our dependent variables in this study: the share of adults
in a Census tract who are obese, and the share of adults who participate in no
leisure-time physical activity. To improve clarity in our interpretation, we use
the complement of the second variable --- the share of tract adults who
participate in {\em some} physical activity --- even if the amount is not
sufficient to affect overall health. Both indicators are estimated for the year
2016.

The CDC 500 cities project makes its data available through the Socrata API.
The url endpoints for each data object are different, though we have identified
them as below. We pre-filter the data to New York to save ourselves and the
API a bit of time. For each URL endpoint, get the data through Socrata (you will
need your own Socrata API key), filter to the FIPS codes we specified above, and
trim to only the data values we want to keep.

```{r cdc500}
cdc_urls <- list(
  "physact" = "https://chronicdata.cdc.gov/resource/axqz-rkkp.json?stateabbr=NY",
  "obesity" = "https://chronicdata.cdc.gov/resource/bjvu-3y7d.json?stateabbr=NY"
)

cdc500 <- lapply(cdc_urls, function(url){
  read.socrata(url, app_token = Sys.getenv("CDC_KEY"),
               stringsAsFactors = FALSE) %>%
    tbl_df() %>%
    filter(tractfips %in% acs$geoid) %>%
    transmute( geoid = tractfips, value = as.numeric(data_value ), year = year)
}) %>%
  bind_rows(.id = "measure") %>%
  spread(measure, value) %>%
  mutate(physact = 100 - physact)
```

Save the dataset for further analysis.
```{r writeout}
tracts <- left_join(acs, cdc500, by = "geoid") %>%
  filter(!is.na(obesity), !is.na(income)) %>% 
  write_rds("data/tracts.rds")
```

### 2019-06-07 02_parks_data.Rmd
Recreate parks dataset
Instead of using the geojson Nico downloaded and manipulated manually, we are
working directly from NYC's open data API. I also made a change by adding
cemeteries and combining shapes that belong to a common park, and removed
tennis courts and baseball diamonds, etc. that are part of a larger facility.

---
title: "Parks Data"
author: "Greg Macfarlane"
date: "6/6/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup}
library(leaflet)
library(tidyverse)
library(RSocrata)
library(leaflet)
library(sf)
```

In this document we get the parks data from the New York City open data
repository and do some cleaning. First, we get the parks dataset. The original
data dictionary is available at 
[on Github](https://github.com/CityOfNewYork/nyc-planimetrics/blob/master/Capture_Rules.md#open-space)
```{r parks}
parks_url <- "https://data.cityofnewyork.us/api/geospatial/y6ja-fw4f?method=export&format=GeoJSON"
parks <- st_read(parks_url, stringsAsFactors = FALSE) %>%
  mutate(shape_area = as.numeric(shape_area))
```

## Cleaning
The map of Flushing Meadows in Queens below shows some of the difficulties of this dataset:
  - First, the park is constructed of multiple outlines that limits the size of 
  the total park. This makes Flushing Meadows appear smaller than Central Park, 
  which is a single large park. 
  - Second, the dataset includes tennis parks and baseball fields as separate 
  facilities.
  - Third, parking lots for stadia (in this case Citi Field) are included as 
  open park space. We should remove these as they are categorically unlike other
  green spaces.
  - Fourth, important green spaces like cemeteries are in a different dataset.

```{r fm1}
leaflet(st_buffer(parks %>% filter(grepl("Flushing Meadows", park_name)), dist = 0.000001)) %>%
  addProviderTiles(providers$Esri.WorldGrayCanvas) %>%
  addPolygons(label = ~as.character(park_name), stroke = 0.5)
```

First, we manually remove the park facilities corresponding to stadia and their
associated parking lots, and then filter out facilities that are not explicitly
park boundaries, as identified by the code `4980`.

```{r notparks}
notparks <- c(9498000833, 14498000872, 14498000794, # citi field, Yankee stadium, garage
              9498000631)  # USTA Billie Jean Tennis Center
parks <- parks %>% 
  filter(feat_code == 4980) %>%
  filter(!(source_id %in% notparks))
```

```{r fm2}
leaflet(st_buffer(parks %>% filter(grepl("Flushing Meadows", park_name)), dist = 0.000001)) %>%
  addProviderTiles(providers$Esri.WorldGrayCanvas) %>%
  addPolygons(label = ~as.character(park_name), stroke = 0.5)
```

With those areas removed, we build a 30-foot buffer around each park and 
dissolve interior boundaries. This will make parks that are effectively the same
facility a single polygon feature. We also re-calculate the area of the parks in
acres and remove parks smaller than half an acre.

```{r dissolve}
dissolved <- parks %>%
  #filter(grepl("Flushing Meadows", park_name)) %>%
  st_transform(3628) %>%
  st_buffer(30) %>%
  group_by(parknum) %>%
  summarise(area = sum(shape_area),
            park_name = park_name[1]) %>%
  mutate(sqft = st_area(.), acres = units::set_units(sqft, acres)) 
```

```{r fm3}
leaflet(st_transform(dissolved, 4326) ) %>%
  addProviderTiles(providers$Esri.WorldGrayCanvas) %>%
  addPolygons(stroke = 0.5)
```

### Cemeteries
Some important green spaces that can be used for physical activity but are not
parks include cemeteries. These are stored in a separate dataset called Open
Space (Other) with the feature code `2500`.

```{r cemeteries}
cemeteries_url <- "https://data.cityofnewyork.us/api/geospatial/pckb-8r2z?method=export&format=GeoJSON"
cemeteries <- st_read(cemeteries_url) %>%
  filter(feature_co == 2500)
```

```{r d_cemeteries}
dissolved_cemeteries <- cemeteries %>%
  st_transform(3628) %>%
  st_buffer(5) %>%
  mutate(sqft = st_area(.), acres = units::set_units(sqft, acres))
```

```{r cemeteries_map}
leaflet(st_transform(dissolved_cemeteries, 4326)) %>%
  addProviderTiles(providers$Esri.WorldGrayCanvas) %>%
  addPolygons(stroke = 0.5)
```

Now we can join the cemeteries data to the parks data and write out the results
```{r write}
rbind(
  dissolved %>% transmute(name = park_name, acres, type = "park"),
  dissolved_cemeteries %>% transmute(name, acres, type = "cemetery")
) %>%
  filter(as.numeric(acres) > 0.5) %>%
  st_simplify(preserveTopology = TRUE) %>%
  write_rds("data/open_spaces.rds")
```

### 2019-06-17 03_logsums.Rmd
Calculate the distance and size-based logsums

---
title: "Logsums"
author: "Greg Macfarlane"
date: "6/7/2019"
output: html_document
---

```{r setup}
library(tidyverse)
library(sf)
library(spdep)
library(leaflet)
```

In this document we calculate the distance between each tract in New York City 
and each park to help calculate a logsum-based measure of accessibility. We 
cleaned and gathered the data in the previous two pages.

```{r load}
open_spaces <- read_rds("data/open_spaces.rds")
tracts <- read_rds("data/tracts.rds")
```

We are going to do a point-to-polygon distance calculation. The geometric centroid
of the tracts are not satisfying, so we will use the population-weighted centroid
instead.

```{r pop_weighted_centroids}
pop_weighted_centroids <- tracts %>% tbl_df() %>%
  dplyr::select(geoid) %>%
  left_join(
    read_csv("https://www2.census.gov/geo/docs/reference/cenpop2010/tract/CenPop2010_Mean_TR36.txt") %>%
      transmute(geoid = str_c(STATEFP, COUNTYFP, TRACTCE), LATITUDE, LONGITUDE)
  ) %>%
  # convert to sf and project into the feet-based projection used in the
  # parks dataset.
  st_as_sf(crs = 4326, coords = c("LONGITUDE", "LATITUDE")) %>%
  st_transform(3628)
```

The population-weighted centroid also serves as the orientation for the spatial
weights matrix.

```{r W}
# determine which tracts are neighbors of each other. Need to be less than
# 1.8 miles away from the centroids
tracts.dnn <- dnearneigh(as(pop_weighted_centroids, "Spatial"), 0, 1.8 * 5280)
# calculate the inverse distance to use as a weight on the neighbor connection
dists <- nbdists(tracts.dnn, as(pop_weighted_centroids, "Spatial"))
dists.inv <- lapply(dists, function(x) 1 / x)
# get the spatial weights matrix and its trace to use in any impact analyses
W <- nb2listw(neighbours = tracts.dnn, glist = dists.inv,
              zero.policy = TRUE, style = "W")
trMC <- trW(as(W, "CsparseMatrix"), type="MC") # trace used in montecarlo impacts
print(W, zero.policy = TRUE)
```

## Distances
We want to make sure that the distance between a park and a tract centroid is
based on the edge of the polygon instead of the centroid thereof, so that spaces
at the corners of Central park, for instance, don't appear as longer than they should be.
It seems that things are working appropriately.

```{r test_measurement}
central_park <- open_spaces %>% filter(name == "Central Park")
pop_weighted_centroids$central_park <- log(as.numeric(st_distance(pop_weighted_centroids, central_park)))

dmeasure <- colorNumeric(palette = "Blues", domain = pop_weighted_centroids$central_park)
leaflet(pop_weighted_centroids %>% st_transform(4326)) %>%
  addProviderTiles(providers$Esri.WorldGrayCanvas) %>%
  addCircleMarkers(color = ~dmeasure(central_park))
```

Now we can calculate everything.
```{r distances}
# distances from all tract centroids to all parks
distances <- st_distance(pop_weighted_centroids, open_spaces, byid = TRUE) %>%
  units::set_units(miles) %>%
  units::drop_units()

# assert that a tract must be at least 1/10 mile from a park
distances <- pmax(distances, 0.1)
```

```{r write}
write_rds(distances, "data/distances.rds")
write_rds(W, "data/W.rds")
```

## Logsums
Here's the function we use to calculate the logsums
```{r}
#' Calculate destination choice logsums from a distance matrix
#'
#' @param d An $n\times p$ matrix with the distance from all tracts to
#'   all parks
#' @param sizes A p-length vector of park sizes
#' @param tweets A p-length vector of tweets at parks
#' @param betas A vector containing the size, distance, and tweet coefficients.
#'   If we submit two variables the tweets are ignored.
#'
#' @return An n-length vector containing the weighted log-sum based
#'   accessibility between a tract and all parks.
#' @details If we have n tracts and p parks, distances needs to be a
#'
calculate_park_logsums <- function(d, sizes, tweets = NULL,
                                   betas = c(-0.4,0.2,0.001)){

  # A is n x p
  a <- betas[1] * d

  # B is p x 1
  b <- betas[2] * sizes

  if(!is.null(tweets))
    b <- b + betas[3] * tweets

  # calculate observed utility by adding the weighted park-level attributes
  # to the columns of the matrix
  # V is n x p, with b added by-column to each element in a
  V <- sweep(a, 2, b, `+`)

  # log-sum of exponentiated utility, Output is n-length vector
  log(rowSums(exp(V)))

}
```

### 2019-07-15 02_parks_data.Rmd
Revise open spaces builder
Calculate trails, playgrounds, courts, etc.

@@
 
+The New York City open data portal also contains a list of designated trails 
+within parks.
+
+```{r trails}
+trails <- read_csv("https://data.cityofnewyork.us/api/views/vjbm-hsyr/rows.csv?accessType=DOWNLOAD")
+trails2 <- jsonlite::fromJSON("https://www.nycgovparks.org/bigapps/DPR_Hiking_001.json")
+parks_with_trails <- c(trails$ParkID, trails2$Prop_ID)
+```
+
 ## Cleaning
@@
   - Second, the dataset includes tennis parks and baseball fields as separate 
-  facilities.
+  facilities. We want to include these as attributes of their containing park
+  rather than independent facilities.
   - Third, parking lots for stadia (in this case Citi Field) are included as 
@@
 First, we manually remove the park facilities corresponding to stadia and their
-associated parking lots, and then filter out facilities that are not explicitly
-park boundaries, as identified by the code `4980`.
+associated parking lots, and then tag facilities that are not explicitly
+park boundaries.
 
@@
               9498000631)  # USTA Billie Jean Tennis Center
+
 parks <- parks %>% 
-  filter(feat_code == 4980) %>%
-  filter(!(source_id %in% notparks))
-```
-
-```{r fm2}
-leaflet(st_buffer(parks %>% filter(grepl("Flushing Meadows", park_name)), dist = 0.000001)) %>%
-  addProviderTiles(providers$Esri.WorldGrayCanvas) %>%
-  addPolygons(label = ~as.character(park_name), stroke = 0.5)
+  filter(!(source_id %in% notparks)) %>%
+  mutate(
+    courts = ifelse(grepl("Courts", landuse), TRUE, FALSE),
+    playgrounds = ifelse(grepl("Playground", landuse), TRUE, FALSE),
+    trails = ifelse(parknum %in% parks_with_trails, TRUE, FALSE)
+  ) 
 ```
@@
 With those areas removed, we build a 30-foot buffer around each park and 
-dissolve interior boundaries. This will make parks that are effectively the same
-facility a single polygon feature. We also re-calculate the area of the parks in
-acres and remove parks smaller than half an acre.
+dissolve interior boundaries based on the park number. Tennis courts, etc. become
+boolean variables indicating whether the park has the facilities or not. This
+will make parks that are effectively the same facility a single polygon feature.
+We also re-calculate the area of the parks in acres and remove parks smaller
+than half an acre.
 
@@
 dissolved <- parks %>%
-  #filter(grepl("Flushing Meadows", park_name)) %>%
-  st_transform(3628) %>%
-  st_buffer(30) %>%
+  filter(!is.na(parknum)) %>%
   group_by(parknum) %>%
-  summarise(area = sum(shape_area),
-            park_name = park_name[1]) %>%
-  mutate(sqft = st_area(.), acres = units::set_units(sqft, acres)) 
+  filter(shape_area > 0.5 * 43560 | courts) %>%
+  summarise(
+    area = sum(shape_area), 
+    courts = any(courts), 
+    playgrounds = any(playgrounds),
+    trails = any(trails),
+    park_name = park_name[1]
+  ) %>%
+  mutate(sqft = st_area(.), acres = units::set_units(sqft, acres)) %>%
+  st_transform(3628)
 ```
@@
   addProviderTiles(providers$Esri.WorldGrayCanvas) %>%
-  addPolygons(stroke = 0.5)
+  addPolygons(stroke = 0.5,)
 ```
@@
 rbind(
-  dissolved %>% transmute(name = park_name, acres, type = "park"),
-  dissolved_cemeteries %>% transmute(name, acres, type = "cemetery")
+  dissolved %>% 
+    transmute(id = parknum, name = park_name, acres, courts, playgrounds, trails, 
+              type = "park"),
+  dissolved_cemeteries %>% 
+    transmute(id = source_id, name, acres, courts = FALSE, playgrounds = FALSE, 
+              trails = FALSE, type = "cemetery")
   ) %>%
@@
   st_simplify(preserveTopology = TRUE) %>%
-  write_rds("data/open_spaces.rds")
+  write_rds("data/open_spaces.rds") %>%
+  geojsonio::geojson_write(file = "data/open_spaces.geojson")
 ```

### 2019-07-15 parks_access/ui.R

@@ -1,0 +1,68 @@
+#
+# This is the user-interface definition of a Shiny web application. You can
+# run the application by clicking 'Run App' above.
+#
+# Find out more about building applications with Shiny here:
+#
+#    http://shiny.rstudio.com/
+#
+
+library(shiny)
+library(leaflet)
+
+vars <- c(
+    "Is SuperZIP?" = "superzip",
+    "Centile score" = "centile",
+    "College education" = "college",
+    "Median income" = "income",
+    "Population" = "adultpop"
+)
+
+
+navbarPage(
+    "Park Accessibility", id="nav",
+    
+    tabPanel(
+        "Interactive map",
+        div(class="outer",
+            
+            tags$head(
+                # Include our custom CSS
+                includeCSS("styles.css"),
+                includeScript("gomap.js")
+            ),
+            
+            # If not using custom CSS, set height of leafletOutput to a number instead of percent
+            leafletOutput("map", width="100%", height="100%"),
+            
+            # Shiny versions prior to 0.11 should use class = "modal" instead.
+            absolutePanel(
+                id = "controls", class = "panel panel-default", fixed = TRUE,
+                top = 60, left = 30, right = "auto", bottom = "auto",
+                width = 330, height = "auto",
+                
+                h2("Tract Accessibility"),
+                
+                sliderInput("distance_coef", "Distance Effect", min = -5, max = -0.01,
+                            step = 0.1, value = -1.9),
+                sliderInput("size_coef", "Size Effect", min = 0.01, max = 5,
+                            step = 0.1, value = .3),
+                conditionalPanel("input.color == 'superzip' || input.size == 'superzip'",
+                                 # Only prompt for threshold when coloring or sizing by superzip
+                                 numericInput("threshold", "SuperZIP threshold (top n percentile)", 5)
+                ),
+                
+                plotOutput("histCentile", height = 200),
+                plotOutput("scatterObesity", height = 250)
+            ),
+            
+            tags$div(
+                id="cite",
+                'Data compiled for ', tags$em('Coming Apart: The State of White America, 1960–2010'), ' by Charles Murray (Crown Forum, 2012).'
+            )
+        )
+    ),
+    
+    conditionalPanel("false", icon("crosshair"))
+    
+)

### 2019-07-15 03_logsums.Rmd
Revise logsum function
It's now more simple with a basic impedance and size term.

@@
 ## Logsums
-Here's the function we use to calculate the logsums
+
+Here's the function we use to calculate the logsums. 
 ```{r}
@@
 #'
-#' @param d An $n\times p$ matrix with the distance from all tracts to
+#' @param impedance An $n\times p$ matrix with the distance from all tracts to
 #'   all parks
-#' @param sizes A p-length vector of park sizes
-#' @param tweets A p-length vector of tweets at parks
-#' @param betas A vector containing the size, distance, and tweet coefficients.
-#'   If we submit two variables the tweets are ignored.
+#' @param size_term A p-length vector of the park size terms
 #'
@@
 #'
-calculate_park_logsums <- function(d, sizes, tweets = NULL,
-                                   betas = c(-0.4,0.2,0.001)){
-
-  # A is n x p
-  a <- betas[1] * d
-
-  # B is p x 1
-  b <- betas[2] * sizes
-
-  if(!is.null(tweets))
-    b <- b + betas[3] * tweets
+calculate_park_logsums <- function(impedance, size_term){
 
@@
   # V is n x p, with b added by-column to each element in a
-  V <- sweep(a, 2, b, `+`)
+  V <- sweep(impedance, 2, size_term, `+`)
 
@@
   log(rowSums(exp(V)))
-
 }
 ```
+
+```{r gravity}
+logsum_vars <- tracts %>%
+  transmute(
+    geoid, 
+    # Log-sum based utilities, without and with Twitter data
+    access_ls = calculate_park_logsums(
+      log(distances), open_spaces$acres, betas = c(-0.5, 0.05)),
+    # Normalize the logsum onto the Z-scale
+    access_ls_n = (access_ls - mean(access_ls) ) / sd(access_ls)
+  ) %>%
+  st_set_geometry(NULL)
+```
+
+```{r binary}
+tracts_access <- tracts %>%
+  left_join(logsum_vars, by = "geoid") %>%
+  mutate(access_025 = ifelse(geoid %in% inside_025$geoid, TRUE, FALSE))
+
+tracts_sp <- as(tracts_access, "Spatial")
+```
+
+```{r}
+# this interactive map is much easier to create and explore
+pal <- colorQuantile("GnBu", tracts_access$access_ls_n, n = 5)
+bin <- colorFactor("Dark2", tracts_access$access_025)
+leaflet(tracts_access) %>%
+  addProviderTiles(providers$CartoDB.Positron) %>%
+  addPolygons(group = "access", color = ~ pal(access_ls_n),
+              label = ~as.character(round(access_ls_n,2))) %>%
+  # addPolygons(group = "tweets", color = ~ pal(tweets_ls),
+  #             label = ~as.character(round(tweets_ls,2))) %>%
+  addPolygons(group = "1/4 mile", color = ~ bin(access_025)) %>%
+  addLayersControl(baseGroups = c("access", "tweets", "1/4 mile"))
+```

### 2019-07-15 R/logsums.R

@@ -1,0 +1,20 @@
+#' Calculate destination choice logsums from a distance matrix
+#'
+#' @param impedance An $n\times p$ matrix with the distance from all tracts to
+#'   all parks
+#' @param size_term A p-length vector of the park size terms
+#'
+#' @return An n-length vector containing the weighted log-sum based
+#'   accessibility between a tract and all parks.
+#' @details If we have n tracts and p parks, distances needs to be a
+#'
+calculate_park_logsums <- function(impedance, size_term){
+  
+  # calculate observed utility by adding the weighted park-level attributes
+  # to the columns of the matrix
+  # V is n x p, with b added by-column to each element in a
+  V <- sweep(impedance, 2, size_term, `+`)
+  
+  # log-sum of exponentiated utility, Output is n-length vector
+  log(rowSums(exp(V)))
+}

### 2019-07-15 parks_access/server.R
Add shiny app
This app allows a user to play with the coefficients and estimate the effect of changing parameters on the effect of park access on health.

@@ -1,0 +1,97 @@
+#
+# This is the server logic of a Shiny web application. You can run the
+# application by clicking 'Run App' above.
+#
+# Find out more about building applications with Shiny here:
+#
+#    http://shiny.rstudio.com/
+#
+
+library(shiny)
+library(here)
+library(sf)
+library(leaflet)
+library(tidyverse)
+
+# load data
+openspaces <- read_rds(here("data/open_spaces.rds"))
+distances <- read_rds(here("data/distances.rds"))
+tracts <- read_rds(here("data/tracts.rds")) %>% st_transform(4326)
+source(here("R/logsums.R"))
+
+# Define server logic required to draw a histogram
+shinyServer(function(input, output) {
+    
+    # Create the map
+    output$map <- renderLeaflet({
+        leaflet() %>%
+            addProviderTiles(providers$Esri.WorldGrayCanvas) %>%
+            setView(lat = 40.7128, lng = -74.0060, zoom = 11)
+    })
+    
+    # Calculate the log-sum values for park choice
+    colorData <- reactive({
+        distance_c <- input$distance_coef
+        size_c <- input$size_coef
+        courts_c <- 0
+        playgrounds_c <- 0
+        trails_c <- 0
+        
+        size_term <- openspaces %>%
+            mutate(size_term  = log(as.numeric(acres)) * scoef + 
+                       courts * courts_c +
+                       playgrounds * playgrounds_c + 
+                       trails * trails_c
+                   ) %>%
+            pull(size_term)
+        
+        suppressWarnings(
+            
+            ls <- calculate_park_logsums(impedance = log(distances) * distance_c, 
+                                         size_term = size_term)
+        )
+        
+        (ls - mean(ls)) / sd(ls)
+        
+    })
+    
+    output$histCentile <- renderPlot({
+        hist(colorData(), 
+             main = "Accessibility",
+             xlab = "Percentile",
+             xlim = range(colorData()),
+             col = '#00DD00',
+             border = 'white')
+    })
+    
+    output$scatterObesity <- renderPlot({
+        df <- data_frame(
+            obesity = tracts$obesity,
+            access = colorData()
+        )
+        
+        ggplot(df, aes(x = access, y = obesity)) +
+            geom_point() +
+            stat_smooth(method = "lm")
+    })
+    
+    
+    # This observer is responsible for maintaining the circles and legend,
[…]

### 2019-07-15 parks_access/server.R
Updates to application

@@ -31,10 +31,10 @@ shinyServer(function(input, output) {
     
     # Calculate the log-sum values for park choice
     colorData <- reactive({
-        distance_c <- input$distance_coef
-        size_c <- input$size_coef
+        distance_c <- -1 * input$distance_c
+        size_c <- input$size_c
         courts_c <- 0
-        playgrounds_c <- 0
+        playgrounds_c <- input$playground
         trails_c <- 0
         
         size_term <- openspaces %>%
@@ -72,7 +72,8 @@ shinyServer(function(input, output) {
         
         ggplot(df, aes(x = access, y = obesity)) +
             geom_point() +
-            stat_smooth(method = "lm")
+            stat_smooth(method = "lm") + 
+            xlab("Access Score") + ylab("Obesity Rate")
     })
     
     

### 2019-07-15 parks_access/ui.R

@@ -10,15 +10,6 @@
 library(shiny)
 library(leaflet)
 
-vars <- c(
-    "Is SuperZIP?" = "superzip",
-    "Centile score" = "centile",
-    "College education" = "college",
-    "Median income" = "income",
-    "Population" = "adultpop"
-)
-
-
 navbarPage(
     "Park Accessibility", id="nav",
     
@@ -43,10 +34,12 @@ navbarPage(
                 
                 h2("Tract Accessibility"),
                 
-                sliderInput("distance_coef", "Distance Effect", min = -5, max = -0.01,
-                            step = 0.1, value = -1.9),
-                sliderInput("size_coef", "Size Effect", min = 0.01, max = 5,
+                sliderInput("distance_c", "Distance Effect (negative)", min = 0.1, max = 5,
+                            step = 0.1, value = 1.9),
+                sliderInput("size_c", "Size Effect (positive)", min = 0.01, max = 5,
                             step = 0.1, value = .3),
+                sliderInput("playground", "Playground Effect", min = 0, max = 5,
+                            step = 1, value = 1),
                 conditionalPanel("input.color == 'superzip' || input.size == 'superzip'",
                                  # Only prompt for threshold when coloring or sizing by superzip
                                  numericInput("threshold", "SuperZIP threshold (top n percentile)", 5)

### 2019-07-17 03_logsums.Rmd
Readjust location of logsum calculator script

--- 2019-06-17 03_logsums.Rmd
@@
 ```{r setup}
+knitr::opts_chunk$set(cache = TRUE)
 library(tidyverse)
@@
 
-Now we can calculate everything.
+Now we can calculate the distance from every park to every tract population
+centroid, and write the distances and neighbors weights matrix to a file.
 ```{r distances}
@@
 distances <- pmax(distances, 0.1)
-```
 
-```{r write}
 write_rds(distances, "data/distances.rds")
@@
 ## Logsums
-Here's the function we use to calculate the logsums
-```{r}
-#' Calculate destination choice logsums from a distance matrix
-#'
-#' @param d An $n\times p$ matrix with the distance from all tracts to
-#'   all parks
-#' @param sizes A p-length vector of park sizes
-#' @param tweets A p-length vector of tweets at parks
-#' @param betas A vector containing the size, distance, and tweet coefficients.
-#'   If we submit two variables the tweets are ignored.
-#'
-#' @return An n-length vector containing the weighted log-sum based
-#'   accessibility between a tract and all parks.
-#' @details If we have n tracts and p parks, distances needs to be a
-#'
-calculate_park_logsums <- function(d, sizes, tweets = NULL,
-                                   betas = c(-0.4,0.2,0.001)){
 
-  # A is n x p
-  a <- betas[1] * d
+Here's the function we use to calculate the logsums. 
+```{r calculate_park_logsums}
+source("R/logsums.R")
+print(calculate_park_logsums)
+```
 
-  # B is p x 1
-  b <- betas[2] * sizes
+We use this function with asserted beta values of -1.98 and 0.3 to calculate the
+accessibility logsum.
+```{r logsum_vars}
+logsum_vars <- tracts %>%
+  transmute(
+    geoid, 
+    # Log-sum based utilities, without and with Twitter data
+    access_ls = calculate_park_logsums(
+      log(distances) * -1.98, log(open_spaces$acres) * 0.3
+    ),
+    # Normalize the logsum onto the Z-scale
+    access_ls_n = (access_ls - mean(access_ls) ) / sd(access_ls)
+  ) %>%
+  st_set_geometry(NULL)
+```
 
-  if(!is.null(tweets))
-    b <- b + betas[3] * tweets
+We are also interested in looking at what happens when the tracts are within a 
+10-minute walk of a park, the threshold established by the Trust for Public Lands.
+```{r nyc10mw}
+access_10mw <- st_read("data/nyc_10mw.geojson") %>%
+  summarise(d = 1)
 
-  # calculate observed utility by adding the weighted park-level attributes
-  # to the columns of the matrix
-  # V is n x p, with b added by-column to each element in a
-  V <- sweep(a, 2, b, `+`)
+inside_access <- pop_weighted_centroids %>%
+  st_transform(4326) %>%
+  st_join(access_10mw, st_intersects) %>%
+  filter(!is.na(d))
 
-  # log-sum of exponentiated utility, Output is n-length vector
-  log(rowSums(exp(V)))
+tracts_access <- tracts %>%
+  left_join(logsum_vars, by = "geoid") %>%
+  mutate(walk_10 = ifelse(geoid %in% inside_access$geoid, TRUE, FALSE)) %>%
+  write_rds("data/tracts_acces.rds")
+```
 
-}
+Here's a map of the values 
+```{r access_map}
+# this interactive map is much easier to create and explore
+pal <- colorQuantile("GnBu", tracts_access$access_ls_n, n = 5)
+bin <- colorFactor("Dark2", tracts_access$walk_10)
+leaflet(tracts_access) %>%
+  addProviderTiles(providers$Esri.WorldGrayCanvas) %>%
+  addPolygons(group = "access", color = ~ pal(access_ls_n),
+              label = ~as.character(round(access_ls_n,2))) %>%
+  # addPolygons(group = "tweets", color = ~ pal(tweets_ls),
+  #             label = ~as.character(round(tweets_ls,2))) %>%
+  addPolygons(group = "10-minute walk", color = ~ bin(walk_10)) %>%
+  addLayersControl(baseGroups = c("access", "tweets", "10-minute walk"))
 ```

### 2019-07-17 04_estimation.Rmd
Readjust location of logsum calculator script

---
title: "04_estimation"
author: "Greg Macfarlane"
date: "6/17/2019"
output: html_document
---

```{r setup}
knitr::opts_chunk$set(cache = TRUE)
library(tidyverse)
library(sf)
library(spatialreg)
library(texreg)
```

We load the data prepared previously. There is a file for each park and its 
attribute, for each tract and its attributes, and the distance matrix between 
parks and tracts.

```{r loaddata}
tracts_access <- read_rds("data/tracts_acces.rds")
W <- read_rds("data/W.rds")
trMC <- trMC <- trW(as(W, "CsparseMatrix"), type="MC")
tracts_sp <- as(tracts_access, "Spatial")
```

```{r base_formula}
base_formula <- formula(
  ~ log(density) + log(income) +
    fulltime + college + single +
    youth + young_adults + seniors + # need to leave out a category for collinearity
    black + asian + hispanic + other)
```

```{r spatial selection}
physact_base_sem <- errorsarlm(update(base_formula, physact ~ .),
                               data = tracts_sp, listw = W, zero.policy = TRUE)
physact_base_sdm <- lagsarlm(update(base_formula, physact ~ .),
                             data = tracts_sp, listw = W, zero.policy = TRUE,
                             type = "mixed")
test_sdmsem <- lmtest::lrtest(physact_base_sem, physact_base_sdm)
```

```{r access_sdm}
# estimate models
pa_access_sem <- update(physact_base_sem, .~ . + access_ls)
pa_quarter_sem <- update(physact_base_sem, .~ . + walk_10)

pa_models <- list("Base" = physact_base_sem,
                  "Access: logsum" = pa_access_sem,
                  "Access: 10-min walk" = pa_quarter_sem)
```

```{r screen_pa_models}
view_kable(
htmlreg(pa_models, digits = 4, table = FALSE, single.row = TRUE, 
                   caption.above = TRUE, caption = "Spatial Error Model ",
          stars = c(0.001, 0.01, 0.05, 0.1) )
)
```

```{r}
view_kable <- function(x){
  tab <- paste(capture.output(x))
  tf <- tempfile(fileext = ".html")
  writeLines(tab, tf)
  viewer <- getOption("viewer")
  viewer(tf)
}
```

```{r obesity_models}
obesity_models <- lapply(pa_models, function(model){
  update(update(model, obesity ~ . + physact))
})

names(obesity_models) <- names(pa_models)
```

```{r screen_obesity_models}
screenreg(obesity_models, digits = 4, table = FALSE)
```

```{r screen_obese_models, eval = FALSE}
  screenreg(obesity_models, digits = 4, table = FALSE, ci.force = TRUE,
          single.row = TRUE, caption = "Spatial Error Model Estimates of Effect on Obesity Rates",
          caption.above = TRUE, custom.coef.names = c(
            "(Intercept)", "log(Density)", "log(Income)",
            "Fulltime", "College-educated",  "Single Adults",
            "Youth (0-17)", "Young adults (18-34)",
            "Seniors (65+)", "Black population share",
            "Asian population share",
            "Hispanic population share", "Other Minorities",
            "Physical activity",
            "Spatial correlation", "Access: Logsum", "Access: 10-min walk"
          ))
```

```{r obesityplot}
names_for_terms <- c(
  "(Intercept)", "log(density)", "log(Income)",
  "Fulltime", "College-educated",  "Single Adults",
  "Youth (0-17)", "Young adults (18-34)",
  "Seniors (65+)", "Black population share",
  "Asian population share",
  "Hispanic population share", "Other Minorities",
  "$\\gamma$: spatial correlation","Physical activity",
  "Access: Logsum", "Access: 10-min walk"
)
termnames <- tibble(
  name = names_for_terms,
  term = c("Intercept", "log(density)", "log(income)", "fulltime", "college", "single",
           "youth", "young_adults", "seniors", "black", "asian", "hispanic", "other",
           "lag", "physact", "access_ls", "walk_10TRUE"))
source("R/impacts_extractor.R")
obesity_impacts <- lapply(obesity_models, function(x) impacts_extractor(x, trMC)) %>%
  bind_rows(.id = "model")  %>%
  left_join(termnames, by = "term") %>%
  mutate(name = factor(name, levels = rev(names_for_terms)))

ggplot(obesity_impacts %>% filter(effect == "Total"), 
       aes(x = name, ymin = `2.5%`, ymax = `97.5%`,  y = `50%`, color = model)) +
  geom_abline(slope = 0, intercept = 0, color = "gray") +
  geom_errorbar(position = "dodge2") +
  scale_color_brewer("Model", palette = "Set1") +
  #geom_point(position = "dodge2") +
  ylab("Simulated Total Impact on Obesity Rate") +
  coord_flip() +
  #facet_wrap(~effect) +
  theme_bw() +
  theme(legend.position = "bottom", 
        axis.text.y = element_text(size = 10),
        axis.title.y = element_blank())
```

### 2019-07-17 R/impacts_extractor.R

@@ -1,0 +1,22 @@
+#' Extract impacts estimates from a spatial lag model as a tidy dataframe
+#' 
+#' @param sdm A spatial lag model, estimated by lagsarlm
+impacts_extractor <- function(sdm, trMC) {
+  
+  impacts_summary <- summary(impacts(sdm, tr=trMC, R=1000), zstats = TRUE)
+  
+  coef <- list(
+    Direct = impacts_summary$direct_sum,
+    Indirect = impacts_summary$indirect_sum,
+    Total = impacts_summary$total_sum
+  ) %>%
+    lapply(function(s) {
+      tibble(
+        term = names(s$quantiles[,1]),
+        `2.5%` = s$quantiles[,1],
+        `50%` = s$quantiles[,3],
+        `97.5%` = s$quantiles[,5]
+      )
+    }) %>%
+    bind_rows(.id = "effect")
+}

### 2019-07-17 R/logsums.R

@@ -16,5 +16,10 @@ calculate_park_logsums <- function(impedance, size_term){
   V <- sweep(impedance, 2, size_term, `+`)
   
   # log-sum of exponentiated utility, Output is n-length vector
-  log(rowSums(exp(V)))
+  log(rowSums(exp(V), na.rm = TRUE))
+}
+
+
+get_nearest <- function(impedance) {
+  
 }

### 2019-07-17 parks_access/server.R
Edits to shiny app

@@ -12,6 +12,7 @@ library(here)
 library(sf)
 library(leaflet)
 library(tidyverse)
+library(broom)
 
 # load data
 openspaces <- read_rds(here("data/open_spaces.rds"))
@@ -34,20 +35,23 @@ shinyServer(function(input, output) {
         distance_c <- -1 * input$distance_c
         size_c <- input$size_c
         courts_c <- 0
-        playgrounds_c <- input$playground
+        playgrounds_c <- 0
         trails_c <- 0
         
         size_term <- openspaces %>%
-            mutate(size_term  = log(as.numeric(acres)) * scoef + 
+            mutate(size_term  = log(as.numeric(acres)) * size_c + 
                        courts * courts_c +
                        playgrounds * playgrounds_c + 
                        trails * trails_c
                    ) %>%
             pull(size_term)
         
+        d <- distances
+        d[d > input$maxdist] <- NA
+        
         suppressWarnings(
             
-            ls <- calculate_park_logsums(impedance = log(distances) * distance_c, 
+            ls <- calculate_park_logsums(impedance = log(d) * distance_c, 
                                          size_term = size_term)
         )
         
@@ -65,21 +69,24 @@ shinyServer(function(input, output) {
     })
     
     output$scatterObesity <- renderPlot({
-        df <- data_frame(
-            obesity = tracts$obesity,
-            access = colorData()
-        )
+        df <- tracts %>% mutate(access = colorData()) 
         
-        ggplot(df, aes(x = access, y = obesity)) +
-            geom_point() +
-            stat_smooth(method = "lm") + 
-            xlab("Access Score") + ylab("Obesity Rate")
+        fit <- lm(obesity ~ log(density) + log(income) +
+                           fulltime + college + single +
+                           youth + young_adults + seniors + 
+                           black + asian + hispanic + other + access,
+                       data = df)
+        
+        sjPlot::plot_model(fit, type = "pred", terms = c("access"))
+        
+        
     })
     
     
     # This observer is responsible for maintaining the circles and legend,
     # according to the variables the user has chosen to map to color and size.
     observe({
+        
         
         cd <- as.numeric(colorData())
         pal <- colorBin("viridis", cd, bins = c(-Inf, -3, -2, -1, 1, 2, 3, Inf))

### 2019-07-17 parks_access/ui.R

@@ -38,8 +38,8 @@ navbarPage(
                             step = 0.1, value = 1.9),
                 sliderInput("size_c", "Size Effect (positive)", min = 0.01, max = 5,
                             step = 0.1, value = .3),
-                sliderInput("playground", "Playground Effect", min = 0, max = 5,
-                            step = 1, value = 1),
+                sliderInput("maxdist", "Maximum distance", min = 0, max = 20,
+                            step = 1, value = 20),
                 conditionalPanel("input.color == 'superzip' || input.size == 'superzip'",
                                  # Only prompt for threshold when coloring or sizing by superzip
                                  numericInput("threshold", "SuperZIP threshold (top n percentile)", 5)

### 2019-08-13 02_parks_data.Rmd
Add twitter data to analysis
Also estimate models given the coefficients found by Kinnell, et al.

@@
 
-Now we can join the cemeteries data to the parks data and write out the results
+Now we can join the cemeteries data to the parks data and write out the results.
 ```{r write}
-rbind(
+open_spaces <- rbind(
   dissolved %>% 
@@
   st_simplify(preserveTopology = TRUE) %>%
-  write_rds("data/open_spaces.rds") %>%
-  geojsonio::geojson_write(file = "data/open_spaces.geojson")
+  write_rds("data/open_spaces.rds")
+
+geojsonio::geojson_write(open_spaces, file = "data/open_spaces.geojson")
 ```

### 2019-08-13 03_logsums.Rmd
Add twitter data to analysis
Also estimate models given the coefficients found by Kinnell, et al.

@@
 library(leaflet)
+library(lubridate)
 ```
@@
 
+## Tweet Counts
+
+We obtained geolocated tweets sent from within the boundaries of each park for
+the period from July through October, 2014.
+
+```{r tweets}
+tweets <- read_csv("data/tweet_counts.csv") %>%
+  filter(id %in% open_spaces$id) %>%
+  gather(date, count, PK_7_1:PK_10_31) %>%
+  separate(date, c("pk", "month", "day"), sep = "_") %>%
+  mutate(date = as_date(str_c("2014", month, day, sep = "-"))) %>%
+  dplyr::select(id, date, count) %>%
+  mutate(
+    month = month(date, TRUE),
+    wday = wday(date, TRUE)
+  ) 
+```
+
+We have a question about how consistent the twitter data is by month or across
+days of the week. Somewhat surprisingly, the twitter activity is lowest on saturday, 
+and then next lowest on Sunday.
+
+```{r wday}
+tweets %>%
+  ggplot(aes(x = wday)) +
+  geom_bar()
+```
+
+August is very low! Let's make sure to use September or October.
+
+```{r month}
+tweets %>%
+  ggplot(aes(x = month)) +
+  geom_bar()
+```
+
+Let's look at the within-park consistency or variability of twitter activity.
+It appears that there is some variation, but that parks with high use typically 
+have high use.
+
+```{r consistency}
+tweets %>%
+  filter(month == "Sep") %>%
+  ggplot(aes(x = date, y = count + 1, group = id)) +
+  geom_line(alpha = 0.5) + scale_y_log10()
+```
+
+Let's calculate the weekday average for each park in September and then go with
+that.
+
+```{r tweets_summary}
+(tweets_summary <- tweets %>%
+  filter(month == "Sep") %>%
+  #filter(!wday %in% c("Sat", "Sun")) %>%
+  group_by(id) %>%
+  summarise(
+    tweet_average = mean(count),
+    tweet_count = sum(count)
+  ) %>%
+  arrange(-tweet_count))
+ggplot(tweets_summary, aes(x = tweet_count)) +
+  geom_histogram()
+
+open_spaces <- open_spaces %>%
+  left_join(tweets_summary, by = "id") %>%
+  mutate_at(
+    vars(starts_with("tweet")), 
+    funs(replace_na(., 0))
+  ) 
+```
+
 ## Logsums
@@
 ```{r logsum_vars}
+open_spaces$acres <- as.numeric(open_spaces$acres)
 logsum_vars <- tracts %>%
@@
     access_ls = calculate_park_logsums(
-      log(distances) * -1.98, log(open_spaces$acres) * 0.3
+      log(distances) * -1.768, log(open_spaces$acres) * 0.373
     ),
+    tweets_ls = calculate_park_logsums(
+      log(distances) * -1.768, 
+      log(open_spaces$acres) * 0.373 + 
+        0.1 * yeo.johnson(open_spaces$tweet_count, lambda = 0)
+    ),
+    multi_ls = calculate_park_logsums(
+      log(distances) * -1.768, 
+      log(open_spaces$acres) * 0.373 + 
+        open_spaces$trails * 0.99 + 
+        open_spaces$playgrounds * 0.26 + 
+        open_spaces$courts * 0.43
+    ),
+  ) %>%
+  mutate_at(
+    vars(ends_with("_ls")),
     # Normalize the logsum onto the Z-scale
-    access_ls_n = (access_ls - mean(access_ls) ) / sd(access_ls)
+    funs( (. - mean(.) ) / sd(.))
   ) %>%
-  st_set_geometry(NULL)
+  st_set_geometry(NULL) %>%
+  as_tibble()
 ```
@@
   mutate(walk_10 = ifelse(geoid %in% inside_access$geoid, TRUE, FALSE)) %>%
-  write_rds("data/tracts_acces.rds")
+  write_rds("data/tracts_access.rds")
 ```
 
-Here's a map of the values 
+Here's a map of the values. Note that there is also a shiny app in this project that
+allows the user to set different values for the logsum parameters.
 ```{r access_map}
 # this interactive map is much easier to create and explore
-pal <- colorQuantile("GnBu", tracts_access$access_ls_n, n = 5)
+pal <- colorQuantile("GnBu", c(tracts_access$access_ls, tracts_access$multi_ls), n = 5)
 bin <- colorFactor("Dark2", tracts_access$walk_10)
@@
   addProviderTiles(providers$Esri.WorldGrayCanvas) %>%
-  addPolygons(group = "access", color = ~ pal(access_ls_n),
-              label = ~as.character(round(access_ls_n,2))) %>%
-  # addPolygons(group = "tweets", color = ~ pal(tweets_ls),
-  #             label = ~as.character(round(tweets_ls,2))) %>%
+  addPolygons(group = "access", color = ~ pal(access_ls),
+              label = ~as.character(round(access_ls, 2))) %>%
+  addPolygons(group = "tweets", color = ~ pal(tweets_ls),
+              label = ~as.character(round(tweets_ls, 2))) %>%
+  addPolygons(group = "Kinner", color = ~ pal(multi_ls),
+              label = ~as.character(round(multi_ls, 2))) %>%
   addPolygons(group = "10-minute walk", color = ~ bin(walk_10)) %>%
-  addLayersControl(baseGroups = c("access", "tweets", "10-minute walk"))
+  addLayersControl(baseGroups = c("access", "tweets", "Kinner", "10-minute walk"))
 ```

### 2019-08-13 04_estimation.Rmd
Add twitter data to analysis
Also estimate models given the coefficients found by Kinnell, et al.

@@
 ```{r loaddata}
-tracts_access <- read_rds("data/tracts_acces.rds")
+tracts_access <- read_rds("data/tracts_access.rds")
 W <- read_rds("data/W.rds")
@@
 ```
+
+The base formula includes all of the tract-level covariates.
 
@@
 
+```{r}
+names_for_terms <- c(
+  "(Intercept)", "log(Density)", "log(Income)",
+  "Fulltime", "College-educated",  "Single Adults",
+  "Youth (0-17)", "Young adults (18-34)",
+  "Seniors (65+)", "Black population share",
+  "Asian population share",
+  "Hispanic population share", "Other Minorities",
+  "$\\gamma$: spatial correlation","Physical activity",
+  "Logsum", "Tweets", "Attributes", "10-min walk"
+)
+
+termnames <- tibble(
+  name = names_for_terms,
+  term = c("Intercept", "log(density)", "log(income)", "fulltime", "college",
+           "single", "youth", "young_adults", "seniors", "black", "asian", 
+           "hispanic", "other",
+           "lag", "physact", "access_ls", "tweets_ls", "multi_ls", "walk_10TRUE"))
+```
+
+We estimate an SEM and SDM version of the base formula, to see if a LRT can 
+exclude the SDM. It doesn't, so we use the SDM going forward. This makes the 
+impacts analysis a little more difficult, but it's not a huge deal.
+
 ```{r spatial selection}
@@
                              type = "mixed")
-test_sdmsem <- lmtest::lrtest(physact_base_sem, physact_base_sdm)
+(test_sdmsem <- lmtest::lrtest(physact_base_sem, physact_base_sdm))
 ```
+
+Now we can add all four access measures to the formula one after the other.
 
@@
 # estimate models
-pa_access_sem <- update(physact_base_sem, .~ . + access_ls)
-pa_quarter_sem <- update(physact_base_sem, .~ . + walk_10)
+pa_access_sdm  <- update(physact_base_sdm, .~ . + access_ls)
+pa_tweets_sdm  <- update(physact_base_sdm, .~ . + tweets_ls)
+pa_multi_sdm   <- update(physact_base_sdm, .~ . + multi_ls)
+pa_walk10_sdm  <- update(physact_base_sdm, .~ . + walk_10)
 
-pa_models <- list("Base" = physact_base_sem,
-                  "Access: logsum" = pa_access_sem,
-                  "Access: 10-min walk" = pa_quarter_sem)
+pa_models <- list("Base"        = physact_base_sdm,
+                  "Logsum"      = pa_access_sdm,
+                  "Tweets"      = pa_tweets_sdm,
+                  "Attributes"  = pa_multi_sdm,
+                  "10-min walk" = pa_walk10_sdm)
 ```
@@
 ```{r screen_pa_models}
+view_kable <- function(x){
+  tab <- paste(capture.output(x))
+  tf <- tempfile(fileext = ".html")
+  writeLines(tab, tf)
+  viewer <- getOption("viewer")
+  viewer(tf)
+}
 view_kable(
@@
 
-```{r}
-view_kable <- function(x){
-  tab <- paste(capture.output(x))
-  tf <- tempfile(fileext = ".html")
-  writeLines(tab, tf)
-  viewer <- getOption("viewer")
-  viewer(tf)
-}
+Let's look at the impacts. The total effect of each park access measure is
+significant at the 95% level. Indeed, it is the only
+
+```{r impacts}
+source(here("R/impacts_extractor.R"))
+
+pa_impacts <- lapply(pa_models, function(x) impacts_extractor(x, trMC)) %>%
+  bind_rows(.id = "model")  %>%
+  left_join(termnames, by = "term") %>%
+  mutate(name = factor(name, levels = rev(names_for_terms)))
+
+ggplot(pa_impacts, 
+       aes(x = name, ymin = `2.5%`, ymax = `97.5%`,  y = `50%`, color = model)) +
+  geom_abline(slope = 0, intercept = 0, color = "gray") +
+  geom_errorbar(position = "dodge2") +
+  facet_wrap(~effect, scales = "free_x") +
+  scale_color_brewer("Model", palette = "Set1") +
+  #geom_point(position = "dodge2") +
+  ylab("Simulated Total Impact on Physical Activity Rate") +
+  coord_flip() +
+  #facet_wrap(~effect) +
+  theme_bw() +
+  theme(legend.position = "bottom", 
+        axis.text.y = element_text(size = 10),
+        axis.title.y = element_blank())
 ```
@@
 ```{r screen_obesity_models}
-screenreg(obesity_models, digits = 4, table = FALSE)
-```
-
-```{r screen_obese_models, eval = FALSE}
-  screenreg(obesity_models, digits = 4, table = FALSE, ci.force = TRUE,
-          single.row = TRUE, caption = "Spatial Error Model Estimates of Effect on Obesity Rates",
-          caption.above = TRUE, custom.coef.names = c(
-            "(Intercept)", "log(Density)", "log(Income)",
-            "Fulltime", "College-educated",  "Single Adults",
-            "Youth (0-17)", "Young adults (18-34)",
-            "Seniors (65+)", "Black population share",
-            "Asian population share",
-            "Hispanic population share", "Other Minorities",
-            "Physical activity",
-            "Spatial correlation", "Access: Logsum", "Access: 10-min walk"
-          ))
+view_kable(
+  htmlreg(obesity_models, digits = 4, table = FALSE, single.row = TRUE, 
+                   caption.above = TRUE, caption = "Spatial Error Model ",
+          stars = c(0.001, 0.01, 0.05, 0.1) )
+)
 ```
@@
 ```{r obesityplot}
-names_for_terms <- c(
-  "(Intercept)", "log(density)", "log(Income)",
-  "Fulltime", "College-educated",  "Single Adults",
-  "Youth (0-17)", "Young adults (18-34)",
-  "Seniors (65+)", "Black population share",
-  "Asian population share",
-  "Hispanic population share", "Other Minorities",
-  "$\\gamma$: spatial correlation","Physical activity",
-  "Access: Logsum", "Access: 10-min walk"
-)
-termnames <- tibble(
-  name = names_for_terms,
-  term = c("Intercept", "log(density)", "log(income)", "fulltime", "college", "single",
-           "youth", "young_adults", "seniors", "black", "asian", "hispanic", "other",
-           "lag", "physact", "access_ls", "walk_10TRUE"))
-source("R/impacts_extractor.R")
 obesity_impacts <- lapply(obesity_models, function(x) impacts_extractor(x, trMC)) %>%
@@
 
-ggplot(obesity_impacts %>% filter(effect == "Total"), 
+ggplot(obesity_impacts, 
        aes(x = name, ymin = `2.5%`, ymax = `97.5%`,  y = `50%`, color = model)) +
@@
   geom_errorbar(position = "dodge2") +
+  facet_wrap(~effect, scales = "free_x") +
   scale_color_brewer("Model", palette = "Set1") +
   #geom_point(position = "dodge2") +
-  ylab("Simulated Total Impact on Obesity Rate") +
+  ylab("Simulated Total Impact on Physical Activity Rate") +
   coord_flip() +
@@
 ```
+
+```{r models}
+write_rds(pa_models, "data/pa_models.rds")
+write_rds(obesity_models, "data/obesity_models.rds")
+```

### 2019-09-17 02_parks_data.Rmd
Add twitter data to parks data builder

--- 2019-07-15 02_parks_data.Rmd
@@
 library(sf)
+library(lubridate)
 ```
@@
 
-Now we can join the cemeteries data to the parks data and write out the results
+Now we can join the cemeteries data to the parks data and get a single polygons
+layer.
 ```{r write}
-rbind(
+open_spaces <- rbind(
   dissolved %>% 
@@
   filter(as.numeric(acres) > 0.5) %>%
-  st_simplify(preserveTopology = TRUE) %>%
-  write_rds("data/open_spaces.rds") %>%
-  geojsonio::geojson_write(file = "data/open_spaces.geojson")
+  st_simplify(preserveTopology = TRUE)
 ```
+
+## Tweet Counts
+
+We obtained geolocated tweets sent from within the boundaries of each park for
+the period from July through October, 2014.
+
+```{r tweets}
+tweets <- read_csv("data/tweet_counts.csv") %>%
+  filter(id %in% open_spaces$id) %>%
+  gather(date, count, PK_7_1:PK_10_31) %>%
+  separate(date, c("pk", "month", "day"), sep = "_") %>%
+  mutate(date = as_date(str_c("2014", month, day, sep = "-"))) %>%
+  dplyr::select(id, date, count) %>%
+  mutate(
+    month = month(date, TRUE),
+    wday = wday(date, TRUE)
+  ) 
+```
+
+We have a question about how consistent the twitter data is by month or across
+days of the week. Somewhat surprisingly, the twitter activity is lowest on saturday, 
+and then next lowest on Sunday.
+
+```{r wday}
+tweets %>%
+  ggplot(aes(x = wday)) +
+  geom_bar()
+```
+
+August is very low! Let's make sure to use September or October.
+
+```{r month}
+tweets %>%
+  ggplot(aes(x = month)) +
+  geom_bar()
+```
+
+Let's look at the within-park consistency or variability of twitter activity.
+It appears that there is some variation, but that parks with high use typically 
+have high use.
+
+```{r consistency}
+tweets %>%
+  filter(month == "Sep") %>%
+  ggplot(aes(x = date, y = count + 1, group = id)) +
+  geom_line(alpha = 0.5) + scale_y_log10()
+```
+
+Let's calculate the daily average for each park  as well as the total tweets in
+September and then go with that.
+
+```{r tweets_summary}
+(tweets_summary <- tweets %>%
+  filter(month == "Sep") %>%
+  filter(!wday %in% c("Sat", "Sun")) %>%
+  group_by(id) %>%
+  summarise(
+    tweet_average = mean(count),
+    tweet_count = sum(count)
+  ) %>%
+  arrange(-tweet_count))
+ggplot(tweets_summary, aes(x = tweet_count)) +
+  geom_histogram()
+
+open_spaces <- open_spaces %>%
+  left_join(tweets_summary, by = "id") %>%
+  mutate_at(
+    vars(starts_with("tweet")), 
+    list(~replace_na(., 0))
+  ) 
+```
+
+Now we write out the data for the future.
+```{r write}
+write_rds(open_spaces, "data/open_spaces.rds")
+geojsonio::geojson_write(open_spaces, file = "data/open_spaces.geojson")
+```

### 2019-09-17 03_logsums.Rmd
Add twitter data to parks data builder

@@
 
-## Tweet Counts
-
-We obtained geolocated tweets sent from within the boundaries of each park for
-the period from July through October, 2014.
-
-```{r tweets}
-tweets <- read_csv("data/tweet_counts.csv") %>%
-  filter(id %in% open_spaces$id) %>%
-  gather(date, count, PK_7_1:PK_10_31) %>%
-  separate(date, c("pk", "month", "day"), sep = "_") %>%
-  mutate(date = as_date(str_c("2014", month, day, sep = "-"))) %>%
-  dplyr::select(id, date, count) %>%
-  mutate(
-    month = month(date, TRUE),
-    wday = wday(date, TRUE)
-  ) 
-```
-
-We have a question about how consistent the twitter data is by month or across
-days of the week. Somewhat surprisingly, the twitter activity is lowest on saturday, 
-and then next lowest on Sunday.
-
-```{r wday}
-tweets %>%
-  ggplot(aes(x = wday)) +
-  geom_bar()
-```
-
-August is very low! Let's make sure to use September or October.
-
-```{r month}
-tweets %>%
-  ggplot(aes(x = month)) +
-  geom_bar()
-```
-
-Let's look at the within-park consistency or variability of twitter activity.
-It appears that there is some variation, but that parks with high use typically 
-have high use.
-
-```{r consistency}
-tweets %>%
-  filter(month == "Sep") %>%
-  ggplot(aes(x = date, y = count + 1, group = id)) +
-  geom_line(alpha = 0.5) + scale_y_log10()
-```
-
-Let's calculate the weekday average for each park in September and then go with
-that.
-
-```{r tweets_summary}
-(tweets_summary <- tweets %>%
-  filter(month == "Sep") %>%
-  #filter(!wday %in% c("Sat", "Sun")) %>%
-  group_by(id) %>%
-  summarise(
-    tweet_average = mean(count),
-    tweet_count = sum(count)
-  ) %>%
-  arrange(-tweet_count))
-ggplot(tweets_summary, aes(x = tweet_count)) +
-  geom_histogram()
-
-open_spaces <- open_spaces %>%
-  left_join(tweets_summary, by = "id") %>%
-  mutate_at(
-    vars(starts_with("tweet")), 
-    funs(replace_na(., 0))
-  ) 
-```
-
 ## Logsums

### 2019-09-17 03_logsums.Rmd
Update logsums page

@@
 library(lubridate)
+library(VGAM)
 ```
@@
     # Normalize the logsum onto the Z-scale
-    funs( (. - mean(.) ) / sd(.))
+    list(~ (. - mean(.) ) / sd(.))
   ) %>%

### 2019-09-19 manuscript/manuscript.Rmd
Draft manuscript

---
title: >
  Modeling the impacts of park access on health outcomes: a choice-based 
  accessibility approach
author:
  - name: Gregory Macfarlane
    email: gregmacfarlane@byu.edu
    affiliation: Brigham Young University
    corresponding: gregmacfarlane@byu.edu
  - name: Nico Boyd
    email:
    affiliation: Fehr and Peers 
  - name: John E. Taylor
    email: jetaylor@gatech.edu
    affiliation: Georgia Institute of Technology
  - name: Kari Watkins
    email: kariwatkins@gatech.edu
    affiliation: Georgia Institute of Technology
address:
  - code: Brigham Young University
    address: Civil and Environmental Engineering Department, Brigham Young University 430 Engineering Building, Provo, UT, 84602
  - code: Fehr and Peers
    address: Los Angeles, California
  - code: Georgia Institute of Technology
    address: School of Civil and Environmental Engineering, Georgia Institute of Technology, 755 Atlantic Drive, Atlanta, GA, 30332
abstract: >
  Recent research has underscored the potential for public green spaces to
  influence individual and societal health outcomes, but empirical measurements
  of such influences have yielded mixed results to date, with particular
  disagreement surrounding how access to parks ought to be defined while
  controlling alternate explanations. In this paper we present a comprehensive
  measure of park accessibility drawn from random utility choice theory, which
  avoids arbitrary assertions of proximity while incorporating potentially
  numerous amenities and attributes of both the parks and the population. We
  apply this choice-based accessibility measure to correlate Census tract-level
  obesity and physical activity rate estimates from the Centers for Disease
  Control and Prevention's 500 Cities project with tract-level American
  Community Survey socioeconomic data in New York City, paired with geographic
  parks data from New York City. Controlling for the
  socioeconomic variables and spatially correlated error terms, we show a
  positive and significant relationship between park access and physical
  activity rates, and a clear and significant negative relationship between park
  access and obesity rates. In doing so, this research contributes a more
  comprehensive modeling approach for measuring the impact of park access on
  health, and may improve our understanding of the role  parks and access to
  them can serve in furthering public health objectives.
author_summary: >
  Greg Macfarlane is an assistant professor of Civil Engineering at Brigham
  Young University in Provo, Utah.

output: 
  rticles::elsevier_article:
    includes: 
      in_header: preamble.tex
csl: elsevier-harvard.csl
bibliography: library.bib
---

```{r setup, cache = FALSE, echo = FALSE, message = FALSE, warning = FALSE}
library(tidyverse)
library(geojsonio)
library(rgdal)
library(rgeos)
library(maptools)
library(spdep)
library(sf)
library(VGAM)
library(qwraps2)
library(knitr)
library(kableExtra)
library(texreg)
library(here)

options(tigris_use_cache = TRUE)
opts_chunk$set(cache=TRUE, message = FALSE, echo = FALSE, warning = FALSE)
library(leaflet)

knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark=",", drop0trailing = TRUE)
})

```

# Introduction

The United States and other developed nations face an epidemic of obesity and
chronic diseases, including cardiovascular diseases, chronic respiratory
diseases, diabetes, stroke, joint and bone diseases, and cancer. These diseseases
can severely limit the lifespan of affected individuals [@WHO2014], with 
substantial financial costs for treatment borne both privately and socially
[@Finkelstein2009]. Though a moderate amount of regular physical activity
has been established as an effective strategy for reducing and managing obesity
and many of the aforementioned chronic diseases [@CDC2009; @Durstine2013],
a large portion of U.S. adults do not participate in sufficient physical
activity [@Wolf2008].

Historically, most large-scale health promotion efforts focused on
individual-level interventions intended to educate people about healthy
lifestyles and behaviors, touching on topics including diet and exercise.
Over the last few years a new social model of health has evolved, treating health
``as an outcome of the effects of socioeconomic status, culture,
environmental conditions, housing, employment and community influences.''[@Duhl1999, p.7]
In this new paradigm, resources provided via civil infrastructure --- in
particular parks and other public green spaces --- play a crucial role in
promoting and sustaining public health [@Bedimo-Rung2005; @Coutts2008].
After all, it does little to lecture individuals on the importance of exercise
if their community is built in such a way that such exercise is expensive,
unenjoyable, or unsafe.

In spite of the potential for green spaces to influence public health outcomes 
and numerous studies attempting to empirically estimate the strength of these
outcomes, evidence to date has been mixed. A major challenge researchers have
faced is a proliferation of techniques for measuring access to green spaces, of
which many are plausible but lack robust theoretical basis. In this
paper, we present a holistic and flexible measurement for park accessibility
based in activity location choice theory. This choice-based accessibility measure
compares the continuous distance to all parks in the region, weighted against
the sizes of the each park and other assorted amenities.

We apply this measurement to study the link between
park accessibility and attractiveness and Census tract-level aggregate physical
activity participation and obesity rates in New York City, controlling for
spatially correlated unobserved effect and tract-level socioeconomic
characteristics. We find a positive relationship where the least park-accessible
tracts have an expected physical activity participation rate roughly a full
percentage point lower than the most accessible tracts; a traditional
quarter-mile buffer analysis estimates a similar albeit marginally less
significant effect. However, we also find a strong and significant correlation
between the choice-based park accessibility metric and decreased obesity rates
--- again controlling for spatial correlation, socioeconomic attributes, and
physical activity rates. In this case a traditional buffer analysis does not
show significance.

We also demonstrate how the choice-based accessibility metric can potentially be
expanded to account for other measures of a park's attractiveness including its
observed social media activity and the presence of various park amenities.
The paper concludes with a discussion of opportunities for future research.

# Literature Review 
\label{sec:litreview}

Numerous previous studies have found relationships between characteristics of
the built environment and aspects of physical, mental, social, and economic
health. For the purposes of this study, it is clear that parks and other
vegetated areas support outdoor physical activity in ways distinct from other
urban environments [@Giles-Corti2005; @Wells2007].  In spite of these generally
positive findings, the evidence of a specific link between green space and
physical activity is somewhat mixed.

<!-- Rewrite this section: 
  - Cross-metropolitan studies are somewhat clear?
  - Within-metropolitan studies are limited
-->

@Wolf2008 reports that people self-identify as more active and attain a
higher quality of life when a greater portion of their environment is greenspace.
@Larson2016 similarly used self-reported scores on the Gallup-Healthways
Wellbeing Index to evaluate the relationship between different areas of
wellbeing, including physical health, and park quantity, quality, and
accessibility in 44 U.S. cities. While the authors found positive associations
between wellbeing and park quality and accessibility, these relationships were
not statistically significant. A study by @West2012 used park data from
the Trust for Public Land’s 2010 City Park Facts and public health data from the
Behavioral Risk Factor Surveillance System (BRFSS) to examine relationships
between the density of parkland, parkland per capita, and levels of physical
activity and obesity for 67 metropolitan statistical areas in the U.S. The study
found a significant, positive association between park density and physical
activity and a significant, negative association between park density and
obesity. Conversely, @Richardson2012 examined the relationship between
urban greenspace and selected mortality rates, and though the authors did not
find a statistically significant relationship between the quantity of urban
greenspace and mortality caused by lung cancer, diabetes, heart disease or car
accidents, they did find that all-cause mortality was oddly, *higher* in
greener cities. In a meta-analysis of 20 peer reviewed journal articles
exploring the relationship between parks and objectively measured physical
activity, @Bancroft2015 found that five studies reported a significant
positive association between the two, six studies produced mixed results, and
nine studies found no association at all.

While several of the aforementioned studies reported results consistent with the
hypothesis that park access and use confer health benefits stemming from
increased physical activity and attendant decreases in obesity, the large
majority of extant research has been conducted at the level of the city or
metropolitan statistical area. Metropolitan-level analyses do not capture the
within-city variation in accessibility to parks that exist in many cities. Some
cities with large amounts of total greenspace may nevertheless unequally
distribute this space throughout the city, leading to areas with poor access.
Conversely, a city with a smaller overall proportion of greenspace may give all
of its citizens better access to sufficient greenspace to meet their needs or
wants for physical activity. Considering access at the neighborhood level within
a single city may also eliminate some regional or cultural fixed effects
affecting metropolitan-level analyses.

In a study of neighborhoods in New York City, @Stark2014 used
hierarchical linear models to explore relationships between the proportion of
zip codes that was park space, the cleanliness of parks, and the body mass index
of adult residents. The authors found that a higher proportion of park space in
a neighborhood was associated with a lower BMI for its residents, and lower park
cleanliness scores were associated with a higher BMI, suggesting that increasing
the supply of clean, well-maintained parks could positively impact adult BMI.

## Choice-based Accessibility

Consider that an individual is choosing a park for a recreation activity.
If we apply random utility choice theory, specifically the multinomial
logit model [@McFadden1974], the expected probability of individual
$i$ choosing park $j$ from the set of all regional parks $J$ is
\begin{equation}\label{eq:mnl}
P(j | V_{ij}) = \frac{\exp(V_{ij})}{\sum_{p \in J}\exp(V_{ip})}
\end{equation}
where parks are differentiated from each other by their relative measurable
utilities $V_{ij}$. In principle, $V$ may include any measurable attributes of either
the choice maker or the park. In this study we use a linear formulation of
\begin{equation}\label{eq:v_sd}
V_{ij} = size_j\lambda_s + distance_{ij}\lambda_d
\end{equation}
incorporating the size of the park in acres and the distance of the park from
the census tract $i$ in miles. The coefficients $\vect{\lambda}$ can be
estimated from household surveys, though in the absence of a survey we
may assert reasonable values.

A key theoretical outcome of random utility choice models is that the
consumer surplus to individual $i$, or the total weighted value of all
alternatives in individual $i$'s choice set, can
be obtained as the logarithm of the sum in the denominator of the choice
probability equation [@Small1981]:
\begin{equation}\label{eq:cs}
C_i = \ln\left({\sum_{p \in J}\exp(V_{ip})}\right)
\end{equation}
There are several advantages to such a log-sum defined metric relative to
buffer-based accessibility metrics more commonly found in the literature. First,
all individuals are defined as having some access to all parks, rather than an
arbitrary cutoff asserted by the researcher.
This allows for the fact that some people are more or less sensitive to
distances, and that distance is a continuous, non-binary phenomenon.
It defies reason to assume a person living 1.1 miles
from a park has functionally different accessibility than someone living at 0.9 miles.
Second, the random utility formulation
allows the researcher to include any attribute of the park as part of its utility
specification; in this case, we consider the size of the park weighted against its
distance as an element of relative accessibility. This suggests that
not all parks are equal, and that a large park such as Central Park in Manhattan
may provide health and activity benefits over a much larger area than a smaller
community square.

Note that this formulation is an extension of gravity-based accessibility
statistics, in the same way that the gravity-based trip distribution model
is a specific case of
a destination-choice model [@Daly1982]. But the extension is meaningful and
allows us to consider more attributes of the park or the individual beyond size
and impedance. For example, we can aggregate the number of tweets emanating from
a park as a measure of the park's attractiveness beyond its size. The
utility for the choice maker from Equation \ref{eq:v_sd} then becomes
\begin{equation}\label{eq:v_sdt}
V_{ij} = size_j\lambda_s + distance_{ij}\lambda_d + tweets_j\lambda_t
\end{equation}

In spite of its flexibility and basis in choice theory, accessibility measures
based in log-sums have not received much application in the accessibility
literature compared with distance-based or even gravity-based measures.
@Zhang2011 present a metric with a similar functional form, though the
authors arrive at it from a motivation other than destination choice theory.
Log-sums are commonly used, however, in alternatives analyses of transit
infrastructure improvements [@DeJong2007]. A reason for this is likely that
a regional travel demand model is available to the analysts, thus making
calibrated and multimodal logsums readily available [@Geurs2010].

# Empirical Application
In this section, we develop a model with data for New York City, where
we compute a holistic logsum-based accessibility to parks measure and model the
relationship between this measure and physical activity rates, controlling for
spatial effects and socioeconomic factors. We subsequently model the effect
of the accessibility metric on obesity rates, accounting for physical activity and
the other controls. Finally, we model the relationship between a modified logsum
measure considering geolocated Twitter data and physical activity and obesity rates.

## Data

This study uses data available to the public from a variety of federal and state
data agencies. The datasets, as well as the analysis code, are available on GitHub
at \url{https://github.com/gregmacfarlane/parks_access}.

```{r tracts}
# built in 01_health_data.Rmd and 03_logsums.Rmd
tracts <- read_rds(here("data/tracts_access.rds"))
```

The Centers for Disease Control and Prevention makes small-area estimates on
key health indicators available through its 500 Cities data program [@CDC5002016].
The indicators are multilevel aggregations and imputations of BRFSS responses
[@Wang2018; @Wang2017], and have been recently used to study the tract-level
link between gentrification and urban health [@Gibbons2018]. We use two
indicators as our dependent variables in this study: the share of adults
in a Census tract who are obese, and the share of adults who participate in no
leisure-time physical activity. To improve clarity in our interpretation, we use
the complement of the second variable --- the share of tract adults who
participate in *some* physical activity --- even if the amount is not sufficient
to affect overall health. Both indicators are estimated for the year 2016.

To the health data, we join socioeconomic data collected through the Census
Bureau API via the \texttt{tidycensus} package for R [@Walker2019]. The
primary dataset is a geographic polygons layer of Census tracts in the five
boroughs of New York City. We append to each Census tract relevant
sociodemographic data for each tract from the American Community Survey
2013-2017 5-year estimates. For a small handful of tracts in our sample, Census
supressed the median income estimate; these appear to be primarily wealthy
tracts and in almost all cases the CDC estimates of obesity and physical
activity are missing as well. After removing these tracts from the estimation
dataset, we have `r nrow(tracts)` complete cases. Table \ref{tab:tractsdata}
presents key descriptive statistics for these data.

```{r parks}
# This data is created in 02_parks_data.Rmd
parks <- read_rds(here("data/open_spaces.rds"))
```

In a destination choice framework, the tracts represent the ``origins'' and
``destinations'' are parks and green spaces in New York City.
We retrieved a polygons layer of public parks and greenspaces within New York City’s
municipal boundaries and checked it for accuracy and relevance [@nycparks].
Upon inspection, we removed several facilities that do not qualify as
publicly accessible green space, such as Yankee Stadium, Citi Field, and their
surrounding parking lots. We also removed parks of less than half an acre in
size, as these appear to be predominantly planted medians rather than legitimate
public green space. We also consolidated individual geographic polygons
comprising a single facility --- as is the case in Flushing Meadows --- and
eliminated sub-facilities such as tennis courts or baseball fields included within
larger park facilities. Instead of these sub-facilities, we created 
variables for each park indicating the presence of sports courts, playgrounds,
and trails.

To this dataset of parks and regularized green spaces, we add a polygons layer of
cemeteries in New York that are open to the public. Cemeteries are important
green spaces that can be used for many types of physical activity. These
operations leave us with `r nrow(parks)` distinct parks. For each park and cemetery
we generate calculate the size of the park in acres. Using a Twitter application
programming interface (API) implemented with the Python package Tweepy,  we also
collected and stored tweets containing geotags of precise geographic coordinates
located within the boundaries of the parks; from this information,
we were able to segregate tweets that were generated within a park in September
2014. This geolocated twitter activity could provide an additional point of information
on the degree to which individual parks are actually used [@Wang2016].

```{r tractsdata, results="asis", message=FALSE, warning=FALSE, cache=FALSE}
# This is an index pairing the variable names with the order we want them
# to be shown in in the table.
tracts_data_index <- tibble(
  variable =  c(
    "obesity", "physact", "income",
    "density", "fulltime", "college", "single",
    "youth", "young_adults",  "seniors", "black", "asian", "hispanic",
    "other"),
  source = c("CDC 500 Cities", "CDC 500 Cities",
             rep("ACS", 12))
) %>%
  mutate(order = row_number())

# Get the tract SE / health data, calculate group statistics, and get it
# in the right order
tract_summary <- tracts %>%
  st_set_geometry(NULL) %>%
  tbl_df() %>%
  dplyr::select(tracts_data_index$variable) %>%
  gather(variable, value) %>%
  group_by(variable) %>%
  summarise(
    min = min(value),
    `msd` = paste(median_iqr(value)),
    max = max(value)
  ) %>%
  inner_join(tracts_data_index) %>%
  arrange(order) %>%
  mutate(
    variable = c(
      "Obesity: Share of adults over 18 who are obese",
      "Physical Activity: Share of adults over 18 who engage in some leisure-time physical activity",
      "Income: Median tract income",
      "Density: Households per square kilometer",
      "Fulltime: Share of adults over 18 with full-time work",
      "College: Share of adults over 24 with a college degree",
      "Single: Share of adults over 18 living alone or in a non-partnership household",
      "Youth: Share of population under 18",
      "Young adults: Share of population between 18 and 34",
      "Seniors: Share of population who are 65 and over",
      "Black: Share of population who is black",
      "Asian: Share of population who is Asian",
      "Hispanic: Share of population who is Hispanic",
      "Other: Share of population who belong to other minority groups")
  ) %>%
  dplyr::select(-order)

tract_rows <- nrow(tract_summary)

park_summary <- parks %>%
  st_set_geometry(NULL) %>%
  # TODO: This should be tweets
  dplyr::select(acres, courts, playgrounds, trails, tweet_count) %>% 
  gather(variable, value) %>%
  group_by(variable) %>%
  summarise(
    min = min(value),
    `msd` = paste(median_iqr(value)),
    max = max(value)
  ) %>%
  mutate(
    variable = c("Size: Park size in acres",
                 "Courts: Presence of sport courts / ball fields",
                 "Playgrounds: Presence of playgrounds",
                 "Trails: Presence of trails",
                 "Tweets: Tweets emanating from park in September 2014"),
    source = c(rep("NYC", 4), "Twitter API")
    )

bind_rows(tract_summary, park_summary) %>%
  separate(variable, c("var", "desc"), sep = ": ") %>%
  mutate(
    msd = str_replace(msd, " \\(", "\\\\\\\\ \\("),
    msd = str_c("\\makecell{", msd, "}")
  ) %>%
  kable(escape = FALSE, digits = 2, format = "latex",
        table.envir = "table*", booktabs = TRUE,
        caption = "Descriptive Statistics of Tract and Park Variables",
        col.names = c(" ", "Description", "Minimum", "Median (IQR)", "Maximum", "Source")) %>%
  kable_styling(latex_options = "scale_down") %>%
  column_spec(2, width = "2in") %>%
  group_rows(paste("Tract Variables, N =", nrow(tracts)), 1, tract_rows) %>%
  group_rows(paste("Park Variables, N =", nrow(parks)), tract_rows + 1, tract_rows + nrow(park_summary))
```

## Model 
\label{subsec:model}

We predict the rate of physical activity ($y$) in a census tract as a
function of the tract's sociodemographic characteristics and choice-based
accessibility to parks with the following  specification:
\begin{equation}\label{eq:themodel}
 y_i = f(\vect{x}_i, C_i, g(W, \vect{y}, \vect{X}))
\end{equation}
where $\vect{x}_i$ is a vector of tract-level sociodemographic attributes,
$C_i$ is a choice-based accessibility measure for the tract computed from
Equation \ref{eq:cs} and $g(W, \vect{y}, X)$ represents the impact of spatial
neighborhood effects on the outcome.

Using tracts as the unit of observation in the model allows us to consider the
availability of parks at a sub-metropolitan level, but it also introduces the problem
of spatial correlation of unobserved errors and spatial dependence in the data
generating process [@Cliff1970; @Anselin1980]. Spatial correlation occurs
when spatially-distributed unobservable or missing variables (school quality,
neighborhood prestige, etc.) influence the modeled outcomes. Spatial dependence
occurs when the outcome *depends* on the outcome in neighboring areas; for
example, seeing neighbors exercising may encourage exercise. The relaxed spatial
Durbin model (SDM) proposed by @Burridge1981 controls for both processes:
\begin{equation}\label{eq:sdm}
  \vect{y}= \rho W\vect{y} + X\vect{\beta} + WX\vect{\gamma} + \vect{\epsilon}
\end{equation}
where $\rho$ is the estimated spatial correlation between the outcome variables
$y_i, y_j, \ldots  \in \vect{y}$, $W$ is a matrix specifying the spatial
relationship between observations $i$ and $j$ in the dataset,
$\vect{\beta}$ is a vector of estimable coefficients relating the attributes $X$
of an observation to its outcome, and $\vect{\gamma}$ is a vector of
estimated coefficients relating the attributes of an observation's *neighbors*
to its outcome. If only correlation and not dependence exists in the data
generating process, it may  be more efficient to estimate a restricted
spatial autoregressive model and therefore
save degrees of freedom in the estimation. @tra_autoregression_paper
illustrate a decision algorithm originally proposed by @Florax2003 which uses
a likelihood ratio test of the SDM against the restricted spatial error model (SEM):
\begin{align}
{\boldsymbol y} &= X{\boldsymbol \beta} + {\boldsymbol u},  {\boldsymbol u} = \gamma W {\boldsymbol u} +
{\boldsymbol \epsilon} \label{eq:SEM}\\
{\boldsymbol y} &= X{\boldsymbol \beta} + (I-\gamma W)^{-1}{\boldsymbol \epsilon}\notag
\end{align}
If the likelihood ratio test rejects that the models are equivalent, then the SDM
should be used because its estimates are unbiased. One consequence of using the SDM
is that the estimated coefficients do not represent the

The researcher must assert $W$ *a priori*, though there are several
common specifications \citep{Dubin1998}. In this study we specify that tracts
with population-weighted centroids located within 1.8 Euclidean miles of each
other are considered neighbors, and the strength of the relationship is the
row-standardized (each row sums to 1) inverse of the distance between them:
\begin{equation}\label{eq:weightsrule}
W_{ij} = \begin{cases}
  {\frac{d_{ij}^{-1}} {\sum_{k=1}^n d_{ik}^{-1}}} & \text{for $d_{ij} \leq 1.8$ miles}\\
  0  & \text{for $d_{ij} > 1.8$ miles}
  \end{cases}
\end{equation}

```{r weights, warning = FALSE}
# This are developed in 03_logsums.Rmd
distances <- read_rds(here("data/distances.rds"))
W <- read_rds(here("data/W.rds"))
trMC <- trW(as(W, "CsparseMatrix"), type="MC")
```
This is a similar specification to that used by  \citet{tra_autoregression_paper}
in a study of home prices in Atlanta. We selected this specification after
comparing overall model likelihoods between it and a specification where tracts
sharing a boundary are considered neighbors.

## Accessibility 
\label{subsec:accessibility}

Extant destination choice models used in practice typically use travel time in
minutes as a travel impedance term, and employment by sector as a size term or
attraction component. Typically such models handle recreational trips together with
other non-work and non-school trips, and we therefore can find no previously
estimated coefficients using size terms relevant to park acreage or amenities.
Given this gap in the literature, we instead assert plausible values for
$\beta$ to generate the choice-based accessibility statistic used in this study.

The functional form of the accessibility statistic is adapted from
Equation \ref{eq:v_sd} by log-transforming first the distance (Euclidean, in miles)
between the park boundaries and population-weighted tract centroids and second the
park size (in acres).
\begin{equation}\label{eq:v_logged}
V_{ij} = \log(size_j)\lambda_s + \log(distance_{ij})\lambda_d
\end{equation}
We then calculate the consumer surplus $C$  (log-sum of the exponentiated
utilities) for each tract and standardize the result,
\begin{equation}\label{eq:v_logged}
C_i' = \frac{C_i - \bar{\vect{C}}}{sd(\vect{C})}
\end{equation}

We initially estimated potential values of the $\lambda$ coefficients by
applying a limited-memory, box-constrained optimization algorithm
maximizing the model log-likehood.\footnote{Using the {\texttt nlm} function
in R [@RCoreTeam2018]} The constraint required that the coefficient on
size be positive and that on distance negative; all else equal, we assert people
will prefer to use larger parks and parks that are nearer to their residence. This
resulted in $\lambda_d = -1.98$  and $\lambda_s = 0.000$. Though the ``most
likely'' parameter value, in this case it was unsatisfactory for two reasons:
first, our prior assertion that park size is a valuable attribute of a park, and
second the observation that with these maximum likelihood values tracts
bordering on the corners of Central Park were measured with poor overall
accessibility, an unacceptably unintuitive result. We subsequently adjusted the
$\lambda_s$ value to $0.3$; the relative ratio of the coefficients implies that
all else equal, an individual would travel 6.6 times further to access a park
twice as large.

Figure \ref{fig:map} shows a map of New York City with each tract highlighted
based on its relative accessibility score. The most continuous region of good park
access is in upper Manhattan and the Bronx, bracketed by Central Park and the
Bronx River. Conversely, some of the poorest-accessibility areas are in
Brooklyn tracts not immediately adjacent to Prospect Park. Because the
accessibility statistic is normalized, the worst values are slightly below $-3$,
the best somewhere above $3$.

```{r map, fig.env="figure*", echo=FALSE, message=FALSE, warning=FALSE, fig.height=4, fig.cap="Normalized choice-based park accessibility log-sum values in New York City."}
library(ggmap)
map <- ggmap(
  get_stamenmap(unname(st_bbox(tracts)), 
                maptype = "toner-lite"), extent = "device")
map +
  geom_sf(data = tracts, inherit.aes=FALSE,
          aes(fill = cut(access_ls, breaks = c(-Inf, -3, -2, -1, 0, 2, 3, Inf))),
          alpha = 0.8, color = NA) +
  scale_fill_brewer("Normalized Log-sum", palette = "GnBu")
```

## Results

```{r results}
pa_models <- read_rds(here("data/pa_models.rds"))
obesity_models <- read_rds(here("data/obesity_models.rds"))
```

```{r termnames}
names_for_terms <- c(
  "(Intercept)", "log(Density)", "log(Income)",
  "Fulltime", "College-educated",  "Single Adults",
  "Youth (0-17)", "Young adults (18-34)",
  "Seniors (65+)", "Black population share",
  "Asian population share",
  "Hispanic population share", "Other Minorities",
  "$\\gamma$: spatial correlation","Physical activity",
  "Logsum", "Tweets", "Attributes", "10-min walk"
)

termnames <- tibble(
  name = names_for_terms,
  term = c("Intercept", "log(density)", "log(income)", "fulltime", "college",
           "single", "youth", "young_adults", "seniors", "black", "asian", 
           "hispanic", "other",
           "lag", "physact", "access_ls", "tweets_ls", "multi_ls", "walk_10TRUE"))
```

We estimated SDM and SEM models regressing the physical activity rate
against the base covariates (without any accessibility component). A likelihood
ratio test failed rejected that the SDM is different from the SEM, so we use
the SDM specification only going forward. Recall that in an SDM the effect of a
covariate on the dependent variable is *not* the estimated coefficient. As a
consequence of this Table \ref{tab:pa_models} presents the estimated
coefficients for the base model with the socioecononomic controls and
no representation of park accessibility. For the most part the coefficients are
highly significant and of the expected sign. Tracts with higher shares
of full-time workers, college-educated adults, young adults, and high-income
households all show a greater share of individuals engaging in regular physical
activity. Conversely, tracts with greater population density and a greater
share of single adults, children, seniors, minorities of all types, and low
income households all have lower modeled rates of physical activity.

To this base model we add a measure of park accessibility considered in two
ways: a logsum-based statistic as described earlier and a more typical quarter-mile
binary access buffer. The estimated coefficients for these models are also
given in Table \ref{tab:pa_models}. In both accessibility specifications,
the access measure is positively correlated with physical activity rates; all else
equal, people in tracts with higher accessibility to parks have higher estimated
rates of physical activity. Though the estimated coefficient on the quarter-mile
buffer appears to have a larger absolute value than the logsum-based statistic,
this masks a key difference in the specification worth further comment.
The logsum allows for variation in access unavailable in the buffer-based method.
In our dataset almost every tract
(`r round(sum(tracts$access_025) / nrow(tracts) * 100, 0)`%) is within
a quarter-mile of *some* kind of park, but this park may not be large enough
to support physical activities all individuals would like to participate in.
Because tracts with only adequate park access are grouped with tracts having
excellent park access, the overall effect is comparatively unclear. The logsum-based
coefficient, on the other hand, suggests going from the least-accessible ($-3.0$)
to the most-accessible ($3.0$) tract implies roughly a $1.1$ percentage point
rise in estimated physical activity rates.

```{r effectsplot, results = "asis"}
texreg(pa_models[c("Base", "Logsum", "10-min walk")], digits = 4,
       booktabs = TRUE, use.packages = FALSE, 
       caption = "SEM Coefficients Predicting Physical Activity Rates",
       caption.above = TRUE,
       custom.note = "%stars. Standard errors in parentheses.")
```
\end{table*}

We now consider the impacts of a model where the dependent variable is
the *obesity* rate, and physical activity becomes an independent covariate
alongside the controlling variables and the accessibility metric.
Table \ref{tab:obese_models} again presents the base model without
any accessiblity measure, and models with accessibility captured through a
logsum and through a 1/4 mile buffer. As in the
physical activity models, the coefficients are typically significant and
of the expected sign, with a few exceptions: in this case an increasing hispanic
population share  and an increasing share of children have no significant
relationship on obesity. Unlike in the physical activity models however,
the inference on the accessibility statistic *does* change between
specifications. The 1/4 mile buffer neither substantially improves the model
fit nor is its term significant at any threshold, but the accessibility logsum
indicates a significant negative correlation: moving from the least to most
accessible tract decreases the expected obesity rate by approximately half a
percentage point.

```{r obesemodelchart, results="asis"}
texreg(obesity_models, digits = 4, 
       booktabs = TRUE, use.packages = FALSE, 
       caption = "SEM Coefficients Predicting Obesity Rates",
       caption.above = TRUE,
       custom.note = "%stars. Standard errors in parentheses.")
```

\subsection{Additional Amenities}

As discussed when presenting the choice-based accessibility metric above,
a key benefit it offers is the natural way in which park amenities beyond simply size
can be accommodated. For example, the number of tweets emanating from a park
might be seen as a measure of the park's popularity, or a proxy for its use. It
may be construed that parks with high popularity or use contain other amenities
that encourage residents to use the park space, raising physical activity rates
and lowering obesity rates beyond what would be expected with the park's size
and proximity alone. It is reasonable to question whether park size and Twitter
activity are highly correlated, and thus would result in a double-counting of
park size in the accessibility statistic. In our data the number of tweets is
positively but only loosely correlated  with park
size ($\\rho = $),
indicating that the Twitter data in fact could provide new information or proxy
for the desired amenities.

To test this hypothesis, we can use the twitter data described earlier and
suggested in Equation \ref{eq:v_sdt}. In this application, we again
log-transform all the components of utility:
\begin{equation}\label{eq:v_logsdt}
V_{ij} = \log(size_j)\lambda_s + \log(distance_{ij})\lambda_d + g(tweets_j)\lambda_t
\end{equation}
where $g(x)$ is a Yeo-Johnson transformation to preserve cases where $log(0)$
would be otherwise undefined \citep{Yeo2000}. As before, there is little
information by which to determine the values of $\lambda$ in this utility
specification; we use the previous values with the addition of $\lambda_t =
0.1$. The ratio between the utility coefficients implies residents would travel
almost twenty times as far or use a park three times smaller if it had twice the
Twitter activity, all else equal.

Figure \ref{fig:tweets_map} shows the percent change in the normalized log
sum statistic after including the twitter information. There is not a recognizable
overarching pattern to the changes, though tracts immediately surrounding
Prospect Park and Central Park gain even more relative accessibility, and tracts
in midtown Manhattan, Queens, and southern Bronx tend to lose some.

```{r tweets_map, eval = FALSE, echo=FALSE, message=FALSE, warning=FALSE, fig.height=4, fig.cap="Percent change in relative accessibility to parks when accounting for Twitter activity."}
map +
  geom_sf(data = tracts %>%
            mutate(diff = tweets_ls - access_ls,
                   pct_diff = diff / access_ls * 100),
          inherit.aes=FALSE,
          aes(fill = cut(pct_diff, quantile(pct_diff,
                                            probs = seq(0, 1, by = 0.1)))),
          alpha = 0.8, color = NA) +
  scale_fill_brewer("Percent Change", palette = "PiYG")
```

Table \ref{tab:tweets_coefs} presents the estimated coefficients relating
accessibility to obesity and physical activity rates, with and without the
inclusion of Twitter data. In both cases, including twitter information in
the accessibility statistic tempers the strength of the relationship with the
dependent variable and modestly widens the standard error without substantively
affecting the significance of the test statistics or the interpretation.
From this limited example, we cannot say whether Twitter activity enhances the
ability of parks to increase physical activity rates or lower obesity rates,
though further investigation of this and other park amenities would certainly
be warranted.

# Limitations and Future Research Direction

We readily acknowledge limitations in this study. As in any study conducted
with areal data, we are at risk of falling victim to the ecological inference
fallacy, where aggregate statistics mask or contradict disaggregated or
individual-level trends. A large-sample survey of individuals in New York City,
including measured physical activities and obesity would always be preferable
to the tract-level data used in this study. It would also be
preferrable to have obtained the $\vect{\lambda}$ accessibility utility coefficients
from a high-quality survey of leisure destination choice rather than
asserting them to match our prior expectations of what constitutes quality
park access. An ideal survey to address the question would incorporate both sets
of questions: physical activity and health data on one hand and park use (including
which parks were used and how frequently) on the other. As no such dataset
exists to our knowledge, this tract-level aggregate analysis with asserted
utility coefficients is the possibility that remains.

This paper presents a holistic accessibility statistic that could, in theory,
accommodate many attributes of the destination parks as well as the people who
might use them. As an illustration: the park-going population could be separated
into at least four delineated clusters, each preferring different amenities of a
park:
\begin{itemize}
 \item{runners and cyclists: long, interesting trail systems}
 \item{sports players: soccer fields, basketball courts, or baseball diamonds}
 \item{families with small children: water features and playgrounds}
 \item{casual users: water features, gardens, performances, etc.}
\end{itemize}
An analyst could then compute the accessibility logsum for each cluster with
different utility values for each park's amenities, and obtain a measure of
a neighborhood's accessibility to park features that its residents most care
about. In this paper, we proceed only incrementally beyond this theory by
adding Twitter activity as an element of a park's attractiveness above and
beyond its size. Exploring additional amenities or market segmentation strategies
could provide a more definitive understanding of the relationship between park
accessibility and health outcomes.

As a travel impedance measure, we used the Euclidean distance between each tract's
population-weighted centroid and the nearest point on the edge of a park's border.
Euclidean distances have well-rehearsed limitations regarding their fidelity with
the underlying infrastructure network, etc. Network-based distances can also
suffer from challenges when applied to multimodal problems; these challenges are
exacerbated when the non-highway mode share is high, as is likely when considering
access to parks. A better metric of travel impedance may be a mode choice model
logsum, which weights all travel alternatives against each other.

Finally, this study is primarily focused on the hypothesis that accessibility to
parks encourages physical activity, which in turn reduces obesity. There are a
multitude of other hypotheses that might be proposed and tested with the basic
methodology we have employed here, or competing explanations for the outcomes we
have observed. It is distinctly possible, for instance, that individuals who wish
to exercise regularly in parks choose to live near them. Given that the CDC models
generating the obesity and physical activity estimates presumably include variables
likely to influence such preferences (income, etc.), our investigation cannot
isolate the preferences from the effect. Controlling for such a
self-selection effect would be necessary to isolate the exogenous
impacts of park access on obesity or other health outcomes. And regarding these
other variables: this study did not consider potential relationships between park
access and hospitalization rates, life expectancy, respiratory disease,
mental health, or any number of potential beneficial outcomes hypothesized
or explored in the existing literature. Exploring these connections and their
underlying mechanisms should be a priority as city planners and urban architects
attempt to improve the quality of life of urban residents in the future.

# Conclusion

Increased physical activity and decreased obesity rates are critical measures of
improvement in public health. Although many have theorized the link between park
accessibility and these metrics, previous literature has produced mixed
findings, perhaps owing to the range of variables modeled and the coarse spatial
scale of the analyses. Using New York City as a case study, we presented a
holistic and flexible measurement for
park accessibility that compares the continuous distance to all parks in the
region, weighted against the size of the park and its other amenities. In terms
of physical activity, we found a positive relationship where the least
park-accessible tracts have an expected physical activity participation rate
roughly one percentage point lower than the most accessible tracts. In terms of
obesity, we also found a strong and significant correlation between increased
park accessibility and decreased obesity rates, controlling for
spatial correlation, socioeconomic attributes, and physical activity rates.

In both cases a traditional, buffer-based analysis estimated a weaker relationship
with greater uncertainty. Buffer analyses are relatively common in the literature,
perhaps because of the widespread availability of GIS software. In spite of their
widespread use, they are relatively limited in terms of both their theoretical
underpinnings and their flexibility to accommodate attributes of parks beyond
their proximity. And even proximity may not be adequately handled, as the buffer
distance may be arbitrarily asserted by the researcher. The model we develop and
apply in this paper extends buffer driven models to contribute a more
comprehensive and flexible approach for measuring the impact of park access on
health outcomes. Adopting choice-based accessibilities of the kind used in this
study will allow researchers to
encompass the full range of park amenities in their accessibility analyses.
This will in turn enable planners to consider how multiple attributes of a park
--- from its location to its size to its amenities and beyond --- benefit the health
of the community the park serves.

## Acknowledgements
This project was funded by the Speedwell Foundation. We are grateful to Rachel
Samuels for helping to assemble the geolocated Twitter data.

# References {#references .unnumbered}

### 2019-09-24 03_logsums.Rmd
Move spatial weights calculation to estimation file
It makes more sense to think about the spatial weights as a function of the estimation rather than a function of the logsums. But this requires that we export a couple of additional datasets.

@@
   st_as_sf(crs = 4326, coords = c("LONGITUDE", "LATITUDE")) %>%
-  st_transform(3628)
+  st_transform(3628) %>%
+  write_rds("data/pop_weighted_centroids.rds")
+
 ```
@@
 # calculate the inverse distance to use as a weight on the neighbor connection
-dists <- nbdists(tracts.dnn, as(pop_weighted_centroids, "Spatial"))
-dists.inv <- lapply(dists, function(x) 1 / x)
-# get the spatial weights matrix and its trace to use in any impact analyses
-W <- nb2listw(neighbours = tracts.dnn, glist = dists.inv,
-              zero.policy = TRUE, style = "W")
-trMC <- trW(as(W, "CsparseMatrix"), type="MC") # trace used in montecarlo impacts
-print(W, zero.policy = TRUE)
+tract_dists <- nbdists(tracts.dnn, as(pop_weighted_centroids, "Spatial"))
+write_rds(tract_dists, "data/tract_distances.rds")
 ```
@@
 write_rds(distances, "data/distances.rds")
-write_rds(W, "data/W.rds")
 ```

### 2019-09-24 04_estimation.Rmd
Rebuild estimation notes
In this new analysis we land on the SDEM specification with out a lagged access term. We consider the econometric as well as the philosophical perspective in landing on this specification.

--- 2019-07-17 04_estimation.Rmd
@@
 library(tidyverse)
+library(broom)
 library(sf)
+library(spdep)
 library(spatialreg)
 library(texreg)
+library(here)
+library(dotwhisker)
+
+view_kable <- function(x){
+  if(isTRUE(getOption('knitr.in.progress'))){
+    x
+  } else {
+    tab <- paste(capture.output(x))
+    tf <- tempfile(fileext = ".html")
+    writeLines(tab, tf)
+    viewer <- getOption("viewer")
+    viewer(tf)
+  }
+}
 ```
 
-We load the data prepared previously. There is a file for each park and its 
-attribute, for each tract and its attributes, and the distance matrix between 
-parks and tracts.
+In this document we attempt to determine the correct spatial weights matrix and
+spatial spillovers specification. There are a few different questions we need
+to answer in this analysis:
 
-```{r loaddata}
-tracts_access <- read_rds("data/tracts_acces.rds")
-W <- read_rds("data/W.rds")
-trMC <- trMC <- trW(as(W, "CsparseMatrix"), type="MC")
-tracts_sp <- as(tracts_access, "Spatial")
+  - What is the most likely $W$?
+  - What is the econometrically "correct" specification of the model?
+  - Does this change depending on which matrix we end up using?
+  - Does this change depending on the dependent variable?
+
+## Spatial Weights Matrix
+A spatial econometric model represents the connections and spillovers between 
+regions with a matrix $W$. There are a few different ways to represent this
+matrix, but we will consider the simplest. First, let's load the shapefile of 
+the regions with the accessibility logsums attached.
+
+```{r tracts}
+tracts_access <- read_rds("data/tracts_access.rds")
 ```
+
+### Inverse distance weights
+My Atlanta house price study considered that houses within 1.8 miles of each
+other were "neighbors," with the strength of the relationship decaying with 
+the inverse of the distance between them. We can build the same matrix using 
+the population-weighted centroid of the tract as the observation point.
+
+```{r Winv}
+pop_weighted_centroids <- read_rds("data/pop_weighted_centroids.rds")
+
+# determine which tracts are neighbors of each other. Need to be less than
+# 1.8 miles away from the centroids
+tracts.dnn <- dnearneigh(pop_weighted_centroids, 0, 1.8 * 5280)
+# calculate the inverse distance to use as a weight on the neighbor connection
+tract_dists <- nbdists(tracts.dnn, as(pop_weighted_centroids, "Spatial"))
+
+tract_dists.inv <- lapply(tract_dists, function(x) 1 / x)
+# get the spatial weights matrix and its trace to use in any impact analyses
+Winv <- nb2listw(neighbours = tracts.dnn, glist = tract_dists.inv,
+                 zero.policy = TRUE, style = "W")
+print(Winv, zero.policy = TRUE)
+```
+
+### Contiguity weights
+
+Other investigations will often use a contiguity matrix where adjacent or
+bordering regions are considered neighbors.
+
+```{r Wcontig}
+tracts.adj <- poly2nb(tracts_access)
+Wcontig <- nb2listw(tracts.adj, style = "W", zero.policy = TRUE)
+print(Wcontig, zero.policy = TRUE)
+```
+
+## Spatial Econometric Selection
+
+There is some uncertainty over which model we should use for interpretation. 
+Part of the issue is that there is both an econometric / statistical approach as
+well as a intuition / behavioral understanding approach.
+
+In the intutive approach, it is easy to understand why physical activity and 
+obesity rates may be correlated in space. Individuals in neighboring tracts are
+likely to share cultural and experiential attributes that influence physical
+activity rates, and obesity. They eat at the same restaurants, attend the same
+schools, etc. This suggests that a model with correlated error components (the SEM),
+$$y = X\beta + u; u = \lambda W u + \epsilon$$
+is most applicable. It is less understandable why a dependency spillover (like the SAR),
+$$y = \rho W y + X\beta + \epsilon$$
+is warranted. This would imply that individuals in tract $i$ are obese *because* 
+individuals in tract $j$ are obese. It may be more likely that attributes of neighboring
+zones affect the outcome variable, as in the SLX model,
+$$y = X\beta + \gamma W X + \epsilon$$
+and the SDEM model,
+$$y = X\beta + \gamma W X + u; u = \lambda W u + \epsilon$$
+This kind of model suggests that the socioeconomic attributes of surrounding zones
+can affect the physical activity rates or obesity in the target zone, but that
+the outcome of a particular obesity rate is locally determined.
+
+The final model is the SDM, a complete linear combination of the SAR and SEM,
+$$y = \rho W y + X\beta + \gamma W X + \epsilon$$
+This would imply that obesity is a function of socioeconomic factors in the
+local and neighboring zones, *and* the obesity in those neighboring zones. This 
+seems to be a stretch.
+
+But here's where the econometric argument comes in. If the true DGP is an SEM
+and you use an OLS model to predict it, the coefficients will be unbiased but 
+with incorrectly small standard errors, affecting hypothesis tests. If the true 
+DGP is SDM but you use an OLS or SEM model, you have a missing variable and your
+estimates are inconsistent. Thus it is possible to test for whether the correct
+specification has been achieved independently of the rationale inherent in the
+model specification.
+
+### OLS vs SEM
+The base formula includes all of the tract-level covariates.
 
@@
 
-```{r spatial selection}
-physact_base_sem <- errorsarlm(update(base_formula, physact ~ .),
-                               data = tracts_sp, listw = W, zero.policy = TRUE)
-physact_base_sdm <- lagsarlm(update(base_formula, physact ~ .),
-                             data = tracts_sp, listw = W, zero.policy = TRUE,
-                             type = "mixed")
-test_sdmsem <- lmtest::lrtest(physact_base_sem, physact_base_sdm)
+Let's begin by estimating the OLS and SEM versions of the physical activity model
+as a function of the socioeconomic attributes (X) and the accesibility.
+
+$$PhysAct = X\beta + \beta_{access}*access + u; u = \lambda W u + \epsilon$$
+We will consider both spatial weights matrices.
+
+```{r ols_vs_sem}
+access_ols <- lm(update(base_formula, physact ~ . + access_ls), data = tracts_access)
+access_sem_wd <- errorsarlm(update(base_formula, physact ~ . + access_ls),
+                            data = tracts_access, listw = Winv, zero.policy = TRUE)
+access_sem_wc <- errorsarlm(update(base_formula, physact ~ . + access_ls),
+                            data = tracts_access, listw = Wcontig, zero.policy = TRUE)
+
+ols_vs_sem <- list("OLS" = access_ols, "SEM dist" = access_sem_wd, 
+                   "SEM cont" = access_sem_wd)
 ```
 
+In this case the null hypothesis is that both models (the OLS and SEM) are equally
+good representations of the underlying DGP (or at least provide consistent estimates
+of $\beta$). This suggests a Hausman-style test of the equality of the parameter 
+coefficients,
+$$H = (\beta_1 - \beta_2)^T (\Sigma_2 - \Sigma_1)^{-1} (\beta_1 - \beta_2)$$
+where the null hypothesis is that $\beta_{OLS} = \beta_{SEM}$
+
+```{r sp_hausman}
+sp_hausman <- function(ols, sem) {
+  b1 <- ols$coefficients
+  b2 <- sem$coefficients
+  db <- b1 - b2
+
+  V1 <- vcov(ols)
+  V2 <- vcov(sem)[rownames(V1), colnames(V1)]
+  dV <- V2 - V1
+
+  tibble(
+    Hstat = t(db) %*% MASS::ginv(dV) %*% db, 
+    "p-value" = pchisq(Hstat, df = Matrix::rankMatrix(dV))
+  )
+}
+
+sp_hausman(access_ols, access_sem_wd)
+sp_hausman(access_ols, access_sem_wc)
+```
+
+In both cases, we reject the null hypothesis that the coefficient estimates are
+the same and conclude that the true DGP is not likely OLS or SEM. Still, it's worth
+considering just how far apart the estimates are.
+
+```{r tidy.sarlm}
+tidy.sarlm <- function(x){
+  s <- summary(x)
+  df <- length(s$residuals) - length(s$coefficients) - 1
+  tibble(
+    term = gsub("[\\(\\)]", "\\.", rownames(s$Coef)),
+    estimate = s$Coef[,1],
+    std.error = s$Coef[,2],
+    statistic = estimate / std.error,
+    p.value = 2*(pt(abs(statistic), Inf, lower.tail = FALSE))
+  )
+}
+lapply(ols_vs_sem, tidy) %>%
+  bind_rows(.id = "model") %>%
+  dwplot() + scale_x_continuous(limits = c(-0.3, 1))
+```
+
+In the plot above `log(income)` is considerably larger than other variables but
+the estimates from the three models for that coefficient are similar. That said, 
+the only estimates that differ significantly between the OLS and SEM model are
+  - `log(density)`: in the case of the SEM models the coefficient is not a significant predictor.
+  - `college`: in the SEM models the coefficient takes a different sign with
+  physical activity *increasing* with college education.
+  - `access_ls`: this is our variable of interest.
+
+I'm curious what happens when we remove density from the base model.
+
+```{r nodensity}
+# take log(density) out of the bare access model
+nodensity <- lapply(ols_vs_sem, function(model) {
+  update(model, . ~ . - log(density))
+})
+lapply(nodensity, tidy) %>%
+  bind_rows(.id = "model") %>%
+  dwplot() + scale_x_continuous(limits = c(-0.3, 1))
+```
+
+Basically the same thing. It's worth looking at whether the same thing is happening
+in the obesity model.
+
+```{r obesity_sem}
+obesity_sem <- lapply(ols_vs_sem, function(model) {
+  update(model, obesity ~ . + physact)
+})
+lapply(obesity_sem, tidy) %>%
+  bind_rows(.id = "model") %>%
+  dwplot() 
+```
+
+Yup. Okay, given that, the question is whether adding lagged
+variables $\gamma W X$ to the model will resolve the discrepancy.
+
+### SLX vs SDEM
+
+The same basic logic applies to the SLX and SDEM models; if there is no dependence
+relationship among the $y$ variables, then the SLX and SDEM will have unbiased
+estimates of $\beta$ and $\gamma$.
+
+```{r access_slx}
+access_slx_wd <- lmSLX(update(base_formula, physact ~ . + access_ls), 
+                       data = tracts_access, listw = Winv, zero.policy = TRUE)
+access_slx_wc <- lmSLX(update(base_formula, physact ~ . + access_ls), 
+                       data = tracts_access, listw = Wcontig, zero.policy = TRUE)
+access_sdem_wd <- errorsarlm(update(base_formula, physact ~ . + access_ls),
+                            data = tracts_access, listw = Winv, zero.policy = TRUE,
+                            Durbin = TRUE)
+access_sdem_wc <- errorsarlm(update(base_formula, physact ~ . + access_ls),
+                            data = tracts_access, listw = Wcontig, zero.policy = TRUE, 
+                            Durbin = TRUE)
+slx_vs_sdem <- list(
+  "Dist SLX" = access_slx_wd, 
+  "Dist SDEM" = access_sdem_wd, 
+  "Contig SDEM" = access_sdem_wc,
+  "Contig SLX" = access_slx_wc
+)
+```
+
+As before, we can try a Hausman-style test, but in this case the covariance
+matrix appears poorly defined and we therefore get a negative test statistic.
+```{r slx_hausman}
+slx_hausman <- function(slx, sdem) {
+  b1 <- slx$coefficients
+  b2 <- sdem$coefficients
+  db <- b1 - b2
+
+  V1 <- vcov(slx)
+  V2 <- vcov(sdem)[names(b2), names(b2) ]
+  dV <- V2 - V1
+
+  tibble(
+    Hstat = t(db) %*% MASS::ginv(dV) %*% db, 
+    "p-value" = pchisq(Hstat, df = Matrix::rankMatrix(dV))
+  )
+}
+slx_hausman(access_slx_wc, access_sdem_wc)
+slx_hausman(access_slx_wd, access_sdem_wd)
+```
+
+Let's look at the tidied dataframes instead.
+
+```{r visual_compare}
+lapply(slx_vs_sdem, tidy) %>%
+  bind_rows(.id = "model") %>%
+  dwplot() + scale_x_continuous(limits = c(-0.5, 0.5))
+lapply(slx_vs_sdem, tidy) %>%
+  bind_rows(.id = "model") %>%
+  dwplot() 
+```
+
+Hey! This looks good! The direct effects are basically the same in all four models,
+with some disagreement in some lagged regressors. Unfortunately for this study,
+the access logsum variable is not directly significant. But this does point to a 
+potential way forwards: what if we don't lag that variable?
+
+```{r lagged_vars}
+contiglagged_vars <- tracts_access %>%
+  st_set_geometry(NULL) %>%
+  as_tibble() %>%
+  transmute_at(
+    vars(density, income, fulltime, college, single, youth, young_adults, seniors, black, asian, hispanic, other),
+    ~lag.listw(Wcontig, .)
+  ) %>%
+  mutate(geoid = tracts_access$geoid) %>%
+  dplyr::select(geoid, everything())
+
+names(contiglagged_vars)[-1] <- str_c("lag.", names(contiglagged_vars)[-1])
+contiglagged_tracts <- tracts_access %>% left_join(contiglagged_vars, by = "geoid")
+```
+
+This is a good model. Access is significant, the direct effects are significant
+and mostly in the correct sign, lagged variables are also significant.
+
+```{r physact_sdem}
+access_sdem_wc <- errorsarlm(update(base_formula, physact ~ . + 
+                                      log(lag.density) + log(lag.income) + 
+                                      lag.fulltime + lag.college + lag.single + lag.youth + 
+                                      lag.young_adults + lag.seniors + lag.black + lag.asian + 
+                                      lag.hispanic + lag.other + access_ls),
+                             data = contiglagged_tracts, listw = Wcontig, zero.policy = TRUE)
+```
+
+## Physical activity models
+Now to estimate the other models we are considering in the analysis.
+
+```{r estimate_sdems}
+base_sdem <- update(access_sdem_wc, formula = . ~ . - access_ls,
+                    data = contiglagged_tracts, listw = Wcontig, zero.policy = TRUE)
+
+# estimate models
+pa_access_sdm <- access_sdem_wc
+pa_tweets_sdm  <- update(base_sdem, .~ . + tweets_ls)
+pa_multi_sdm   <- update(base_sdem, .~ . + multi_ls)
+pa_walk10_sdm  <- update(base_sdem, .~ . + walk_10)
+```
+
+Now we can add all four access measures to the formula one after the other.
+
 ```{r access_sdm}
-# estimate models
-pa_access_sem <- update(physact_base_sem, .~ . + access_ls)
-pa_quarter_sem <- update(physact_base_sem, .~ . + walk_10)
-
-pa_models <- list("Base" = physact_base_sem,
-                  "Access: logsum" = pa_access_sem,
-                  "Access: 10-min walk" = pa_quarter_sem)
+pa_models <- list("Base"        = base_sdem,
+                  "Logsum"      = pa_access_sdm,
+                  "Tweets"      = pa_tweets_sdm,
+                  "Attributes"  = pa_multi_sdm,
+                  "10-min walk" = pa_walk10_sdm)
 ```
@@
 ```{r screen_pa_models}
+
 view_kable(
@@
 )
-```
-
-```{r}
-view_kable <- function(x){
-  tab <- paste(capture.output(x))
-  tf <- tempfile(fileext = ".html")
-  writeLines(tab, tf)
-  viewer <- getOption("viewer")
-  viewer(tf)
-}
 ```
@@
 ```{r screen_obesity_models}
-screenreg(obesity_models, digits = 4, table = FALSE)
+view_kable(
+  htmlreg(obesity_models, digits = 3, table = FALSE, single.row = TRUE, 
+                   caption.above = TRUE, caption = "Spatial Error Model ",
+          stars = c(0.001, 0.01, 0.05, 0.1) )
+)
 ```
 
-```{r screen_obese_models, eval = FALSE}
-  screenreg(obesity_models, digits = 4, table = FALSE, ci.force = TRUE,
-          single.row = TRUE, caption = "Spatial Error Model Estimates of Effect on Obesity Rates",
-          caption.above = TRUE, custom.coef.names = c(
-            "(Intercept)", "log(Density)", "log(Income)",
-            "Fulltime", "College-educated",  "Single Adults",
-            "Youth (0-17)", "Young adults (18-34)",
-            "Seniors (65+)", "Black population share",
-            "Asian population share",
-            "Hispanic population share", "Other Minorities",
-            "Physical activity",
-            "Spatial correlation", "Access: Logsum", "Access: 10-min walk"
-          ))
+```{r models}
+write_rds(pa_models, "data/pa_models.rds")
+write_rds(obesity_models, "data/obesity_models.rds")
 ```
-
-```{r obesityplot}
-names_for_terms <- c(
-  "(Intercept)", "log(density)", "log(Income)",
-  "Fulltime", "College-educated",  "Single Adults",
-  "Youth (0-17)", "Young adults (18-34)",
-  "Seniors (65+)", "Black population share",
-  "Asian population share",
-  "Hispanic population share", "Other Minorities",
-  "$\\gamma$: spatial correlation","Physical activity",
-  "Access: Logsum", "Access: 10-min walk"
-)
-termnames <- tibble(
-  name = names_for_terms,
-  term = c("Intercept", "log(density)", "log(income)", "fulltime", "college", "single",
-           "youth", "young_adults", "seniors", "black", "asian", "hispanic", "other",
-           "lag", "physact", "access_ls", "walk_10TRUE"))
-source("R/impacts_extractor.R")
-obesity_impacts <- lapply(obesity_models, function(x) impacts_extractor(x, trMC)) %>%
-  bind_rows(.id = "model")  %>%
-  left_join(termnames, by = "term") %>%
-  mutate(name = factor(name, levels = rev(names_for_terms)))
-
-ggplot(obesity_impacts %>% filter(effect == "Total"), 
-       aes(x = name, ymin = `2.5%`, ymax = `97.5%`,  y = `50%`, color = model)) +
-  geom_abline(slope = 0, intercept = 0, color = "gray") +
-  geom_errorbar(position = "dodge2") +
-  scale_color_brewer("Model", palette = "Set1") +
-  #geom_point(position = "dodge2") +
-  ylab("Simulated Total Impact on Obesity Rate") +
-  coord_flip() +
-  #facet_wrap(~effect) +
-  theme_bw() +
-  theme(legend.position = "bottom", 
-        axis.text.y = element_text(size = 10),
-        axis.title.y = element_blank())
-```

### 2019-09-28 04_estimation.Rmd
Rewrite econometrics to consider SDEM

@@
 ---
-title: "04_estimation"
+title: "Model "
 author: "Greg Macfarlane"
@@
 ```{r models}
+write_rds(slx_vs_sdem, "data/slx_vs_sdem.rds")
 write_rds(pa_models, "data/pa_models.rds")

### 2019-09-28 manuscript/manuscript.Rmd
Rewrite econometrics to consider SDEM

@@
 
-We predict the rate of physical activity ($y$) in a census tract as a
-function of the tract's sociodemographic characteristics and choice-based
-accessibility to parks with the following  specification:
+We predict either the physical activity or the obesity rate ($y$) in a census
+tract as a linear function of the tract's sociodemographic characteristics $X$
+and accessibility to parks ($A$),
 \begin{equation}\label{eq:themodel}
- y_i = f(\vect{x}_i, C_i, g(W, \vect{y}, \vect{X}))
+ y = X\beta + \beta_{a}A + \varepsilon
 \end{equation}
-where $\vect{x}_i$ is a vector of tract-level sociodemographic attributes,
-$C_i$ is a choice-based accessibility measure for the tract computed from
-Equation \ref{eq:cs} and $g(W, \vect{y}, X)$ represents the impact of spatial
-neighborhood effects on the outcome.
 
-Using tracts as the unit of observation in the model allows us to consider the
-availability of parks at a sub-metropolitan level, but it also introduces the problem
-of spatial correlation of unobserved errors and spatial dependence in the data
-generating process [@Cliff1970; @Anselin1980]. Spatial correlation occurs
-when spatially-distributed unobservable or missing variables (school quality,
-neighborhood prestige, etc.) influence the modeled outcomes. Spatial dependence
-occurs when the outcome *depends* on the outcome in neighboring areas; for
-example, seeing neighbors exercising may encourage exercise. The relaxed spatial
-Durbin model (SDM) proposed by @Burridge1981 controls for both processes:
-\begin{equation}\label{eq:sdm}
-  \vect{y}= \rho W\vect{y} + X\vect{\beta} + WX\vect{\gamma} + \vect{\epsilon}
+As the observations are related to each other spatially, it is likely that this
+process involves spatial spillovers of one kind or another. A complete treatment of
+spatial econometrics is not warranted here; the reader is directed to
+@LeSage2009 as well as @LeSage2014.
+Suffice it to say that the presence of spatial data generating processes can
+negatively affect econometric interpretation in a variety of ways. Each of these
+process relies on spatial autoregression, where elements of some random
+variable $x$ are spatially dependent on other elements, 
+\begin{equation}\label{eq:autoregression}
+ x = \rho W x + \varepsilon
 \end{equation}
-where $\rho$ is the estimated spatial correlation between the outcome variables
-$y_i, y_j, \ldots  \in \vect{y}$, $W$ is a matrix specifying the spatial
-relationship between observations $i$ and $j$ in the dataset,
-$\vect{\beta}$ is a vector of estimable coefficients relating the attributes $X$
-of an observation to its outcome, and $\vect{\gamma}$ is a vector of
-estimated coefficients relating the attributes of an observation's *neighbors*
-to its outcome. If only correlation and not dependence exists in the data
-generating process, it may  be more efficient to estimate a restricted
-spatial autoregressive model and therefore
-save degrees of freedom in the estimation. @tra_autoregression_paper
-illustrate a decision algorithm originally proposed by @Florax2003 which uses
-a likelihood ratio test of the SDM against the restricted spatial error model (SEM):
-\begin{align}
-{\boldsymbol y} &= X{\boldsymbol \beta} + {\boldsymbol u},  {\boldsymbol u} = \gamma W {\boldsymbol u} +
-{\boldsymbol \epsilon} \label{eq:SEM}\\
-{\boldsymbol y} &= X{\boldsymbol \beta} + (I-\gamma W)^{-1}{\boldsymbol \epsilon}\notag
-\end{align}
-If the likelihood ratio test rejects that the models are equivalent, then the SDM
-should be used because its estimates are unbiased. One consequence of using the SDM
-is that the estimated coefficients do not represent the
+with the strength of dependence an estimated parameter $\rho$, the structure of 
+dependence governed by the asserted matrix $W$ (details of $W$ follow below),
+and some random uncorrelated residual $\varepsilon$. A collection of models is
+available to represent spatial autodependence in the model residuals, the 
+independent variables, and the dependent variable.
 
-The researcher must assert $W$ *a priori*, though there are several
-common specifications \citep{Dubin1998}. In this study we specify that tracts
-with population-weighted centroids located within 1.8 Euclidean miles of each
-other are considered neighbors, and the strength of the relationship is the
-row-standardized (each row sums to 1) inverse of the distance between them:
-\begin{equation}\label{eq:weightsrule}
-W_{ij} = \begin{cases}
-  {\frac{d_{ij}^{-1}} {\sum_{k=1}^n d_{ik}^{-1}}} & \text{for $d_{ij} \leq 1.8$ miles}\\
-  0  & \text{for $d_{ij} > 1.8$ miles}
-  \end{cases}
+The specific spatial model applied is both an econometric choice
+--- as improperly specified spatial models can lead to inconsistent estimates of
+model parameters and standard errors --- as well as a philosophical choice about
+the likely structure of spillovers in the problem at hand. In case of physical
+activity and obesity rates, we believe that these outcomes
+are locally determined: That is, a particular individual decides whether or not
+to participate in physical activity independently of whether his or her neighbors
+participate in physical activity. Mathematically, we assert that the autodependence
+relationship on the dependent variable $y = \rho W y + \varepsilon$ has 
+$\rho = 0$ in the current case.
+
+With this relationship ruled out, it remains a possibility that the 
+model residuals are spatially dependent,
+\begin{equation}\label{eq:SEM}
+ y = X\beta + \beta_a A + u; u = \lambda W u + \varepsilon
 \end{equation}
+that the outcome is partially dependent on the socioeconomic variables in *neighboring*
+tracts,
+\begin{equation}\label{eq:SLX}
+ y = X\beta + \beta_a A + W X \lambda + \varepsilon
+\end{equation}
+or a linear combination of both.
+\begin{equation}\label{eq:SDEM}
+ y = X\beta + \beta_a A + W X \gamma + u; u = \lambda W u + \varepsilon 
+\end{equation}
+These models are referred as the spatial error model (SEM), the spatial lag of
+$X$ model (SLX), and the spatial Durbin error model (SDEM). @LeSage2014 suggest
+that a Hausman-style test of the estimates of $\beta$ derived from the OLS 
+(Equation \ref{eq:themodel}) and SEM (Equation \ref{eq:SEM}) can identify whether
+the estimates are consistent. If the $\beta$ estimates are dissimilar, both 
+specifications are inappropriate as they contain untreated omitted variables.
+Similarly, if the SLX and SDEM estimates are dissimilar it is an indication of 
+missing variables in that specification. On the other hand if the estimates of
+both pairs of models are similar and the residual correlation parameter $\lambda$
+is non-zero, the model accounting for spatially dependent residuals will produce 
+proper estimates of the model standard errors.
+
+Note that in the lag-$X$ specifications (SLX and SDEM) we exclude the accessiblity 
+component $A$, that is we do *not* consider that the accessibility
+in a neighboring zone will have an effect on physical activity or obesity rates.
+In a practical sense, this is because the accessibility term $A$ is itself spatially
+determined.
+
+### Spatial Weights
+
+The spatial weights matrix $W$ is constructed of individual elements where
+$w_{ij} = 0$ if observations $i$ and $j$ are spatially independent of each other,
+and $w_{ij} > 0$ if $i$ and $j$ are spatially related in some way. 
+@Dubin1998 presents details on constructing $W$, but in this study we
+assume that tracts sharing at least one common border point are neighbors of
+each other. The elements of $W$ are then row-standardized so that each observation
+has an equal total influence from all its neighbors.
 
@@
 ```
-This is a similar specification to that used by  \citet{tra_autoregression_paper}
-in a study of home prices in Atlanta. We selected this specification after
-comparing overall model likelihoods between it and a specification where tracts
-sharing a boundary are considered neighbors.
 
@@
 ```{r termnames}
-names_for_terms <- c(
-  "(Intercept)", "log(Density)", "log(Income)",
-  "Fulltime", "College-educated",  "Single Adults",
-  "Youth (0-17)", "Young adults (18-34)",
-  "Seniors (65+)", "Black population share",
-  "Asian population share",
-  "Hispanic population share", "Other Minorities",
-  "$\\gamma$: spatial correlation","Physical activity",
-  "Logsum", "Tweets", "Attributes", "10-min walk"
+base_termnames <- c(
+  "(Intercept)", "log(Density)", "log(Income)", "Fulltime", "College-educated",  "Single Adults",
+  "Youth (0-17)", "Young adults (18-34)", "Seniors (65+)", "Black population share",
+  "Asian population share", "Hispanic population share", "Other Minorities"
 )
 
-termnames <- tibble(
-  name = names_for_terms,
-  term = c("Intercept", "log(density)", "log(income)", "fulltime", "college",
-           "single", "youth", "young_adults", "seniors", "black", "asian", 
-           "hispanic", "other",
-           "lag", "physact", "access_ls", "tweets_ls", "multi_ls", "walk_10TRUE"))
+names_for_terms <- c(
+  base_termnames, str_c("$\\gamma$: ", base_termnames[-1]),
+  "$\\lambda$: spatial correlation"
+)
+
+access_terms <- c("Logsum", "Tweets",  "Attributes", "10-min walk")
 ```

### 2019-10-01 04_estimation.Rmd
Cleanup estimation

@@
 
-```{r screen_pa_models}
-
+```{r screen_pa_models, results = "asis"}
 view_kable(
@@
 
-```{r screen_obesity_models}
+```{r screen_obesity_models, results="asis"}
 view_kable(

### 2019-10-01 manuscript/manuscript.Rmd
Rewrite literature review - initial
This edit restructures the presentation of the utility-based accessibility measure to focus more clearly on extensions and similarities with the gravity model. Need to revise references accordingly.

@@
 title: >
-  Modeling the impacts of park access on health outcomes: a choice-based 
+  Modeling the impacts of park access on health outcomes: a utility-based 
   accessibility approach
@@
 lifestyles and behaviors, touching on topics including diet and exercise.
-Over the last few years a new social model of health has evolved, treating health
+Over the last several years a new social model of health has evolved, treating health
 ``as an outcome of the effects of socioeconomic status, culture,
@@
 particular parks and other public green spaces --- play a crucial role in
-promoting and sustaining public health [@Bedimo-Rung2005; @Coutts2008].
+promoting and sustaining public health [@Bedimo-Rung2005; Wells2007; @Coutts2008].
 After all, it does little to lecture individuals on the importance of exercise
@@
 paper, we present a holistic and flexible measurement for park accessibility
-based in activity location choice theory. This choice-based accessibility measure
+based in activity location choice theory. This utility-based accessibility measure
 compares the continuous distance to all parks in the region, weighted against
-the sizes of the each park and other assorted amenities.
+the sizes of each park and its other assorted amenities.
 
@@
 
-We also demonstrate how the choice-based accessibility metric can potentially be
+We also demonstrate how the utility-based accessibility metric can potentially be
 expanded to account for other measures of a park's attractiveness including its
@@
 
-Numerous previous studies have found relationships between characteristics of
-the built environment and aspects of physical, mental, social, and economic
-health. For the purposes of this study, it is clear that parks and other
-vegetated areas support outdoor physical activity in ways distinct from other
-urban environments [@Giles-Corti2005; @Wells2007].  In spite of these generally
-positive findings, the evidence of a specific link between green space and
-physical activity is somewhat mixed.
-
-<!-- Rewrite this section: 
-  - Cross-metropolitan studies are somewhat clear?
-  - Within-metropolitan studies are limited
--->
-
-@Wolf2008 reports that people self-identify as more active and attain a
-higher quality of life when a greater portion of their environment is greenspace.
+The large majority of extant research on the topic of park access and public health
+outcomes has been involved comparing metropolitan regions against each other. For example,
+a study by @West2012 used park data from
+the Trust for Public Land’s 2010 City Park Facts and public health data from the
+Behavioral Risk Factor Surveillance System (BRFSS) to examine the relationship
+between the density of park land and physical activity and obesity rates for 67
+metropolitan statistical areas in the U.S. The findings in this case conformed to 
+expectation; that is, the study found a significant positive association
+between park density and physical activity and a significant negative
+association between park density and obesity.
 @Larson2016 similarly used self-reported scores on the Gallup-Healthways
-Wellbeing Index to evaluate the relationship between different areas of
-wellbeing, including physical health, and park quantity, quality, and
-accessibility in 44 U.S. cities. While the authors found positive associations
-between wellbeing and park quality and accessibility, these relationships were
-not statistically significant. A study by @West2012 used park data from
-the Trust for Public Land’s 2010 City Park Facts and public health data from the
-Behavioral Risk Factor Surveillance System (BRFSS) to examine relationships
-between the density of parkland, parkland per capita, and levels of physical
-activity and obesity for 67 metropolitan statistical areas in the U.S. The study
-found a significant, positive association between park density and physical
-activity and a significant, negative association between park density and
-obesity. Conversely, @Richardson2012 examined the relationship between
-urban greenspace and selected mortality rates, and though the authors did not
+Wellbeing Index to evaluate the relationship between physical health and park
+quantity, quality, and accessibility in 44 U.S. cities. While the authors found
+positive associations between wellbeing and park quality and accessibility,
+these relationships were not statistically significant.
+Conversely, @Richardson2012 examined the relationship between total urban
+greenspace and mortality rates for selected maladies; though the authors did not
 find a statistically significant relationship between the quantity of urban
 greenspace and mortality caused by lung cancer, diabetes, heart disease or car
-accidents, they did find that all-cause mortality was oddly, *higher* in
-greener cities. In a meta-analysis of 20 peer reviewed journal articles
-exploring the relationship between parks and objectively measured physical
-activity, @Bancroft2015 found that five studies reported a significant
-positive association between the two, six studies produced mixed results, and
-nine studies found no association at all.
+accidents, they did find that all-cause mortality was oddly, *higher* in greener
+cities. Finally, in a meta-analysis of 20 peer reviewed journal articles exploring the
+relationship between parks and objectively measured physical activity,
+@Bancroft2015 found that five studies reported a significant positive
+association between the two, six studies produced mixed results, and nine
+studies found no association at all.
 
-While several of the aforementioned studies reported results consistent with the
-hypothesis that park access and use confer health benefits stemming from
-increased physical activity and attendant decreases in obesity, the large
-majority of extant research has been conducted at the level of the city or
-metropolitan statistical area. Metropolitan-level analyses do not capture the
+Metropolitan-level analyses such as those described above do not capture the
 within-city variation in accessibility to parks that exist in many cities. Some
@@
 a single city may also eliminate some regional or cultural fixed effects
-affecting metropolitan-level analyses.
+affecting metropolitan-level analyses. In a study of neighborhoods in New York
+City, @Stark2014 found that a higher proportion of park space in a neighborhood
+was associated with a lower BMI for its residents, and lower park cleanliness
+scores were associated with a higher BMI, suggesting that increasing the supply
+of clean, well-maintained parks could positively impact adult BMI.
 
-In a study of neighborhoods in New York City, @Stark2014 used
-hierarchical linear models to explore relationships between the proportion of
-zip codes that was park space, the cleanliness of parks, and the body mass index
-of adult residents. The authors found that a higher proportion of park space in
-a neighborhood was associated with a lower BMI for its residents, and lower park
-cleanliness scores were associated with a higher BMI, suggesting that increasing
-the supply of clean, well-maintained parks could positively impact adult BMI.
+## Park Accessibility Measures
 
-## Choice-based Accessibility
+Loosely defined, the *accessibility* of an arbitrary place describes the ease
+with which people can accomplish activities there. Accessibility is an abstract
+concept with tempting quantifiability, perhaps explaining the proliferation of
+calculation mechanisms. @Dong2006 present a helpful mathematical heirarchy of
+common mechanisms, which we follow here. Consider a person residing at
+point $i$ in a city with parks $j \in 1 \ldots J$. An analyst might consider
+point $i$ as "having access" to a park if the distance to the park $d_ij$  is less than some threshold
+$D$,
 
-Consider that an individual is choosing a park for a recreation activity.
-If we apply random utility choice theory, specifically the multinomial
-logit model [@McFadden1974], the expected probability of individual
-$i$ choosing park $j$ from the set of all regional parks $J$ is
-\begin{equation}\label{eq:mnl}
-P(j | V_{ij}) = \frac{\exp(V_{ij})}{\sum_{p \in J}\exp(V_{ip})}
+\begin{equation}\ref{eq:isochrone}
+A_i = \begin{cases} 
+      1 & d_{ij}\leq D\\
+      0 & d_{ij} > D
+   \end{cases}
+\end{equation}
+
+Variations of this isochrone-based framework are easily derived and relatively common. 
+@ParkScore is a sophisticated application of this approach where $d_{ij}$ is a
+carefully calculated 10-minute network-bound walk, with a demographic analysis of
+areas within and without this threshold. In other applications $D$ might be more variably defined,
+such as "Does a park exist within the census tract?". The indicator function could also be
+modified into the total number of parks or percent of park space within radius $D$ of point $i$.
+
+A somewhat more holistic approach is the so-called "gravity" accessibility
+statistic. In this case the accessibility of a point is the denominator of the 
+gravity formulation of a trip distribution model,
+
+\begin{equation}\ref{eq:gravity}
+A_i = \sum_{j = 1}^J S_j f(d_{ij})
+\end{equation}
+
+where $S_j$ is the "size" of each park literally (i.e. acres) or abstractly (i.e.
+trip attractions) and $f(d_ij)$ is a monotonically decreasing cost function,
+usually a negative exponential. @Dong2006 note that the isochrone framework is a
+special case of the gravity model where $f(d_{ij})$ is a binary function.
+
+A third accessibility mechanism is a utility-based specification, termed as such
+for being derived from random utility choice theory. Consider that an individual
+living at point $i$ is choosing a park for a recreation activity. If we apply the multinomial logit
+model [@McFadden1974], the expected consumer surplus enjoyed by this individual 
+can be shown to be 
+\begin{equation}\label{eq:utility}
+A_i = \ln\left({\sum_{j = 1}^J\exp(V_{ij})}\right) + C
 \end{equation}
 where parks are differentiated from each other by their relative measurable
-utilities $V_{ij}$. In principle, $V$ may include any measurable attributes of either
-the choice maker or the park. In this study we use a linear formulation of
-\begin{equation}\label{eq:v_sd}
-V_{ij} = size_j\lambda_s + distance_{ij}\lambda_d
+*utilities* $V_{ij}$. $C$ is an unknown constant, but the difference in consumer
+surplus between two points $i$ and $k$ can be quantitatively compared as 
+$A_i - A_k$. In principle, $V$ may include any measurable attributes of either
+the choice maker or the park, and is typically represented as a linear-in-parameters
+function of destination attributes $X_j$ and the travel cost $d_{ij}$,
+\begin{equation}\label{eq:utility}
+V_{ij} = X_j\beta + \beta_d * d_{ij}
 \end{equation}
-incorporating the size of the park in acres and the distance of the park from
-the census tract $i$ in miles. The coefficients $\vect{\lambda}$ can be
-estimated from household surveys, though in the absence of a survey we
+the census tract $i$ in miles. The coefficients $\vect{\beta}$ can be
+are frequently estimated from household surveys, though in the absence of a survey we
 may assert reasonable values.
 
-A key theoretical outcome of random utility choice models is that the
-consumer surplus to individual $i$, or the total weighted value of all
-alternatives in individual $i$'s choice set, can
-be obtained as the logarithm of the sum in the denominator of the choice
-probability equation [@Small1981]:
-\begin{equation}\label{eq:cs}
-C_i = \ln\left({\sum_{p \in J}\exp(V_{ip})}\right)
-\end{equation}
-There are several advantages to such a log-sum defined metric relative to
-buffer-based accessibility metrics more commonly found in the literature. First,
+Note that the gravity formulation is itself a special case of the utility-based
+specification where $\exp(X_j\beta + \beta_d d_{ij}) = X_j f(d_{ij})$ [@Daly1982].
+The distinction between gravity and utility-based specification is meaningful, 
+however. Primarily, it becomes possible to construct accessibility statistics based
+on revealed behavioral preferences rather than calibrated or asserted values.
+
+Both gravity and utility-based specifications hold several advantages relative to
+isochrone-based accessibility metrics more commonly found in the literature. First,
 all individuals are defined as having some access to all parks, rather than an
@@
 
-Note that this formulation is an extension of gravity-based accessibility
-statistics, in the same way that the gravity-based trip distribution model
-is a specific case of
-a destination-choice model [@Daly1982]. But the extension is meaningful and
-allows us to consider more attributes of the park or the individual beyond size
-and impedance. For example, we can aggregate the number of tweets emanating from
-a park as a measure of the park's attractiveness beyond its size. The
-utility for the choice maker from Equation \ref{eq:v_sd} then becomes
-\begin{equation}\label{eq:v_sdt}
-V_{ij} = size_j\lambda_s + distance_{ij}\lambda_d + tweets_j\lambda_t
-\end{equation}
-
 In spite of its flexibility and basis in choice theory, accessibility measures
-based in log-sums have not received much application in the accessibility
+based in choice maker utility have not received much application in the accessibility
 literature compared with distance-based or even gravity-based measures.
+@Vale2016 also present a descriptive classification of
+active accessibility mechanisms, though these authors curiously dismiss
+utility-based metrics for incorporating randomness. The accessibility
+formula presented in \ref{eq:utility} is the expectation of a random utility process,
+and is not in and of itself random any more than the gravity model.
 @Zhang2011 present a metric with a similar functional form, though the

### 2019-10-01 manuscript/manuscript.Rmd
Rewrite literature review to focus more on accessibility methods.

@@
 a single city may also eliminate some regional or cultural fixed effects
-affecting metropolitan-level analyses. In a study of neighborhoods in New York
-City, @Stark2014 found that a higher proportion of park space in a neighborhood
-was associated with a lower BMI for its residents, and lower park cleanliness
-scores were associated with a higher BMI, suggesting that increasing the supply
-of clean, well-maintained parks could positively impact adult BMI.
+affecting metropolitan-level analyses.
 
@@
 with which people can accomplish activities there. Accessibility is an abstract
-concept with tempting quantifiability, perhaps explaining the proliferation of
+concept with tempting quantifiability [@Handy1997], perhaps explaining the proliferation of
 calculation mechanisms. @Dong2006 present a helpful mathematical heirarchy of
@@
 point $i$ in a city with parks $j \in 1 \ldots J$. An analyst might consider
-point $i$ as "having access" to a park if the distance to the park $d_ij$  is less than some threshold
-$D$,
+point $i$ as "having access" to a park if the distance to the park $d_ij$  within an
+"isochrone," or less than some threshold $D$,
 
-\begin{equation}\ref{eq:isochrone}
+\begin{equation}\label{eq:isochrone}
 A_i = \begin{cases} 
@@
 
-Variations of this isochrone-based framework are easily derived and relatively common. 
-@ParkScore is a sophisticated application of this approach where $d_{ij}$ is a
+Variations of this isochrone-based framework are easily derived and relatively
+common. 
+@Dias2019 considered road safety perception as an extenuating factor in the
+effective distance to a park.
+ParkScore [@parkscore2019] is a sophisticated application of this approach where $d_{ij}$ is a
 carefully calculated 10-minute network-bound walk, with a demographic analysis of
-areas within and without this threshold. In other applications $D$ might be more variably defined,
-such as "Does a park exist within the census tract?". The indicator function could also be
-modified into the total number of parks or percent of park space within radius $D$ of point $i$.
+areas within and without this threshold. In other applications $D$ might be more
+variably defined, such as the presence or percent of green space within a
+political or statistical boundary [@Mitchell2008].
+The indicator function could also be modified into the total number of parks or
+percent of park space within radius $D$ of point $i$ [@Kascynski2014].
+In a study of neighborhoods in New York
+City, @Stark2014 found that a higher proportion of park space in a neighborhood
+was associated with a lower BMI for its residents, and lower park cleanliness
+scores were associated with a higher BMI, suggesting that increasing the supply
+of clean, well-maintained parks could positively impact adult BMI.
 
-A somewhat more holistic approach is the so-called "gravity" accessibility
+In spite of the flexibility of adapted isochrone techniques, the arbritrary
+definitions necessarily imposed by researchers can inhibit holistic analysis,
+may have been inititially motivated by computational limitations [@Logan2017].
+A somewhat more complete approach is the so-called "gravity" accessibility
 statistic. In this case the accessibility of a point is the denominator of the
 gravity formulation of a trip distribution model,
-
-\begin{equation}\ref{eq:gravity}
+\begin{equation}\label{eq:gravity}
 A_i = \sum_{j = 1}^J S_j f(d_{ij})
 \end{equation}
-
 where $S_j$ is the "size" of each park literally (i.e. acres) or abstractly (i.e.
@@
 special case of the gravity model where $f(d_{ij})$ is a binary function. 
+@Giles-Corti2005 compare gravity-based accessibility scores with an isochrone
+specification and show that the former are more predictive of walking behavior;
+that is, the attributes of a park matter influence walking more than merely the
+distance to it. @Zhang2011 present a population-weighted gravity-based
+accessibility to parks metric with a national rather than metropolitan scope, 
+though they do not examine its correlation with health outcomes.
 
@@
 for being derived from random utility choice theory. Consider that an individual
-living at point $i$ is choosing a park for a recreation activity. If we apply the multinomial logit
-model [@McFadden1974], the expected consumer surplus enjoyed by this individual 
-can be shown to be 
+living at point $i$ is choosing a park for a recreation activity. If we apply
+the multinomial logit model [@McFadden1974], the expected consumer surplus
+enjoyed by this individual can be shown to be
 \begin{equation}\label{eq:utility}
@@
 surplus between two points $i$ and $k$ can be quantitatively compared as 
-$A_i - A_k$. In principle, $V$ may include any measurable attributes of either
+$A_i - A_k$ [@Bruce1977]. In principle, $V$ may include any measurable attributes of either
 the choice maker or the park, and is typically represented as a linear-in-parameters
@@
 however. Primarily, it becomes possible to construct accessibility statistics based
-on revealed behavioral preferences rather than calibrated or asserted values.
+on revealed behavioral preferences rather than calibrated or asserted values [@Handy1997].
 
-Both gravity and utility-based specifications hold several advantages relative to
-isochrone-based accessibility metrics more commonly found in the literature. First,
-all individuals are defined as having some access to all parks, rather than an
-arbitrary cutoff asserted by the researcher.
-This allows for the fact that some people are more or less sensitive to
-distances, and that distance is a continuous, non-binary phenomenon.
-It defies reason to assume a person living 1.1 miles
-from a park has functionally different accessibility than someone living at 0.9 miles.
-Second, the random utility formulation
-allows the researcher to include any attribute of the park as part of its utility
-specification; in this case, we consider the size of the park weighted against its
-distance as an element of relative accessibility. This suggests that
-not all parks are equal, and that a large park such as Central Park in Manhattan
-may provide health and activity benefits over a much larger area than a smaller
-community square.
+Both gravity and utility-based specifications hold several advantages relative
+to isochrone-based accessibility metrics more commonly found in the literature.
+First, all individuals are defined as having some access to all parks, rather
+than an arbitrary cutoff asserted by the researcher. This allows for the fact
+that some people are more or less sensitive to distances, and that distance is a
+continuous, non-binary phenomenon. It defies reason to assume a person living
+1.1 miles from a park has functionally different accessibility than someone
+living at 0.9 miles. Second, the random utility formulation allows the
+researcher to include any attribute of the park as part of its utility
+specification. This suggests that not all parks are equal, and that a large park
+such as Central Park in Manhattan may provide health and activity benefits over
+a much larger area than a smaller community square.
 
-In spite of its flexibility and basis in choice theory, accessibility measures
-based in choice maker utility have not received much application in the accessibility
+In spite of its flexibility and basis in choice theory, utility-based
+accessibility measures have not received much application in the accessibility
 literature compared with distance-based or even gravity-based measures.
-@Vale2016 also present a descriptive classification of
-active accessibility mechanisms, though these authors curiously dismiss
-utility-based metrics for incorporating randomness. The accessibility
-formula presented in \ref{eq:utility} is the expectation of a random utility process,
-and is not in and of itself random any more than the gravity model.
-@Zhang2011 present a metric with a similar functional form, though the
-authors arrive at it from a motivation other than destination choice theory.
-Log-sums are commonly used, however, in alternatives analyses of transit
-infrastructure improvements [@DeJong2007]. A reason for this is likely that
-a regional travel demand model is available to the analysts, thus making
-calibrated and multimodal logsums readily available [@Geurs2010].
+@Vale2016 present a descriptive classification of active accessibility techniques, and
+explicitly dismiss utility-based metrics for incorporating randomness. The
+accessibility formula presented in \ref{eq:utility} is the expectation of a
+random utility process, and is not in and of itself random any more than the
+gravity model is random.
+Utility-based accessibility metrics are commonly used, however, in alternatives
+analyses of transit infrastructure improvements [@DeJong2007]. A reason for this
+is likely that a regional travel demand model is available to the analysts, thus
+making calibrated and multimodal logsums readily available [@Geurs2010].
 
@@
 In this section, we develop a model with data for New York City, where
-we compute a holistic logsum-based accessibility to parks measure and model the
-relationship between this measure and physical activity rates, controlling for
-spatial effects and socioeconomic factors. We subsequently model the effect
-of the accessibility metric on obesity rates, accounting for physical activity and
-the other controls. Finally, we model the relationship between a modified logsum
-measure considering geolocated Twitter data and physical activity and obesity rates.
+we compute a set of utility-based accessibility to parks scores for each tract
+and model the relationship between this measure and physical activity rates,
+controlling for spatial effects and socioeconomic factors. We subsequently model
+the effect of the accessibility metric on obesity rates, accounting for physical
+activity and the other controls.
 
@@
 
-In a destination choice framework, the tracts represent the ``origins'' and
-``destinations'' are parks and green spaces in New York City.
+In a destination choice framework, the tracts represent the "origins" and
+"destinations" are parks and green spaces in New York City.
 We retrieved a polygons layer of public parks and greenspaces within New York City’s
@@
 These models are referred as the spatial error model (SEM), the spatial lag of
-$X$ model (SLX), and the spatial Durbin error model (SDEM). @LeSage2014 suggest
+$X$ model (SLX), and the spatial Durbin error model (SDEM). @Pace2008 suggest
 that a Hausman-style test of the estimates of $\beta$ derived from the OLS 
@@
 ```{r results}
+slx_vs_sdem <- read_rds(here("data/slx_vs_sdem.rds"))
 pa_models <- read_rds(here("data/pa_models.rds"))

### 2019-10-02 manuscript/manuscript.Rmd
Revise methodology section

@@
 In spite of the flexibility of adapted isochrone techniques, the arbritrary
-definitions necessarily imposed by researchers can inhibit holistic analysis,
-may have been inititially motivated by computational limitations [@Logan2017].
+definitions necessarily imposed by researchers in its application can inhibit
+holistic analysis [@Logan2017].
 A somewhat more complete approach is the so-called "gravity" accessibility
@@
 special case of the gravity model where $f(d_{ij})$ is a binary function. 
-@Giles-Corti2005 compare gravity-based accessibility scores with an isochrone
-specification and show that the former are more predictive of walking behavior;
-that is, the attributes of a park matter influence walking more than merely the
-distance to it. @Zhang2011 present a population-weighted gravity-based
-accessibility to parks metric with a national rather than metropolitan scope, 
-though they do not examine its correlation with health outcomes.
+@Giles-Corti2005 compare various gravity-based accessibility scores with an
+isochrone specification and show that the former are more predictive of walking
+behavior; that is, the attributes of a park matter influence walking more than
+merely the distance to it. @Zhang2011 present a population-weighted
+gravity-based accessibility to parks metric with a national rather than
+metropolitan scope, though they do not examine its correlation with health
+outcomes.
 
@@
 function of destination attributes $X_j$ and the travel cost $d_{ij}$,
-\begin{equation}\label{eq:utility}
+\begin{equation}\label{eq:utilityV}
 V_{ij} = X_j\beta + \beta_d * d_{ij}
 \end{equation}
-the census tract $i$ in miles. The coefficients $\vect{\beta}$ can be
-are frequently estimated from household surveys, though in the absence of a survey we
-may assert reasonable values.
+The coefficients $\vect{\beta}$ are frequently estimated from household
+surveys, though in the absence of a survey we may assert reasonable values.
 
@@
 living at 0.9 miles. Second, the random utility formulation allows the
-researcher to include any attribute of the park as part of its utility
-specification. This suggests that not all parks are equal, and that a large park
-such as Central Park in Manhattan may provide health and activity benefits over
-a much larger area than a smaller community square.
+researcher to include -- in principle -- any attribute of the park as part of
+its utility specification. This suggests that not all parks are equal, and that
+a large park with many amenities such as Central Park in Manhattan may provide
+health and activity benefits over a much larger area than a smaller community
+square.
 
@@
 
-In a destination choice framework, the tracts represent the "origins" and
+In a destination choice framework, the tracts represent the "origins" and the
 "destinations" are parks and green spaces in New York City.
@@
 eliminated sub-facilities such as tennis courts or baseball fields included within
-larger park facilities. Instead of these sub-facilities, we created 
-variables for each park indicating the presence of sports courts, playgrounds,
-and trails.
+larger park facilities. Instead of these distinct sub-facilities, we created 
+variables for each containing park indicating the presence of sports courts,
+playgrounds, and trails.
 
@@
 
+## Accessibility 
+\label{subsec:accessibility}
+
+We calculate a set of utility-based accessibility statistics for each tract
+in New York City. The most basic utility specification includes only the
+the park size in acres and the distance from the population-weighted tract centroid
+to the boundary of the park in miles,
+\begin{equation}\label{eq:u_access}
+V_{ij} = \lambda_s * \log(size_j) + \lambda_d * \log(distance_{ij})
+\end{equation}
+The logarithmic transform allows for diminishing marginal utility of distance
+and park size: A 1-mile increase to a trip matters more for a 1-mile trip than a
+10-mile trip. @Macfarlane2019 estimated destination choice 
+parameters for park trips in the Alameda County (Oakland), California using
+this utility specification, obtaining values of $\lambda_s = 0.373$ and 
+$\lambda_d = -1.98$. The ratio of these estimates implies people are willing to
+travel roughly six times further to reach a park twice as large. In the absence 
+of park trip destination choice coefficients in New York City, we apply these
+previous estimates.
+
+The second utility specification is adapted from a park destination choice model
+estimated by @Kinnell2006 in New Jersey. In this study the authors used a revealed
+preference survey to determine which factors of a park and its surrounding environment
+affected its selection. By bringing over common variables, we can create a second
+utility specification as
+\begin{equation}\label{eq:u_multi}
+V_{ij} = \lambda_s * \log(size_j) + \lambda_d * \log(distance_{ij}) + \lambda_t * trails + \\
+  \lambda_{c} * courts + \lambda_p * playgrounds
+\end{equation}
+with $\lambda_t = 0.99$, $\lambda_c = 0.43$, and $\lambda_p = 0.26$. @Kinnell 
+did not transform their size and distance estimates, so we retain the previously 
+estimated and applied values. We assume that the other covariates in the @Kinnell
+model which we do not have available to us (e.g., boat launches, picnic areas) are
+orthogonal to the included parameters and leaving them out will not affect the
+values of the included coefficients.
+
+The final utility specification includes the number of geolocated tweets
+emanating from within the park in September of 2014 in addition to the
+basic specification in Equation \ref{eq:u_access},
+\begin{equation}\label{eq:u_tweets}
+V_{ij} = \lambda_s * \log(size_j) + \lambda_d * \log(distance_{ij}) + \lambda_{tw} * YJ(tweets)
+\end{equation}
+with $YJ(x)$ being a Yeo-Johnson transformation that implements a diminishing
+marginal return similar to $log(x)$, but where $YJ(0) = 0$ [@Yeo2000]. In this
+case we have no external information describing how destination choice to
+parks may be affected by the twitter activity in the park, so we assert a 
+value of $\lambda_{tw} = 0.1$
+
+We then calculate the utility-based accessibility of each tract $A_i$ as defined
+in Equation \ref{eq:utility} under each utility specification. Recall that the 
+total value of the accessibility is relative to an unknown scalar $C$; for this 
+reason we standardize the accessibility values for all tracts within each
+utility specification, 
+\begin{equation}\label{eq:v_logged}
+A_i' = \frac{A_i - \bar{A}}{sd(A)}
+\end{equation}
+
+Figure \ref{fig:map} shows a map of New York City with each tract highlighted
+based on its relative basic utility-based accessibility score (Equation
+\ref{eq:u_access}). The most continuous region of good park access is in upper
+Manhattan and the Bronx, bracketed by Central Park and the Bronx River.
+Conversely, some of the poorest-accessibility areas are in Brooklyn tracts not
+immediately adjacent to Prospect Park. Because the accessibility statistic is
+normalized, the worst values are slightly below $-3$, the best somewhere above
+$3$.
+
+For comparative purposes, we also employ an isochrone analysis using the
+10-minute walk threshold calculated for ParkScore [@parkscore2019]. If the
+population-weighted centroid of a tract is within a 10-minute walk of a green space
+as defined by ParkScore, the tract is considered as having "access" to a park.
+The centroid is necessary as all tracts in New York City have at least *some* 
+intersection with the 10-minute walk buffer; as it is, only 
+`r sum(!tracts$walk_10)` of the `r nrow(tracts)` tract centroids are not located 
+in this buffer.
+
+```{r map, fig.env="figure*", echo=FALSE, message=FALSE, warning=FALSE, fig.height=4, fig.cap="Normalized choice-based park accessibility log-sum values in New York City."}
+library(ggmap)
+map <- ggmap(
+  get_stamenmap(unname(st_bbox(tracts)), 
+                maptype = "toner-lite"), extent = "device")
+map +
+  geom_sf(data = tracts, inherit.aes=FALSE,
+          aes(fill = cut(access_ls, breaks = c(-Inf, -3, -2, -1, 0, 2, 3, Inf))),
+          alpha = 0.8, color = NA) +
+  scale_fill_brewer("Normalized Log-sum", palette = "GnBu")
+```
+
 ## Model 
@@
 assume that tracts sharing at least one common border point are neighbors of
-each other. The elements of $W$ are then row-standardized so that each observation
-has an equal total influence from all its neighbors.
+each other^[We also considered a distance-discounted weights matrix, which
+produced similar results. This matrix is selected for simplicity.]. The elements
+of $W$ are then row-standardized so that each observation has an equal total
+influence from all its neighbors.
 
@@
 trMC <- trW(as(W, "CsparseMatrix"), type="MC")
-```
-
-## Accessibility 
-\label{subsec:accessibility}
-
-Extant destination choice models used in practice typically use travel time in
-minutes as a travel impedance term, and employment by sector as a size term or
-attraction component. Typically such models handle recreational trips together with
-other non-work and non-school trips, and we therefore can find no previously
-estimated coefficients using size terms relevant to park acreage or amenities.
-Given this gap in the literature, we instead assert plausible values for
-$\beta$ to generate the choice-based accessibility statistic used in this study.
-
-The functional form of the accessibility statistic is adapted from
-Equation \ref{eq:v_sd} by log-transforming first the distance (Euclidean, in miles)
-between the park boundaries and population-weighted tract centroids and second the
-park size (in acres).
-\begin{equation}\label{eq:v_logged}
-V_{ij} = \log(size_j)\lambda_s + \log(distance_{ij})\lambda_d
-\end{equation}
-We then calculate the consumer surplus $C$  (log-sum of the exponentiated
-utilities) for each tract and standardize the result,
-\begin{equation}\label{eq:v_logged}
-C_i' = \frac{C_i - \bar{\vect{C}}}{sd(\vect{C})}
-\end{equation}
-
-We initially estimated potential values of the $\lambda$ coefficients by
-applying a limited-memory, box-constrained optimization algorithm
-maximizing the model log-likehood.\footnote{Using the {\texttt nlm} function
-in R [@RCoreTeam2018]} The constraint required that the coefficient on
-size be positive and that on distance negative; all else equal, we assert people
-will prefer to use larger parks and parks that are nearer to their residence. This
-resulted in $\lambda_d = -1.98$  and $\lambda_s = 0.000$. Though the ``most
-likely'' parameter value, in this case it was unsatisfactory for two reasons:
-first, our prior assertion that park size is a valuable attribute of a park, and
-second the observation that with these maximum likelihood values tracts
-bordering on the corners of Central Park were measured with poor overall
-accessibility, an unacceptably unintuitive result. We subsequently adjusted the
-$\lambda_s$ value to $0.3$; the relative ratio of the coefficients implies that
-all else equal, an individual would travel 6.6 times further to access a park
-twice as large.
-
-Figure \ref{fig:map} shows a map of New York City with each tract highlighted
-based on its relative accessibility score. The most continuous region of good park
-access is in upper Manhattan and the Bronx, bracketed by Central Park and the
-Bronx River. Conversely, some of the poorest-accessibility areas are in
-Brooklyn tracts not immediately adjacent to Prospect Park. Because the
-accessibility statistic is normalized, the worst values are slightly below $-3$,
-the best somewhere above $3$.
-
-```{r map, fig.env="figure*", echo=FALSE, message=FALSE, warning=FALSE, fig.height=4, fig.cap="Normalized choice-based park accessibility log-sum values in New York City."}
-library(ggmap)
-map <- ggmap(
-  get_stamenmap(unname(st_bbox(tracts)), 
-                maptype = "toner-lite"), extent = "device")
-map +
-  geom_sf(data = tracts, inherit.aes=FALSE,
-          aes(fill = cut(access_ls, breaks = c(-Inf, -3, -2, -1, 0, 2, 3, Inf))),
-          alpha = 0.8, color = NA) +
-  scale_fill_brewer("Normalized Log-sum", palette = "GnBu")
 ```

### 2019-10-03 04_estimation.Rmd
Corrrect spatial chi-squared test statistic

@@
     Hstat = t(db) %*% MASS::ginv(dV) %*% db, 
-    "p-value" = pchisq(Hstat, df = Matrix::rankMatrix(dV))
+    "p-value" = pchisq(Hstat, df = Matrix::rankMatrix(dV), lower.tail = FALSE)
   )

### 2019-10-03 04_estimation.Rmd
Export models estimated without lagged accessibility coefficients

@@
 
-```{r physact_sdem}
-access_sdem_wc <- errorsarlm(update(base_formula, physact ~ . + 
-                                      log(lag.density) + log(lag.income) + 
-                                      lag.fulltime + lag.college + lag.single + lag.youth + 
-                                      lag.young_adults + lag.seniors + lag.black + lag.asian + 
-                                      lag.hispanic + lag.other + access_ls),
+```{r nolag_access}
+access_slx_wc <- lm(update(
+  base_formula, physact ~ . +  log(lag.density) + log(lag.income) + 
+    lag.fulltime + lag.college + lag.single + lag.youth +  lag.young_adults + 
+    lag.seniors + lag.black + lag.asian + lag.hispanic + lag.other + access_ls),
+  data = contiglagged_tracts)
+
+access_sdem_wc <- errorsarlm(update(
+  base_formula, physact ~ . +  log(lag.density) + log(lag.income) + 
+    lag.fulltime + lag.college + lag.single + lag.youth +  lag.young_adults + 
+    lag.seniors + lag.black + lag.asian + lag.hispanic + lag.other + access_ls), 
   data = contiglagged_tracts, listw = Wcontig, zero.policy = TRUE)
+```
+
+```{r nolag_access_tests}
+slx_hausman(access_slx_wc, access_sdem_wc)
+slx1_vs_sdem1 <- list("SLX" = access_slx_wc, "SDEM" = access_sdem_wc)
+
+screenreg(slx1_vs_sdem1, ci.force = TRUE)
 ```
@@
 ```{r models}
-write_rds(slx_vs_sdem, "data/slx_vs_sdem.rds")
+write_rds(slx1_vs_sdem1, "data/slx_vs_sdem.rds")
 write_rds(pa_models, "data/pa_models.rds")

### 2019-10-03 04_estimation.Rmd
Add discussion of SLX vs SDEM tests

@@
   bind_rows(.id = "model") %>%
-  dwplot() + scale_x_continuous(limits = c(-0.5, 0.5))
+  dwplot() + scale_x_continuous(limits = c(-0.5, 0.6))
 lapply(slx_vs_sdem, tidy) %>%

### 2019-10-03 manuscript/manuscript.Rmd
Add discussion of SLX vs SDEM tests

@@
 options(tigris_use_cache = TRUE)
-opts_chunk$set(cache=TRUE, message = FALSE, echo = FALSE, warning = FALSE)
+opts_chunk$set(cache=FALSE, message = FALSE, echo = FALSE, warning = FALSE)
 library(leaflet)
@@
 `r sum(!tracts$walk_10)` of the `r nrow(tracts)` tract centroids are not located 
-in this buffer.
+within this buffer.
 
@@
 with the strength of dependence an estimated parameter $\rho$, the structure of 
-dependence governed by the asserted matrix $W$ (details of $W$ follow below),
+spatial dependence governed by the asserted matrix $W$ (details of $W$ follow below),
 and some random uncorrelated residual $\varepsilon$. A collection of models is
@@
 names_for_terms <- c(
-  base_termnames, str_c("$\\gamma$: ", base_termnames[-1]),
-  "$\\lambda$: spatial correlation"
+  base_termnames, str_c("$\\gamma$: ", base_termnames[-1])
 )
 
+lambda <- "$\\lambda$: spatial correlation"
 access_terms <- c("Logsum", "Tweets",  "Attributes", "10-min walk")
+```
+
+```{r slx_hausman}
+slx_hausman <- function(slx, sdem) {
+  b1 <- slx$coefficients
+  b2 <- sdem$coefficients
+  db <- b1 - b2
+
+  V1 <- vcov(slx)[names(b1), names(b1) ]
+  V2 <- vcov(sdem)[names(b2), names(b2) ]
+  dV <- V2 - V1
+
+  tibble(
+    Hstat = t(db) %*% MASS::ginv(dV) %*% db, 
+    "p-value" = pchisq(Hstat, df = Matrix::rankMatrix(dV), lower.tail = FALSE)
+  )
+}
+
+slx_sdem_htest <- slx_hausman(slx_vs_sdem[[1]], slx_vs_sdem[[2]])
+```
+
+To determine which spatial effects specification was appropriate, we estimated
+SLX and SDEM models of physical activity participation rates as a function of
+tract covariates and  accessibility. These two models are presented in Table 
+\ref{tab:slx-sdem}. With only a few exceptions, the SLX and SDEM coefficient
+estimates for corresponding covariates lie within the 95\% confidence intervals
+of the other model. A Hausman-style test [@LeSage2008] on the coefficients 
+assumes a null hypothesis that the coefficients are equivalent; this test 
+produces $p$-value of only $`r slx_sdem_htest[2]`$. Though this statistic is
+technically beneath a common hypothesis test threshold of $\alpha = 0.05$, we
+fail to reject the null hypothesis that the coefficients are equivalent, as 
+the differences are not practically different from each other. The consequences
+of rejecting the null hypothesis in this case would be to suggest a model with 
+spatial dependence of the dependent variable; as stated above, we feel that such
+a relationship is unreasonable. As a consequence of these analyses, we adopt the
+SDEM specification moving forward as the spatial lag of the errors is 
+significant and the overal log likelihood of the SDEM is higher than the SLX 
+specification.
+
+```{r slx-sdem, results = "asis"}
+texreg(slx_vs_sdem, single.row = TRUE, ci.force = TRUE, 
+       custom.coef.names = c(names_for_terms, "Accessibility", lambda), 
+       # Goodness of fit (LM and SP are different)
+       custom.gof.rows = list(
+         "Log Likelihood" = lapply(slx_vs_sdem, logLik) %>% unlist(),
+         "Num. Obs." = lapply(slx_vs_sdem, function(s) length(s$residuals))
+       ),
+       include.rsquared = F, include.adjrs = F, include.aic = F, include.loglik = F,
+       include.parameters = F, include.nobs = F,
+       use.packages = FALSE, booktabs = TRUE,
+       caption = "Comparison of SLX and SDEM Coefficients",
+       caption.above = TRUE)
 ```

### 2019-10-03 04_estimation.Rmd
Add lagged physical activity to obesity models

@@
   transmute_at(
-    vars(density, income, fulltime, college, single, youth, young_adults, seniors, black, asian, hispanic, other),
+    vars(density, income, fulltime, college, single, youth, young_adults, seniors, black, asian, hispanic, other, physact),
     ~lag.listw(Wcontig, .)
@@
 obesity_models <- lapply(pa_models, function(model){
-  update(update(model, obesity ~ . + physact))
+  update(update(model, obesity ~ . + physact + lag.physact))
 })

### 2019-10-03 manuscript/manuscript.Rmd
Work on results discussion

@@
 
-```{r map, fig.env="figure*", echo=FALSE, message=FALSE, warning=FALSE, fig.height=4, fig.cap="Normalized choice-based park accessibility log-sum values in New York City."}
+```{r map, fig.env="figure*", echo=FALSE, message=FALSE, warning=FALSE, fig.height=4, fig.cap="Normalized utility-based park accessibility values in New York City."}
 library(ggmap)
@@
           alpha = 0.8, color = NA) +
-  scale_fill_brewer("Normalized Log-sum", palette = "GnBu")
+  scale_fill_brewer("Accessibility", palette = "GnBu")
 ```
@@
 ```{r slx-sdem, results = "asis"}
-texreg(slx_vs_sdem, single.row = TRUE, ci.force = TRUE, 
+texreg(slx_vs_sdem, single.row = TRUE, ci.force = TRUE,  digits = 4,
        custom.coef.names = c(names_for_terms, "Accessibility", lambda), 
@@
        caption = "Comparison of SLX and SDEM Coefficients",
+       label = "tab:slx-sdem",
        caption.above = TRUE)
@@
 
-We estimated SDM and SEM models regressing the physical activity rate
-against the base covariates (without any accessibility component). A likelihood
-ratio test failed rejected that the SDM is different from the SEM, so we use
-the SDM specification only going forward. Recall that in an SDM the effect of a
-covariate on the dependent variable is *not* the estimated coefficient. As a
-consequence of this Table \ref{tab:pa_models} presents the estimated
-coefficients for the base model with the socioecononomic controls and
-no representation of park accessibility. For the most part the coefficients are
-highly significant and of the expected sign. Tracts with higher shares
-of full-time workers, college-educated adults, young adults, and high-income
-households all show a greater share of individuals engaging in regular physical
-activity. Conversely, tracts with greater population density and a greater
-share of single adults, children, seniors, minorities of all types, and low
-income households all have lower modeled rates of physical activity.
+The coefficients in the SDEM model are of two general types: the direct effect
+resulting from a tract's own attributes and the indirect effect ($\gamma$)
+resulting from the spatially-weighted attributes of its neighbors. For example, a
+percentage point increase in the share of young adults in a tract increases the
+expected physical activity rate in a tract by 
+`r slx_vs_sdem[[2]]$coefficients["young_adults"]` percentage points, and a
+percentage point increase in the share of young adults
+*in neighboring tracts* increases the expected physical activity rate by an 
+*additional* `r slx_vs_sdem[[2]]$coefficients["lag.young_adults"]` percentage
+points. This opportunity to examine spatial spillovers of attributes is a key 
+benefit of using a spatial model.
 
-To this base model we add a measure of park accessibility considered in two
-ways: a logsum-based statistic as described earlier and a more typical quarter-mile
-binary access buffer. The estimated coefficients for these models are also
-given in Table \ref{tab:pa_models}. In both accessibility specifications,
-the access measure is positively correlated with physical activity rates; all else
-equal, people in tracts with higher accessibility to parks have higher estimated
-rates of physical activity. Though the estimated coefficient on the quarter-mile
-buffer appears to have a larger absolute value than the logsum-based statistic,
-this masks a key difference in the specification worth further comment.
-The logsum allows for variation in access unavailable in the buffer-based method.
-In our dataset almost every tract
-(`r round(sum(tracts$access_025) / nrow(tracts) * 100, 0)`%) is within
-a quarter-mile of *some* kind of park, but this park may not be large enough
-to support physical activities all individuals would like to participate in.
-Because tracts with only adequate park access are grouped with tracts having
-excellent park access, the overall effect is comparatively unclear. The logsum-based
-coefficient, on the other hand, suggests going from the least-accessible ($-3.0$)
-to the most-accessible ($3.0$) tract implies roughly a $1.1$ percentage point
-rise in estimated physical activity rates.
+For the most part the direct coefficients are highly significant and of the
+expected sign. Tracts with higher shares of full-time workers, college-educated
+adults, young adults, and high-income households all show a greater share of
+individuals engaging in regular physical activity. Conversely, tracts with
+greater population density and a greater share of single adults, children,
+seniors, minorities, and low income households all have lower modeled expected
+rates of physical activity. The indirect coefficients are less clearly significant,
+with only density, median tract income, some age groups, and some minority groups
+showing an indirect effect.
 
-```{r effectsplot, results = "asis"}
-texreg(pa_models[c("Base", "Logsum", "10-min walk")], digits = 4,
+Table \ref{tab:pa-models} present the estimated spatial lag and accessibility
+coefficients for three models using different specifications of the utility
+equation, as well as the ten-minute walk buffer calculated by ParkScore. 
+Note that the model called "Size and Distance" is precisely the model
+labeled "SDEM" in Table \ref{tab:slx-sdm}. The controllling covariates are
+suppressed for clarity but do not change substantially across the four specifications.
+Complete model estimates are available from the authors. Each of the three
+utility-based specifications is significant at the $\alpha = 0.05$ level or lower,
+and is of the hypothesized directionality. That is, residents living in tracts 
+with increased utility-based accessiblity to green spaces show a significantly
+higher physical activity participation rate. Taking the rough mean of the three
+model rates, moving from the least-accessible tract ($A_i = -3$) to the
+most-accessible tract ($A_i = 3$) is expected to raise the physical activity rate
+by `r 6 * .2` percentage points. With the understanding of the full 95\% confidence
+interval, we could suggest that the true effect of excellent versus poor park access
+is anywhere between `r 6 * .05` and `r 6 * .35` percentage points.
+
+The 10-minute walk buffer is considerably less useful at isolating the effects
+of park "access" on physical activity rates. As so few tracts are located
+outside of the buffer, the standard error of the estimated effect is large and implies
+an effect on activity rates anywhere from a loss of `r 6 * .37` percentage points
+to a gain of `r 6 * 1.5`.
+
+```{r pa-models, results = "asis"}
+texreg(pa_models[c(2:5)], digits = 4, ci.force = TRUE,
        booktabs = TRUE, use.packages = FALSE, 
-       caption = "SEM Coefficients Predicting Physical Activity Rates",
-       caption.above = TRUE,
-       custom.note = "%stars. Standard errors in parentheses.")
+       custom.model.names = c("Size and Distance", "Twitter", "Amenities", "ParkScore"),
+       custom.coef.map = list(
+         "lambda" = "$\\lambda$: spatial correlation", 
+         "access_ls" = "Size and Distance", 
+         "multi_ls" = "Amenities", 
+         "tweets_ls" = "Twitter Activity", 
+         "walk_10TRUE" = "10-minute walk"),
+       caption = "Estimated Effect of Accessibility on Physical Activity Rates",
+       label = "tab:pa-models",
+       caption.above = TRUE, include.aic = F, include.lr = F,
+       custom.note = "%stars 95\\% confidence interval in brackets.")
 ```
-\end{table*}
 
@@
 the *obesity* rate, and physical activity becomes an independent covariate
-alongside the controlling variables and the accessibility metric.
-Table \ref{tab:obese_models} again presents the base model without
+alongside the controlling variables and the accessibility metrics.
+Table \ref{tab:obesity-models} presents estimates of the effect of all three
+utility-based accessibility measures as well as the 10-minute walk buffer. 
+without
 any accessiblity measure, and models with accessibility captured through a
@@
 
-```{r obesemodelchart, results="asis"}
-texreg(obesity_models, digits = 4, 
+```{r obesity-models, results="asis"}
+screenreg(obesity_models[c(2:5)], digits = 4, ci.force = TRUE, 
        booktabs = TRUE, use.packages = FALSE, 
-       caption = "SEM Coefficients Predicting Obesity Rates",
-       caption.above = TRUE,
-       custom.note = "%stars. Standard errors in parentheses.")
+       custom.model.names = c("Size and Distance", "Twitter", "Amenities", "ParkScore"),
+       custom.coef.map = list(
+         "physact" = "Physical Activity", 
+         "lag.physact" = "$\\gamma$: Physical Activity",
+         "lambda" = "$\\lambda$: spatial correlation", 
+         "access_ls" = "Size and Distance", 
+         "multi_ls" = "Amenities", 
+         "tweets_ls" = "Twitter Activity", 
+         "walk_10TRUE" = "10-minute walk"),
+       caption = "Estimated Effect of Accessibility on Physical Activity Rates",
+       label = "tab:obesity-models",
+       caption.above = TRUE, include.aic = F, include.lr = F,
+       custom.note = "%stars 95\\% confidence interval in brackets.")
 ```
-
-\subsection{Additional Amenities}
-
-As discussed when presenting the choice-based accessibility metric above,
-a key benefit it offers is the natural way in which park amenities beyond simply size
-can be accommodated. For example, the number of tweets emanating from a park
-might be seen as a measure of the park's popularity, or a proxy for its use. It
-may be construed that parks with high popularity or use contain other amenities
-that encourage residents to use the park space, raising physical activity rates
-and lowering obesity rates beyond what would be expected with the park's size
-and proximity alone. It is reasonable to question whether park size and Twitter
-activity are highly correlated, and thus would result in a double-counting of
-park size in the accessibility statistic. In our data the number of tweets is
-positively but only loosely correlated  with park
-size ($\\rho = $),
-indicating that the Twitter data in fact could provide new information or proxy
-for the desired amenities.
-
-To test this hypothesis, we can use the twitter data described earlier and
-suggested in Equation \ref{eq:v_sdt}. In this application, we again
-log-transform all the components of utility:
-\begin{equation}\label{eq:v_logsdt}
-V_{ij} = \log(size_j)\lambda_s + \log(distance_{ij})\lambda_d + g(tweets_j)\lambda_t
-\end{equation}
-where $g(x)$ is a Yeo-Johnson transformation to preserve cases where $log(0)$
-would be otherwise undefined \citep{Yeo2000}. As before, there is little
-information by which to determine the values of $\lambda$ in this utility
-specification; we use the previous values with the addition of $\lambda_t =
-0.1$. The ratio between the utility coefficients implies residents would travel
-almost twenty times as far or use a park three times smaller if it had twice the
-Twitter activity, all else equal.
-
-Figure \ref{fig:tweets_map} shows the percent change in the normalized log
-sum statistic after including the twitter information. There is not a recognizable
-overarching pattern to the changes, though tracts immediately surrounding
-Prospect Park and Central Park gain even more relative accessibility, and tracts
-in midtown Manhattan, Queens, and southern Bronx tend to lose some.
-
-```{r tweets_map, eval = FALSE, echo=FALSE, message=FALSE, warning=FALSE, fig.height=4, fig.cap="Percent change in relative accessibility to parks when accounting for Twitter activity."}
-map +
-  geom_sf(data = tracts %>%
-            mutate(diff = tweets_ls - access_ls,
-                   pct_diff = diff / access_ls * 100),
-          inherit.aes=FALSE,
-          aes(fill = cut(pct_diff, quantile(pct_diff,
-                                            probs = seq(0, 1, by = 0.1)))),
-          alpha = 0.8, color = NA) +
-  scale_fill_brewer("Percent Change", palette = "PiYG")
-```
-
-Table \ref{tab:tweets_coefs} presents the estimated coefficients relating
-accessibility to obesity and physical activity rates, with and without the
-inclusion of Twitter data. In both cases, including twitter information in
-the accessibility statistic tempers the strength of the relationship with the
-dependent variable and modestly widens the standard error without substantively
-affecting the significance of the test statistics or the interpretation.
-From this limited example, we cannot say whether Twitter activity enhances the
-ability of parks to increase physical activity rates or lower obesity rates,
-though further investigation of this and other park amenities would certainly
-be warranted.
 

### 2019-10-04 manuscript/manuscript.Rmd
NEW DRAFT

@@
   disagreement surrounding how access to parks ought to be defined while
-  controlling alternate explanations. In this paper we present a comprehensive
+  controlling for alternate explanations. In this paper we apply a comprehensive
   measure of park accessibility drawn from random utility choice theory, which
@@
   numerous amenities and attributes of both the parks and the population. We
-  apply this choice-based accessibility measure to correlate Census tract-level
+  apply this utility-based accessibility measure to correlate Census tract-level
   obesity and physical activity rate estimates from the Centers for Disease
@@
   Community Survey socioeconomic data in New York City, paired with geographic
-  parks data from New York City. Controlling for the
+  open space data from New York City. Controlling for the
   socioeconomic variables and spatially correlated error terms, we show a
   positive and significant relationship between park access and physical
-  activity rates, and a clear and significant negative relationship between park
-  access and obesity rates. In doing so, this research contributes a more
+  activity rates. The data also suggest a negative relationship between park
+  access and obesity rates, beyond what is expected through physical activity
+  and socioeconomics.
+  In doing so, this research contributes a more
   comprehensive modeling approach for measuring the impact of park access on
@@
 knit_hooks$set(inline = function(x) {
-  prettyNum(x, big.mark=",", drop0trailing = TRUE)
+  prettyNum(x, big.mark=",", digits = 4, drop0trailing = TRUE)
 })
@@
 lifestyles and behaviors, touching on topics including diet and exercise.
-Over the last several years a new social model of health has evolved, treating health
+Over the last several years a new *social* model of health has evolved,
+described by @Duhl1999 
 ``as an outcome of the effects of socioeconomic status, culture,
-environmental conditions, housing, employment and community influences.''[@Duhl1999, p.7]
+environmental conditions, housing, employment and community influences''[-@Duhl1999, p.7].
 In this new paradigm, resources provided via civil infrastructure --- in
 particular parks and other public green spaces --- play a crucial role in
-promoting and sustaining public health [@Bedimo-Rung2005; Wells2007; @Coutts2008].
+promoting and sustaining public health [@Bedimo-Rung2005; @Wells2007; @Coutts2008].
 After all, it does little to lecture individuals on the importance of exercise
@@
 which many are plausible but lack robust theoretical basis. In this
-paper, we present a holistic and flexible measurement for park accessibility
+paper, we apply a holistic and flexible measurement for park accessibility
 based in activity location choice theory. This utility-based accessibility measure
@@
 
-We apply this measurement to study the link between
-park accessibility and attractiveness and Census tract-level aggregate physical
-activity participation and obesity rates in New York City, controlling for
-spatially correlated unobserved effect and tract-level socioeconomic
-characteristics. We find a positive relationship where the least park-accessible
-tracts have an expected physical activity participation rate roughly a full
-percentage point lower than the most accessible tracts; a traditional
-quarter-mile buffer analysis estimates a similar albeit marginally less
-significant effect. However, we also find a strong and significant correlation
-between the choice-based park accessibility metric and decreased obesity rates
---- again controlling for spatial correlation, socioeconomic attributes, and
-physical activity rates. In this case a traditional buffer analysis does not
-show significance.
-
-We also demonstrate how the utility-based accessibility metric can potentially be
-expanded to account for other measures of a park's attractiveness including its
-observed social media activity and the presence of various park amenities.
-The paper concludes with a discussion of opportunities for future research.
+We apply this measurement to study the link between park accessibility and
+attractiveness and Census tract-level aggregate physical activity participation
+and obesity rates in New York City, controlling for spatially correlated
+unobserved effects, spatial spillovers of covariates, and tract-level
+socioeconomic characteristics. We also demonstrate how the utility-based
+accessibility metric can potentially be expanded to account for other measures
+of a park's attractiveness including its observed social media activity and the
+presence of various park amenities. The paper concludes with a discussion of
+opportunities for future research.
 
@@
 outcomes has been involved comparing metropolitan regions against each other. For example,
-a study by @West2012 used park data from
-the Trust for Public Land’s 2010 City Park Facts and public health data from the
+@West2012 used park data from
+the Trust for Public Land’s 2010 "City Park Facts" and public health data from the
 Behavioral Risk Factor Surveillance System (BRFSS) to examine the relationship
@@
 greenspace and mortality caused by lung cancer, diabetes, heart disease or car
-accidents, they did find that all-cause mortality was oddly, *higher* in greener
+accidents, they did find that all-cause mortality was --- oddly --- *higher* in greener
 cities. Finally, in a meta-analysis of 20 peer reviewed journal articles exploring the
@@
 point $i$ in a city with parks $j \in 1 \ldots J$. An analyst might consider
-point $i$ as "having access" to a park if the distance to the park $d_ij$  within an
-"isochrone," or less than some threshold $D$,
+point $i$ as "having access" to a park if the distance to the park $d_{ij}$ is 
+within an "isochrone," or a geometric buffer defined by some threshold $D$,
 
@@
 common. 
-@Dias2019 considered road safety perception as an extenuating factor in the
-effective distance to a park.
-ParkScore [@parkscore2019] is a sophisticated application of this approach where $d_{ij}$ is a
-carefully calculated 10-minute network-bound walk, with a demographic analysis of
+ParkScore [@parkscore2019] is a sophisticated application of this approach where $D$ is a
+carefully calculated 10-minute network-bound walk, paired with a demographic analysis of
 areas within and without this threshold. In other applications $D$ might be more
 variably defined, such as the presence or percent of green space within a
-political or statistical boundary [@Mitchell2008].
-The indicator function could also be modified into the total number of parks or
-percent of park space within radius $D$ of point $i$ [@Kascynski2014].
-In a study of neighborhoods in New York
-City, @Stark2014 found that a higher proportion of park space in a neighborhood
-was associated with a lower BMI for its residents, and lower park cleanliness
-scores were associated with a higher BMI, suggesting that increasing the supply
-of clean, well-maintained parks could positively impact adult BMI.
+political or statistical boundary [@Mitchell2008; @Stark2014] or within a specific distance
+threshold [@Kaczynski2014]. It is also possible to attenuate an isochrone with 
+various factors; for instance, @Dias2019 considered road safety perception as an
+extenuating factor in the effective distance to a park.
 
@@
 A somewhat more complete approach is the so-called "gravity" accessibility
-statistic. In this case the accessibility of a point is the denominator of the
+statistic. In this case the accessibility of point $i$ is the denominator of the
 gravity formulation of a trip distribution model,
@@
 where $S_j$ is the "size" of each park literally (i.e. acres) or abstractly (i.e.
-trip attractions) and $f(d_ij)$ is a monotonically decreasing cost function,
+trip attractions) and $f(d_{ij})$ is a monotonically decreasing cost function,
 usually a negative exponential. @Dong2006 note that the isochrone framework is a
-special case of the gravity model where $f(d_{ij})$ is a binary function. 
+special case of the gravity model where $f(d_{ij})$ is a binary function and
+$S_j = 1$.
 @Giles-Corti2005 compare various gravity-based accessibility scores with an
@@
 behavior; that is, the attributes of a park matter influence walking more than
-merely the distance to it. @Zhang2011 present a population-weighted
-gravity-based accessibility to parks metric with a national rather than
-metropolitan scope, though they do not examine its correlation with health
-outcomes.
+merely the distance to it. @Zhang2011 develop a population-weighted,
+gravity-based accessibility to parks metric with a national scope, though they
+do not examine its correlation with health outcomes.
 
@@
 where parks are differentiated from each other by their relative measurable
-*utilities* $V_{ij}$. $C$ is an unknown constant, but the difference in consumer
+*utilities*, $V_{ij}$. $C$ is an unknown constant, but the difference in consumer
 surplus between two points $i$ and $k$ can be quantitatively compared as 
@@
 Note that the gravity formulation is itself a special case of the utility-based
-specification where $\exp(X_j\beta + \beta_d d_{ij}) = X_j f(d_{ij})$ [@Daly1982].
-The distinction between gravity and utility-based specification is meaningful, 
-however. Primarily, it becomes possible to construct accessibility statistics based
-on revealed behavioral preferences rather than calibrated or asserted values [@Handy1997].
+specification where $\exp(X_j\beta + \beta_d d_{ij}) = X_j f(d_{ij})$
+[@Daly1982]. The distinction between gravity and utility-based specification is
+meaningful, however. Primarily, it becomes possible to construct accessibility
+statistics based on revealed behavioral preferences rather than calibrated or
+asserted values [@Handy1997]. @Kaczynski2016 present what is effectively a 
+utility-based accessibility score they call "ParkIndex", with the explicit
+motivation of developing a uniformly applicable park accessibility statistic,
+though they limit this statistic as a way to add heterogeneity within an
+isochrone analysis.
 
@@
 continuous, non-binary phenomenon. It defies reason to assume a person living
-1.1 miles from a park has functionally different accessibility than someone
-living at 0.9 miles. Second, the random utility formulation allows the
+11 minutes via walking from a park always has meaningfully different
+accessibility than someone living 9 minutes away. Second, the random utility
+formulation allows the
 researcher to include -- in principle -- any attribute of the park as part of
@@
 
-This study uses data available to the public from a variety of federal and state
-data agencies. The datasets, as well as the analysis code, are available on GitHub
-at \url{https://github.com/gregmacfarlane/parks_access}.
-
 ```{r tracts}
@@
 
+This study uses data available to the public from a variety of federal and state
+data agencies^[The datasets, as well as the analysis code, are available on GitHub
+at \url{https://github.com/gregmacfarlane/parks_access}.].
 The Centers for Disease Control and Prevention makes small-area estimates on
@@
 the complement of the second variable --- the share of tract adults who
-participate in *some* physical activity --- even if the amount is not sufficient
-to affect overall health. Both indicators are estimated for the year 2016.
+participate in *some* physical activity --- even if the amount may not be
+sufficient to affect overall health. Both indicators are obtained for the year
+2016.
 
@@
 boroughs of New York City. We append to each Census tract relevant
-sociodemographic data for each tract from the American Community Survey
+socioeconomic data for each tract from the American Community Survey
 2013-2017 5-year estimates. For a small handful of tracts in our sample, Census
@@
 size, as these appear to be predominantly planted medians rather than legitimate
-public green space. We also consolidated individual geographic polygons
+public green space. We consolidated individual geographic polygons
 comprising a single facility --- as is the case in Flushing Meadows --- and
@@
 green spaces that can be used for many types of physical activity. These
-operations leave us with `r nrow(parks)` distinct parks. For each park and cemetery
-we generate calculate the size of the park in acres. Using a Twitter application
+operations leave us with `r nrow(parks)` distinct green spaces; for simplicity 
+we will refer to both parks and cemeteries as "parks" going forward. 
+For each park and 
+we calculate the size of the park in acres. Using a Twitter application
 programming interface (API) implemented with the Python package Tweepy,  we also
@@
 travel roughly six times further to reach a park twice as large. In the absence 
-of park trip destination choice coefficients in New York City, we apply these
+of park trip destination choice coefficients in New York City, we adopt these
 previous estimates.
 
-The second utility specification is adapted from a park destination choice model
-estimated by @Kinnell2006 in New Jersey. In this study the authors used a revealed
-preference survey to determine which factors of a park and its surrounding environment
-affected its selection. By bringing over common variables, we can create a second
-utility specification as
+@Kinnell2006 surveyed park users in New Jersey and applied a multinomial logit
+model to determine which factors influenced its perceived utility as a park
+trip destination. By transferring estimates of common variables between our
+data and this survey-based model, we can create a second utility specification
+as
 \begin{equation}\label{eq:u_multi}
@@
 \end{equation}
-with $\lambda_t = 0.99$, $\lambda_c = 0.43$, and $\lambda_p = 0.26$. @Kinnell 
+with $\lambda_t = 0.99$, $\lambda_c = 0.43$, and $\lambda_p = 0.26$. Kinnell et al.\
 did not transform their size and distance estimates, so we retain the previously 
-estimated and applied values. We assume that the other covariates in the @Kinnell
+estimated and applied values. We assume that the other covariates in the 
 model which we do not have available to us (e.g., boat launches, picnic areas) are
@@
 
-The final utility specification includes the number of geolocated tweets
+The third utility specification includes the number of geolocated tweets
 emanating from within the park in September of 2014 in addition to the
@@
 tract as a linear function of the tract's sociodemographic characteristics $X$
-and accessibility to parks ($A$),
+and accessibility to parks $A$,
 \begin{equation}\label{eq:themodel}
@@
 the likely structure of spillovers in the problem at hand. In case of physical
-activity and obesity rates, we believe that these outcomes
-are locally determined: That is, a particular individual decides whether or not
-to participate in physical activity independently of whether his or her neighbors
-participate in physical activity. Mathematically, we assert that the autodependence
-relationship on the dependent variable $y = \rho W y + \varepsilon$ has 
+activity and obesity rates, we believe that the outcomes are locally dependent:
+That is, a particular individual decides whether or not to participate in
+physical activity independently of whether his or her neighbors
+participate in physical activity. This does not mean that we think it impossible that
+the socioeconomic variables of neighboring tracts do not play a role. Mathematically, we assert that the autodependence
+relationship on the dependent variable $y = \rho W y + \ldots$ has 
 $\rho = 0$ in the current case.
@@
 \begin{equation}\label{eq:SLX}
- y = X\beta + \beta_a A + W X \lambda + \varepsilon
+ y = X\beta + \beta_a A + W X \gamma + \varepsilon
 \end{equation}
@@
 estimates for corresponding covariates lie within the 95\% confidence intervals
-of the other model. A Hausman-style test [@LeSage2008] on the coefficients 
+of the other model. A Hausman-style test [@Pace2008] on the coefficients 
 assumes a null hypothesis that the coefficients are equivalent; this test 
@@
 fail to reject the null hypothesis that the coefficients are equivalent, as 
-the differences are not practically different from each other. The consequences
+the differences are at no point practically different from each other. The consequences
 of rejecting the null hypothesis in this case would be to suggest a model with 
@@
        label = "tab:slx-sdem",
+       custom.note = "%stars $y = $ tract-level physical activity rate.",
        caption.above = TRUE)
@@
 Note that the model called "Size and Distance" is precisely the model
-labeled "SDEM" in Table \ref{tab:slx-sdm}. The controllling covariates are
-suppressed for clarity but do not change substantially across the four specifications.
+labeled "SDEM" in Table \ref{tab:slx-sdem}. The controlling covariates are
+suppressed for clarity but do not change meaningfully across the four specifications.
 Complete model estimates are available from the authors. Each of the three
@@
 higher physical activity participation rate. Taking the rough mean of the three
-model rates, moving from the least-accessible tract ($A_i = -3$) to the
+estimated utility-based coefficient, moving from the least-accessible tract ($A_i = -3$) to the
 most-accessible tract ($A_i = 3$) is expected to raise the physical activity rate
@@
        booktabs = TRUE, use.packages = FALSE, 
-       custom.model.names = c("Size and Distance", "Twitter", "Amenities", "ParkScore"),
+       custom.model.names = c("Size and Distance", "Twitter", "Amenities", "10-Minute Walk"),
        custom.coef.map = list(
@@
 We now consider the impacts of a model where the dependent variable is
-the *obesity* rate, and physical activity becomes an independent covariate
+the *obesity* rate in a tract, and physical activity becomes an independent covariate
 alongside the controlling variables and the accessibility metrics.
@@
 utility-based accessibility measures as well as the 10-minute walk buffer. 
-without
-any accessiblity measure, and models with accessibility captured through a
-logsum and through a 1/4 mile buffer. As in the
-physical activity models, the coefficients are typically significant and
-of the expected sign, with a few exceptions: in this case an increasing hispanic
-population share  and an increasing share of children have no significant
-relationship on obesity. Unlike in the physical activity models however,
-the inference on the accessibility statistic *does* change between
-specifications. The 1/4 mile buffer neither substantially improves the model
-fit nor is its term significant at any threshold, but the accessibility logsum
-indicates a significant negative correlation: moving from the least to most
-accessible tract decreases the expected obesity rate by approximately half a
-percentage point.
+As before, the estimates of the other variables are available from the authors.
+The correlation between physical activity rates and obesity is clear; for every
+percentage point increase in physical activity rate, the expected obesity rate
+drops by $0.43$ percentage points in all four accessiblity specifications.
+The indirect effect of physical activity rates on obesity in neighboring zones
+is inconsequential, supporting our methodological assertion that public health
+variables are not spatially dependent, though the factors leading to them may be.
+
+As far as the accessibility values are concerned, none of the three
+utility-based specifications nor the ParkScore 10-minute walk buffer are
+correlated with obesity rates at the traditional 95\% confidence interval. 
+It is important to consider the implications of the full range of the confidence
+interval, however [@Amrhein2019]. The results suggest that after controlling
+for tract socioeconomic variables, physical activity rates, and spatially correlated
+error terms, obesity rates in tracts with excellent park accessibility are expected 
+to be between `r 6 * 0.15` percentage points lower and `r 6 * .0053` percentage 
+points higher than tracts with poor park accessibility. This range of values 
+suggests that accessibility to parks may have obesity-reducing effects beyond
+the effect of accessibility on physical activity rates worth further study.
 
 ```{r obesity-models, results="asis"}
-screenreg(obesity_models[c(2:5)], digits = 4, ci.force = TRUE, 
+texreg(obesity_models[c(2:5)], digits = 4, ci.force = TRUE, 
        booktabs = TRUE, use.packages = FALSE, 
-       custom.model.names = c("Size and Distance", "Twitter", "Amenities", "ParkScore"),
+       custom.model.names = c("Size and Distance", "Twitter", "Amenities", "10-Minute Walk"),
        custom.coef.map = list(
@@
 including measured physical activities and obesity would always be preferable
-to the tract-level data used in this study. It would also be
-preferrable to have obtained the $\vect{\lambda}$ accessibility utility coefficients
-from a high-quality survey of leisure destination choice rather than
-asserting them to match our prior expectations of what constitutes quality
-park access. An ideal survey to address the question would incorporate both sets
-of questions: physical activity and health data on one hand and park use (including
-which parks were used and how frequently) on the other. As no such dataset
-exists to our knowledge, this tract-level aggregate analysis with asserted
-utility coefficients is the possibility that remains.
+to the tract-level data used in this study. An ideal survey to address the
+question would incorporate both sets of questions: physical activity and health
+data on one hand and park use (including which parks were used and how
+frequently) on the other. As no such dataset exists to our knowledge, this
+tract-level aggregate analysis with asserted and transferred utility
+coefficients is the possibility that remains.
 
-This paper presents a holistic accessibility statistic that could, in theory,
-accommodate many attributes of the destination parks as well as the people who
-might use them. As an illustration: the park-going population could be separated
-into at least four delineated clusters, each preferring different amenities of a
-park:
+This paper applies a previously-presented but little-used accessibility
+statistic that could, in theory, accommodate many attributes of the destination
+parks as well as the people who might use them. As an illustration: the
+park-going population could be separated into at least four delineated clusters,
+each preferring different amenities of a park:
 \begin{itemize}
@@
 \end{itemize}
-An analyst could then compute the accessibility logsum for each cluster with
-different utility values for each park's amenities, and obtain a measure of
+An analyst could then compute the utility-based accessibility for each cluster
+with different utility values for each park's amenities, and obtain a measure of
 a neighborhood's accessibility to park features that its residents most care
-about. In this paper, we proceed only incrementally beyond this theory by
-adding Twitter activity as an element of a park's attractiveness above and
-beyond its size. Exploring additional amenities or market segmentation strategies
-could provide a more definitive understanding of the relationship between park
-accessibility and health outcomes.
+about. In this paper, we proceed only incrementally towards this by adding
+Twitter activity and some selected park amenities as an element of each park's 
+attractiveness above and beyond its size. Exploring detailed definitions of
+an increased number of amenities on one hand, and market segmentation strategies
+on the other, could provide a more nuanced understanding of the relationship
+between park accessibility and health outcomes.
 
@@
 access to parks. A better metric of travel impedance may be a mode choice model
-logsum, which weights all travel alternatives against each other.
+logsum, which weights all alternative travel alternatives against each other. 
+We leave this as a recommendation for future research.
+
+We compared our utility-based accessibility to a well-constructed isochrone
+that has attracted attention in the literature. That said, virtually all tracts
+in New York City are within this specific isochrone. It is possible that this 
+isochrone may be more discriminating of park access in other cities, or that a
+different definition would yield different results in New York City. This
+observation however reinforces our suggestion that a measure explicitly based in
+the utility of access is warranted.
 
@@
 to exercise regularly in parks choose to live near them. Given that the CDC models
-generating the obesity and physical activity estimates presumably include variables
+informing the small-area obesity and physical activity estimates presumably include variables
 likely to influence such preferences (income, etc.), our investigation cannot
@@
 scale of the analyses. Using New York City as a case study, we presented a
-holistic and flexible measurement for
-park accessibility that compares the continuous distance to all parks in the
-region, weighted against the size of the park and its other amenities. In terms
-of physical activity, we found a positive relationship where the least
-park-accessible tracts have an expected physical activity participation rate
-roughly one percentage point lower than the most accessible tracts. In terms of
-obesity, we also found a strong and significant correlation between increased
-park accessibility and decreased obesity rates, controlling for
-spatial correlation, socioeconomic attributes, and physical activity rates.
+holistic and flexible measurement for park accessibility that compares the
+continuous distance to all parks in the region, weighted against the size of the
+park and its other amenities, with weights determinable through revealed
+preferences. In terms of physical activity, we found a positive relationship
+where the least park-accessible tracts have an expected physical activity
+participation rate between `r 6 * .05` and `r 6 * .35` percentage points lower than the most
+accessible tracts. We also found a suggestive though not sigificant relationship
+between park accessiblity and expected obesity rates *in addition to* the effect
+of physical activity participation.
 
-In both cases a traditional, buffer-based analysis estimated a weaker relationship
-with greater uncertainty. Buffer analyses are relatively common in the literature,
-perhaps because of the widespread availability of GIS software. In spite of their
-widespread use, they are relatively limited in terms of both their theoretical
-underpinnings and their flexibility to accommodate attributes of parks beyond
-their proximity. And even proximity may not be adequately handled, as the buffer
-distance may be arbitrarily asserted by the researcher. The model we develop and
-apply in this paper extends buffer driven models to contribute a more
-comprehensive and flexible approach for measuring the impact of park access on
-health outcomes. Adopting choice-based accessibilities of the kind used in this
-study will allow researchers to
-encompass the full range of park amenities in their accessibility analyses.
-This will in turn enable planners to consider how multiple attributes of a park
---- from its location to its size to its amenities and beyond --- benefit the health
-of the community the park serves.
+In both cases a common, isochrone-based analysis estimated a statistically weak
+relationship with greater uncertainty. Isochrone analyses are relatively common in
+the literature, perhaps because of the widespread availability of and training
+in GIS software. In spite of their widespread use, isochrones are relatively
+limited in terms of both their theoretical underpinnings and their flexibility
+to accommodate attributes of parks beyond their proximity. And even proximity
+may not be adequately handled, as the isochrone threshold may be arbitrarily
+asserted by the researcher. The model we apply in this paper extends
+a more comprehensive and flexible approach
+for measuring the impact of park access on health outcomes. Adopting
+utility-based accessibilities of the kind used in this study will allow
+researchers to encompass the full range of park amenities in their accessibility
+analyses, and to separate the definition of access from the study of its effects.
+This will in turn enable planners to consider how multiple attributes
+of a park --- from its location to its size to its amenities and beyond ---
+benefit the health of the community the park serves.
 

### 2019-10-28 manuscript/manuscript.Rmd
Correct the distance decay utility parameter

@@
 this utility specification, obtaining values of $\lambda_s = 0.373$ and 
-$\lambda_d = -1.98$. The ratio of these estimates implies people are willing to
+$\lambda_d = -1.76$. The ratio of these estimates implies people are willing to
 travel roughly six times further to reach a park twice as large. In the absence 

### 2019-10-28 poster/handout_graphics.R
Make a poster for the UDOT conference

@@ -1,0 +1,63 @@
+library(spdep)
+library(tidyverse)
+library(dotwhisker)
+library(here)
+library(broom)
+
+# Load models ==========
+slx_vs_sdem <- read_rds(here("data/slx_vs_sdem.rds"))
+pa_models <- read_rds(here("data/pa_models.rds"))
+obesity_models <- read_rds(here("data/obesity_models.rds"))
+
+
+# Plot of model coefficients (Results) ==================
+tidy.sarlm <- function(x){
+  s <- summary(x)
+  df <- length(s$residuals) - length(s$coefficients) - 1
+  tibble(
+    term = gsub("[\\(\\)]", "\\.", rownames(s$Coef)),
+    estimate = s$Coef[,1],
+    std.error = s$Coef[,2],
+    statistic = estimate / std.error,
+    p.value = 2*(pt(abs(statistic), Inf, lower.tail = FALSE))
+  )
+}
+
+weird <- scales::trans_new("signed_log",
+                           transform=function(x) sign(x)*sqrt(abs(x)),
+                           inverse=function(x) sign(x)*(abs(x)^2))
+
+terms <- list(
+  `Physical Activity` = lapply(pa_models, tidy) %>%
+    bind_rows(.id = "model"),
+  `Obesity` = lapply(obesity_models, tidy) %>%
+    bind_rows(.id = "model")
+) %>%
+  bind_rows(.id = "dv")  %>%
+  mutate(
+    conf.low = estimate - 1.96 * std.error,
+    conf.high = estimate + 1.96 * std.error,
+    term = ifelse(term %in% c("access_ls", "tweets_ls", "multi_ls", "walk_10TRUE"), "access", term)
+  )
+
+
+dwplot(terms %>% 
+         filter(term != ".Intercept.", model != "Base") %>%
+         filter(term %in% c("log.density.", "log.income.", "fulltime", "college", 
+                            "access", "single", "youth", "young_adults", "seniors",
+                            "black", "asian", "hispanic", "other", "physact"))
+) +
+  geom_vline(xintercept = 0, lty = "dotted") + 
+  facet_wrap(~dv) +
+  scale_x_continuous(trans = weird) +
+  scale_color_discrete("Accessibility") +
+  theme_bw()
+
+
+# Ammo Bar ==========
+lapply(slx_vs_sdem, tidy) %>%
+  bind_rows(.id = "model") %>%
[…]

### 2019-11-06 manuscript/appendix.Rmd
Add appendix

---
output:
  html_document:
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = F)
library(here)
library(tidyverse)
library(spdep)
library(knitr)
library(kableExtra)
library(texreg)
```

## Appendix

In this appendix we present the complete estimation results for the models 
relating different definitions of access to physical activity (in Table
\ref{tab:pa-fullmodels}) and to obesity (in Table \ref{tab:ob-fullmodels}). In
each case we also present a base model with no accessibility statistics for
comparison.

```{r}
pa_models <- read_rds(here("data/pa_models.rds"))
obesity_models <- read_rds(here("data/obesity_models.rds"))
```

```{r}
base_termnames <- c(
  "(Intercept)", "log(Density)", "log(Income)", "Fulltime", "College-educated",  "Single Adults",
  "Youth (0-17)", "Young adults (18-34)", "Seniors (65+)", "Black population share",
  "Asian population share", "Hispanic population share", "Other Minorities"
)

names_for_terms <- c(
  base_termnames, str_c("$\\gamma$: ", base_termnames[-1])
)

lambda <- "$\\lambda$: spatial correlation"
access_terms <- c("Size and Distance", "Tweets",  "Attributes", "10-min walk")

ob_names <- c(base_termnames, "Physical Activity Rate")
ob_names <- c(
  ob_names, str_c("$\\gamma$: ", ob_names[-1])
)

```

```{r pa-fullmodels, results = "asis"}
texreg(pa_models, digits = 4, ci.force = TRUE,
       booktabs = TRUE, use.packages = FALSE, 
       custom.coef.names = c(names_for_terms, lambda, access_terms),
       custom.model.names = c("No Access", access_terms),
       caption = "Estimated Effect of Accessibility on Physical Activity Rates",
       label = "tab:pa-fullmodels",
       caption.above = TRUE, include.aic = F, include.lr = F,
       scalebox = 0.7,
       custom.note = "%stars 95\\% confidence interval in brackets.")
```

```{r ob-fullmodels, results="asis"}
texreg(obesity_models, digits = 4, ci.force = TRUE,
       booktabs = TRUE, use.packages = FALSE, 
       custom.coef.names = c(ob_names, lambda, access_terms),
       custom.model.names = c("No Access", "Size and Distance", "Twitter", "Amenities", "10-Minute Walk"),
       caption = "Estimated Effect of Accessibility on Physical Activity Rates",
       label = "tab:ob-fullmodels",
       caption.above = TRUE, include.aic = F, include.lr = F, scalebox = 0.7,
       custom.note = "%stars 95\\% confidence interval in brackets.")
```

### 2019-11-06 manuscript/manuscript.Rmd
Add appendix
Edits suggested by Kari

@@
 abstract: >
-  Recent research has underscored the potential for public green spaces to
-  influence individual and societal health outcomes, but empirical measurements
-  of such influences have yielded mixed results to date, with particular
-  disagreement surrounding how access to parks ought to be defined while
-  controlling for alternate explanations. In this paper we apply a comprehensive
-  measure of park accessibility drawn from random utility choice theory, which
-  avoids arbitrary assertions of proximity while incorporating potentially
-  numerous amenities and attributes of both the parks and the population. We
-  apply this utility-based accessibility measure to correlate Census tract-level
-  obesity and physical activity rate estimates from the Centers for Disease
-  Control and Prevention's 500 Cities project with tract-level American
-  Community Survey socioeconomic data in New York City, paired with geographic
-  open space data from New York City. Controlling for the
-  socioeconomic variables and spatially correlated error terms, we show a
-  positive and significant relationship between park access and physical
-  activity rates. The data also suggest a negative relationship between park
-  access and obesity rates, beyond what is expected through physical activity
-  and socioeconomics.
-  In doing so, this research contributes a more
-  comprehensive modeling approach for measuring the impact of park access on
-  health, and may improve our understanding of the role  parks and access to
-  them can serve in furthering public health objectives.
+  Recent research has underscored the potential for public green spaces to influence individual and societal health outcomes, but empirical measurements of such influences have yielded mixed results to date, with particular disagreement surrounding how access to parks ought to be defined while controlling for alternate explanations.
+In this paper we apply a comprehensive measure of park accessibility drawn from random utility choice theory, which avoids arbitrary assertions of proximity while incorporating potentially numerous amenities and attributes of both the parks and the population.
+We apply this utility-based accessibility measure to correlate Census tract-level obesity and physical activity rate estimates from the Centers for Disease Control and Prevention's 500 Cities project with tract-level American Community Survey socioeconomic data in New York City, paired with geographic open space data from New York City.
+Controlling for the socioeconomic variables and spatially correlated error terms, we show a positive and significant relationship between park access and physical activity rates.
+The data also suggest a negative relationship between park access and obesity rates, beyond what is expected through physical activity and socioeconomics.
+In doing so, this research contributes a more comprehensive modeling approach for measuring the impact of park access on health, and may improve our understanding of the role  parks and access to them can serve in furthering public health objectives.
 author_summary: >
@@
       in_header: preamble.tex
+      after_body: appendix.md
 csl: elsevier-harvard.csl
@@
 The large majority of extant research on the topic of park access and public health
-outcomes has been involved comparing metropolitan regions against each other. For example,
+outcomes has been involved with comparing metropolitan regions against each other. For example,
 @West2012 used park data from
@@
 carefully calculated 10-minute network-bound walk, paired with a demographic analysis of
-areas within and without this threshold. In other applications $D$ might be more
+areas within and outside of this threshold. In other applications $D$ might be more
 variably defined, such as the presence or percent of green space within a
@@
 explicitly dismiss utility-based metrics for incorporating randomness. The
-accessibility formula presented in \ref{eq:utility} is the expectation of a
+accessibility formula presented in Equation \ref{eq:utility} is the expectation of a
 random utility process, and is not in and of itself random any more than the
@@
 we will refer to both parks and cemeteries as "parks" going forward. 
-For each park and 
-we calculate the size of the park in acres. Using a Twitter application
+For each park, 
+we calculate the size of the park in acres. Finally, using a Twitter application
 programming interface (API) implemented with the Python package Tweepy,  we also
@@
 10-mile trip. @Macfarlane2019 estimated destination choice 
-parameters for park trips in the Alameda County (Oakland), California using
-this utility specification, obtaining values of $\lambda_s = 0.373$ and 
+parameters for park trips in the Alameda County (Oakland), California by applying
+this utility specification to passively collected mobile device data, obtaining values of $\lambda_s = 0.373$ and 
 $\lambda_d = -1.76$. The ratio of these estimates implies people are willing to
-travel roughly six times further to reach a park twice as large. In the absence 
-of park trip destination choice coefficients in New York City, we adopt these
-previous estimates.
+travel roughly six times further to reach a park twice as large. We do not have
+access to the necessary data to repeat the @Macfarlane2019 methodology in New
+York is cost-prohibitive, and the public parks datasets in Alameda County are
+not sufficiently detailed to perform the present accessibility analysis there.
+In the absence of park trip destination choice coefficients in New York City, we
+adopt these previous estimates.
 
 @Kinnell2006 surveyed park users in New Jersey and applied a multinomial logit
-model to determine which factors influenced its perceived utility as a park
+model to determine which factors influence a park's perceived utility as a park
 trip destination. By transferring estimates of common variables between our
@@
 emanating from within the park in September of 2014 in addition to the
-basic specification in Equation \ref{eq:u_access},
+amenities in Equation \ref{eq:u_multi},
 \begin{equation}\label{eq:u_tweets}
-V_{ij} = \lambda_s * \log(size_j) + \lambda_d * \log(distance_{ij}) + \lambda_{tw} * YJ(tweets)
+V_{ij} = \lambda_s * \log(size_j) + \lambda_d * \log(distance_{ij}) + \lambda_t * trails + \\
+  \lambda_{c} * courts + \lambda_p * playgrounds + \lambda_{tw} * YJ(tweets)
 \end{equation}
@@
 negatively affect econometric interpretation in a variety of ways. Each of these
-process relies on spatial autoregression, where elements of some random
+processes rely on spatial autoregression, where elements of some random
 variable $x$ are spatially dependent on other elements, 
@@
 suppressed for clarity but do not change meaningfully across the four specifications.
-Complete model estimates are available from the authors. Each of the three
+Complete model estimates are available in the Appendix. Each of the three
 utility-based specifications is significant at the $\alpha = 0.05$ level or lower,
@@
 utility-based accessibility measures as well as the 10-minute walk buffer. 
-As before, the estimates of the other variables are available from the authors.
+As before, the estimates of the other variables are available in the Appendix.
 The correlation between physical activity rates and obesity is clear; for every
@@
          "walk_10TRUE" = "10-minute walk"),
-       caption = "Estimated Effect of Accessibility on Physical Activity Rates",
+       caption = "Estimated Effect of Accessibility on Obesity Rates",
        label = "tab:obesity-models",
@@
 This project was funded by the Speedwell Foundation. We are grateful to Rachel
-Samuels for helping to assemble the geolocated Twitter data.
+Samuels and Neda Madi for helping to assemble the geolocated Twitter data.
 

### 2019-11-11 manuscript/manuscript.Rmd
Change back to Sage, draft sent to JET and Nico

@@
   accessibility approach
+runninghead: Macfarlane \emph{et al}.
 author:
   - name: Gregory Macfarlane
-    email: gregmacfarlane@byu.edu
-    affiliation: Brigham Young University
-    corresponding: gregmacfarlane@byu.edu
+    num: 1
   - name: Nico Boyd
-    email:
-    affiliation: Fehr and Peers 
+    num: 2
   - name: John E. Taylor
-    email: jetaylor@gatech.edu
-    affiliation: Georgia Institute of Technology
+    num: 3
   - name: Kari Watkins
-    email: kariwatkins@gatech.edu
-    affiliation: Georgia Institute of Technology
+    num: 3
 address:
-  - code: Brigham Young University
-    address: Civil and Environmental Engineering Department, Brigham Young University 430 Engineering Building, Provo, UT, 84602
-  - code: Fehr and Peers
-    address: Los Angeles, California
-  - code: Georgia Institute of Technology
-    address: School of Civil and Environmental Engineering, Georgia Institute of Technology, 755 Atlantic Drive, Atlanta, GA, 30332
+  - code: 1
+    address: Civil and Environmental Engineering Department, Brigham Young University 
+  - code: 2
+    address: Fehr and Peers, Los Angeles, California
+  - code: 3
+    address: School of Civil and Environmental Engineering, Georgia Institute of Technology
+corrauth: "Gregory Macfarlane, 430 Engineering Building, Provo UT 84663"
+email: gregmacfarlane@gmail.com
 abstract: >
@@
 In doing so, this research contributes a more comprehensive modeling approach for measuring the impact of park access on health, and may improve our understanding of the role  parks and access to them can serve in furthering public health objectives.
-author_summary: >
-  Greg Macfarlane is an assistant professor of Civil Engineering at Brigham
-  Young University in Provo, Utah.
-
+keywords: Accessibility; Green Space
+classoption:
+  - shortAfour
 output: 
-  rticles::elsevier_article:
+  rticles::sage_article:
+    keep_md: yes
+    keep_tex: yes
     includes: 
@@
       after_body: appendix.md
-csl: elsevier-harvard.csl
 bibliography: library.bib
+bibliographystyle: sageh.bst
 ---
@@
 \begin{equation}\label{eq:u_multi}
-V_{ij} = \lambda_s * \log(size_j) + \lambda_d * \log(distance_{ij}) + \lambda_t * trails + \\
-  \lambda_{c} * courts + \lambda_p * playgrounds
+\begin{split}
+V_{ij} & = \lambda_s * \log(size_j) + \lambda_d * \log(distance_{ij}) + \\ 
+  & \quad \lambda_t * trails + \lambda_{c} * courts + \lambda_p * playgrounds
+\end{split}
 \end{equation}
@@
 emanating from within the park in September of 2014 in addition to the
-amenities in Equation \ref{eq:u_multi},
+size and distance terms in Equation \ref{eq:u_access},
 \begin{equation}\label{eq:u_tweets}
-V_{ij} = \lambda_s * \log(size_j) + \lambda_d * \log(distance_{ij}) + \lambda_t * trails + \\
-  \lambda_{c} * courts + \lambda_p * playgrounds + \lambda_{tw} * YJ(tweets)
+\begin{split}
+V_{ij} &= \lambda_s * \log(size_j) + \lambda_d * \log(distance_{ij}) + \\ 
+  &\quad \lambda_{tw} * YJ(tweets)
+\end{split}
 \end{equation}
@@
 Figure \ref{fig:map} shows a map of New York City with each tract highlighted
-based on its relative basic utility-based accessibility score (Equation
+based on its relative size and distance utility-based accessibility score (Equation
 \ref{eq:u_access}). The most continuous region of good park access is in upper
@@
 
+\begin{table*}
+\caption{Comparison of SLX and SDEM Coefficients}
+\label{tab:slx-sdem}
 ```{r slx-sdem, results = "asis"}
@@
        caption = "Comparison of SLX and SDEM Coefficients",
-       label = "tab:slx-sdem",
+       label = "tab:slx-sdem",table = FALSE,
        custom.note = "%stars $y = $ tract-level physical activity rate.",
@@
 ```
+\end{table*}
 
@@
 
+\begin{table*}
+\caption{Estimated Effect of Accessibility on Physical Activity Rates}
+\label{tab:pa-models}
 ```{r pa-models, results = "asis"}
@@
        caption = "Estimated Effect of Accessibility on Physical Activity Rates",
-       label = "tab:pa-models",
+       label = "tab:pa-models", table = FALSE,
        caption.above = TRUE, include.aic = F, include.lr = F,
@@
 
+\begin{table*}
+\caption{Estimated Effect of Accessibility on Obesity Rates}
+\label{tab:obesity-models}
 ```{r obesity-models, results="asis"}
@@
        caption = "Estimated Effect of Accessibility on Obesity Rates",
-       label = "tab:obesity-models",
+       label = "tab:obesity-models", table = FALSE,
        caption.above = TRUE, include.aic = F, include.lr = F,
@@
 
-## Acknowledgements
+\begin{acks}
 This project was funded by the Speedwell Foundation. We are grateful to Rachel
 Samuels and Neda Madi for helping to assemble the geolocated Twitter data.
+\end{acks}
 

### 2019-11-13 manuscript/manuscript.Rmd
Edits for grammar.

@@
 isochrone specification and show that the former are more predictive of walking
-behavior; that is, the attributes of a park matter influence walking more than
+behavior; that is, the attributes of a park influence walking more than
 merely the distance to it. @Zhang2011 develop a population-weighted,
@@
 in New York City. The most basic utility specification includes only the
-the park size in acres and the distance from the population-weighted tract centroid
+park size in acres and the distance from the population-weighted tract centroid
 to the boundary of the park in miles,
@@
 10-mile trip. @Macfarlane2019 estimated destination choice 
-parameters for park trips in the Alameda County (Oakland), California by applying
+parameters for park trips in Alameda County (Oakland), California by applying
 this utility specification to passively collected mobile device data, obtaining values of $\lambda_s = 0.373$ and 
@@
 access to the necessary data to repeat the @Macfarlane2019 methodology in New
-York is cost-prohibitive, and the public parks datasets in Alameda County are
+York, and the public parks datasets in Alameda County are
 not sufficiently detailed to perform the present accessibility analysis there.
@@
 
-Table \ref{tab:pa-models} present the estimated spatial lag and accessibility
+Table \ref{tab:pa-models} presents the estimated spatial lag and accessibility
 coefficients for three models using different specifications of the utility
@@
 higher physical activity participation rate. Taking the rough mean of the three
-estimated utility-based coefficient, moving from the least-accessible tract ($A_i = -3$) to the
+estimated utility-based coefficients, moving from the least-accessible tract
+($A_i = -3$) to the
 most-accessible tract ($A_i = 3$) is expected to raise the physical activity rate

### 2019-11-18 manuscript/manuscript.Rmd
JT edits

@@
 chronic diseases, including cardiovascular diseases, chronic respiratory
-diseases, diabetes, stroke, joint and bone diseases, and cancer. These diseseases
+diseases, diabetes, stroke, joint and bone diseases, and cancer. These diseases
 can severely limit the lifespan of affected individuals [@WHO2014], with 
@@
 promoting and sustaining public health [@Bedimo-Rung2005; @Wells2007; @Coutts2008].
-After all, it does little to lecture individuals on the importance of exercise
+After all, it does little to educate individuals on the importance of exercise
 if their community is built in such a way that such exercise is expensive,
@@
 faced is a proliferation of techniques for measuring access to green spaces, of
-which many are plausible but lack robust theoretical basis. In this
+which many are plausible but lack robust theoretical bases. In this
 paper, we apply a holistic and flexible measurement for park accessibility
@@
 We apply this measurement to study the link between park accessibility and
-attractiveness and Census tract-level aggregate physical activity participation
+attractiveness and census tract-level aggregate physical activity participation
 and obesity rates in New York City, controlling for spatially correlated
@@
 The large majority of extant research on the topic of park access and public health
-outcomes has been involved with comparing metropolitan regions against each other. For example,
-@West2012 used park data from
+outcomes has been focused on comparing metropolitan regions against each other.
+For example, @West2012 used park data from
 the Trust for Public Land’s 2010 "City Park Facts" and public health data from the
@@
 of its citizens better access to sufficient greenspace to meet their needs or
-wants for physical activity. Considering access at the neighborhood level within
+desires for physical activity. Considering access at the neighborhood level within
 a single city may also eliminate some regional or cultural fixed effects
@@
 \end{equation}
-with $\lambda_t = 0.99$, $\lambda_c = 0.43$, and $\lambda_p = 0.26$. Kinnell et al.\
-did not transform their size and distance estimates, so we retain the previously 
-estimated and applied values. We assume that the other covariates in the 
-model which we do not have available to us (e.g., boat launches, picnic areas) are
-orthogonal to the included parameters and leaving them out will not affect the
-values of the included coefficients.
+with $\lambda_t = 0.99$, $\lambda_c = 0.43$, and $\lambda_p = 0.26$. Kinnell et
+al. did not transform their size and distance estimates, so we retain the
+previously estimated and applied values. We assume that the other covariates in
+the model which we do not have available to us (e.g., boat launches, picnic
+areas) are orthogonal to the included parameters and leaving them out will not
+affect the values of the included coefficients.
 

### 2019-12-09 01_health_data.Rmd
Add mental health indicator to dataset

@@
   "physact" = "https://chronicdata.cdc.gov/resource/axqz-rkkp.json?stateabbr=NY",
-  "obesity" = "https://chronicdata.cdc.gov/resource/bjvu-3y7d.json?stateabbr=NY"
+  "obesity" = "https://chronicdata.cdc.gov/resource/bjvu-3y7d.json?stateabbr=NY",
+  "mhealth" = "https://chronicdata.cdc.gov/resource/i2ek-k3pa.json?stateabbr=NY"
 )

### 2020-01-29 manuscript/submission/manuscript.tex
Add submission files

\documentclass[Afour,sageh.bst]{sagej}

\usepackage{moreverb,url,natbib, multirow, tabularx}
\usepackage[colorlinks,bookmarksopen,bookmarksnumbered,citecolor=red,urlcolor=red]{hyperref}

\usepackage{natbib}

\usepackage{bm}
     \def\Var{{\rm Var}\,}
     \def\Cov{{\rm Cov}\,}
     \def\mean{{\rm mean}\,}
     \def\E{{\rm E}\,}
  	 \def\Corr{{\rm Corr}\,}
\newcommand{\vect}[1]{\boldsymbol{#1}}

\usepackage{hyperref}
\usepackage{rotating}
\usepackage{booktabs}
\usepackage{makecell}

\begin{document}

\title{Modeling the impacts of park access on health outcomes: a utility-based
accessibility approach}

\runninghead{XXXX \emph{et al}.}

\author{XXXX \affilnum{1}, XXXX \affilnum{2}, XXXX\affilnum{3}, XXXX\affilnum{3}}

\affiliation{
\affilnum{1}{XXXX}\\
\affilnum{2}{XXXX}\\
\affilnum{3}{XXXX}}

\corrauth{XXXX}

\email{\href{XXXX}{\nolinkurl{XXXX}}}

\begin{abstract}
Recent research has underscored the potential for public green spaces to
influence individual and societal health outcomes, but empirical
measurements of such influences have yielded mixed results to date, with
particular disagreement surrounding how access to parks ought to be
defined while controlling for alternate explanations. In this paper we
apply a comprehensive measure of park accessibility drawn from random
utility choice theory, which avoids arbitrary assertions of proximity
while incorporating potentially numerous amenities and attributes of
both the parks and the population. We apply this utility-based
accessibility measure to correlate Census tract-level obesity and
physical activity rate estimates from the Centers for Disease Control
and Prevention's 500 Cities project with tract-level American Community
Survey socioeconomic data in New York City, paired with geographic open
space data from New York City. Controlling for the socioeconomic
variables and spatially correlated error terms, we show a positive and
significant relationship between park access and physical activity
rates. The data also suggest a negative relationship between park access
and obesity rates, beyond what is expected through physical activity and
socioeconomics. In doing so, this research contributes a more
comprehensive modeling approach for measuring the impact of park access
on health, and may improve our understanding of the role parks and
access to them can serve in furthering public health objectives.
\end{abstract}

\keywords{Accessibility; Green Space; Public Health}

\maketitle

\clearpage
\newpage
\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

The United States and other developed nations face an epidemic of
obesity and chronic diseases, including cardiovascular diseases, chronic
respiratory diseases, diabetes, stroke, joint and bone diseases, and
cancer. These diseases can severely limit the lifespan of affected
individuals \citep{WHO2014}, with substantial financial costs for
treatment borne both privately and socially \citep{Finkelstein2009}.
Though a moderate amount of regular physical activity has been
established as an effective strategy for reducing and managing obesity
and many of the aforementioned chronic diseases
\citep{CDC2009, Durstine2013}, a large portion of U.S. adults do not
participate in sufficient physical activity \citep{Wolf2008}.

Historically, most large-scale health promotion efforts focused on
individual-level interventions intended to educate people about healthy
lifestyles and behaviors, touching on topics including diet and
exercise. Over the last several years a new \emph{social} model of
health has evolved, described by \citet{Duhl1999} ``as an outcome of the
effects of socioeconomic status, culture, environmental conditions,
housing, employment and community
influences''\citeyearpar[p.7]{Duhl1999}. In this new paradigm, resources
provided via civil infrastructure --- in particular parks and other
public green spaces --- play a crucial role in promoting and sustaining
public health \citep{Bedimo-Rung2005, Wells2007, Coutts2008}. After all,
it does little to educate individuals on the importance of exercise if
their community is built in such a way that such exercise is expensive,
unenjoyable, or unsafe.

In spite of the potential for green spaces to influence public health
outcomes and numerous studies attempting to empirically estimate the
strength of these outcomes, evidence to date has been mixed. A major
challenge researchers have faced is a proliferation of techniques for
measuring access to green spaces, of which many are plausible but lack
robust theoretical bases. In this paper, we apply a holistic and
flexible measurement for park accessibility based in activity location
choice theory. This utility-based accessibility measure compares the
continuous distance to all parks in the region, weighted against the
sizes of each park and its other assorted amenities.

We apply this measurement to study the link between park accessibility
and attractiveness and census tract-level aggregate physical activity
participation and obesity rates in New York City, controlling for
spatially correlated unobserved effects, spatial spillovers of
covariates, and tract-level socioeconomic characteristics. We also
demonstrate how the utility-based accessibility metric can potentially
be expanded to account for other measures of a park's attractiveness
including its observed social media activity and the presence of various
park amenities. The paper concludes with a discussion of opportunities
for future research.

\hypertarget{literature-review}{%
\section{Literature Review}\label{literature-review}}

\label{sec:litreview}

The large majority of extant research on the topic of park access and
public health outcomes has been focused on comparing metropolitan
regions against each other. For example, \citet{West2012} used park data
from the Trust for Public Land's 2010 ``City Park Facts'' and public
health data from the Behavioral Risk Factor Surveillance System (BRFSS)
to examine the relationship between the density of park land and
physical activity and obesity rates for 67 metropolitan statistical
areas in the U.S. The findings in this case conformed to expectation;
that is, the study found a significant positive association between park
density and physical activity and a significant negative association
between park density and obesity. \citet{Larson2016} similarly used
self-reported scores on the Gallup-Healthways Wellbeing Index to
evaluate the relationship between physical health and park quantity,
quality, and accessibility in 44 U.S. cities. While the authors found
positive associations between wellbeing and park quality and
accessibility, these relationships were not statistically significant.
Conversely, \citet{Richardson2012} examined the relationship between
total urban greenspace and mortality rates for selected maladies; though
the authors did not find a statistically significant relationship
between the quantity of urban greenspace and mortality caused by lung
cancer, diabetes, heart disease or car accidents, they did find that
all-cause mortality was --- oddly --- \emph{higher} in greener cities.
Finally, in a meta-analysis of 20 peer reviewed journal articles
exploring the relationship between parks and objectively measured
physical activity, \citet{Bancroft2015} found that five studies reported
a significant positive association between the two, six studies produced
mixed results, and nine studies found no association at all.

Metropolitan-level analyses such as those described above do not capture
the within-city variation in accessibility to parks that exist in many
cities. Some cities with large amounts of total greenspace may
nevertheless unequally distribute this space throughout the city,
leading to areas with poor access. Conversely, a city with a smaller
overall proportion of greenspace may give all of its citizens better
access to sufficient greenspace to meet their needs or desires for
physical activity. Considering access at the neighborhood level within a
single city may also eliminate some regional or cultural fixed effects
affecting metropolitan-level analyses.

\hypertarget{park-accessibility-measures}{%
\subsection{Park Accessibility
Measures}\label{park-accessibility-measures}}

Loosely defined, the \emph{accessibility} of an arbitrary place
describes the ease with which people can accomplish activities there.
Accessibility is an abstract concept with tempting quantifiability
\citep{Handy1997}, perhaps explaining the proliferation of calculation
mechanisms. \citet{Dong2006} present a helpful mathematical heirarchy of
common mechanisms, which we follow here. Consider a person residing at
point \(i\) in a city with parks \(j \in 1 \ldots J\). An analyst might
consider point \(i\) as ``having access'' to a park if the distance to
the park \(d_{ij}\) is within an ``isochrone,'' or a geometric buffer
defined by some threshold \(D\),

\begin{equation}\label{eq:isochrone}
A_i = \begin{cases} 
      1 & d_{ij}\leq D\\
      0 & d_{ij} > D
   \end{cases}
\end{equation}

Variations of this isochrone-based framework are easily derived and
relatively common. ParkScore \citep{parkscore2019} is a sophisticated
application of this approach where \(D\) is a carefully calculated
10-minute network-bound walk, paired with a demographic analysis of
areas within and outside of this threshold. In other applications \(D\)
might be more variably defined, such as the presence or percent of green
space within a political or statistical boundary
\citep{Mitchell2008, Stark2014} or within a specific distance threshold
\citep{Kaczynski2014}. It is also possible to attenuate an isochrone
with various factors; for instance, \citet{Dias2019} considered road
safety perception as an extenuating factor in the effective distance to
a park.

In spite of the flexibility of adapted isochrone techniques, the
arbritrary definitions necessarily imposed by researchers in its
application can inhibit holistic analysis \citep{Logan2017}. A somewhat
more complete approach is the so-called ``gravity'' accessibility
statistic. In this case the accessibility of point \(i\) is the
denominator of the gravity formulation of a trip distribution model,
\begin{equation}\label{eq:gravity}
A_i = \sum_{j = 1}^J S_j f(d_{ij})
\end{equation} where \(S_j\) is the ``size'' of each park literally
(i.e.~acres) or abstractly (i.e. trip attractions) and \(f(d_{ij})\) is
a monotonically decreasing cost function, usually a negative
exponential. \citet{Dong2006} note that the isochrone framework is a
special case of the gravity model where \(f(d_{ij})\) is a binary
function and \(S_j = 1\). \citet{Giles-Corti2005} compare various
gravity-based accessibility scores with an isochrone specification and
show that the former are more predictive of walking behavior; that is,
the attributes of a park influence walking more than merely the distance
to it. \citet{Zhang2011} develop a population-weighted, gravity-based
accessibility to parks metric with a national scope, though they do not
examine its correlation with health outcomes.

A third accessibility mechanism is a utility-based specification, termed
as such for being derived from random utility choice theory. Consider
that an individual living at point \(i\) is choosing a park for a
recreation activity. If we apply the multinomial logit model
\citep{McFadden1974}, the expected consumer surplus enjoyed by this
individual can be shown to be \begin{equation}\label{eq:utility}
A_i = \ln\left({\sum_{j = 1}^J\exp(V_{ij})}\right) + C
\end{equation} where parks are differentiated from each other by their
relative measurable \emph{utilities}, \(V_{ij}\). \(C\) is an unknown
constant, but the difference in consumer surplus between two points
\(i\) and \(k\) can be quantitatively compared as \(A_i - A_k\)
\citep{Bruce1977}. In principle, \(V\) may include any measurable
attributes of either the choice maker or the park, and is typically
represented as a linear-in-parameters function of destination attributes
\(X_j\) and the travel cost \(d_{ij}\),
\begin{equation}\label{eq:utilityV}
V_{ij} = X_j\beta + \beta_d * d_{ij}
\end{equation} The coefficients \(\vect{\beta}\) are frequently
estimated from household surveys, though in the absence of a survey we
may assert reasonable values.

Note that the gravity formulation is itself a special case of the
utility-based specification where
\(\exp(X_j\beta + \beta_d d_{ij}) = X_j f(d_{ij})\) \citep{Daly1982}.
The distinction between gravity and utility-based specification is
meaningful, however. Primarily, it becomes possible to construct
accessibility statistics based on revealed behavioral preferences rather
than calibrated or asserted values \citep{Handy1997}.
\citet{Kaczynski2016} present what is effectively a utility-based
accessibility score they call ``ParkIndex'', with the explicit
motivation of developing a uniformly applicable park accessibility
statistic, though they limit this statistic as a way to add
heterogeneity within an isochrone analysis.

Both gravity and utility-based specifications hold several advantages
relative to isochrone-based accessibility metrics more commonly found in
the literature. First, all individuals are defined as having some access
to all parks, rather than an arbitrary cutoff asserted by the
researcher. This allows for the fact that some people are more or less
sensitive to distances, and that distance is a continuous, non-binary
phenomenon. It defies reason to assume a person living 11 minutes via
walking from a park always has meaningfully different accessibility than
someone living 9 minutes away. Second, the random utility formulation
allows the researcher to include -- in principle -- any attribute of the
park as part of its utility specification. This suggests that not all
parks are equal, and that a large park with many amenities such as
Central Park in Manhattan may provide health and activity benefits over
a much larger area than a smaller community square.

In spite of its flexibility and basis in choice theory, utility-based
accessibility measures have not received much application in the
accessibility literature compared with distance-based or even
gravity-based measures. \citet{Vale2016} present a descriptive
classification of active accessibility techniques, and explicitly
dismiss utility-based metrics for incorporating randomness. The
accessibility formula presented in Equation \ref{eq:utility} is the
expectation of a random utility process, and is not in and of itself
random any more than the gravity model is random. Utility-based
accessibility metrics are commonly used, however, in alternatives
analyses of transit infrastructure improvements \citep{DeJong2007}. A
reason for this is likely that a regional travel demand model is
available to the analysts, thus making calibrated and multimodal logsums
readily available \citep{Geurs2010}.

\hypertarget{empirical-application}{%
\section{Empirical Application}\label{empirical-application}}

In this section, we develop a model with data for New York City, where
we compute a set of utility-based accessibility to parks scores for each
tract and model the relationship between this measure and physical
activity rates, controlling for spatial effects and socioeconomic
factors. We subsequently model the effect of the accessibility metric on
obesity rates, accounting for physical activity and the other controls.

\hypertarget{data}{%
\subsection{Data}\label{data}}

This study uses data available to the public from a variety of federal
and state data agencies\footnote{The datasets, as well as the analysis
  code, are available on GitHub at
  \url{https://github.com/gregmacfarlane/parks_access}.}. The Centers
for Disease Control and Prevention makes small-area estimates on key
health indicators available through its 500 Cities data program
\citep{CDC5002016}. The indicators are multilevel aggregations and
imputations of BRFSS responses \citep{Wang2018, Wang2017}, and have been
recently used to study the tract-level link between gentrification and
urban health \citep{Gibbons2018}. We use two indicators as our dependent
variables in this study: the share of adults in a Census tract who are
obese, and the share of adults who participate in no leisure-time
physical activity. To improve clarity in our interpretation, we use the
complement of the second variable --- the share of tract adults who
participate in \emph{some} physical activity --- even if the amount may
not be sufficient to affect overall health. Both indicators are obtained
for the year 2016.

To the health data, we join socioeconomic data collected through the
Census Bureau API via the \texttt{tidycensus} package for R
\citep{Walker2019}. The primary dataset is a geographic polygons layer
of Census tracts in the five boroughs of New York City. We append to
each Census tract relevant socioeconomic data for each tract from the
American Community Survey 2013-2017 5-year estimates. For a small
handful of tracts in our sample, Census supressed the median income
estimate; these appear to be primarily wealthy tracts and in almost all
cases the CDC estimates of obesity and physical activity are missing as
well. After removing these tracts from the estimation dataset, we have
2,102 complete cases. Table \ref{tab:tractsdata} presents key
descriptive statistics for these data.

In a destination choice framework, the tracts represent the ``origins''
and the ``destinations'' are parks and green spaces in New York City. We
retrieved a polygons layer of public parks and greenspaces within New
York City's municipal boundaries and checked it for accuracy and
relevance \citep{nycparks}. Upon inspection, we removed several
facilities that do not qualify as publicly accessible green space, such
as Yankee Stadium, Citi Field, and their surrounding parking lots. We
also removed parks of less than half an acre in size, as these appear to
be predominantly planted medians rather than legitimate public green
space. We consolidated individual geographic polygons comprising a
single facility --- as is the case in Flushing Meadows --- and
eliminated sub-facilities such as tennis courts or baseball fields
included within larger park facilities. Instead of these distinct
sub-facilities, we created variables for each containing park indicating
the presence of sports courts, playgrounds, and trails.

To this dataset of parks and regularized green spaces, we add a polygons
layer of cemeteries in New York that are open to the public. Cemeteries
are important green spaces that can be used for many types of physical
activity. These operations leave us with 1,277 distinct green spaces;
for simplicity we will refer to both parks and cemeteries as ``parks''
going forward. For each park, we calculate the size of the park in
acres. Finally, using a Twitter application programming interface (API)
implemented with the Python package Tweepy, we also collected and stored
tweets containing geotags of precise geographic coordinates located
within the boundaries of the parks; from this information, we were able
to segregate tweets that were generated within a park in September 2014.
This geolocated twitter activity could provide an additional point of
information on the degree to which individual parks are actually used
\citep{Wang2016}.

\begin{table*}

\caption{\label{tab:tractsdata}Descriptive Statistics of Tract and Park Variables}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{l>{\raggedright\arraybackslash}p{2in}rlrl}
\toprule
  & Description & Minimum & Median (IQR) & Maximum & Source\\
\midrule
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Tract Variables, N = 2102}}\\
\hspace{1em}Obesity & Share of adults over 18 who are obese & 10.20 & \makecell{24.90\\ (19.83, 30.80)} & 45.40 & CDC 500 Cities\\
\hspace{1em}Physical Activity & Share of adults over 18 who engage in some leisure-time physical activity & 45.90 & \makecell{72.10\\ (66.60, 76.77)} & 90.70 & CDC 500 Cities\\
\hspace{1em}Income & Median tract income & 9053.00 & \makecell{59,592.50\\ (41,928.25, 79,092.75)} & 250001.00 & ACS\\
\hspace{1em}Density & Households per square kilometer & 9.20 & \makecell{5,848.46\\ (3,173.62, 9,674.36)} & 43621.52 & ACS\\
\hspace{1em}Fulltime & Share of adults over 18 with full-time work & 8.80 & \makecell{49.48\\ (44.45, 55.29)} & 100.00 & ACS\\
\hspace{1em}College & Share of adults over 24 with a college degree & 0.61 & \makecell{16.30\\ (12.37, 20.11)} & 44.94 & ACS\\
\hspace{1em}Single & Share of adults over 18 living alone or in a non-partnership household & 16.38 & \makecell{59.39\\ (50.30, 68.65)} & 100.00 & ACS\\
\hspace{1em}Youth & Share of population under 18 & 0.00 & \makecell{20.54\\ (16.79, 24.92)} & 64.07 & ACS\\
\hspace{1em}Young adults & Share of population between 18 and 34 & 0.00 & \makecell{25.73\\ (21.66, 29.98)} & 86.75 & ACS\\
\hspace{1em}Seniors & Share of population who are 65 and over & 0.00 & \makecell{12.83\\ (9.47, 16.88)} & 89.88 & ACS\\
\hspace{1em}Black & Share of population who is black & 0.00 & \makecell{10.03\\ (2.13, 44.62)} & 220.65 & ACS\\
\hspace{1em}Asian & Share of population who is Asian & 0.00 & \makecell{7.66\\ (2.40, 20.78)} & 88.07 & ACS\\
\hspace{1em}Hispanic & Share of population who is Hispanic & 0.00 & \makecell{19.07\\ (9.39, 41.07)} & 96.27 & ACS\\
\hspace{1em}Other & Share of population who belong to other minority groups & 0.00 & \makecell{0.00\\ (0.00, 0.53)} & 19.47 & ACS\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Park Variables, N = 1277}}\\
\hspace{1em}Size & Park size in acres & 0.50 & \makecell{1.66\\ (0.95, 5.62)} & 1961.00 & NYC\\
\hspace{1em}Courts & Presence of sport courts / ball fields & 0.00 & \makecell{0.00\\ (0.00, 0.00)} & 1.00 & NYC\\
\hspace{1em}Playgrounds & Presence of playgrounds & 0.00 & \makecell{0.00\\ (0.00, 1.00)} & 1.00 & NYC\\
\hspace{1em}Trails & Presence of trails & 0.00 & \makecell{0.00\\ (0.00, 0.00)} & 1.00 & NYC\\
\hspace{1em}Tweets & Tweets emanating from park in September 2014 & 0.00 & \makecell{0.00\\ (0.00, 2.00)} & 1593.00 & Twitter API\\
\bottomrule
\end{tabular}}
\end{table*}

\hypertarget{accessibility}{%
\subsection{Accessibility}\label{accessibility}}

\label{subsec:accessibility}

We calculate a set of utility-based accessibility statistics for each
tract in New York City. The most basic utility specification includes
only the park size in acres and the distance from the
population-weighted tract centroid to the boundary of the park in miles,
\begin{equation}\label{eq:u_access}
V_{ij} = \lambda_s * \log(size_j) + \lambda_d * \log(distance_{ij})
\end{equation} The logarithmic transform allows for diminishing marginal
utility of distance and park size: A 1-mile increase to a trip matters
more for a 1-mile trip than a 10-mile trip. \citet{Macfarlane2019}
estimated destination choice parameters for park trips in Alameda County
(Oakland), California by applying this utility specification to
passively collected mobile device data, obtaining values of
\(\lambda_s = 0.373\) and \(\lambda_d = -1.76\). The ratio of these
estimates implies people are willing to travel roughly six times further
to reach a park twice as large. We do not have access to the necessary
data to repeat the \citet{Macfarlane2019} methodology in New York, and
the public parks datasets in Alameda County are not sufficiently
detailed to perform the present accessibility analysis there. In the
absence of park trip destination choice coefficients in New York City,
we adopt these previous estimates.

\citet{Kinnell2006} surveyed park users in New Jersey and applied a
multinomial logit model to determine which factors influence a park's
perceived utility as a park trip destination. By transferring estimates
of common variables between our data and this survey-based model, we can
create a second utility specification as
\begin{equation}\label{eq:u_multi}
\begin{split}
V_{ij} & = \lambda_s * \log(size_j) + \lambda_d * \log(distance_{ij}) + \\ 
  & \quad \lambda_t * trails + \lambda_{c} * courts + \lambda_p * playgrounds
\end{split}
\end{equation} with \(\lambda_t = 0.99\), \(\lambda_c = 0.43\), and
\(\lambda_p = 0.26\). Kinnell et al.~did not transform their size and
distance estimates, so we retain the previously estimated and applied
values. We assume that the other covariates in the model which we do not
have available to us (e.g., boat launches, picnic areas) are orthogonal
to the included parameters and leaving them out will not affect the
values of the included coefficients.

The third utility specification includes the number of geolocated tweets
emanating from within the park in September of 2014 in addition to the
size and distance terms in Equation \ref{eq:u_access},
\begin{equation}\label{eq:u_tweets}
\begin{split}
V_{ij} &= \lambda_s * \log(size_j) + \lambda_d * \log(distance_{ij}) + \\ 
  &\quad \lambda_{tw} * YJ(tweets)
\end{split}
\end{equation} with \(YJ(x)\) being a Yeo-Johnson transformation that
implements a diminishing marginal return similar to \(log(x)\), but
where \(YJ(0) = 0\) \citep{Yeo2000}. In this case we have no external
information describing how destination choice to parks may be affected
by the twitter activity in the park, so we assert a value of
\(\lambda_{tw} = 0.1\)

We then calculate the utility-based accessibility of each tract \(A_i\)
as defined in Equation \ref{eq:utility} under each utility
specification. Recall that the total value of the accessibility is
relative to an unknown scalar \(C\); for this reason we standardize the
accessibility values for all tracts within each utility specification,
\begin{equation}\label{eq:v_logged}
A_i' = \frac{A_i - \bar{A}}{sd(A)}
\end{equation}

Figure \ref{fig:map} shows a map of New York City with each tract
highlighted based on its relative size and distance utility-based
accessibility score (Equation \ref{eq:u_access}). The most continuous
region of good park access is in upper Manhattan and the Bronx,
bracketed by Central Park and the Bronx River. Conversely, some of the
poorest-accessibility areas are in Brooklyn tracts not immediately
adjacent to Prospect Park. Because the accessibility statistic is
normalized, the worst values are slightly below \(-3\), the best
somewhere above \(3\).

For comparative purposes, we also employ an isochrone analysis using the
10-minute walk threshold calculated for ParkScore \citep{parkscore2019}.
If the population-weighted centroid of a tract is within a 10-minute
walk of a green space as defined by ParkScore, the tract is considered
as having ``access'' to a park. The centroid is necessary as all tracts
in New York City have at least \emph{some} intersection with the
10-minute walk buffer; as it is, only 24 of the 2,102 tract centroids
are not located within this buffer.

\begin{figure*}
\includegraphics{map-1} \caption{Normalized utility-based park accessibility values in New York City.}\label{fig:map}
\end{figure*}

\hypertarget{model}{%
\subsection{Model}\label{model}}

\label{subsec:model}

We predict either the physical activity or the obesity rate (\(y\)) in a
census tract as a linear function of the tract's sociodemographic
characteristics \(X\) and accessibility to parks \(A\),
\begin{equation}\label{eq:themodel}
 y = X\beta + \beta_{a}A + \varepsilon
\end{equation}

As the observations are related to each other spatially, it is likely
that this process involves spatial spillovers of one kind or another. A
complete treatment of spatial econometrics is not warranted here; the
reader is directed to \citet{LeSage2009} as well as \citet{LeSage2014}.
Suffice it to say that the presence of spatial data generating processes
can negatively affect econometric interpretation in a variety of ways.
Each of these processes rely on spatial autoregression, where elements
of some random variable \(x\) are spatially dependent on other elements,
\begin{equation}\label{eq:autoregression}
 x = \rho W x + \varepsilon
\end{equation} with the strength of dependence an estimated parameter
\(\rho\), the structure of spatial dependence governed by the asserted
matrix \(W\) (details of \(W\) follow below), and some random
uncorrelated residual \(\varepsilon\). A collection of models is
available to represent spatial autodependence in the model residuals,
the independent variables, and the dependent variable.

The specific spatial model applied is both an econometric choice --- as
improperly specified spatial models can lead to inconsistent estimates
of model parameters and standard errors --- as well as a philosophical
choice about the likely structure of spillovers in the problem at hand.
In case of physical activity and obesity rates, we believe that the
outcomes are locally dependent: That is, a particular individual decides
whether or not to participate in physical activity independently of
whether his or her neighbors participate in physical activity. This does
not mean that we think it impossible that the socioeconomic variables of
neighboring tracts do not play a role. Mathematically, we assert that
the autodependence relationship on the dependent variable
\(y = \rho W y + \ldots\) has \(\rho = 0\) in the current case.

With this relationship ruled out, it remains a possibility that the
model residuals are spatially dependent, \begin{equation}\label{eq:SEM}
 y = X\beta + \beta_a A + u; u = \lambda W u + \varepsilon
\end{equation} that the outcome is partially dependent on the
socioeconomic variables in \emph{neighboring} tracts,
\begin{equation}\label{eq:SLX}
 y = X\beta + \beta_a A + W X \gamma + \varepsilon
\end{equation} or a linear combination of both.
\begin{equation}\label{eq:SDEM}
 y = X\beta + \beta_a A + W X \gamma + u; u = \lambda W u + \varepsilon 
\end{equation} These models are referred as the spatial error model
(SEM), the spatial lag of \(X\) model (SLX), and the spatial Durbin
error model (SDEM). \citet{Pace2008} suggest that a Hausman-style test
of the estimates of \(\beta\) derived from the OLS (Equation
\ref{eq:themodel}) and SEM (Equation \ref{eq:SEM}) can identify whether
the estimates are consistent. If the \(\beta\) estimates are dissimilar,
both specifications are inappropriate as they contain untreated omitted
variables. Similarly, if the SLX and SDEM estimates are dissimilar it is
an indication of missing variables in that specification. On the other
hand if the estimates of both pairs of models are similar and the
residual correlation parameter \(\lambda\) is non-zero, the model
accounting for spatially dependent residuals will produce proper
estimates of the model standard errors.

Note that in the lag-\(X\) specifications (SLX and SDEM) we exclude the
accessiblity component \(A\), that is we do \emph{not} consider that the
accessibility in a neighboring zone will have an effect on physical
activity or obesity rates. In a practical sense, this is because the
accessibility term \(A\) is itself spatially determined.

\hypertarget{spatial-weights}{%
\subsubsection{Spatial Weights}\label{spatial-weights}}

The spatial weights matrix \(W\) is constructed of individual elements
where \(w_{ij} = 0\) if observations \(i\) and \(j\) are spatially
independent of each other, and \(w_{ij} > 0\) if \(i\) and \(j\) are
spatially related in some way. \citet{Dubin1998} presents details on
constructing \(W\), but in this study we assume that tracts sharing at
least one common border point are neighbors of each other\footnote{We
  also considered a distance-discounted weights matrix, which produced
  similar results. This matrix is selected for simplicity.}. The
elements of \(W\) are then row-standardized so that each observation has
an equal total influence from all its neighbors.

\hypertarget{results}{%
\subsection{Results}\label{results}}

To determine which spatial effects specification was appropriate, we
estimated SLX and SDEM models of physical activity participation rates
as a function of tract covariates and accessibility. These two models
are presented in Table \ref{tab:slx-sdem}. With only a few exceptions,
the SLX and SDEM coefficient estimates for corresponding covariates lie
within the 95\% confidence intervals of the other model. A Hausman-style
test \citep{Pace2008} on the coefficients assumes a null hypothesis that
the coefficients are equivalent; this test produces \(p\)-value of only
\(0.03057\). Though this statistic is technically beneath a common
hypothesis test threshold of \(\alpha = 0.05\), we fail to reject the
null hypothesis that the coefficients are equivalent, as the differences
are at no point practically different from each other. The consequences
of rejecting the null hypothesis in this case would be to suggest a
model with spatial dependence of the dependent variable; as stated
above, we feel that such a relationship is unreasonable. As a
consequence of these analyses, we adopt the SDEM specification moving
forward as the spatial lag of the errors is significant and the overal
log likelihood of the SDEM is higher than the SLX specification.

\begin{table*}
\caption{Comparison of SLX and SDEM Coefficients}
\label{tab:slx-sdem}

\begin{tabular}{l c c}
\toprule
 & SLX & SDEM \\
\midrule
(Intercept)                         & $-35.3520 \; [-47.4781; -23.2260]^{*}$ & $-27.2048 \; [-45.0525; -9.3571]^{*}$ \\
log(Density)                        & $0.1057 \; [ -0.0920;   0.3034]$       & $0.2301 \; [  0.0646;  0.3956]^{*}$   \\
log(Income)                         & $6.4092 \; [  5.8339;   6.9845]^{*}$   & $6.2664 \; [  5.7721;  6.7607]^{*}$   \\
Fulltime                            & $0.1365 \; [  0.1130;   0.1601]^{*}$   & $0.1434 \; [  0.1221;  0.1647]^{*}$   \\
College-educated                    & $0.0371 \; [  0.0058;   0.0683]^{*}$   & $0.0313 \; [  0.0042;  0.0583]^{*}$   \\
Single Adults                       & $-0.0488 \; [ -0.0696;  -0.0279]^{*}$  & $-0.0472 \; [ -0.0659; -0.0284]^{*}$  \\
Youth (0-17)                        & $-0.1292 \; [ -0.1643;  -0.0941]^{*}$  & $-0.1300 \; [ -0.1608; -0.0992]^{*}$  \\
Young adults (18-34)                & $0.0395 \; [  0.0122;   0.0669]^{*}$   & $0.0387 \; [  0.0153;  0.0622]^{*}$   \\
Seniors (65+)                       & $0.0301 \; [ -0.0053;   0.0655]$       & $0.0354 \; [  0.0038;  0.0671]^{*}$   \\
Black population share              & $-0.0522 \; [ -0.0653;  -0.0391]^{*}$  & $-0.0536 \; [ -0.0641; -0.0432]^{*}$  \\
Asian population share              & $-0.0941 \; [ -0.1101;  -0.0781]^{*}$  & $-0.0954 \; [ -0.1081; -0.0827]^{*}$  \\
Hispanic population share           & $-0.1134 \; [ -0.1270;  -0.0998]^{*}$  & $-0.1152 \; [ -0.1261; -0.1044]^{*}$  \\
Other Minorities                    & $0.0154 \; [ -0.0957;   0.1265]$       & $-0.0119 \; [ -0.1145;  0.0906]$      \\
$\gamma$: log(Density)              & $1.6773 \; [  1.3277;   2.0269]^{*}$   & $1.1617 \; [  0.7470;  1.5764]^{*}$   \\
$\gamma$: log(Income)               & $1.9854 \; [  1.0562;   2.9146]^{*}$   & $1.6505 \; [  0.5414;  2.7597]^{*}$   \\
$\gamma$: Fulltime                  & $-0.0309 \; [ -0.0756;   0.0138]$      & $-0.0006 \; [ -0.0530;  0.0517]$      \\
$\gamma$: College-educated          & $-0.0002 \; [ -0.0545;   0.0541]$      & $-0.0174 \; [ -0.0819;  0.0471]$      \\
$\gamma$: Single Adults             & $-0.0390 \; [ -0.0764;  -0.0016]^{*}$  & $-0.0210 \; [ -0.0667;  0.0247]$      \\
$\gamma$: Youth (0-17)              & $0.0297 \; [ -0.0348;   0.0941]$       & $0.0205 \; [ -0.0552;  0.0962]$       \\
$\gamma$: Young adults (18-34)      & $0.1318 \; [  0.0847;   0.1789]^{*}$   & $0.0872 \; [  0.0319;  0.1424]^{*}$   \\
$\gamma$: Seniors (65+)             & $0.1505 \; [  0.0860;   0.2151]^{*}$   & $0.1181 \; [  0.0420;  0.1941]^{*}$   \\
$\gamma$: Black population share    & $0.0156 \; [ -0.0010;   0.0321]$       & $0.0102 \; [ -0.0073;  0.0278]$       \\
$\gamma$: Asian population share    & $-0.0325 \; [ -0.0521;  -0.0129]^{*}$  & $-0.0399 \; [ -0.0601; -0.0197]^{*}$  \\
$\gamma$: Hispanic population share & $-0.0028 \; [ -0.0201;   0.0144]$      & $0.0003 \; [ -0.0182;  0.0187]$       \\
$\gamma$: Other Minorities          & $0.2827 \; [  0.0215;   0.5438]^{*}$   & $0.1799 \; [ -0.1104;  0.4703]$       \\
Accessibility                       & $0.4522 \; [  0.3218;   0.5825]^{*}$   & $0.2076 \; [  0.0554;  0.3597]^{*}$   \\
$\lambda$: spatial correlation      &                                        & $0.5813 \; [  0.5344;  0.6282]^{*}$   \\
\midrule
Log Likelihood                      & $-5032.2042$                           & $-4786.9274$                          \\
Num. Obs.                           & $2099$                                 & $2099$                                \\
LR test: statistic                  & $$                                     & $490.5536$                            \\
LR test: p-value                    & $$                                     & $0.0000$                              \\
\bottomrule
\multicolumn{3}{l}{\scriptsize{$^*$ 0 outside the confidence interval. $y = $ tract-level physical activity rate.}}
\end{tabular}
\end{table*}

The coefficients in the SDEM model are of two general types: the direct
effect resulting from a tract's own attributes and the indirect effect
(\(\gamma\)) resulting from the spatially-weighted attributes of its
neighbors. For example, a percentage point increase in the share of
young adults in a tract increases the expected physical activity rate in
a tract by 0.03872 percentage points, and a percentage point increase in
the share of young adults \emph{in neighboring tracts} increases the
expected physical activity rate by an \emph{additional} 0.08718
percentage points. This opportunity to examine spatial spillovers of
attributes is a key benefit of using a spatial model.

For the most part the direct coefficients are highly significant and of
the expected sign. Tracts with higher shares of full-time workers,
college-educated adults, young adults, and high-income households all
show a greater share of individuals engaging in regular physical
activity. Conversely, tracts with greater population density and a
greater share of single adults, children, seniors, minorities, and low
income households all have lower modeled expected rates of physical
activity. The indirect coefficients are less clearly significant, with
only density, median tract income, some age groups, and some minority
groups showing an indirect effect.

Table \ref{tab:pa-models} presents the estimated spatial lag and
accessibility coefficients for three models using different
specifications of the utility equation, as well as the ten-minute walk
buffer calculated by ParkScore. Note that the model called ``Size and
Distance'' is precisely the model labeled ``SDEM'' in Table
\ref{tab:slx-sdem}. The controlling covariates are suppressed for
clarity but do not change meaningfully across the four specifications.
Complete model estimates are available in the Appendix. Each of the
three utility-based specifications is significant at the
\(\alpha = 0.05\) level or lower, and is of the hypothesized
directionality. That is, residents living in tracts with increased
utility-based accessiblity to green spaces show a significantly higher
physical activity participation rate. Taking the rough mean of the three
estimated utility-based coefficients, moving from the least-accessible
tract (\(A_i = -3\)) to the most-accessible tract (\(A_i = 3\)) is
expected to raise the physical activity rate by 1.2 percentage points.
With the understanding of the full 95\% confidence interval, we could
suggest that the true effect of excellent versus poor park access is
anywhere between 0.3 and 2.1 percentage points.

The 10-minute walk buffer is considerably less useful at isolating the
effects of park ``access'' on physical activity rates. As so few tracts
are located outside of the buffer, the standard error of the estimated
effect is large and implies an effect on activity rates anywhere from a
loss of 2.22 percentage points to a gain of 9.

\begin{table*}
\caption{Estimated Effect of Accessibility on Physical Activity Rates}
\label{tab:pa-models}

\begin{tabular}{l c c c c}
\toprule
 & Size and Distance & Twitter & Amenities & 10-Minute Walk \\
\midrule
Size and Distance & $0.2076^{*}$        &                     &                     &                      \\
                  & $ [0.0554; 0.3597]$ &                     &                     &                      \\
Amenities         &                     &                     & $0.1975^{*}$        &                      \\
                  &                     &                     & $ [0.0428; 0.3522]$ &                      \\
Twitter Activity  &                     & $0.2229^{*}$        &                     &                      \\
                  &                     & $ [0.0659; 0.3799]$ &                     &                      \\
10-minute walk    &                     &                     &                     & $0.5682$             \\
                  &                     &                     &                     & $ [-0.3638; 1.5001]$ \\
\midrule
Num. obs.         & $2099$              & $2099$              & $2099$              & $2099$               \\
Parameters        & $28$                & $28$                & $28$                & $28$                 \\
Log Likelihood    & $-4786.9274$        & $-4786.6411$        & $-4787.3677$        & $-4789.6660$         \\
\bottomrule
\multicolumn{5}{l}{\scriptsize{$^*$ 0 outside the confidence interval. 95\% confidence interval in brackets.}}
\end{tabular}
\end{table*}

We now consider the impacts of a model where the dependent variable is
the \emph{obesity} rate in a tract, and physical activity becomes an
independent covariate alongside the controlling variables and the
accessibility metrics. Table \ref{tab:obesity-models} presents estimates
of the effect of all three utility-based accessibility measures as well
as the 10-minute walk buffer. As before, the estimates of the other
variables are available in the Appendix. The correlation between
physical activity rates and obesity is clear; for every percentage point
increase in physical activity rate, the expected obesity rate drops by
\(0.43\) percentage points in all four accessiblity specifications. The
indirect effect of physical activity rates on obesity in neighboring
zones is inconsequential, supporting our methodological assertion that
public health variables are not spatially dependent, though the factors
leading to them may be.

As far as the accessibility values are concerned, none of the three
utility-based specifications nor the ParkScore 10-minute walk buffer are
correlated with obesity rates at the traditional 95\% confidence
interval. It is important to consider the implications of the full range
of the confidence interval, however \citep{Amrhein2019}. The results
suggest that after controlling for tract socioeconomic variables,
physical activity rates, and spatially correlated error terms, obesity
rates in tracts with excellent park accessibility are expected to be
between 0.9 percentage points lower and 0.0318 percentage points higher
than tracts with poor park accessibility. This range of values suggests
that accessibility to parks may have obesity-reducing effects beyond the
effect of accessibility on physical activity rates worth further study.

\begin{table*}
\caption{Estimated Effect of Accessibility on Obesity Rates}
\label{tab:obesity-models}

\begin{tabular}{l c c c c}
\toprule
 & Size and Distance & Twitter & Amenities & 10-Minute Walk \\
\midrule
Physical Activity           & $-0.4251^{*}$         & $-0.4250^{*}$         & $-0.4251^{*}$         & $-0.4256^{*}$         \\
                            & $ [-0.4463; -0.4039]$ & $ [-0.4462; -0.4038]$ & $ [-0.4463; -0.4039]$ & $ [-0.4468; -0.4045]$ \\
$\gamma$: Physical Activity & $-0.0321$             & $-0.0317$             & $-0.0318$             & $-0.0362$             \\
                            & $ [-0.0841;  0.0199]$ & $ [-0.0838;  0.0203]$ & $ [-0.0839;  0.0203]$ & $ [-0.0882;  0.0158]$ \\
Size and Distance           & $-0.0688$             &                       &                       &                       \\
                            & $ [-0.1440;  0.0064]$ &                       &                       &                       \\
Amenities                   &                       &                       & $-0.0695$             &                       \\
                            &                       &                       & $ [-0.1472;  0.0083]$ &                       \\
Twitter Activity            &                       & $-0.0731$             &                       &                       \\
                            &                       & $ [-0.1516;  0.0053]$ &                       &                       \\
10-minute walk              &                       &                       &                       & $-0.3573$             \\
                            &                       &                       &                       & $ [-0.7650;  0.0505]$ \\
\midrule
Num. obs.                   & $2099$                & $2099$                & $2099$                & $2099$                \\
Parameters                  & $30$                  & $30$                  & $30$                  & $30$                  \\
Log Likelihood              & $-3194.8851$          & $-3194.8268$          & $-3194.9556$          & $-3195.0152$          \\
\bottomrule
\multicolumn{5}{l}{\scriptsize{$^*$ 0 outside the confidence interval. 95\% confidence interval in brackets.}}
\end{tabular}
\end{table*}

\hypertarget{limitations-and-future-research-direction}{%
\section{Limitations and Future Research
Direction}\label{limitations-and-future-research-direction}}

We readily acknowledge limitations in this study. As in any study
conducted with areal data, we are at risk of falling victim to the
ecological inference fallacy, where aggregate statistics mask or
contradict disaggregated or individual-level trends. A large-sample
survey of individuals in New York City, including measured physical
activities and obesity would always be preferable to the tract-level
data used in this study. An ideal survey to address the question would
incorporate both sets of questions: physical activity and health data on
one hand and park use (including which parks were used and how
frequently) on the other. As no such dataset exists to our knowledge,
this tract-level aggregate analysis with asserted and transferred
utility coefficients is the possibility that remains.

This paper applies a previously-presented but little-used accessibility
statistic that could, in theory, accommodate many attributes of the
destination parks as well as the people who might use them. As an
illustration: the park-going population could be separated into at least
four delineated clusters, each preferring different amenities of a park:

\begin{itemize}
 \item{runners and cyclists: long, interesting trail systems}
 \item{sports players: soccer fields, basketball courts, or baseball diamonds}
 \item{families with small children: water features and playgrounds}
 \item{casual users: water features, gardens, performances, etc.}
\end{itemize}

An analyst could then compute the utility-based accessibility for each
cluster with different utility values for each park's amenities, and
obtain a measure of a neighborhood's accessibility to park features that
its residents most care about. In this paper, we proceed only
incrementally towards this by adding Twitter activity and some selected
park amenities as an element of each park's attractiveness above and
beyond its size. Exploring detailed definitions of an increased number
of amenities on one hand, and market segmentation strategies on the
other, could provide a more nuanced understanding of the relationship
between park accessibility and health outcomes.

As a travel impedance measure, we used the Euclidean distance between
each tract's population-weighted centroid and the nearest point on the
edge of a park's border. Euclidean distances have well-rehearsed
limitations regarding their fidelity with the underlying infrastructure
network, etc. Network-based distances can also suffer from challenges
when applied to multimodal problems; these challenges are exacerbated
when the non-highway mode share is high, as is likely when considering
access to parks. A better metric of travel impedance may be a mode
choice model logsum, which weights all alternative travel alternatives
against each other. We leave this as a recommendation for future
research.

We compared our utility-based accessibility to a well-constructed
isochrone that has attracted attention in the literature. That said,
virtually all tracts in New York City are within this specific
isochrone. It is possible that this isochrone may be more discriminating
of park access in other cities, or that a different definition would
yield different results in New York City. This observation however
reinforces our suggestion that a measure explicitly based in the utility
of access is warranted.

Finally, this study is primarily focused on the hypothesis that
accessibility to parks encourages physical activity, which in turn
reduces obesity. There are a multitude of other hypotheses that might be
proposed and tested with the basic methodology we have employed here, or
competing explanations for the outcomes we have observed. It is
distinctly possible, for instance, that individuals who wish to exercise
regularly in parks choose to live near them. Given that the CDC models
informing the small-area obesity and physical activity estimates
presumably include variables likely to influence such preferences
(income, etc.), our investigation cannot isolate the preferences from
the effect. Controlling for such a self-selection effect would be
necessary to isolate the exogenous impacts of park access on obesity or
other health outcomes. And regarding these other variables: this study
did not consider potential relationships between park access and
hospitalization rates, life expectancy, respiratory disease, mental
health, or any number of potential beneficial outcomes hypothesized or
explored in the existing literature. Exploring these connections and
their underlying mechanisms should be a priority as city planners and
urban architects attempt to improve the quality of life of urban
residents in the future.

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}

Increased physical activity and decreased obesity rates are critical
measures of improvement in public health. Although many have theorized
the link between park accessibility and these metrics, previous
literature has produced mixed findings, perhaps owing to the range of
variables modeled and the coarse spatial scale of the analyses. Using
New York City as a case study, we presented a holistic and flexible
measurement for park accessibility that compares the continuous distance
to all parks in the region, weighted against the size of the park and
its other amenities, with weights determinable through revealed
preferences. In terms of physical activity, we found a positive
relationship where the least park-accessible tracts have an expected
physical activity participation rate between 0.3 and 2.1 percentage
points lower than the most accessible tracts. We also found a suggestive
though not sigificant relationship between park accessiblity and
expected obesity rates \emph{in addition to} the effect of physical
activity participation.

In both cases a common, isochrone-based analysis estimated a
statistically weak relationship with greater uncertainty. Isochrone
analyses are relatively common in the literature, perhaps because of the
widespread availability of and training in GIS software. In spite of
their widespread use, isochrones are relatively limited in terms of both
their theoretical underpinnings and their flexibility to accommodate
attributes of parks beyond their proximity. And even proximity may not
be adequately handled, as the isochrone threshold may be arbitrarily
asserted by the researcher. The model we apply in this paper extends a
more comprehensive and flexible approach for measuring the impact of
park access on health outcomes. Adopting utility-based accessibilities
of the kind used in this study will allow researchers to encompass the
full range of park amenities in their accessibility analyses, and to
separate the definition of access from the study of its effects. This
will in turn enable planners to consider how multiple attributes of a
park --- from its location to its size to its amenities and beyond ---
benefit the health of the community the park serves.

\bibliographystyle{sageh.bst}
\bibliography{manuscript.bbl}

\appendix
\section{Appendix}

In this appendix we present the complete estimation results for the models 
relating different definitions of access to physical activity (in Table
\ref{tab:pa-fullmodels}) and to obesity (in Table \ref{tab:ob-fullmodels}). In
each case we also present a base model with no accessibility statistics for
comparison.

\begin{table*}
\caption{Estimated Effects of Accessibility and Controls on Physical Activity Rates}
\begin{center}
\scalebox{0.7}{
\begin{tabular}{l c c c c c}
\toprule
 & No Access & Size and Distance & Tweets & Attributes & 10-min walk \\
\midrule
(Intercept)                         & $-25.9256^{*}$         & $-27.2048^{*}$         & $-26.5608^{*}$         & $-27.2431^{*}$         & $-26.1786^{*}$         \\
                                    & $ [-43.9792; -7.8720]$ & $ [-45.0525; -9.3571]$ & $ [-44.3812; -8.7404]$ & $ [-45.1016; -9.3846]$ & $ [-44.2194; -8.1378]$ \\
log(Density)                        & $0.2249^{*}$           & $0.2301^{*}$           & $0.2280^{*}$           & $0.2281^{*}$           & $0.2201^{*}$           \\
                                    & $ [  0.0594;  0.3905]$ & $ [  0.0646;  0.3956]$ & $ [  0.0626;  0.3934]$ & $ [  0.0626;  0.3936]$ & $ [  0.0544;  0.3858]$ \\
log(Income)                         & $6.2290^{*}$           & $6.2664^{*}$           & $6.2575^{*}$           & $6.2632^{*}$           & $6.2277^{*}$           \\
                                    & $ [  5.7342;  6.7239]$ & $ [  5.7721;  6.7607]$ & $ [  5.7636;  6.7513]$ & $ [  5.7688;  6.7575]$ & $ [  5.7331;  6.7224]$ \\
Fulltime                            & $0.1442^{*}$           & $0.1434^{*}$           & $0.1434^{*}$           & $0.1433^{*}$           & $0.1444^{*}$           \\
                                    & $ [  0.1228;  0.1656]$ & $ [  0.1221;  0.1647]$ & $ [  0.1220;  0.1647]$ & $ [  0.1220;  0.1646]$ & $ [  0.1230;  0.1658]$ \\
College-educated                    & $0.0307^{*}$           & $0.0313^{*}$           & $0.0316^{*}$           & $0.0307^{*}$           & $0.0315^{*}$           \\
                                    & $ [  0.0036;  0.0578]$ & $ [  0.0042;  0.0583]$ & $ [  0.0046;  0.0586]$ & $ [  0.0036;  0.0577]$ & $ [  0.0043;  0.0586]$ \\
Single Adults                       & $-0.0475^{*}$          & $-0.0472^{*}$          & $-0.0474^{*}$          & $-0.0469^{*}$          & $-0.0478^{*}$          \\
                                    & $ [ -0.0663; -0.0287]$ & $ [ -0.0659; -0.0284]$ & $ [ -0.0661; -0.0286]$ & $ [ -0.0657; -0.0282]$ & $ [ -0.0667; -0.0290]$ \\
Youth (0-17)                        & $-0.1302^{*}$          & $-0.1300^{*}$          & $-0.1304^{*}$          & $-0.1300^{*}$          & $-0.1307^{*}$          \\
                                    & $ [ -0.1611; -0.0993]$ & $ [ -0.1608; -0.0992]$ & $ [ -0.1611; -0.0996]$ & $ [ -0.1608; -0.0992]$ & $ [ -0.1615; -0.0998]$ \\
Young adults (18-34)                & $0.0372^{*}$           & $0.0387^{*}$           & $0.0387^{*}$           & $0.0388^{*}$           & $0.0370^{*}$           \\
                                    & $ [  0.0137;  0.0606]$ & $ [  0.0153;  0.0622]$ & $ [  0.0153;  0.0621]$ & $ [  0.0153;  0.0622]$ & $ [  0.0135;  0.0605]$ \\
Seniors (65+)                       & $0.0384^{*}$           & $0.0354^{*}$           & $0.0348^{*}$           & $0.0359^{*}$           & $0.0380^{*}$           \\
                                    & $ [  0.0068;  0.0701]$ & $ [  0.0038;  0.0671]$ & $ [  0.0032;  0.0664]$ & $ [  0.0043;  0.0675]$ & $ [  0.0064;  0.0697]$ \\
Black population share              & $-0.0537^{*}$          & $-0.0536^{*}$          & $-0.0536^{*}$          & $-0.0535^{*}$          & $-0.0535^{*}$          \\
                                    & $ [ -0.0642; -0.0433]$ & $ [ -0.0641; -0.0432]$ & $ [ -0.0640; -0.0432]$ & $ [ -0.0639; -0.0431]$ & $ [ -0.0639; -0.0430]$ \\
Asian population share              & $-0.0961^{*}$          & $-0.0954^{*}$          & $-0.0954^{*}$          & $-0.0955^{*}$          & $-0.0963^{*}$          \\
                                    & $ [ -0.1088; -0.0834]$ & $ [ -0.1081; -0.0827]$ & $ [ -0.1081; -0.0827]$ & $ [ -0.1082; -0.0829]$ & $ [ -0.1090; -0.0837]$ \\
Hispanic population share           & $-0.1148^{*}$          & $-0.1152^{*}$          & $-0.1153^{*}$          & $-0.1153^{*}$          & $-0.1147^{*}$          \\
                                    & $ [ -0.1256; -0.1039]$ & $ [ -0.1261; -0.1044]$ & $ [ -0.1261; -0.1044]$ & $ [ -0.1261; -0.1044]$ & $ [ -0.1255; -0.1038]$ \\
Other Minorities                    & $-0.0161$              & $-0.0119$              & $-0.0126$              & $-0.0115$              & $-0.0170$              \\
                                    & $ [ -0.1190;  0.0867]$ & $ [ -0.1145;  0.0906]$ & $ [ -0.1151;  0.0899]$ & $ [ -0.1141;  0.0910]$ & $ [ -0.1199;  0.0858]$ \\
$\gamma$: log(Density)              & $1.1804^{*}$           & $1.1617^{*}$           & $1.1491^{*}$           & $1.1685^{*}$           & $1.1668^{*}$           \\
                                    & $ [  0.7624;  1.5984]$ & $ [  0.7470;  1.5764]$ & $ [  0.7341;  1.5642]$ & $ [  0.7539;  1.5831]$ & $ [  0.7484;  1.5851]$ \\
$\gamma$: log(Income)               & $1.5660^{*}$           & $1.6505^{*}$           & $1.6211^{*}$           & $1.6398^{*}$           & $1.5611^{*}$           \\
                                    & $ [  0.4473;  2.6848]$ & $ [  0.5414;  2.7597]$ & $ [  0.5135;  2.7288]$ & $ [  0.5305;  2.7491]$ & $ [  0.4433;  2.6790]$ \\
$\gamma$: Fulltime                  & $0.0029$               & $-0.0006$              & $-0.0009$              & $0.0002$               & $0.0025$               \\
                                    & $ [ -0.0498;  0.0556]$ & $ [ -0.0530;  0.0517]$ & $ [ -0.0532;  0.0514]$ & $ [ -0.0521;  0.0525]$ & $ [ -0.0502;  0.0551]$ \\
$\gamma$: College-educated          & $-0.0190$              & $-0.0174$              & $-0.0163$              & $-0.0193$              & $-0.0212$              \\
                                    & $ [ -0.0842;  0.0461]$ & $ [ -0.0819;  0.0471]$ & $ [ -0.0808;  0.0482]$ & $ [ -0.0839;  0.0452]$ & $ [ -0.0863;  0.0440]$ \\
$\gamma$: Single Adults             & $-0.0218$              & $-0.0210$              & $-0.0218$              & $-0.0198$              & $-0.0215$              \\
                                    & $ [ -0.0680;  0.0243]$ & $ [ -0.0667;  0.0247]$ & $ [ -0.0674;  0.0239]$ & $ [ -0.0655;  0.0259]$ & $ [ -0.0676;  0.0246]$ \\
$\gamma$: Youth (0-17)              & $0.0169$               & $0.0205$               & $0.0200$               & $0.0217$               & $0.0161$               \\
                                    & $ [ -0.0594;  0.0932]$ & $ [ -0.0552;  0.0962]$ & $ [ -0.0557;  0.0956]$ & $ [ -0.0540;  0.0975]$ & $ [ -0.0602;  0.0923]$ \\
$\gamma$: Young adults (18-34)      & $0.0827^{*}$           & $0.0872^{*}$           & $0.0872^{*}$           & $0.0884^{*}$           & $0.0823^{*}$           \\
                                    & $ [  0.0270;  0.1384]$ & $ [  0.0319;  0.1424]$ & $ [  0.0320;  0.1425]$ & $ [  0.0331;  0.1437]$ & $ [  0.0267;  0.1380]$ \\
$\gamma$: Seniors (65+)             & $0.1207^{*}$           & $0.1181^{*}$           & $0.1161^{*}$           & $0.1198^{*}$           & $0.1204^{*}$           \\
                                    & $ [  0.0440;  0.1974]$ & $ [  0.0420;  0.1941]$ & $ [  0.0400;  0.1921]$ & $ [  0.0437;  0.1958]$ & $ [  0.0438;  0.1971]$ \\
$\gamma$: Black population share    & $0.0096$               & $0.0102$               & $0.0104$               & $0.0099$               & $0.0096$               \\
                                    & $ [ -0.0081;  0.0273]$ & $ [ -0.0073;  0.0278]$ & $ [ -0.0071;  0.0279]$ & $ [ -0.0077;  0.0274]$ & $ [ -0.0081;  0.0273]$ \\
$\gamma$: Asian population share    & $-0.0429^{*}$          & $-0.0399^{*}$          & $-0.0398^{*}$          & $-0.0405^{*}$          & $-0.0428^{*}$          \\
                                    & $ [ -0.0631; -0.0226]$ & $ [ -0.0601; -0.0197]$ & $ [ -0.0599; -0.0196]$ & $ [ -0.0606; -0.0203]$ & $ [ -0.0630; -0.0225]$ \\
$\gamma$: Hispanic population share & $0.0026$               & $0.0003$               & $0.0001$               & $0.0002$               & $0.0025$               \\
                                    & $ [ -0.0160;  0.0212]$ & $ [ -0.0182;  0.0187]$ & $ [ -0.0184;  0.0185]$ & $ [ -0.0183;  0.0186]$ & $ [ -0.0161;  0.0210]$ \\
$\gamma$: Other Minorities          & $0.1695$               & $0.1799$               & $0.1770$               & $0.1798$               & $0.1756$               \\
                                    & $ [ -0.1225;  0.4616]$ & $ [ -0.1104;  0.4703]$ & $ [ -0.1132;  0.4672]$ & $ [ -0.1106;  0.4702]$ & $ [ -0.1165;  0.4677]$ \\
$\lambda$: spatial correlation      & $0.5920^{*}$           & $0.5813^{*}$           & $0.5809^{*}$           & $0.5815^{*}$           & $0.5914^{*}$           \\
                                    & $ [  0.5458;  0.6382]$ & $ [  0.5344;  0.6282]$ & $ [  0.5339;  0.6278]$ & $ [  0.5346;  0.6284]$ & $ [  0.5451;  0.6376]$ \\
Size and Distance                   &                        & $0.2076^{*}$           &                        &                        &                        \\
                                    &                        & $ [  0.0554;  0.3597]$ &                        &                        &                        \\
Tweets                              &                        &                        & $0.2229^{*}$           &                        &                        \\
                                    &                        &                        & $ [  0.0659;  0.3799]$ &                        &                        \\
Attributes                          &                        &                        &                        & $0.1975^{*}$           &                        \\
                                    &                        &                        &                        & $ [  0.0428;  0.3522]$ &                        \\
10-min walk                         &                        &                        &                        &                        & $0.5682$               \\
                                    &                        &                        &                        &                        & $ [ -0.3638;  1.5001]$ \\
\midrule
Num. obs.                           & $2099$                 & $2099$                 & $2099$                 & $2099$                 & $2099$                 \\
Parameters                          & $27$                   & $28$                   & $28$                   & $28$                   & $28$                   \\
Log Likelihood                      & $-4790.3792$           & $-4786.9274$           & $-4786.6411$           & $-4787.3677$           & $-4789.6660$           \\
\bottomrule
\multicolumn{6}{l}{\scriptsize{$^*$ 0 outside the confidence interval. 95\% confidence interval in brackets.}}
\end{tabular}
}
\label{tab:pa-fullmodels}
\end{center}
\end{table*}

\begin{table*}
\caption{Estimated Effects of Accessibility and Controls on Obesity Rates}
\begin{center}
\scalebox{0.7}{
\begin{tabular}{l c c c c c}
\toprule
 & No Access & Size and Distance & Twitter & Amenities & 10-Minute Walk \\
\midrule
(Intercept)                         & $69.6657^{*}$         & $69.9773^{*}$         & $69.8388^{*}$         & $69.9833^{*}$         & $69.7516^{*}$         \\
                                    & $ [59.1228; 80.2086]$ & $ [59.4547; 80.4999]$ & $ [59.3196; 80.3579]$ & $ [59.4480; 80.5185]$ & $ [59.2183; 80.2850]$ \\
log(Density)                        & $-0.0343$             & $-0.0370$             & $-0.0366$             & $-0.0367$             & $-0.0305$             \\
                                    & $ [-0.1115;  0.0429]$ & $ [-0.1141;  0.0402]$ & $ [-0.1137;  0.0406]$ & $ [-0.1139;  0.0404]$ & $ [-0.1078;  0.0467]$ \\
log(Income)                         & $-0.3886^{*}$         & $-0.4015^{*}$         & $-0.4001^{*}$         & $-0.4021^{*}$         & $-0.3882^{*}$         \\
                                    & $ [-0.6649; -0.1122]$ & $ [-0.6780; -0.1251]$ & $ [-0.6765; -0.1238]$ & $ [-0.6786; -0.1256]$ & $ [-0.6643; -0.1121]$ \\
Fulltime                            & $-0.0117^{*}$         & $-0.0116^{*}$         & $-0.0116^{*}$         & $-0.0116^{*}$         & $-0.0119^{*}$         \\
                                    & $ [-0.0227; -0.0007]$ & $ [-0.0226; -0.0006]$ & $ [-0.0226; -0.0006]$ & $ [-0.0225; -0.0006]$ & $ [-0.0229; -0.0009]$ \\
College-educated                    & $0.0372^{*}$          & $0.0371^{*}$          & $0.0370^{*}$          & $0.0372^{*}$          & $0.0367^{*}$          \\
                                    & $ [ 0.0237;  0.0506]$ & $ [ 0.0236;  0.0505]$ & $ [ 0.0235;  0.0504]$ & $ [ 0.0237;  0.0506]$ & $ [ 0.0233;  0.0502]$ \\
Single Adults                       & $0.0017$              & $0.0017$              & $0.0018$              & $0.0017$              & $0.0019$              \\
                                    & $ [-0.0078;  0.0112]$ & $ [-0.0078;  0.0112]$ & $ [-0.0077;  0.0113]$ & $ [-0.0078;  0.0112]$ & $ [-0.0076;  0.0114]$ \\
Youth (0-17)                        & $0.0074$              & $0.0075$              & $0.0076$              & $0.0075$              & $0.0077$              \\
                                    & $ [-0.0080;  0.0227]$ & $ [-0.0078;  0.0228]$ & $ [-0.0077;  0.0230]$ & $ [-0.0078;  0.0229]$ & $ [-0.0076;  0.0231]$ \\
Young adults (18-34)                & $-0.0119^{*}$         & $-0.0125^{*}$         & $-0.0125^{*}$         & $-0.0125^{*}$         & $-0.0118^{*}$         \\
                                    & $ [-0.0234; -0.0005]$ & $ [-0.0239; -0.0010]$ & $ [-0.0239; -0.0010]$ & $ [-0.0240; -0.0011]$ & $ [-0.0232; -0.0004]$ \\
Seniors (65+)                       & $-0.0896^{*}$         & $-0.0886^{*}$         & $-0.0884^{*}$         & $-0.0887^{*}$         & $-0.0894^{*}$         \\
                                    & $ [-0.1052; -0.0740]$ & $ [-0.1042; -0.0730]$ & $ [-0.1040; -0.0728]$ & $ [-0.1043; -0.0731]$ & $ [-0.1050; -0.0738]$ \\
Black population share              & $0.0533^{*}$          & $0.0533^{*}$          & $0.0533^{*}$          & $0.0533^{*}$          & $0.0532^{*}$          \\
                                    & $ [ 0.0483;  0.0583]$ & $ [ 0.0484;  0.0583]$ & $ [ 0.0483;  0.0583]$ & $ [ 0.0483;  0.0582]$ & $ [ 0.0482;  0.0581]$ \\
Asian population share              & $-0.1043^{*}$         & $-0.1044^{*}$         & $-0.1044^{*}$         & $-0.1044^{*}$         & $-0.1042^{*}$         \\
                                    & $ [-0.1106; -0.0981]$ & $ [-0.1107; -0.0982]$ & $ [-0.1107; -0.0982]$ & $ [-0.1106; -0.0982]$ & $ [-0.1104; -0.0979]$ \\
Hispanic population share           & $-0.0042$             & $-0.0039$             & $-0.0039$             & $-0.0039$             & $-0.0042$             \\
                                    & $ [-0.0098;  0.0014]$ & $ [-0.0095;  0.0017]$ & $ [-0.0095;  0.0018]$ & $ [-0.0096;  0.0017]$ & $ [-0.0098;  0.0014]$ \\
Other Minorities                    & $-0.0639^{*}$         & $-0.0650^{*}$         & $-0.0650^{*}$         & $-0.0652^{*}$         & $-0.0632^{*}$         \\
                                    & $ [-0.1141; -0.0137]$ & $ [-0.1152; -0.0149]$ & $ [-0.1152; -0.0149]$ & $ [-0.1153; -0.0150]$ & $ [-0.1134; -0.0131]$ \\
Physical Activity Rate              & $-0.5805^{*}$         & $-0.5825^{*}$         & $-0.5808^{*}$         & $-0.5834^{*}$         & $-0.5674^{*}$         \\
                                    & $ [-0.8179; -0.3431]$ & $ [-0.8193; -0.3456]$ & $ [-0.8176; -0.3439]$ & $ [-0.8205; -0.3463]$ & $ [-0.8050; -0.3298]$ \\
$\gamma$: log(Density)              & $0.0755$              & $0.0372$              & $0.0407$              & $0.0388$              & $0.0880$              \\
                                    & $ [-0.6347;  0.7857]$ & $ [-0.6728;  0.7473]$ & $ [-0.6691;  0.7504]$ & $ [-0.6718;  0.7494]$ & $ [-0.6217;  0.7976]$ \\
$\gamma$: log(Income)               & $-0.0010$             & $-0.0005$             & $-0.0004$             & $-0.0007$             & $-0.0007$             \\
                                    & $ [-0.0302;  0.0282]$ & $ [-0.0296;  0.0287]$ & $ [-0.0295;  0.0288]$ & $ [-0.0299;  0.0284]$ & $ [-0.0299;  0.0285]$ \\
$\gamma$: Fulltime                  & $0.0869^{*}$          & $0.0867^{*}$          & $0.0864^{*}$          & $0.0870^{*}$          & $0.0885^{*}$          \\
                                    & $ [ 0.0505;  0.1233]$ & $ [ 0.0504;  0.1230]$ & $ [ 0.0501;  0.1228]$ & $ [ 0.0506;  0.1233]$ & $ [ 0.0521;  0.1250]$ \\
$\gamma$: College-educated          & $-0.0108$             & $-0.0107$             & $-0.0106$             & $-0.0109$             & $-0.0112$             \\
                                    & $ [-0.0365;  0.0150]$ & $ [-0.0364;  0.0149]$ & $ [-0.0363;  0.0151]$ & $ [-0.0367;  0.0148]$ & $ [-0.0369;  0.0146]$ \\
$\gamma$: Single Adults             & $-0.0356$             & $-0.0359$             & $-0.0356$             & $-0.0362$             & $-0.0351$             \\
                                    & $ [-0.0777;  0.0065]$ & $ [-0.0779;  0.0061]$ & $ [-0.0776;  0.0064]$ & $ [-0.0782;  0.0059]$ & $ [-0.0772;  0.0070]$ \\
$\gamma$: Youth (0-17)              & $-0.0296$             & $-0.0312^{*}$         & $-0.0312^{*}$         & $-0.0315^{*}$         & $-0.0291$             \\
                                    & $ [-0.0605;  0.0014]$ & $ [-0.0622; -0.0002]$ & $ [-0.0622; -0.0002]$ & $ [-0.0626; -0.0005]$ & $ [-0.0601;  0.0018]$ \\
$\gamma$: Young adults (18-34)      & $-0.0276$             & $-0.0266$             & $-0.0260$             & $-0.0270$             & $-0.0275$             \\
                                    & $ [-0.0690;  0.0138]$ & $ [-0.0680;  0.0147]$ & $ [-0.0674;  0.0154]$ & $ [-0.0684;  0.0144]$ & $ [-0.0689;  0.0139]$ \\
$\gamma$: Seniors (65+)             & $0.0155^{*}$          & $0.0154^{*}$          & $0.0154^{*}$          & $0.0155^{*}$          & $0.0153^{*}$          \\
                                    & $ [ 0.0050;  0.0259]$ & $ [ 0.0051;  0.0258]$ & $ [ 0.0050;  0.0258]$ & $ [ 0.0051;  0.0259]$ & $ [ 0.0049;  0.0258]$ \\
$\gamma$: Black population share    & $-0.0504^{*}$         & $-0.0509^{*}$         & $-0.0509^{*}$         & $-0.0507^{*}$         & $-0.0506^{*}$         \\
                                    & $ [-0.0640; -0.0368]$ & $ [-0.0645; -0.0373]$ & $ [-0.0645; -0.0373]$ & $ [-0.0643; -0.0371]$ & $ [-0.0642; -0.0371]$ \\
$\gamma$: Asian population share    & $0.0214^{*}$          & $0.0226^{*}$          & $0.0227^{*}$          & $0.0226^{*}$          & $0.0215^{*}$          \\
                                    & $ [ 0.0088;  0.0341]$ & $ [ 0.0099;  0.0353]$ & $ [ 0.0100;  0.0354]$ & $ [ 0.0099;  0.0354]$ & $ [ 0.0088;  0.0342]$ \\
$\gamma$: Hispanic population share & $0.0707$              & $0.0691$              & $0.0693$              & $0.0692$              & $0.0670$              \\
                                    & $ [-0.0777;  0.2190]$ & $ [-0.0791;  0.2173]$ & $ [-0.0789;  0.2175]$ & $ [-0.0790;  0.2174]$ & $ [-0.0813;  0.2153]$ \\
$\gamma$: Other Minorities          & $-0.4259^{*}$         & $-0.4251^{*}$         & $-0.4250^{*}$         & $-0.4251^{*}$         & $-0.4256^{*}$         \\
                                    & $ [-0.4471; -0.4047]$ & $ [-0.4463; -0.4039]$ & $ [-0.4462; -0.4038]$ & $ [-0.4463; -0.4039]$ & $ [-0.4468; -0.4045]$ \\
$\gamma$: Physical Activity Rate    & $-0.0351$             & $-0.0321$             & $-0.0317$             & $-0.0318$             & $-0.0362$             \\
                                    & $ [-0.0872;  0.0169]$ & $ [-0.0841;  0.0199]$ & $ [-0.0838;  0.0203]$ & $ [-0.0839;  0.0203]$ & $ [-0.0882;  0.0158]$ \\
$\lambda$: spatial correlation      & $0.8003^{*}$          & $0.7988^{*}$          & $0.7988^{*}$          & $0.7998^{*}$          & $0.8001^{*}$          \\
                                    & $ [ 0.7706;  0.8301]$ & $ [ 0.7689;  0.8287]$ & $ [ 0.7689;  0.8287]$ & $ [ 0.7700;  0.8296]$ & $ [ 0.7703;  0.8299]$ \\
Size and Distance                   &                       & $-0.0688$             &                       &                       &                       \\
                                    &                       & $ [-0.1440;  0.0064]$ &                       &                       &                       \\
Tweets                              &                       &                       & $-0.0731$             &                       &                       \\
                                    &                       &                       & $ [-0.1516;  0.0053]$ &                       &                       \\
Attributes                          &                       &                       &                       & $-0.0695$             &                       \\
                                    &                       &                       &                       & $ [-0.1472;  0.0083]$ &                       \\
10-min walk                         &                       &                       &                       &                       & $-0.3573$             \\
                                    &                       &                       &                       &                       & $ [-0.7650;  0.0505]$ \\
\midrule
Num. obs.                           & $2099$                & $2099$                & $2099$                & $2099$                & $2099$                \\
Parameters                          & $29$                  & $30$                  & $30$                  & $30$                  & $30$                  \\
Log Likelihood                      & $-3196.4885$          & $-3194.8851$          & $-3194.8268$          & $-3194.9556$          & $-3195.0152$          \\
\bottomrule
\multicolumn{6}{l}{\scriptsize{$^*$ 0 outside the confidence interval. 95\% confidence interval in brackets.}}
\end{tabular}
}
\label{tab:ob-fullmodels}
\end{center}
\end{table*}

\end{document}

### 2020-01-29 03_accessibility.Rmd
Rebuild website

--- 2019-09-24 03_logsums.Rmd
@@
 
-```{r setup}
+```{r setup, include=FALSE}
 knitr::opts_chunk$set(cache = TRUE)
@@
 library(spdep)
+library(spatialreg)
 library(leaflet)

### 2020-01-29 docs/R/logsums.R

@@ -1,0 +1,25 @@
+#' Calculate destination choice logsums from a distance matrix
+#'
+#' @param impedance An $n\times p$ matrix with the distance from all tracts to
+#'   all parks
+#' @param size_term A p-length vector of the park size terms
+#'
+#' @return An n-length vector containing the weighted log-sum based
+#'   accessibility between a tract and all parks.
+#' @details If we have n tracts and p parks, distances needs to be a
+#'
+calculate_park_logsums <- function(impedance, size_term){
+  
+  # calculate observed utility by adding the weighted park-level attributes
+  # to the columns of the matrix
+  # V is n x p, with b added by-column to each element in a
+  V <- sweep(impedance, 2, size_term, `+`)
+  
+  # log-sum of exponentiated utility, Output is n-length vector
+  log(rowSums(exp(V), na.rm = TRUE))
+}
+
+
+get_nearest <- function(impedance) {
+  
+}

### 2020-01-29 05_mental_health.Rmd
Initial mental health analysis

---
title: "Mental Health Analysis"
author: "Greg Macfarlane"
date: "12/6/2019"
output: html_document
---
```{r setup, include=FALSE, cache=FALSE}
knitr::opts_chunk$set(cache = TRUE)
library(tidyverse)
library(leaflet)
library(sf)
library(spatialreg)
library(spdep)
library(VGAM)
```

In this document, I explore whether the park accessibility scores we have
estimated previously are also correlated with mental health in the way that they
suggest a correlation with obesity.

## Mental Health Data
The CDC's *500 Cities* project contains modeled health outcome, prevention, and 
risk factor data at the census tract level for the 500 largest cities in the
United States. The modeled health outcomes include arthritis, asthma, diabetes, 
heart disease, etc. including mental health. This outcome is defined as:

> Respondents aged ≥18 years who report 14 or more days during the past 30 days
during which their mental health was not good.

The data are derived from the Behavioral Risk Factor Surveillance System (BRFSS)
surveys, which are then modeled to project estimates at small-scales. 
We obtained mental health data for tracts in New York City.

```{r loadtracts}
tracts <- read_rds("data/tracts_access.rds") %>%
  st_transform(4326)
tracts$mhealth <- read_rds("data/tracts.rds") %>% pull(mhealth)
```

The median population-weighted tract seems to have about 12% of people reporting 
poor mental health.

```{r mhealth-hist}
ggplot(tracts, aes(x = mhealth, weight = population)) +
  geom_histogram() + theme_bw() + 
  xlab("% in tract reporting 14 of last 30 days with poor mental health") + 
  ylab("Population-weighted tracts")
```

The places with the worst mental health appear to be concentrated in the Bronx
and in Brooklyn, and the best in Manhattan's upper east side. At first glance,
This would suggest it is heavily correlated with income.

```{r mhealth-map}
pal <- colorBin("viridis", n = 10, domain = tracts$mhealth)
leaflet(tracts) %>%
  addProviderTiles(providers$Esri.WorldGrayCanvas) %>%
  addPolygons(stroke = 0.5, color = ~pal(mhealth), fillOpacity = 0.6) %>%
  addLegend(pal = pal, values = ~mhealth)
```

## Accessibility

We can also calculate a utility-based accessibility score for each tract to the
parks in the region. This score includes the number of parks, the size of them,
whether the parks have trails, playgrounds, and ball fields / courts, and the
euclidean distance to the park from the population-weighted tract centroid.

```{r access_map}
# this interactive map is much easier to create and explore
pal <- colorBin("GnBu", c(tracts$access_ls, tracts$multi_ls), n = 5)
leaflet(tracts) %>%
  addProviderTiles(providers$Esri.WorldGrayCanvas) %>%
  addPolygons(group = "Kinner", color = ~ pal(multi_ls),
              label = ~as.character(round(multi_ls, 2))) %>%
  addLegend(pal = pal, values = ~multi_ls, title = "Access Score")
```

## Spatial model
We now estimate a SDEM model where mental health is a response to tract income,
ethnic makeup, age, and other factors. The SDEM model considers spatial spillovers
in the error term and in the independent variables but not in the depdendent variable,

$$ y = X\beta + WX\gamma + u, u = \lambda W u + \varepsilon$$

```{r W}
W <- read_rds("data/W.rds")
models <- read_rds("data/obesity_models.rds")

contiglagged_vars <- tracts %>%
  st_set_geometry(NULL) %>%
  as_tibble() %>%
  transmute_at(
    vars(density, income, fulltime, college, single, youth, young_adults, seniors, black, asian, hispanic, other, physact),
    ~lag.listw(W, ., zero.policy = TRUE)
  ) %>%
  mutate(geoid = tracts$geoid) %>%
  dplyr::select(geoid, everything())

names(contiglagged_vars)[-1] <- str_c("lag.", names(contiglagged_vars)[-1])
lagged_tracts <- tracts %>% left_join(contiglagged_vars, by = "geoid")
```

```{r models}
yj <- function(x) VGAM::yeo.johnson(x, lambda = 0)
mhealth_base <- spatialreg::errorsarlm(
  mhealth ~ yj(density) + yj(income)  + fulltime + college + single + 
    youth + young_adults + seniors + black + asian + hispanic + 
    other +  yj(lag.density) + yj(lag.income) + lag.fulltime + 
    lag.college + lag.single + lag.youth + lag.young_adults + 
    lag.seniors + lag.black + lag.asian + lag.hispanic + lag.other + 
    physact,
  data = lagged_tracts, listw = W, zero.policy = TRUE)
mhealth_accs <- update(mhealth_base, formula = . ~ . + multi_ls)
mhealth_models <- list(base = mhealth_base, access = mhealth_accs)
```

```{r show_models}
texreg::htmlreg(mhealth_models, digits = 5)
```

```{r tidied}
tidy.sarlm <- function(x){
  s <- summary(x)
  df <- length(s$residuals) - length(s$coefficients) - 1
  tibble(
    term = gsub("[\\(\\)]", "\\.", rownames(s$Coef)),
    estimate = s$Coef[,1],
    std.error = s$Coef[,2],
    statistic = estimate / std.error,
    p.value = 2*(pt(abs(statistic), Inf, lower.tail = FALSE))
  )
}

tidied <- lapply(mhealth_models, broom::tidy) %>%
  bind_rows(.id = "model")

```

The model results are suggestive ($p$ value = 
`r filter(tidied, term == "multi_ls") %>% pull(p.value)`). This is the same
outcome we found for the obesity models. But it is worth noting that physical
activity rates are highly correlated with mental health, and access to parks
*is* a strong predictor of physical activity.

```{r dwplot}
weird <- scales::trans_new("signed_log",
                           transform=function(x) sign(x)*sqrt(abs(x)),
                           inverse=function(x) sign(x)*(abs(x)^2))
tidied %>%
  filter(term != ".Intercept.") %>%
  dotwhisker::dw_plot() + 
  theme_bw() + 
  scale_x_continuous(trans = weird)
```

Let's look at some residuals

### 2020-01-29 presentations/mentalhealth/05_mentalhealth_slides.Rmd
Initial mental health analysis

---
title: "Park Access and Mental Health"
author: "Greg Macfarlane | Civil and Environmental Engineering"
date: "12/12/2019"
output: 
  ioslides_presentation:
    widescreen: true
---

```{r setup, include=FALSE, cache = FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = TRUE)
library(tidyverse)
library(leaflet)
library(sf)
library(spatialreg)
library(spdep)
library(VGAM)
library(here)
```

## Accessibility{.pause}

 - How close is my destination?
 - How many destinations can I get to?
 - What is the quality of the destinations I can access?

## Utility-based Accessibility
Choice theory: the total value of a choice set is
$$A_i = \ln\left(\sum_{j\in J}\exp(U_{ij})\right), \quad U_{ij} = \beta_s size_j + \beta_d distance_{ij} + \ldots$$

Where:

  - $U_{ij}$ is the *utility* of person $i$ choosing option $j$
  - $\beta$ represents preferences for an attribute
  - Any attributes can be included

# Mental Health and Parks in New York City

## CDC 500 Cities

  - Derived from the Behavioral Risk Factor Surveillance System (BRFSS)
  - Synthetic data / modeled with margin of error
  - Includes tract-level estimates of obesity rates, physical activity rates, etc. including mental health

<blockquote>
Respondents aged ≥18 years who report 14 or more days during the past 30 days
during which their mental health was not good.
</blockquote>

## Mental Health in NYC
```{r loadtracts, echo = FALSE}
tracts <- read_rds(here("data/tracts_access.rds")) %>%
  st_transform(4326)
tracts$mhealth <- read_rds(here("data/tracts.rds")) %>% pull(mhealth)
```

```{r mhealth-map, echo = FALSE, fig.width=10}
pal <- colorBin("viridis", n = 10, domain = tracts$mhealth)
leaflet(tracts) %>%
  addProviderTiles(providers$Esri.WorldGrayCanvas) %>%
  addPolygons(stroke = 0.5, color = ~pal(mhealth), fillOpacity = 0.6) %>%
  addLegend(pal = pal, values = ~mhealth)
```

## Park Access Data

Estimated values of utility from cellular phone data and from pre-existing
surveys of park use

## Park Access in NYC

```{r access_map, echo = FALSE, fig.width=10}
# this interactive map is much easier to create and explore
pal <- colorBin("GnBu", c(tracts$access_ls, tracts$multi_ls), n = 5)
leaflet(tracts) %>%
  addProviderTiles(providers$Esri.WorldGrayCanvas) %>%
  addPolygons(group = "Kinner", color = ~ pal(multi_ls),
              label = ~as.character(round(multi_ls, 2))) %>%
  addLegend(pal = pal, values = ~multi_ls, title = "Access Score")
```

## Preliminary Econometric Model

```{r mhealth_models, echo = FALSE, results = "asis", warning = FALSE}
mhealth_models <- read_rds(here("presentations/mentalhealth/models.rds"))
texreg::htmlreg(mhealth_models, digits = 4, single.row = TRUE,
                custom.coef.map = list(
                  "yj(density)" = "log(Density)",
                  "yj(income)"  = "log(Income)",
                  "physact" = "Physical Activity Rate",
                  "multi_ls" = "Access to Parks"
                ), include.aic = FALSE, include.nobs = FALSE,
                doctype = FALSE, caption = "", star.symbol = "\\*",
                custom.note = "%stars Standard errors in parentheses.")
```

Model also includes educational attainment, age categories, ethnic group
categories, and spatial spillovers.

## Next Steps

Get more detailed cellular phone, transportation, and land use data

  - Parks including amenities
  - Churches
  - Recreation centers
  - Mental health providers

Better mental health / suicide risk data?

### 2020-03-16 manuscript/manuscript.Rmd
Clean up adding appendix to end of paper
This brings in the appendix as a tex document instead of a markdown document. The tex document
needs to be edited to remove its tex preamble and final end{document} but it seems to work ok.

@@
       in_header: preamble.tex
-      after_body: appendix.md
+      after_body: appendix.tex
 bibliography: library.bib

### 2020-03-16 05_mental_health.Rmd

@@
 # this interactive map is much easier to create and explore
-pal <- colorBin("GnBu", c(tracts$access_ls, tracts$multi_ls), n = 5)
+pal <- colorBin("viridis", c(tracts$access_ls, tracts$multi_ls), n = 5)
 leaflet(tracts) %>%
@@
   addPolygons(group = "Kinner", color = ~ pal(multi_ls),
-              label = ~as.character(round(multi_ls, 2))) %>%
-  addLegend(pal = pal, values = ~multi_ls, title = "Access Score")
+              label = ~as.character(round(multi_ls, 2)), 
+              stroke = FALSE, fillOpacity = 0.7) %>%
+  addLegend(position = "topleft", pal = pal, values = ~multi_ls, title = "Access Score")
 ```
@@
 
-Let's look at some residuals
+### Utah Analysis
+
+```{r}
+tibble("Age" = c("18-25", "26-49", "50+"), "Serious MI" = c(7.5, 5.6, 2.7),
+       "Any MI" = c(25.8, 22.2, 13.8)) %>%
+  mutate(`Any MI` = `Any MI` - `Serious MI`) %>%
+  gather("Type of Mental Illness", "Percent", -Age) %>%
+  ggplot(aes(x = Age, y = Percent, fill = Malady)) +
+  geom_bar(stat = "identity")
+```
+
+Get 500 cities mental health data for Utah County
+
+```{r}
+cdc_urls <- list(
+  "mhealth" = "https://chronicdata.cdc.gov/resource/i2ek-k3pa.json?stateabbr=UT"
+)
+
+cdc500 <- lapply(cdc_urls, function(url){
+  read.socrata(url, app_token = Sys.getenv("CDC_KEY"),
+               stringsAsFactors = FALSE) %>%
+    tbl_df() %>%
+    filter(tractfips %in% acs$geoid) %>%
+    transmute( geoid = tractfips, value = as.numeric(data_value ), year = year)
+}) %>%
+  bind_rows(.id = "measure") 
+```
+
+Get block groups
+```{r}
+bg <- tigris::block_groups("Utah", "Utah", class = "sf") %>%
+  mutate(tract = substr(GEOID, 1, 11)) %>%
+  left_join(cdc500, by = c("tract" = "geoid"))
+```
+
+map
+
+```{r}
+pal <- colorNumeric(palette = "magma", bg$value)
+leaflet(bg) %>% addProviderTiles(providers$Esri.WorldGrayCanvas) %>% 
+  addPolygons(color = ~pal(value))
+```

### 2020-03-16 manuscript/manuscript.Rmd
Updated color palette and breaks, close #4

@@
   geom_sf(data = tracts, inherit.aes=FALSE,
-          aes(fill = cut(access_ls, breaks = c(-Inf, -3, -2, -1, 0, 2, 3, Inf))),
-          alpha = 0.8, color = NA) +
-  scale_fill_brewer("Accessibility", palette = "GnBu")
+          aes(fill = cut(access_ls, breaks = c(-Inf, -3, -2, -1, 0, 1, 2, 3, Inf))),
+          alpha = 0.9, color = NA) +
+  scale_fill_brewer("Accessibility", palette = "RdYlBu")
 ```

### 2020-03-16 manuscript/manuscript.Rmd
Update formulae
Reviewer 2 asked that we be more consistent with our use of matrix and vector annotation. This commit places an explicit boldsymbol around all the variables representing vectors in all equations. Closes #6

@@
 \begin{equation}\label{eq:utilityV}
-V_{ij} = X_j\beta + \beta_d * d_{ij}
+V_{ij} = X_j\boldsymbol{\beta} + \beta_d * d_{ij}
 \end{equation}
-The coefficients $\vect{\beta}$ are frequently estimated from household
+The coefficients $\boldsymbol{\beta}$ are frequently estimated from household
 surveys, though in the absence of a survey we may assert reasonable values.
@@
 Note that the gravity formulation is itself a special case of the utility-based
-specification where $\exp(X_j\beta + \beta_d d_{ij}) = X_j f(d_{ij})$
+specification where $\exp(X_j\boldsymbol{\beta} + \beta_d d_{ij}) = X_j f(d_{ij})$
 [@Daly1982]. The distinction between gravity and utility-based specification is
@@
 \begin{equation}\label{eq:v_logged}
-A_i' = \frac{A_i - \bar{A}}{sd(A)}
+A_i' = \frac{A_i - \bar{\boldsymbol{A}}}
+            {\sigma_{\boldsymbol{A}}}
 \end{equation}
@@
 \begin{equation}\label{eq:themodel}
- y = X\beta + \beta_{a}A + \varepsilon
+ \boldsymbol{y} = X\boldsymbol{\beta} + \beta_{a}\boldsymbol{A} + \boldsymbol{\varepsilon}
 \end{equation}
@@
 \begin{equation}\label{eq:autoregression}
- x = \rho W x + \varepsilon
+ \boldsymbol{x} = \rho W \boldsymbol{x} + \boldsymbol{\varepsilon}
 \end{equation}
@@
 the socioeconomic variables of neighboring tracts do not play a role. Mathematically, we assert that the autodependence
-relationship on the dependent variable $y = \rho W y + \ldots$ has 
+relationship on the dependent variable $\boldsymbol{y} = \rho W \boldsymbol{y} + \ldots$ has 
 $\rho = 0$ in the current case.
@@
 \begin{equation}\label{eq:SEM}
- y = X\beta + \beta_a A + u; u = \lambda W u + \varepsilon
+ \boldsymbol{y} = X\boldsymbol{\beta} + \beta_a \boldsymbol{A} + \boldsymbol{u}; \boldsymbol{u} = \lambda W \boldsymbol{u} + \boldsymbol{\varepsilon}
 \end{equation}
@@
 \begin{equation}\label{eq:SLX}
- y = X\beta + \beta_a A + W X \gamma + \varepsilon
+ \boldsymbol{y} = X\boldsymbol{\beta} + \beta_a \boldsymbol{A} + W X \boldsymbol{\gamma} + \boldsymbol{\varepsilon}
 \end{equation}
@@
 \begin{equation}\label{eq:SDEM}
- y = X\beta + \beta_a A + W X \gamma + u; u = \lambda W u + \varepsilon 
+ \boldsymbol{y} = X\boldsymbol{\beta} + \beta_a \boldsymbol{A} + W X \boldsymbol{\gamma} + \boldsymbol{u}; \boldsymbol{u} = \lambda W \boldsymbol{u} + \boldsymbol{\varepsilon}
 \end{equation}
@@
 $X$ model (SLX), and the spatial Durbin error model (SDEM). @Pace2008 suggest
-that a Hausman-style test of the estimates of $\beta$ derived from the OLS 
+that a Hausman-style test of the estimates of $\boldsymbol{\beta}$ derived from the OLS 
 (Equation \ref{eq:themodel}) and SEM (Equation \ref{eq:SEM}) can identify whether
-the estimates are consistent. If the $\beta$ estimates are dissimilar, both 
+the estimates are consistent. If the $\boldsymbol{\beta}$ estimates are dissimilar, both 
 specifications are inappropriate as they contain untreated omitted variables.
@@
 The coefficients in the SDEM model are of two general types: the direct effect
-resulting from a tract's own attributes and the indirect effect ($\gamma$)
+resulting from a tract's own attributes and the indirect effect ($\boldsymbol{\gamma}$)
 resulting from the spatially-weighted attributes of its neighbors. For example, a

### 2020-03-17 docs/R/impacts_extractor.R
Rebuild website without mental health information
This just complicates the information for now.

@@ -1,22 +1,0 @@
-#' Extract impacts estimates from a spatial lag model as a tidy dataframe
-#' 
-#' @param sdm A spatial lag model, estimated by lagsarlm
-impacts_extractor <- function(sdm, trMC) {
-  
-  impacts_summary <- summary(impacts(sdm, tr=trMC, R=1000), zstats = TRUE)
-  
-  coef <- list(
-    Direct = impacts_summary$direct_sum,
-    Indirect = impacts_summary$indirect_sum,
-    Total = impacts_summary$total_sum
-  ) %>%
-    lapply(function(s) {
-      tibble(
-        term = names(s$quantiles[,1]),
-        `2.5%` = s$quantiles[,1],
-        `50%` = s$quantiles[,3],
-        `97.5%` = s$quantiles[,5]
-      )
-    }) %>%
-    bind_rows(.id = "effect")
-}

### 2020-03-17 manuscript/appendix.Rmd
Add submission files
Remove Twitter analysis from manuscript
The models are still estimated and included in the website for future use and reference, but we can exclude them from the paper. Close #1.

@@
 output:
-  html_document:
-    keep_md: yes
+  pdf_document:
+    keep_tex: yes
 ---
@@
 pa_models <- read_rds(here("data/pa_models.rds"))
+pa_models$Tweets <- NULL
 obesity_models <- read_rds(here("data/obesity_models.rds"))
+obesity_models$Tweets <- NULL
 ```
@@
 lambda <- "$\\lambda$: spatial correlation"
-access_terms <- c("Size and Distance", "Tweets",  "Attributes", "10-min walk")
+access_terms <- c("Size and Distance", "Attributes", "10-min walk")
 
@@
 
+\begin{table*}
+  \caption{\label{tab:pa-fullmodels} Estimated Effect of Accessibility on Physical Activity Rates}
+  \begin{center}
+  \scalebox{0.7}{
 ```{r pa-fullmodels, results = "asis"}
@@
        custom.coef.names = c(names_for_terms, lambda, access_terms),
-       custom.model.names = c("No Access", access_terms),
-       caption = "Estimated Effect of Accessibility on Physical Activity Rates",
-       label = "tab:pa-fullmodels",
+       custom.model.names = c("No Access", access_terms), table = F,
        caption.above = TRUE, include.aic = F, include.lr = F,
-       scalebox = 0.7,
        custom.note = "%stars 95\\% confidence interval in brackets.")
 ```
+}\end{center}
+\end{table*}
 
+\begin{table*}
+  \caption{\label{tab:ob-fullmodels} Estimated Effect of Accessibility on Obesity Rates}
+  \begin{center}
+  \scalebox{0.7}{
 ```{r ob-fullmodels, results="asis"}
@@
        custom.coef.names = c(ob_names, lambda, access_terms),
-       custom.model.names = c("No Access", "Size and Distance", "Twitter", "Amenities", "10-Minute Walk"),
-       caption = "Estimated Effect of Accessibility on Physical Activity Rates",
-       label = "tab:ob-fullmodels",
-       caption.above = TRUE, include.aic = F, include.lr = F, scalebox = 0.7,
+       custom.model.names = c("No Access", access_terms), table = F,
+       caption.above = TRUE, include.aic = F, include.lr = F, 
        custom.note = "%stars 95\\% confidence interval in brackets.")
 ```
+}\end{center}
+\end{table*}

### 2020-03-17 manuscript/manuscript.Rmd
Remove Twitter analysis from manuscript
The models are still estimated and included in the website for future use and reference, but we can exclude them from the paper. Close #1.

@@
 we will refer to both parks and cemeteries as "parks" going forward. 
-For each park, 
-we calculate the size of the park in acres. Finally, using a Twitter application
-programming interface (API) implemented with the Python package Tweepy,  we also
-collected and stored tweets containing geotags of precise geographic coordinates
-located within the boundaries of the parks; from this information,
-we were able to segregate tweets that were generated within a park in September
-2014. This geolocated twitter activity could provide an additional point of information
-on the degree to which individual parks are actually used [@Wang2016].
+For each park, we calculate the size of the park in acres.
 
@@
   st_set_geometry(NULL) %>%
-  # TODO: This should be tweets
-  dplyr::select(acres, courts, playgrounds, trails, tweet_count) %>% 
+  dplyr::select(acres, courts, playgrounds, trails) %>% 
   gather(variable, value) %>%
@@
                  "Playgrounds: Presence of playgrounds",
-                 "Trails: Presence of trails",
-                 "Tweets: Tweets emanating from park in September 2014"),
-    source = c(rep("NYC", 4), "Twitter API")
+                 "Trails: Presence of trails"),
+    source = c(rep("NYC", 4))
   )
@@
 
-We calculate a set of utility-based accessibility statistics for each tract
+We calculate a pair of utility-based accessibility statistics for each tract
 in New York City. The most basic utility specification includes only the
@@
 
-The third utility specification includes the number of geolocated tweets
-emanating from within the park in September of 2014 in addition to the
-size and distance terms in Equation \ref{eq:u_access},
-\begin{equation}\label{eq:u_tweets}
-\begin{split}
-V_{ij} &= \lambda_s * \log(size_j) + \lambda_d * \log(distance_{ij}) + \\ 
-  &\quad \lambda_{tw} * YJ(tweets)
-\end{split}
-\end{equation}
-with $YJ(x)$ being a Yeo-Johnson transformation that implements a diminishing
-marginal return similar to $log(x)$, but where $YJ(0) = 0$ [@Yeo2000]. In this
-case we have no external information describing how destination choice to
-parks may be affected by the twitter activity in the park, so we assert a 
-value of $\lambda_{tw} = 0.1$
-
 We then calculate the utility-based accessibility of each tract $A_i$ as defined
@@
   geom_sf(data = tracts, inherit.aes=FALSE,
-          aes(fill = cut(access_ls, breaks = c(-Inf, -3, -2, -1, 0, 1, 2, 3, Inf))),
+          aes(fill = cut(multi_ls, breaks = c(-Inf, -3, -2, -1, 0, 1, 2, 3, Inf))),
           alpha = 0.9, color = NA) +
@@
 
-The specific spatial model applied is both an econometric choice
---- as improperly specified spatial models can lead to inconsistent estimates of
-model parameters and standard errors --- as well as a philosophical choice about
-the likely structure of spillovers in the problem at hand. In case of physical
+The specific spatial model applied is both an econometric choice --- as
+improperly specified spatial models can lead to inconsistent estimates of model
+parameters and standard errors --- as well as a philosophical choice about the
+likely structure of spillovers in the problem at hand. In case of physical
 activity and obesity rates, we believe that the outcomes are locally dependent:
 That is, a particular individual decides whether or not to participate in
-physical activity independently of whether his or her neighbors
-participate in physical activity. This does not mean that we think it impossible that
-the socioeconomic variables of neighboring tracts do not play a role. Mathematically, we assert that the autodependence
-relationship on the dependent variable $\boldsymbol{y} = \rho W \boldsymbol{y} + \ldots$ has 
-$\rho = 0$ in the current case.
+physical activity independently of whether his or her neighbors participate in
+physical activity. This does not mean that we think it impossible that the
+socioeconomic variables of neighboring tracts do not play a role.
+Mathematically, we assert that the autodependence relationship on the dependent
+variable $\boldsymbol{y} = \rho W \boldsymbol{y} + \ldots$ has $\rho = 0$ in the
+current case.
 
-With this relationship ruled out, it remains a possibility that the 
-model residuals are spatially dependent,
+With this relationship ruled out, it remains a possibility that the model
+residuals are spatially dependent,
 \begin{equation}\label{eq:SEM}
@@
 with increased utility-based accessiblity to green spaces show a significantly
-higher physical activity participation rate. Taking the rough mean of the three
+higher physical activity participation rate. Taking the rough mean of the 2
 estimated utility-based coefficients, moving from the least-accessible tract
@@
 most-accessible tract ($A_i = 3$) is expected to raise the physical activity rate
-by `r 6 * .2` percentage points. With the understanding of the full 95\% confidence
+by `r 6 * .15` percentage points. With the understanding of the full 95\% confidence
 interval, we could suggest that the true effect of excellent versus poor park access
-is anywhere between `r 6 * .05` and `r 6 * .35` percentage points.
+is anywhere between `r 6 * .02` and `r 6 * .3` percentage points.
 
@@
 outside of the buffer, the standard error of the estimated effect is large and implies
-an effect on activity rates anywhere from a loss of `r 6 * .37` percentage points
-to a gain of `r 6 * 1.5`.
+an effect on activity rates anywhere from a loss of `r 6 * .18` percentage points
+to a gain of `r 6 * 1.35`.
 
@@
 ```{r pa-models, results = "asis"}
-texreg(pa_models[c(2:5)], digits = 4, ci.force = TRUE,
+texreg(pa_models[c(2, 4:5)], digits = 4, ci.force = TRUE,
        booktabs = TRUE, use.packages = FALSE, 
-       custom.model.names = c("Size and Distance", "Twitter", "Amenities", "10-Minute Walk"),
+       custom.model.names = c("Size and Distance", "Amenities", "10-Minute Walk"),
        custom.coef.map = list(
@@
          "multi_ls" = "Amenities", 
-         "tweets_ls" = "Twitter Activity", 
          "walk_10TRUE" = "10-minute walk"),
@@
 ```{r obesity-models, results="asis"}
-texreg(obesity_models[c(2:5)], digits = 4, ci.force = TRUE, 
+texreg(obesity_models[c(2, 4:5)], digits = 4, ci.force = TRUE, 
        booktabs = TRUE, use.packages = FALSE, 
-       custom.model.names = c("Size and Distance", "Twitter", "Amenities", "10-Minute Walk"),
+       custom.model.names = c("Size and Distance", "Amenities", "10-Minute Walk"),
        custom.coef.map = list(
@@
 a neighborhood's accessibility to park features that its residents most care
-about. In this paper, we proceed only incrementally towards this by adding
-Twitter activity and some selected park amenities as an element of each park's 
+about. In this paper, we proceed only incrementally towards this by adding some
+selected park amenities as an element of each park's
 attractiveness above and beyond its size. Exploring detailed definitions of
@@
 This project was funded by the Speedwell Foundation. We are grateful to Rachel
-Samuels and Neda Madi for helping to assemble the geolocated Twitter data.
+Samuels and Neda Madi for helping to assemble the data.
 \end{acks}

### 2020-04-07 03_distances.Rmd
Started a python-based analysis with OSMNX
The osmnx package makes network-based calculations easier than anything I've seen before. It does point-to-point calculations, so this commit also contains a way to sample points along the edge of a park.

---
title: "Distances"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(reticulate)
use_condaenv("ox", conda = "~/opt/anaconda3/condabin/conda")
```

We want to calculate network-based distances between blocks in New York City
and the edges of parks.  In this document, we do the following:

  - Obtain a highway network for New York City from OpenStreetMap
  - Determine coordinates for block group centroids and park edge nodes
  - Compute the shortest path between the centroid and the nearest edge node.

To do this, we are going to use the `osmnx` library for  python.

```{python setup}
import osmnx as ox
import networkx as nx

import numpy as np
import pandas as pd
```

## OpenStreetMap

We use the `osmnx` library to get a highway network graph for New York City from 
OpenStreetMap. We

```{python graph}
B = ox.graph_from_place('New York, New York, USA', network_type='drive')
B_proj = ox.project_graph(B)
```

## Block Groups

We get a list of population-weighted block group centroids from Census.

```{python blockgroups}
# get the coordinates from census
url = "https://www2.census.gov/geo/docs/reference/cenpop2010/blkgrp/CenPop2010_Mean_BG36.txt"
blockgroups = pd.read_csv(url)

# pad the county and tract strings, and get the proper data types
blockgroups['COUNTYFP'] = blockgroups['COUNTYFP'].apply('{0:0>3}'.format)
blockgroups['TRACTCE'] = blockgroups['TRACTCE'].apply('{0:0>6}'.format)
blockgroups['LATITUDE'] = blockgroups['LATITUDE'].astype(float)
blockgroups['LONGITUDE'] = blockgroups['LONGITUDE'].astype(float)

# filter to nyc
nyc_counties = ["081", "047", "061", "005", "085"]
blockgroups = blockgroups[blockgroups.COUNTYFP.isin(nyc_counties)]
```

## Open Spaces

We want to calculate distance from the block group centroid to the nearest
edge of each open space. The open spaces data created on the 
[previous page](02_parks_data.html) is a detailed simple features layer with a
polygon for each open space. The `osmnx` graph needs to have point coordinates 
to calculate network-based distances, however. To make this work, we

 1. simplify the polygon geometry to reduce the number of edge vertices. We do this
 with a tolerance of 100 feet.
 2. convert the polygon geometry into a boundary linestring
 3. sample points on the linestring with a density of 1 point every 500 feet. Parks
 with a permeter of less than 500 feet will have a single point.

```{r simplify_spaces}
# get open spaces file
open_spaces <- read_rds("data/open_spaces.rds") %>%
  select(id)  %>%
  # some polygons are way too detailed, so we want to simplify to 100 foot resolution
  st_simplify(dTolerance = 100, preserveTopology = TRUE)

# some parks have multiple polygons. We need these to be simpler individual features 
poly_from_multi <- open_spaces %>%
  filter(st_geometry_type(geometry) == "MULTIPOLYGON") %>%
  st_cast("POLYGON")

linestrings <- open_spaces %>%
  # join the original polygons back with the simplified multipolygons
  filter(st_geometry_type(geometry) != "MULTIPOLYGON") %>%
  rbind(poly_from_multi) %>%
  # cast the polygons to a linestring of the park perimeter
  st_cast("LINESTRING", group_or_split = TRUE)

point_samples <- linestrings %>%
  # sample points along the line, one point per 500 feet.
  st_line_sample(density = 1/500)

# append open space id
open_space_points <- tibble(id = linestrings$id, geometry = point_samples) %>%
  st_as_sf() %>%
  st_cast(to = "POINT")
```

```{r simplified-point-map}
leaflet() %>%
  addProviderTiles(providers$OpenStreetMap) %>%
  addCircleMarkers(data = open_space_points %>% st_transform(4326), radius = 0.001,
                   color = "red") %>%
  addPolygons(data = open_spaces %>% st_transform(4326))
```

```{r}

```

### 2020-04-08 03_distances.Rmd
Find nearest node and shortest paths on network

@@
 import pandas as pd
+import time
+import multiprocessing as mp
 ```
@@
 We use the `osmnx` library to get a highway network graph for New York City from 
-OpenStreetMap. We
+OpenStreetMap. We get the walk network because most people in New York City will
+not be driving to get to their park.
 
 ```{python graph}
-B = ox.graph_from_place('New York, New York, USA', network_type='drive')
-B_proj = ox.project_graph(B)
+graph = ox.graph_from_place('New York, New York, USA', network_type='drive')
+graph_proj = ox.project_graph(graph)
 ```
@@
 # pad the county and tract strings, and get the proper data types
-blockgroups['COUNTYFP'] = blockgroups['COUNTYFP'].apply('{0:0>3}'.format)
-blockgroups['TRACTCE'] = blockgroups['TRACTCE'].apply('{0:0>6}'.format)
+blockgroups.STATEFP = blockgroups.STATEFP.apply(str)
+blockgroups.BLKGRPCE = blockgroups.BLKGRPCE.apply(str)
+blockgroups.COUNTYFP = blockgroups.COUNTYFP.apply('{0:0>3}'.format)
+blockgroups.TRACTCE = blockgroups.TRACTCE.apply('{0:0>6}'.format)
+blockgroups['GEOID'] = blockgroups[['STATEFP', 'COUNTYFP', 'TRACTCE', 'BLKGRPCE']].apply(lambda x: ''.join(x), axis = 1)
+
 blockgroups['LATITUDE'] = blockgroups['LATITUDE'].astype(float)
@@
 blockgroups = blockgroups[blockgroups.COUNTYFP.isin(nyc_counties)]
+blockgroups.set_index('GEOID', inplace=True)
 ```
@@
 point_samples <- linestrings %>%
-  # sample points along the line, one point per 500 feet.
-  st_line_sample(density = 1/500)
+  # sample points along the line, one point per 1000 feet.
+  st_line_sample(density = 1/1000)
 
@@
 ```
+
+The results of this data munging are given below. We have some issues where parks 
+made of multiple polygons end up with internal points. Trying to get rid of these
+by using complex hulls created other problems on linear parks. So we'll just go
+with this.
 
@@
 
-```{r}
+Get the data into a form that we can pass it into python.
+
+```{r park_points}
+park_points <- open_space_points %>%
+  st_transform(4326) %>%
+  mutate(
+    LONGITUDE = st_coordinates(.)[, 1],
+    LATITUDE = st_coordinates(.)[,2]
+  ) %>%
+  st_set_geometry(NULL) %>%
+  as_tibble()
+```
+
+## Distances
+
+First, we bring the park points we sampled into a pandas data frame with
+the park id as the index.
+```{python park_points_py}
+park_points = pd.DataFrame(r.park_points)
+# TODO: run for all park points
+park_ids = park_points.sample(5).id
+
+park_points.set_index('id', inplace=True)
+park_points = park_points.loc[park_ids]
 
 ```
+
+We already created the block group centroids data frame earlier. Let's get the
+nearest network nodes for each of the block groups and each park point.
+
+```{python park_bg_nodes}
+# TODO: run for all block groups
+blockgroups = blockgroups.sample(5)
+
+def findnode(df):
+  df['node'] = df.apply(lambda row: 
+    ox.get_nearest_node(graph, (row.LATITUDE, row.LONGITUDE)), axis=1)
+  return df
+
+def parallelize_dataframe(df, func, n_cores=4):
+  df_split = np.array_split(df, n_cores)
+  pool = Pool(n_cores)
+  df = pd.concat(pool.map(findnode, df_split))
+  pool.close()
+  pool.join()
+  return df
+
+a = time.process_time()
+findnode(blockgroups)
+findnode(park_points)
+b = time.process_time()
+b - a
+```
+
+We want to create a data structure that we can quickly populate with the 
+shortest path between a block group and the nearest park point. This is 
+probably a two-level dictionary.
+
+```{python blockgroup_dict}
+# Create a dictionary for the block groups
+blockgroup_dict = {}
+for i in blockgroups.index.unique():
+  blockgroup_dict[i] = {} # create a dictionary for the parks
+  for j in park_points.index.unique():
+    blockgroup_dict[i][j] = float("inf")
+
+```
+
+Now we want to loop through each block group and all of the park points to figure
+out what the shortest path is.
+
+```{python nearest}
+# loop through block groups
+a = time.process_time()
+for bg in blockgroups.itertuples():
+
+  # loop through parks
+  for park in park_ids:
+    these_points = park_points.loc[[park]]
+
+    # loop through points
+    for point in these_points.itertuples():
+      # get length between park and this edge point
+      length = nx.shortest_path_length(graph_proj, source = bg.node, target=point.node,
+        weight = 'length')
+
+      # check if this is the shortest one we've found; if so, update.
+      if length < blockgroup_dict[bg.Index][park]:
+        blockgroup_dict[bg.Index][park] = length
+
+b = time.process_time()
+b - a 
+```

### 2020-04-09 03_distances.Rmd
Add error handling and python script for data processing

@@
 library(reticulate)
-use_condaenv("ox", conda = "~/opt/anaconda3/condabin/conda")
+library(tidyverse)
+library(sf)
+library(leaflet)
+use_condaenv("ox", conda = "~/opt/anaconda3/condabin/conda", required = TRUE)
 ```
@@
 import time
-import multiprocessing as mp
 ```
@@
 ```{python graph}
-graph = ox.graph_from_place('New York, New York, USA', network_type='drive')
+graph = ox.graph_from_place('New York, New York, USA', network_type='walk')
 graph_proj = ox.project_graph(graph)
@@
 # TODO: run for all park points
-park_ids = park_points.sample(5).id
+park_ids = park_points.sample(2).id
 
@@
     ox.get_nearest_node(graph, (row.LATITUDE, row.LONGITUDE)), axis=1)
-  return df
-
-def parallelize_dataframe(df, func, n_cores=4):
-  df_split = np.array_split(df, n_cores)
-  pool = Pool(n_cores)
-  df = pd.concat(pool.map(findnode, df_split))
-  pool.close()
-  pool.join()
   return df
@@
       # get length between park and this edge point
+      try:
         length = nx.shortest_path_length(graph_proj, source = bg.node, target=point.node,
           weight = 'length')
+      except:
+        length = float("inf")
 
@@
 ```
+
+```{python write}
+park_points.to_csv("data/park_points.csv")
+blockgroups.to_csv("data/blockgroups.csv")
+```

### 2020-04-09 py/park_distances.py

@@ -1,0 +1,165 @@
+import sys
+
+import osmnx as ox
+import networkx as nx
+
+import numpy as np
+import pandas as pd
+import multiprocessing as mp
+import pickle
+
+
+def get_shortest_paths(blockgroups, park_points, graph, ddict):
+    """
+    :param blockgroups:
+    :param park_points:
+    :param graph:
+    :param ddict:
+    :return: dictionary
+    """
+    i = 1
+    for bg in blockgroups.itertuples():
+        # update progress
+        location = i / len(blockgroups) * 100
+        sys.stdout.write("Handling dictionary progress: %d%%  \r" % (location))
+        sys.stdout.flush()
+        i += 1
+
+        # loop through parks
+        for park in park_ids:
+            these_points = park_points.loc[[park]]
+
+            # loop through points
+            for point in these_points.itertuples():
+                # get length between park and this edge point
+                try:
+                    length = nx.shortest_path_length(graph_proj, source=bg.node, target=point.node,
+                                                     weight='length')
+                except:
+                    length = float("inf")
+
+                # check if this is the shortest one we've found; if so, update.
+                if length < ddict[bg.Index][park]:
+                    ddict[bg.Index][park] = length
+
+    return ddict
+
+
+def get_blockgroups(url, counties):
+    """
+    Get block group centroid data from the Census bureau
+    :param url:
+    :return:
+    """
+    # get the coordinates from census
+    blockgroups = pd.read_csv(url)
+
+    # pad the county and tract strings, and get the proper data types
+    blockgroups.STATEFP = blockgroups.STATEFP.apply(str)
+    blockgroups.BLKGRPCE = blockgroups.BLKGRPCE.apply(str)
+    blockgroups.COUNTYFP = blockgroups.COUNTYFP.apply('{0:0>3}'.format)
+    blockgroups.TRACTCE = blockgroups.TRACTCE.apply('{0:0>6}'.format)
+    blockgroups['GEOID'] = blockgroups[['STATEFP', 'COUNTYFP', 'TRACTCE', 'BLKGRPCE']].apply(lambda x: ''.join(x), axis=1)
+
+    blockgroups['LATITUDE'] = blockgroups['LATITUDE'].astype(float)
+    blockgroups['LONGITUDE'] = blockgroups['LONGITUDE'].astype(float)
+
+    # filter to counties
+    blockgroups = blockgroups[blockgroups.COUNTYFP.isin(counties)]
[…]

### 2020-04-11 03_distances.Rmd
Set up python script to take projected graph

@@
 graph = ox.graph_from_place('New York, New York, USA', network_type='walk')
-graph_proj = ox.project_graph(graph)
+# project to 18N, EPSG = 32618
+graph_proj = ox.project_graph(graph, to_crs="+proj=utm +zone=17 +ellps=WGS84 +datum=WGS84 +units=m +no_defs")
+graph_simple = nx.DiGraph(graph_proj)
 ```
@@
 park_points <- open_space_points %>%
-  st_transform(4326) %>%
+  st_transform(32618) %>%
   mutate(
@@
   as_tibble()
+
+write_csv(park_points, "data/park_points_nonode.csv")
 ```
@@
 # TODO: run for all park points
-park_ids = park_points.sample(2).id
+park_ids = park_points.sample(5).id
 

### 2020-04-11 py/park_distances.py

@@ -1,4 +1,5 @@
 import sys
+import os
 
 import osmnx as ox
 import networkx as nx
@@ -7,21 +8,40 @@ import numpy as np
 import pandas as pd
 import multiprocessing as mp
 import pickle
+import time
 
 
-def get_shortest_paths(blockgroups, park_points, graph, ddict):
+def get_shortest_paths(df):
     """
-    :param blockgroups:
-    :param park_points:
-    :param graph:
-    :param ddict:
+    :param df:
     :return: dictionary
     """
+    park_points = pd.read_csv("data/park_points.csv")
+    # TODO: remove sampling
+    park_sample_ids = park_points.sample(2).id
+    park_points.set_index('id', inplace=True)
+    park_points = park_points.loc[park_sample_ids]
+
+    park_ids = park_points.index.unique()
+
+    # get graph information
+    print("Getting graph information")
+    with open("data/graph.file", "rb") as f:
+        graph = pickle.load(f)
+
+    with open("data/graph_proj.file", "rb") as f:
+        graph_proj = pickle.load(f)
+
+    # output file
+    write_file = "data/shortest_paths_" + str(os.getpid()) + ".csv"
+    f = open(write_file, "w+")
+    f.write("geoid, park_id, distance\n")
+
     i = 1
-    for bg in blockgroups.itertuples():
+    for bg in df.itertuples():
         # update progress
-        location = i / len(blockgroups) * 100
-        sys.stdout.write("Handling dictionary progress: %d%%  \r" % (location))
+        location = i / len(df) * 100
+        sys.stdout.write("Getting block group %d, %d%% completed \r" % (i, location))
         sys.stdout.flush()
         i += 1
 
@@ -30,6 +50,7 @@ def get_shortest_paths(blockgroups, park_points, graph, ddict):
             these_points = park_points.loc[[park]]
 
             # loop through points
+            min_dist = float("inf")
             for point in these_points.itertuples():
                 # get length between park and this edge point
                 try:
@@ -39,10 +60,15 @@ def get_shortest_paths(blockgroups, park_points, graph, ddict):
                     length = float("inf")
 
                 # check if this is the shortest one we've found; if so, update.
-                if length < ddict[bg.Index][park]:
-                    ddict[bg.Index][park] = length
+                if length < min_dist:
+                    min_dist = length
 
-    return ddict
[…]

### 2020-04-11 py/park_distances.py
Introduce euclidean screening into shortest paths
If the distance to the park appears less than 5 kilometers, we get the network distance. Also use the Astar algorithm which showed itself to be 30% faster on a small sample.

@@ -3,6 +3,7 @@ import os
 
 import osmnx as ox
 import networkx as nx
+import math
 
 import numpy as np
 import pandas as pd
@@ -18,7 +19,7 @@ def get_shortest_paths(df):
     """
     park_points = pd.read_csv("data/park_points.csv")
     # TODO: remove sampling
-    park_sample_ids = park_points.sample(2).id
+    park_sample_ids = park_points.sample(5).id
     park_points.set_index('id', inplace=True)
     park_points = park_points.loc[park_sample_ids]
 
@@ -52,9 +53,17 @@ def get_shortest_paths(df):
             # loop through points
             min_dist = float("inf")
             for point in these_points.itertuples():
+                # check euclidean distance
+                dx = point.LONGITUDE - bg.LONGITUDE
+                dy = point.LATITUDE - bg.LATITUDE
+                euc_dist = math.sqrt(dx**2 + dy**2)
+                if euc_dist > 5000:
+                    min_dist = euc_dist
+                    break
+
                 # get length between park and this edge point
                 try:
-                    length = nx.shortest_path_length(graph_proj, source=bg.node, target=point.node,
+                    length = nx.astar_path_length(graph_proj, source=bg.node, target=point.node,
                                                      weight='length')
                 except:
                     length = float("inf")
@@ -171,7 +180,7 @@ if __name__ == "__main__":
     # get block groups
     blockgroups = pd.read_csv("data/blockgroups_nonode.csv")
     blockgroups.set_index('GEOID', inplace=True)
-    #blockgroups = blockgroups.sample(20)
+    blockgroups = blockgroups.sample(20)
 
     # get park points
     park_points = pd.read_csv("data/park_points_nonode.csv")
@@ -184,8 +193,10 @@ if __name__ == "__main__":
 
     # create dictionary to fill with shortest paths
     print("Getting shortest paths")
-    ddict = create_ddict(blockgroups.index.unique().array, park_points.index.unique().array)
+    a = time.process_time()
     get_shortest_paths(blockgroups)
+    b = time.process_time()
+    b-a
 
 
 

### 2020-04-11 py/park_distances.py
Use only the one graph

@@ -30,9 +30,6 @@ def get_shortest_paths(df):
     with open("data/graph.file", "rb") as f:
         graph = pickle.load(f)
 
-    with open("data/graph_proj.file", "rb") as f:
-        graph_proj = pickle.load(f)
-
     # output file
     write_file = "data/shortest_paths_" + str(os.getpid()) + ".csv"
     f = open(write_file, "w+")
@@ -63,7 +60,7 @@ def get_shortest_paths(df):
 
                 # get length between park and this edge point
                 try:
-                    length = nx.astar_path_length(graph_proj, source=bg.node, target=point.node,
+                    length = nx.shortest_path_length(graph, source=bg.node, target=point.node,
                                                      weight='length')
                 except:
                     length = float("inf")

### 2020-04-17 py/park_distances.py
Revise distance grabber to run in chunks

@@ -19,15 +19,15 @@ def get_shortest_paths(df):
     """
     park_points = pd.read_csv("data/park_points.csv")
     # TODO: remove sampling
-    park_sample_ids = park_points.sample(5).id
+    #park_sample_ids = park_points.sample(20).id
     park_points.set_index('id', inplace=True)
-    park_points = park_points.loc[park_sample_ids]
+    #park_points = park_points.loc[park_sample_ids]
 
     park_ids = park_points.index.unique()
 
     # get graph information
     print("Getting graph information")
-    with open("data/graph.file", "rb") as f:
+    with open("data/graph_proj.file", "rb") as f:
         graph = pickle.load(f)
 
     # output file
@@ -49,16 +49,19 @@ def get_shortest_paths(df):
 
             # loop through points
             min_dist = float("inf")
+            min_euc = float("inf")
             for point in these_points.itertuples():
                 # check euclidean distance
                 dx = point.LONGITUDE - bg.LONGITUDE
                 dy = point.LATITUDE - bg.LATITUDE
                 euc_dist = math.sqrt(dx**2 + dy**2)
-                if euc_dist > 5000:
-                    min_dist = euc_dist
+                # if the Euclidean distance is more than 5000 meters, we will just use that
+                if euc_dist > 3500:
+                    if euc_dist < min_euc:
+                      min_euc = euc_dist
                     break
 
-                # get length between park and this edge point
+                # If it's within 5km Euclidean, then we will get the network distance
                 try:
                     length = nx.shortest_path_length(graph, source=bg.node, target=point.node,
                                                      weight='length')
@@ -70,10 +73,12 @@ def get_shortest_paths(df):
                     min_dist = length
 
             # write out the length between the block group and this park
-            f.write(str(bg.Index) + ", " + str(park) + ", " + str(min_dist) + "\n")
+            used_distance = min(min_dist, min_euc)
+            f.write(str(bg.Index) + ", " + str(park) + ", " + str(used_distance) + "\n")
 
     # close the buffer
     f.close()
+    sys.stdout.write("\n ====== Finished ======\n")
 
 
 
@@ -114,7 +119,6 @@ def get_graph(place, mode, crs):
 
     # Get the graph and make it a non multigraph
     graph = ox.graph_from_place(place, network_type=mode)
[…]

### 2020-04-20 03_distances.Rmd
Clean up distances file

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(echo = TRUE, python.reticulate = FALSE, cache = TRUE)
 library(reticulate)
@@
 
-```{python setup}
+ > The python calculations in this page are illustrations of the methods
+ performed; the code is not actually literate as the computations do not complete 
+ in a reasonable amount of time. The actual python script is in [py/park_distances.py](py/park_distances.py)
+
+```{python setuppy}
 import osmnx as ox
@@
 import time
+import pickle
 ```
@@
 OpenStreetMap. We get the walk network because most people in New York City will
-not be driving to get to their park.
+not be driving to get to their park. We then project the network into UTM 17N 
+so that all paths will return in meters.
 
 ```{python graph}
-graph = ox.graph_from_place('New York, New York, USA', network_type='walk')
-# project to 18N, EPSG = 32618
-graph_proj = ox.project_graph(graph, to_crs="+proj=utm +zone=17 +ellps=WGS84 +datum=WGS84 +units=m +no_defs")
-graph_simple = nx.DiGraph(graph_proj)
+def get_graph(place, mode, crs):
+    """
+    Get a graph for the place and write both the original graph and the projected directed
+    graph to file
+    :param place:
+    :param mode: One of "drive", "walk", etc.
+    :return: OSMNX projected graph
+    """
+    # Get the graph and make it a non multigraph
+    graph = ox.graph_from_place(place, network_type=mode)
+    # write to file
+    with open("data/graph.file", "wb") as f:
+        pickle.dump(graph, f)
+    # project to UTM zone 18 N and simplify
+    graph_proj = ox.project_graph(graph, to_crs=crs)
+    graph_proj = nx.DiGraph(graph_proj)
+    with open("data/graph_proj.file", "wb") as f:
+        pickle.dump(graph_proj, f)
+    return graph_proj
+```
+
+An image of this graph is shown below, zoomed in on Midtown Manhattan / Columbus
+Circle.
+
+```{r columbus-circle}
+knitr::include_graphics("figs/nyc_network_columbus_circle.png")
 ```
@@
 
-We get a list of population-weighted block group centroids from Census.
+The tract and socioeconomic information is provided at the tract level, but we
+can calculate the accessibility at the block group level. We get a list of
+population-weighted block group centroids from Census, and transform them into 
+UTM17N coordinates.
 
-```{python blockgroups}
+```{r blockgroups}
 # get the coordinates from census
 url = "https://www2.census.gov/geo/docs/reference/cenpop2010/blkgrp/CenPop2010_Mean_BG36.txt"
-blockgroups = pd.read_csv(url)
-
-# pad the county and tract strings, and get the proper data types
-blockgroups.STATEFP = blockgroups.STATEFP.apply(str)
-blockgroups.BLKGRPCE = blockgroups.BLKGRPCE.apply(str)
-blockgroups.COUNTYFP = blockgroups.COUNTYFP.apply('{0:0>3}'.format)
-blockgroups.TRACTCE = blockgroups.TRACTCE.apply('{0:0>6}'.format)
-blockgroups['GEOID'] = blockgroups[['STATEFP', 'COUNTYFP', 'TRACTCE', 'BLKGRPCE']].apply(lambda x: ''.join(x), axis = 1)
-
-blockgroups['LATITUDE'] = blockgroups['LATITUDE'].astype(float)
-blockgroups['LONGITUDE'] = blockgroups['LONGITUDE'].astype(float)
-
-# filter to nyc
-nyc_counties = ["081", "047", "061", "005", "085"]
-blockgroups = blockgroups[blockgroups.COUNTYFP.isin(nyc_counties)]
-blockgroups.set_index('GEOID', inplace=True)
+bg <- read_csv(url, col_types = list(
+  STATEFP = col_character(),
+  COUNTYFP = col_character(),
+  TRACTCE = col_character(),
+  BLKGRPCE = col_character()
+)) %>%
+  filter(COUNTYFP %in% c("081", "047", "061", "005", "085")) %>%
+  transmute(GEOID = str_c(STATEFP, COUNTYFP, TRACTCE, BLKGRPCE),
+            LATITUDE, LONGITUDE) %>%
+  st_as_sf(coords = c("LONGITUDE", "LATITUDE"), crs = 4326) %>%
+  st_transform(32618) %>%
+    mutate(
+    LONGITUDE = st_coordinates(.)[, 1],
+    LATITUDE = st_coordinates(.)[,2]
+  ) %>%
+  st_set_geometry(NULL) %>%
+  as_tibble() %>%
+  write_csv("data/blockgroups_nonode.csv")
 ```
@@
 
-Get the data into a form that we can pass it into python.
+Now, we transform the points into UTM Zone 17N.
 
@@
 
-First, we bring the park points we sampled into a pandas data frame with
+In order to calculate the distances between the block group centroids and the 
+park edge points, we need to look up the nearest point on the network to each
+point.  First, we bring the park points we sampled into a pandas data frame with
 the park id as the index.
+
 ```{python park_points_py}
-park_points = pd.DataFrame(r.park_points)
-# TODO: run for all park points
-park_ids = park_points.sample(5).id
-
-park_points.set_index('id', inplace=True)
-park_points = park_points.loc[park_ids]
-
-```
-
-We already created the block group centroids data frame earlier. Let's get the
-nearest network nodes for each of the block groups and each park point.
-
-```{python park_bg_nodes}
-# TODO: run for all block groups
-blockgroups = blockgroups.sample(5)
-
-def findnode(df):
+def find_node(df):
+    """
+    Function to find the nearest node in a network to lat,long columns in data frame
+    :param df:  Pandas data frame with lat, long information
+    """
+    with open("data/graph_proj.file", "rb") as f:
+        graph = pickle.load(f)
     df['node'] = df.apply(lambda row:
@@
     return df
-
-a = time.process_time()
-findnode(blockgroups)
-findnode(park_points)
-b = time.process_time()
-b - a
 ```
 
-We want to create a data structure that we can quickly populate with the 
-shortest path between a block group and the nearest park point. This is 
-probably a two-level dictionary.
-
-```{python blockgroup_dict}
-# Create a dictionary for the block groups
-blockgroup_dict = {}
-for i in blockgroups.index.unique():
-  blockgroup_dict[i] = {} # create a dictionary for the parks
-  for j in park_points.index.unique():
-    blockgroup_dict[i][j] = float("inf")
-
-```
-
-Now we want to loop through each block group and all of the park points to figure
-out what the shortest path is.
+Now we get the shortest paths. The network is quite large with 122,794 nodes and
+381,656 edges. We also have `r nrow(bg)`  and `r nrow(park_points)`, meaning
+we need to find `r nrow(bg) * nrow(park_points)` shortest paths. Even on my beefy
+computer this can cause some problems. So we use the Euclidean distance if over 
+3.5 km, and only get the shortest paths for points less than 3.5km away.
 
@@
 # loop through block groups
-a = time.process_time()
-for bg in blockgroups.itertuples():
-
+def get_shortest_paths(df):
+    """
+    :param df:
+    """
+    # get graph information
+    print("Getting graph information")
+    with open("data/graph_proj.file", "rb") as f:
+        graph = pickle.load(f)
+    # output file
+    write_file = "data/shortest_paths_" + str(os.getpid()) + ".csv"
+    f = open(write_file, "w+")
+    f.write("geoid, park_id, distance\n")
+    for bg in df.itertuples():
         # loop through parks
@@
             these_points = park_points.loc[[park]]
-
             # loop through points
+            min_dist = float("inf")
+            min_euc = float("inf")
             for point in these_points.itertuples():
-      # get length between park and this edge point
+                # check euclidean distance
+                dx = point.LONGITUDE - bg.LONGITUDE
+                dy = point.LATITUDE - bg.LATITUDE
+                euc_dist = math.sqrt(dx**2 + dy**2)
+                # if the Euclidean distance is more than 3500 meters, we will just use that
+                if euc_dist > 3500:
+                    if euc_dist < min_euc:
+                      min_euc = euc_dist
+                    break
+                # If it's within 3500m Euclidean, then we will get the network distance
                 try:
-        length = nx.shortest_path_length(graph_proj, source = bg.node, target=point.node,
-          weight = 'length')
-      except:
+                    length = nx.shortest_path_length(graph, source=bg.node, target=point.node, weight='length')
+                except: # unless there is no path
                     length = float("inf")
-
                 # check if this is the shortest one we've found; if so, update.
-      if length < blockgroup_dict[bg.Index][park]:
-        blockgroup_dict[bg.Index][park] = length
-
-b = time.process_time()
-b - a 
+                if length < min_dist:
+                    min_dist = length
+            # write out the length between the block group and this park
+            used_distance = min(min_dist, min_euc)
+            f.write(str(bg.Index) + ", " + str(park) + ", " + str(used_distance) + "\n")
+    # close the buffer
+    f.close()
 ```
-
-```{python write}
-park_points.to_csv("data/park_points.csv")
-blockgroups.to_csv("data/blockgroups.csv")
-```

### 2020-04-20 docs/py/park_distances.py

@@ -1,0 +1,187 @@
+import sys
+import os
+
+import osmnx as ox
+import networkx as nx
+import math
+
+import numpy as np
+import pandas as pd
+import multiprocessing as mp
+import pickle
+import time
+
+
+def get_shortest_paths(df):
+    """
+    :param df:
+    :return: dictionary
+    """
+    park_points = pd.read_csv("data/park_points.csv")
+    # TODO: remove sampling
+    #park_sample_ids = park_points.sample(20).id
+    park_points.set_index('id', inplace=True)
+    #park_points = park_points.loc[park_sample_ids]
+
+    park_ids = park_points.index.unique()
+
+    # get graph information
+    print("Getting graph information")
+    with open("data/graph_proj.file", "rb") as f:
+        graph = pickle.load(f)
+
+    # output file
+    write_file = "data/shortest_paths_" + str(os.getpid()) + ".csv"
+    f = open(write_file, "w+")
+    f.write("geoid, park_id, distance\n")
+
+    i = 1
+    for bg in df.itertuples():
+        # update progress
+        location = i / len(df) * 100
+        sys.stdout.write("Getting block group %d, %d%% completed \r" % (i, location))
+        sys.stdout.flush()
+        i += 1
+
+        # loop through parks
+        for park in park_ids:
+            these_points = park_points.loc[[park]]
+
+            # loop through points
+            min_dist = float("inf")
+            min_euc = float("inf")
+            for point in these_points.itertuples():
+                # check euclidean distance
+                dx = point.LONGITUDE - bg.LONGITUDE
+                dy = point.LATITUDE - bg.LATITUDE
+                euc_dist = math.sqrt(dx**2 + dy**2)
+                # if the Euclidean distance is more than 5000 meters, we will just use that
+                if euc_dist > 3500:
+                    if euc_dist < min_euc:
+                      min_euc = euc_dist
+                    break
+
+                # If it's within 5km Euclidean, then we will get the network distance
+                try:
+                    length = nx.shortest_path_length(graph, source=bg.node, target=point.node,
+                                                     weight='length')
+                except:
+                    length = float("inf")
+
+                # check if this is the shortest one we've found; if so, update.
[…]

### 2020-04-20 02_parks_data.Rmd
Updates to build site
Fix problem with B527\r\nB527 parknum

@@
 parks <- st_read(parks_url, stringsAsFactors = FALSE) %>%
-  mutate(shape_area = as.numeric(shape_area))
+  mutate(
+    shape_area = as.numeric(shape_area),
+    parknum = ifelse(parknum == "B527\r\nB527", "B527", parknum) 
+  ) 
 ```
@@
 Now we write out the data for the future.
-```{r write}
+```{r writefiles}
 write_rds(open_spaces, "data/open_spaces.rds")

### 2020-04-20 04_accessibility.Rmd
Calculate logsum-based accessibilities

---
title: "Logsums"
author: "Greg Macfarlane"
date: "6/7/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = TRUE)
library(tidyverse)
library(sf)
library(leaflet)
library(lubridate)
library(VGAM)
```

In this document we calculate the utility-based measure of accessibility, as well
as the 10-minute walk buffer.

## Distances
We cleaned and gathered the data parks data and data for tracts in the previous
two pages, as well as computed the network-based distance between each block
group and the nearest edge point of each park.

```{r load, message=FALSE}
open_spaces <- read_rds("data/open_spaces.rds")
blockgroups <- read_csv("data/blockgroups.csv")

# tigris not working, manual download
#bg_poly <- tigris::block_groups("New York", county =  c("081", "047", "061", "005", "085"))
bg_poly <- st_read("/Users/gregmacfarlane/Library/Caches/tigris/tl_2019_36_bg.shp") %>%
  filter(GEOID %in% blockgroups$GEOID) %>%
  transmute(geoid = GEOID) %>%
  st_transform(32618)
```

In calculating the distances, two things could happen. First, it is possible that
no path is found between the park and the block group centroid; this could be the
result of network miscodings or other errors in the network algorithm. We'll have
to take the results as they come, and we simply remove the park from that block
group's accessibility calculation. The other issue is when a block group centroid
and the park edge point match to the *same* node, resulting in a distance of zero.
Because we are going to log-transform the distance, we add ten meters to all paths.

```{r distance_adjust}
distance_files <- list.files("data/nyc_shortest_paths_3500m/", full.names = TRUE)

read_all_files <- function(pattern = pattern, path = "./"){
  map_df(list.files(path = path, pattern = pattern, full.names = TRUE), read_csv,
         col_types = list(geoid = col_character(), park_id = col_character()))
}
distances <- read_all_files(".csv", "data/nyc_shortest_paths_3500m/") %>%
  # filter out infinite paths
  filter(!is.infinite(distance)) %>%
  # add ten meters to all paths
  mutate(distance = distance + 10)
```

Now we can calculate the utility specification. The first specification uses the
distance and size terms from the Alameda County study. The second specification
adds the amenities with the utilities found by the Kinnell et al. study.

```{r logsums}
logsums <- distances %>%
  left_join(open_spaces %>% st_set_geometry(NULL), by = c("park_id" = "id")) %>%
  mutate(
    distance_miles = (distance + 10) * 0.000621371,
    u_access = -1.768 * log(distance_miles) + 0.373 * log(as.numeric(acres)),
    u_multi = u_access + 
      open_spaces$trails * 0.99 + 
      open_spaces$playgrounds * 0.26 + 
      open_spaces$courts * 0.43
  ) %>%
  group_by(geoid) %>%
  summarise(
    access_ls = log(sum(exp(u_access), na.rm = TRUE)),
    multi_ls = log(sum(exp(u_multi), na.rm = TRUE))
  ) %>%
  mutate_at(
    vars(ends_with("_ls")),
    list(~ (. - mean(., na.rm = TRUE)) / sd(., na.rm = TRUE))
  )

bg_access <- bg_poly %>%
  left_join(logsums, by = "geoid")
```

## 10-minute buffer

We are also interested in looking at what happens when the tracts are within a 
10-minute walk of a park, the threshold established by the Trust for Public Lands.
This is interesting because whereas a limited number of tract centroids failed
to overlap with the 10-minute buffer, all of the block group centroids intersect.

## Accessibility Map
Here's a map of the values. Note that there is also a shiny app in this project
that allows the user to set different values for the logsum parameters.

```{r access_map}
# this interactive map is much easier to create and explore
pal <- colorQuantile("GnBu", c(bg_access$access_ls, bg_access$multi_ls), n = 5)
leaflet(bg_access %>% st_transform(4326)) %>%
  addProviderTiles(providers$Esri.WorldGrayCanvas) %>%
  addPolygons(group = "access", color = ~ pal(access_ls), stroke = 1,
              label = ~as.character(round(access_ls, 2))) %>%
  addPolygons(group = "Kinner", color = ~ pal(multi_ls), stroke = 1,
              label = ~as.character(round(multi_ls, 2))) %>%
  addLayersControl(overlayGroups = c("access", "Kinner"))
```

### 2020-04-20 01_health_data.Rmd
Repo cleanup
This includes a number of edits to the data elements related to switching the unit of analysis from tracts to block groups

@@
 
-```{r setup}
+```{r setup, cache = FALSE}
+knitr::opts_chunk$set(cache = TRUE)
 library(leaflet)

### 2020-04-20 R/logsums.R

@@ -1,25 +1,0 @@
-#' Calculate destination choice logsums from a distance matrix
-#'
-#' @param impedance An $n\times p$ matrix with the distance from all tracts to
-#'   all parks
-#' @param size_term A p-length vector of the park size terms
-#'
-#' @return An n-length vector containing the weighted log-sum based
-#'   accessibility between a tract and all parks.
-#' @details If we have n tracts and p parks, distances needs to be a
-#'
-calculate_park_logsums <- function(impedance, size_term){
-  
-  # calculate observed utility by adding the weighted park-level attributes
-  # to the columns of the matrix
-  # V is n x p, with b added by-column to each element in a
-  V <- sweep(impedance, 2, size_term, `+`)
-  
-  # log-sum of exponentiated utility, Output is n-length vector
-  log(rowSums(exp(V), na.rm = TRUE))
-}
-
-
-get_nearest <- function(impedance) {
-  
-}

### 2020-04-22 04_accessibility.Rmd
Repo cleanup
This includes a number of edits to the data elements related to switching the unit of analysis from tracts to block groups
Use 5000 meter threshold and remove blockgroups with no land

@@
 bg_poly <- st_read("/Users/gregmacfarlane/Library/Caches/tigris/tl_2019_36_bg.shp") %>%
-  filter(GEOID %in% blockgroups$GEOID) %>%
-  transmute(geoid = GEOID) %>%
+  transmute(geoid = GEOID, p_water = AWATER / (AWATER + ALAND)) %>%
+  filter(p_water < 1) %>%
+  filter(geoid %in% blockgroups$GEOID) %>%
   st_transform(32618)
@@
 }
-distances <- read_all_files(".csv", "data/nyc_shortest_paths_3500m/") %>%
+distances <- read_all_files(".csv", "data/nyc_shortest_paths_5000m/") %>%
   # filter out infinite paths
@@
 bg_access <- bg_poly %>%
-  left_join(logsums, by = "geoid")
+  left_join(logsums, by = "geoid") %>%
+  write_rds("data/bg_access.rds")
 ```

### 2020-04-27 05_estimation.Rmd
Remove inverse-distance matrix
The contiguous matrix should be sufficient

--- 2019-10-03 04_estimation.Rmd
@@
 
-```{r tracts}
-tracts_access <- read_rds("data/tracts_access.rds")
+```{r bg_access}
+bg_access <- read_rds("data/bg_access.rds")
 ```
 
-### Inverse distance weights
-My Atlanta house price study considered that houses within 1.8 miles of each
-other were "neighbors," with the strength of the relationship decaying with 
-the inverse of the distance between them. We can build the same matrix using 
-the population-weighted centroid of the tract as the observation point.
+The accessibility is calculated at the block group level, but the other information
+(health, demographics) is available only at the tract level.
 
-```{r Winv}
-pop_weighted_centroids <- read_rds("data/pop_weighted_centroids.rds")
-
-# determine which tracts are neighbors of each other. Need to be less than
-# 1.8 miles away from the centroids
-tracts.dnn <- dnearneigh(pop_weighted_centroids, 0, 1.8 * 5280)
-# calculate the inverse distance to use as a weight on the neighbor connection
-tract_dists <- nbdists(tracts.dnn, as(pop_weighted_centroids, "Spatial"))
-
-tract_dists.inv <- lapply(tract_dists, function(x) 1 / x)
-# get the spatial weights matrix and its trace to use in any impact analyses
-Winv <- nb2listw(neighbours = tracts.dnn, glist = tract_dists.inv,
-                 zero.policy = TRUE, style = "W")
-print(Winv, zero.policy = TRUE)
+```{r tracts}
+mydata <- bg_access %>% 
+  dplyr::mutate(tract = substr(geoid, 0, 11)) %>%
+  left_join(
+    read_rds("data/tracts.rds") %>%
+      st_set_geometry(NULL),
+    by = c("tract" = "geoid")
+  ) %>%
+  filter(!is.na(households))
 ```
@@
 ```{r Wcontig}
-tracts.adj <- poly2nb(tracts_access)
-Wcontig <- nb2listw(tracts.adj, style = "W", zero.policy = TRUE)
+areas_adj <- poly2nb(mydata)
+Wcontig <- nb2listw(areas_adj, style = "W", zero.policy = TRUE)
 print(Wcontig, zero.policy = TRUE)
@@
 ```{r ols_vs_sem}
-access_ols <- lm(update(base_formula, physact ~ . + access_ls), data = tracts_access)
-access_sem_wd <- errorsarlm(update(base_formula, physact ~ . + access_ls),
-                            data = tracts_access, listw = Winv, zero.policy = TRUE)
+access_ols <- lm(update(base_formula, physact ~ . + access_ls), data = mydata)
 access_sem_wc <- errorsarlm(update(base_formula, physact ~ . + access_ls),
-                            data = tracts_access, listw = Wcontig, zero.policy = TRUE)
+                            data = mydata, listw = Wcontig, zero.policy = TRUE)
 
-ols_vs_sem <- list("OLS" = access_ols, "SEM dist" = access_sem_wd, 
-                   "SEM cont" = access_sem_wd)
+ols_vs_sem <- list("OLS" = access_ols, "SEM" = access_sem_wc)
 ```
@@
 
-sp_hausman(access_ols, access_sem_wd)
 sp_hausman(access_ols, access_sem_wc)
@@
 ```{r access_slx}
-access_slx_wd <- lmSLX(update(base_formula, physact ~ . + access_ls), 
-                       data = tracts_access, listw = Winv, zero.policy = TRUE)
 access_slx_wc <- lmSLX(update(base_formula, physact ~ . + access_ls), 
-                       data = tracts_access, listw = Wcontig, zero.policy = TRUE)
-access_sdem_wd <- errorsarlm(update(base_formula, physact ~ . + access_ls),
-                            data = tracts_access, listw = Winv, zero.policy = TRUE,
-                            Durbin = TRUE)
+                       data = mydata, listw = Wcontig, zero.policy = TRUE)
 access_sdem_wc <- errorsarlm(update(base_formula, physact ~ . + access_ls),
-                            data = tracts_access, listw = Wcontig, zero.policy = TRUE, 
+                            data = mydata, listw = Wcontig, zero.policy = TRUE, 
                             Durbin = TRUE)
 slx_vs_sdem <- list(
-  "Dist SLX" = access_slx_wd, 
-  "Dist SDEM" = access_sdem_wd, 
-  "Contig SDEM" = access_sdem_wc,
-  "Contig SLX" = access_slx_wc
+  "SDEM" = access_sdem_wc,
+  "SLX" = access_slx_wc
 )
@@
 
-As before, we can try a Hausman-style test, but in this case the covariance
-matrix appears poorly defined and we therefore get a negative test statistic.
+As before, we can try a Hausman-style test.
 ```{r slx_hausman}
@@
 slx_hausman(access_slx_wc, access_sdem_wc)
-slx_hausman(access_slx_wd, access_sdem_wd)
 ```
@@
 ```{r lagged_vars}
-contiglagged_vars <- tracts_access %>%
-  st_set_geometry(NULL) %>%
+contiglagged_vars <- mydata %>%
   as_tibble() %>%
@@
   ) %>%
-  mutate(geoid = tracts_access$geoid) %>%
+  mutate(geoid = mydata$geoid) %>%
   dplyr::select(geoid, everything())
@@
 names(contiglagged_vars)[-1] <- str_c("lag.", names(contiglagged_vars)[-1])
-contiglagged_tracts <- tracts_access %>% left_join(contiglagged_vars, by = "geoid")
+contiglagged_data <- mydata %>% left_join(contiglagged_vars, by = "geoid")
 ```
@@
     lag.seniors + lag.black + lag.asian + lag.hispanic + lag.other + access_ls),
-  data = contiglagged_tracts)
+  data = contiglagged_data)
 
@@
     lag.seniors + lag.black + lag.asian + lag.hispanic + lag.other + access_ls), 
-  data = contiglagged_tracts, listw = Wcontig, zero.policy = TRUE)
+  data = contiglagged_data, listw = Wcontig, zero.policy = TRUE)
 ```
@@
 base_sdem <- update(access_sdem_wc, formula = . ~ . - access_ls,
-                    data = contiglagged_tracts, listw = Wcontig, zero.policy = TRUE)
+                    data = contiglagged_data, listw = Wcontig, zero.policy = TRUE)
 
@@
 pa_access_sdm <- access_sdem_wc
-pa_tweets_sdm  <- update(base_sdem, .~ . + tweets_ls)
 pa_multi_sdm   <- update(base_sdem, .~ . + multi_ls)
-pa_walk10_sdm  <- update(base_sdem, .~ . + walk_10)
 ```
@@
                   "Logsum"      = pa_access_sdm,
-                  "Tweets"      = pa_tweets_sdm,
-                  "Attributes"  = pa_multi_sdm,
-                  "10-min walk" = pa_walk10_sdm)
+                  "Attributes"  = pa_multi_sdm)
 ```

### 2020-04-27 04_accessibility.Rmd
Add distance check graphic
This check reveals plenty of inconsistencies with the blockgroup-based shortest distance calculations

@@
 ```{r distance_adjust}
-distance_files <- list.files("data/nyc_shortest_paths_3500m/", full.names = TRUE)
-
 read_all_files <- function(pattern = pattern, path = "./"){
@@
   mutate(distance = distance + 10)
+```
+
+```{r check-distances}
+check_id = "M010"
+check <- bg_poly %>%
+  left_join(distances %>% filter(park_id == check_id), by = "geoid") %>%
+  mutate(distance = log(distance + 10)) %>% 
+  st_transform(4326)
+park <- open_spaces %>% st_transform(4326) %>% filter(id == check_id)
+
+pal <- colorNumeric("plasma", check$distance)
+leaflet(check ) %>%
+  addProviderTiles(providers$Esri.WorldGrayCanvas) %>%
+  addPolygons(color = ~pal(distance) ) %>%
+  addPolygons(data = park, color = "green")
 ```

### 2020-05-05 03_distances.Rmd
Recompute euclidean distances
This computes Euclidean distances for block groups and tract centroids to park boundaries. The file is now too large to keep in Git.

--- 2020-04-09 03_distances.Rmd
@@
 ---
-title: "Distances"
+title: "03_distances"
 ---
@@
 knitr::opts_chunk$set(echo = TRUE)
-library(reticulate)
 library(tidyverse)
 library(sf)
-library(leaflet)
-use_condaenv("ox", conda = "~/opt/anaconda3/condabin/conda", required = TRUE)
+counties <- c("081", "047", "061", "005", "085")
 ```
 
-We want to calculate network-based distances between blocks in New York City
-and the edges of parks.  In this document, we do the following:
+A key aspect of accessibility to parks is the distance between parks and
+neighborhoods. There are two different ways to calculate distance:
 
-  - Obtain a highway network for New York City from OpenStreetMap
-  - Determine coordinates for block group centroids and park edge nodes
-  - Compute the shortest path between the centroid and the nearest edge node.
+   - *Euclidean* distances use the straight-line distance between two points.
+   - *Network* distances use the path along a highway or sidewalk network.
 
-To do this, we are going to use the `osmnx` library for  python.
+Both measurements have limitiations. Euclidean distances are particularly
+problematic when there are rivers, interstates, or other impassible features that
+substantially lengthen the distance people travel to get between points. On the
+other hand, there is not lots of data suggesting that people perceive network 
+travel times very well when they are choosing destinations. We originally
+estimated the models for this paper with Euclidean distances, but
+our reviewers suggested we examine network-based distances as well.
 
-```{python setup}
-import osmnx as ox
-import networkx as nx
+Another issue the reviewers identified is the spatial resolution of the analysis.
+We had used tracts, because this is where the socioeconomic and health data are 
+available. But block groups are more geographically precise, and it is possible
+for us to compute the accessibility at that level, if we assume that the 
+socioeconomics and health information is constant across the tract (this is not
+a good assumption, but we can entertain it for the purposes of the response to
+reviewers).
 
-import numpy as np
-import pandas as pd
-import time
+We will use the same parks dataset we assembled [previously](02_parks_data.html).
+
+```{r open_spaces}
+open_spaces <- read_rds("data/open_spaces.rds")
 ```
 
-## OpenStreetMap
+## Euclidean Distances
 
-We use the `osmnx` library to get a highway network graph for New York City from 
-OpenStreetMap. We get the walk network because most people in New York City will
-not be driving to get to their park.
+The geometric centroid of the tract / block group is not a good approximation of
+the center point of the tract from an accessibility standpoint. Thus, we 
+get the population-weighted centroid for tracts and block groups from Census.
 
-```{python graph}
-graph = ox.graph_from_place('New York, New York, USA', network_type='walk')
-graph_proj = ox.project_graph(graph)
+```{r tract_centroids}
+tracts_url <- "https://www2.census.gov/geo/docs/reference/cenpop2010/tract/CenPop2010_Mean_TR36.txt"
+
+tract_centroids <- read_csv(tracts_url) %>%
+  filter(COUNTYFP %in% counties) %>%
+  transmute(geoid = str_c(STATEFP, COUNTYFP, TRACTCE), LATITUDE, LONGITUDE) %>%
+  # convert to sf and project into the feet-based projection used in the
+  # parks dataset.
+  st_as_sf(crs = 4326, coords = c("LONGITUDE", "LATITUDE")) %>%
+  st_transform(3628) 
 ```
 
-## Block Groups
+```{r bg_centroids}
+bg_url <- "https://www2.census.gov/geo/docs/reference/cenpop2010/blkgrp/CenPop2010_Mean_BG36.txt"
 
-We get a list of population-weighted block group centroids from Census.
-
-```{python blockgroups}
-# get the coordinates from census
-url = "https://www2.census.gov/geo/docs/reference/cenpop2010/blkgrp/CenPop2010_Mean_BG36.txt"
-blockgroups = pd.read_csv(url)
-
-# pad the county and tract strings, and get the proper data types
-blockgroups.STATEFP = blockgroups.STATEFP.apply(str)
-blockgroups.BLKGRPCE = blockgroups.BLKGRPCE.apply(str)
-blockgroups.COUNTYFP = blockgroups.COUNTYFP.apply('{0:0>3}'.format)
-blockgroups.TRACTCE = blockgroups.TRACTCE.apply('{0:0>6}'.format)
-blockgroups['GEOID'] = blockgroups[['STATEFP', 'COUNTYFP', 'TRACTCE', 'BLKGRPCE']].apply(lambda x: ''.join(x), axis = 1)
-
-blockgroups['LATITUDE'] = blockgroups['LATITUDE'].astype(float)
-blockgroups['LONGITUDE'] = blockgroups['LONGITUDE'].astype(float)
-
-# filter to nyc
-nyc_counties = ["081", "047", "061", "005", "085"]
-blockgroups = blockgroups[blockgroups.COUNTYFP.isin(nyc_counties)]
-blockgroups.set_index('GEOID', inplace=True)
+bg_centroids <- read_csv(bg_url) %>%
+  filter(COUNTYFP %in% counties) %>%
+  transmute(geoid = str_c(STATEFP, COUNTYFP, TRACTCE, BLKGRPCE), LATITUDE, LONGITUDE) %>%
+  # convert to sf and project into the feet-based projection used in the
+  # parks dataset.
+  st_as_sf(crs = 4326, coords = c("LONGITUDE", "LATITUDE")) %>%
+  st_transform(3628) 
 ```
 
-## Open Spaces
+The `st_distance()` function from the `sf` library is able to compute the 
+Euclidean distance between two sets of shapes, and gets the distance between 
+points and edges of polygons directly. We calculate the distance in miles, 
+and constrain that the minimum distance is 0.1 miles (no one lives in a park).
 
-We want to calculate distance from the block group centroid to the nearest
-edge of each open space. The open spaces data created on the 
-[previous page](02_parks_data.html) is a detailed simple features layer with a
-polygon for each open space. The `osmnx` graph needs to have point coordinates 
-to calculate network-based distances, however. To make this work, we
+```{r distance_table}
+distance_table <- function(points, poly){
+  dists <- st_distance(points, poly, by_element = FALSE) %>%
+    units::set_units(miles) %>%
+    units::drop_units()
 
- 1. simplify the polygon geometry to reduce the number of edge vertices. We do this
- with a tolerance of 100 feet.
- 2. convert the polygon geometry into a boundary linestring
- 3. sample points on the linestring with a density of 1 point every 500 feet. Parks
- with a permeter of less than 500 feet will have a single point.
+  dists <- pmax(dists, 0.1)
 
-```{r simplify_spaces}
-# get open spaces file
-open_spaces <- read_rds("data/open_spaces.rds") %>%
-  select(id)  %>%
-  # some polygons are way too detailed, so we want to simplify to 100 foot resolution
-  st_simplify(dTolerance = 100, preserveTopology = TRUE)
+  rownames(dists) <- points$geoid
+  colnames(dists) <- poly$id
 
-# some parks have multiple polygons. We need these to be simpler individual features 
-poly_from_multi <- open_spaces %>%
-  filter(st_geometry_type(geometry) == "MULTIPOLYGON") %>%
-  st_cast("POLYGON")
+  as_tibble(dists, rownames = "geoid") %>%
+    pivot_longer(cols = -geoid, names_to = "park_id", values_to = "distance")
+}
 
-linestrings <- open_spaces %>%
-  # join the original polygons back with the simplified multipolygons
-  filter(st_geometry_type(geometry) != "MULTIPOLYGON") %>%
-  rbind(poly_from_multi) %>%
-  # cast the polygons to a linestring of the park perimeter
-  st_cast("LINESTRING", group_or_split = TRUE)
-
-point_samples <- linestrings %>%
-  # sample points along the line, one point per 1000 feet.
-  st_line_sample(density = 1/1000)
-
-# append open space id
-open_space_points <- tibble(id = linestrings$id, geometry = point_samples) %>%
-  st_as_sf() %>%
-  st_cast(to = "POINT")
+dist_tr_euc <- distance_table(tract_centroids, open_spaces)
+dist_bg_euc <- distance_table(bg_centroids,    open_spaces)
 ```
 
-The results of this data munging are given below. We have some issues where parks 
-made of multiple polygons end up with internal points. Trying to get rid of these
-by using complex hulls created other problems on linear parks. So we'll just go
-with this.
-
-```{r simplified-point-map}
-leaflet() %>%
-  addProviderTiles(providers$OpenStreetMap) %>%
-  addCircleMarkers(data = open_space_points %>% st_transform(4326), radius = 0.001,
-                   color = "red") %>%
-  addPolygons(data = open_spaces %>% st_transform(4326))
+```{r distances}
+list("tracts" = dist_tr_euc, "blockgroups" = dist_bg_euc) %>%
+  write_rds("data/distances.rds")
 ```
 
-Get the data into a form that we can pass it into python.
+## Network Distances
 
-```{r park_points}
-park_points <- open_space_points %>%
-  st_transform(4326) %>%
-  mutate(
-    LONGITUDE = st_coordinates(.)[, 1],
-    LATITUDE = st_coordinates(.)[,2]
-  ) %>%
-  st_set_geometry(NULL) %>%
-  as_tibble()
-```
-
-## Distances
-
-First, we bring the park points we sampled into a pandas data frame with
-the park id as the index.
-```{python park_points_py}
-park_points = pd.DataFrame(r.park_points)
-# TODO: run for all park points
-park_ids = park_points.sample(2).id
-
-park_points.set_index('id', inplace=True)
-park_points = park_points.loc[park_ids]
-
-```
-
-We already created the block group centroids data frame earlier. Let's get the
-nearest network nodes for each of the block groups and each park point.
-
-```{python park_bg_nodes}
-# TODO: run for all block groups
-blockgroups = blockgroups.sample(5)
-
-def findnode(df):
-  df['node'] = df.apply(lambda row: 
-    ox.get_nearest_node(graph, (row.LATITUDE, row.LONGITUDE)), axis=1)
-  return df
-
-a = time.process_time()
-findnode(blockgroups)
-findnode(park_points)
-b = time.process_time()
-b - a
-```
-
-We want to create a data structure that we can quickly populate with the 
-shortest path between a block group and the nearest park point. This is 
-probably a two-level dictionary.
-
-```{python blockgroup_dict}
-# Create a dictionary for the block groups
-blockgroup_dict = {}
-for i in blockgroups.index.unique():
-  blockgroup_dict[i] = {} # create a dictionary for the parks
-  for j in park_points.index.unique():
-    blockgroup_dict[i][j] = float("inf")
-
-```
-
-Now we want to loop through each block group and all of the park points to figure
-out what the shortest path is.
-
-```{python nearest}
-# loop through block groups
-a = time.process_time()
-for bg in blockgroups.itertuples():
-
-  # loop through parks
-  for park in park_ids:
-    these_points = park_points.loc[[park]]
-
-    # loop through points
-    for point in these_points.itertuples():
-      # get length between park and this edge point
-      try:
-        length = nx.shortest_path_length(graph_proj, source = bg.node, target=point.node,
-          weight = 'length')
-      except:
-        length = float("inf")
-
-      # check if this is the shortest one we've found; if so, update.
-      if length < blockgroup_dict[bg.Index][park]:
-        blockgroup_dict[bg.Index][park] = length
-
-b = time.process_time()
-b - a 
-```
-
-```{python write}
-park_points.to_csv("data/park_points.csv")
-blockgroups.to_csv("data/blockgroups.csv")
-```
+For this

### 2020-05-05 03_distances.Rmd
Calculate shortest path distances

@@
 ---
-title: "03_distances"
+title: "Distances"
 ---
@@
 
-For this
+To calculate network-based distances between block group / tract centroids and
+park boundaries, we employ the `osmnx` library for Python. This is a relatively
+new package that allows users to retrieve networks from OpenStreetMap and 
+compute shortest paths using Python's other network libraries. We retrieve
+a walk network for New York City, and re-project it to UTM zone 18N
+
+```py
+graph = ox.graph_from_place("New York City", network_type='walk')
+# project to UTM zone 18 N and simplify
+graph_proj = ox.project_graph(graph)
+graph_proj = nx.DiGraph(graph_proj)
+```
+
+One limitation of the network calculation is that it only works for nodes on the
+network, and we can only find nearest nodes to points. Thus we need to convert
+the park polygons data into points. But we can't simply have an endless number
+of points because the shortest path calculations are computationally extensive.
+
+So to make this work, we first simplify the parks polygons, convert the boundaries
+to linestrings, and then sample points along the linestring.
+
+```{r park_points, eval = FALSE}
+open_spaces <- open_spaces %>%
+  filter(id == "M010") %>%
+  select(id)  %>%
+  # some polygons are way too detailed, so we want to simplify to 100 foot resolution
+  st_simplify(dTolerance = 100, preserveTopology = TRUE)
+# some parks have multiple polygons. We need these to be simpler individual features 
+poly_from_multi <- open_spaces %>%
+  filter(st_geometry_type(geometry) == "MULTIPOLYGON") %>%
+  st_cast("POLYGON")
+linestrings <- open_spaces %>%
+  # join the original polygons back with the simplified multipolygons
+  filter(st_geometry_type(geometry) != "MULTIPOLYGON") %>%
+  rbind(poly_from_multi) %>%
+  # cast the polygons to a linestring of the park perimeter
+  st_cast("LINESTRING", group_or_split = TRUE) 
+point_samples <- linestrings %>%
+  # sample points along the line, one point per 1000 feet.
+  st_line_sample(density = 1/500) 
+# append open space id
+open_space_points <- tibble(id = linestrings$id, geometry = point_samples) %>%
+  st_as_sf() %>%
+  st_cast(to = "POINT")
+```
+
+```{r open_space_points, echo = FALSE}
+park_points <- read_csv("data/park_points.csv") %>%
+  st_as_sf(coords = c("LONGITUDE", "LATITUDE"), crs = 32618)
+```
+
+We can illustrate what this looks like. Every park has at least one sampled point,
+and some have several. Unfortunately there's not a concave polygon function to help
+us remove all the internal points from the parks.
+
+```{r simplified-point-map}
+leaflet() %>%
+  addProviderTiles(providers$Esri.WorldGrayCanvas) %>%
+  addPolygons(data = open_spaces %>% st_transform(4326), color = "green") %>%
+  addCircleMarkers(data = park_points %>% st_transform(4326), radius = 0.001,
+                   color = "red") 
+```
+
+With `r nrow(open_space_points)` and `r nrow(bg_centroids)`, that suggests we
+need to compute `r nrow(open_space_points) * nrow(bg_centroids)` shortest
+paths. Even on a 20+ core process, this would take several weeks.  As a result,
+we simplify the problem by first identifying the "closest" point of the park
+by Euclidean distance and then computing the network path to that point.
+This introduces some distortion where if the closest Euclidean point is across 
+a river or interstate, the method calculates the network distance to *that*
+point instead of the first point the person would encounter following the
+network. This may end up overstating the true experienced distance.
+
+```py
+# loop through centroids for block group or tract
+for bg in df.itertuples():
+
+    # loop through parks
+    for park in park_ids:
+        these_points = park_points.loc[[park]]
+        min_euc = float("inf")
+
+        # loop through points associated with park
+        for point in these_points.itertuples():
+            # find closest park point by Euclidean distance
+            dx = point.LONGITUDE - bg.LONGITUDE
+            dy = point.LATITUDE - bg.LATITUDE
+            euc_dist = math.sqrt(dx**2 + dy**2)
+
+            if euc_dist < min_euc:
+                min_euc = euc_dist
+                closest_point = point.node
+
+        # compute shortest path between closest_point and centroid
+        try:
+            length = nx.shortest_path_length(graph, source=bg.node, target=closest_point, weight='length')
+        except:
+            # can fail if no path exists
+            length = float("inf")
+```
+
+Calculated this way, the path is calculated in meters.

### 2020-05-05 py/park_distances.py

@@ -1,0 +1,173 @@
+import sys
+import os
+
+import osmnx as ox
+import networkx as nx
+import math
+
+import numpy as np
+import pandas as pd
+import multiprocessing as mp
+import pickle
+import time
+
+
+def get_shortest_paths(df):
+    """
+    :param df:
+    :return: dictionary
+    """
+    park_points = pd.read_csv("data/park_points.csv")
+    # TODO: remove sampling
+    #park_sample_ids = park_points.sample(20).id
+    park_points.set_index('id', inplace=True)
+    #park_points = park_points.loc[park_sample_ids]
+
+    park_ids = park_points.index.unique()
+
+    # get graph information
+    print("Getting graph information")
+    with open("data/graph_proj.file", "rb") as f:
+        graph = pickle.load(f)
+
+    # output file
+    write_file = "data/shortest_paths_" + str(os.getpid()) + ".csv"
+    f = open(write_file, "w+")
+    f.write("geoid, park_id, distance, euc_dist\n")
+
+    i = 1
+    for bg in df.itertuples():
+        # update progress
+        location = i / len(df) * 100
+        sys.stdout.write("Getting block group %d, %d%% completed \r" % (i, location))
+        sys.stdout.flush()
+        i += 1
+
+        # loop through parks
+        for park in park_ids:
+            these_points = park_points.loc[[park]]
+            min_euc = float("inf")
+
+            for point in these_points.itertuples():
+                # find closest park point by Euclidean distance
+                dx = point.LONGITUDE - bg.LONGITUDE
+                dy = point.LATITUDE - bg.LATITUDE
+                euc_dist = math.sqrt(dx**2 + dy**2)
+
+                if euc_dist < min_euc:
+                    min_euc = euc_dist
+                    closest_point = point.node
+
+            try:
+                length = nx.shortest_path_length(graph, source=bg.node, target=closest_point, weight='length')
+            except:
+                length = float("inf")
+
+            # write out the length between the block group and this park
+            f.write(str(bg.Index) + ", " + str(park) + ", " + str(length) + ", " + str(min_euc) + "\n")
+
+    # close the buffer
+    f.close()
+    sys.stdout.write("\n ====== Finished ======\n")
+
+
+
+def get_blockgroups(url, counties):
[…]

### 2020-05-05 01_health_data.Rmd
Clean up file names and headers

--- 2019-12-09 01_health_data.Rmd
@@
 title: "Health Data"
-author: "Greg Macfarlane"
-date: "6/6/2019"
-output: html_document
 ---
@@
                stringsAsFactors = FALSE) %>%
-    tbl_df() %>%
+    as_tibble() %>%
     filter(tractfips %in% acs$geoid) %>%

### 2020-05-05 04_accessibility.Rmd
Clean up file names and headers

--- 2020-04-20 04_accessibility.Rmd
@@
 title: "Logsums"
-author: "Greg Macfarlane"
-date: "6/7/2019"
-output: html_document
 ---
@@
 library(sf)
+library(spdep)
+library(spatialreg)
 library(leaflet)
@@
 
-In this document we calculate the utility-based measure of accessibility, as well
-as the 10-minute walk buffer.
+In this document we calculate the distance between each tract in New York City 
+and each park to help calculate a logsum-based measure of accessibility. We 
+cleaned and gathered the data in the previous two pages.
+
+```{r load}
+open_spaces <- read_rds("data/open_spaces.rds")
+tracts <- read_rds("data/tracts.rds")
+```
+
+We are going to do a point-to-polygon distance calculation. The geometric centroid
+of the tracts are not satisfying, so we will use the population-weighted centroid
+instead.
+
+```{r pop_weighted_centroids}
+pop_weighted_centroids <- tracts %>% as_tibble() %>%
+  dplyr::select(geoid) %>%
+  left_join(
+    read_csv("https://www2.census.gov/geo/docs/reference/cenpop2010/tract/CenPop2010_Mean_TR36.txt") %>%
+      transmute(geoid = str_c(STATEFP, COUNTYFP, TRACTCE), LATITUDE, LONGITUDE)
+  ) %>%
+  # convert to sf and project into the feet-based projection used in the
+  # parks dataset.
+  st_as_sf(crs = 4326, coords = c("LONGITUDE", "LATITUDE")) %>%
+  st_transform(3628) %>%
+  write_rds("data/pop_weighted_centroids.rds")
+
+```
+
+The population-weighted centroid also serves as the orientation for the spatial
+weights matrix.
+
+```{r W}
+# determine which tracts are neighbors of each other. Need to be less than
+# 1.8 miles away from the centroids
+tracts.dnn <- dnearneigh(as(pop_weighted_centroids, "Spatial"), 0, 1.8 * 5280)
+# calculate the inverse distance to use as a weight on the neighbor connection
+tract_dists <- nbdists(tracts.dnn, as(pop_weighted_centroids, "Spatial"))
+write_rds(tract_dists, "data/tract_distances.rds")
+```
 
 ## Distances
-We cleaned and gathered the data parks data and data for tracts in the previous
-two pages, as well as computed the network-based distance between each block
-group and the nearest edge point of each park.
+We want to make sure that the distance between a park and a tract centroid is
+based on the edge of the polygon instead of the centroid thereof, so that spaces
+at the corners of Central park, for instance, don't appear as longer than they should be.
+It seems that things are working appropriately.
 
-```{r load, message=FALSE}
-open_spaces <- read_rds("data/open_spaces.rds")
-blockgroups <- read_csv("data/blockgroups.csv")
+```{r test_measurement}
+central_park <- open_spaces %>% filter(name == "Central Park")
+pop_weighted_centroids$central_park <- log(as.numeric(st_distance(pop_weighted_centroids, central_park)))
 
-# tigris not working, manual download
-#bg_poly <- tigris::block_groups("New York", county =  c("081", "047", "061", "005", "085"))
-bg_poly <- st_read("/Users/gregmacfarlane/Library/Caches/tigris/tl_2019_36_bg.shp") %>%
-  filter(GEOID %in% blockgroups$GEOID) %>%
-  transmute(geoid = GEOID) %>%
-  st_transform(32618)
+dmeasure <- colorNumeric(palette = "Blues", domain = pop_weighted_centroids$central_park)
+leaflet(pop_weighted_centroids %>% st_transform(4326)) %>%
+  addProviderTiles(providers$Esri.WorldGrayCanvas) %>%
+  addCircleMarkers(color = ~dmeasure(central_park))
 ```
 
-In calculating the distances, two things could happen. First, it is possible that
-no path is found between the park and the block group centroid; this could be the
-result of network miscodings or other errors in the network algorithm. We'll have
-to take the results as they come, and we simply remove the park from that block
-group's accessibility calculation. The other issue is when a block group centroid
-and the park edge point match to the *same* node, resulting in a distance of zero.
-Because we are going to log-transform the distance, we add ten meters to all paths.
+Now we can calculate the distance from every park to every tract population
+centroid, and write the distances and neighbors weights matrix to a file.
+```{r distances}
+# distances from all tract centroids to all parks
+distances <- st_distance(pop_weighted_centroids, open_spaces, byid = TRUE) %>%
+  units::set_units(miles) %>%
+  units::drop_units()
 
-```{r distance_adjust}
-distance_files <- list.files("data/nyc_shortest_paths_3500m/", full.names = TRUE)
+# assert that a tract must be at least 1/10 mile from a park
+distances <- pmax(distances, 0.1)
+rownames(distances) <- pop_weighted_centroids$geoid
+colnames(distances) <- open_spaces$id
 
-read_all_files <- function(pattern = pattern, path = "./"){
-  map_df(list.files(path = path, pattern = pattern, full.names = TRUE), read_csv,
-         col_types = list(geoid = col_character(), park_id = col_character()))
-}
-distances <- read_all_files(".csv", "data/nyc_shortest_paths_3500m/") %>%
-  # filter out infinite paths
-  filter(!is.infinite(distance)) %>%
-  # add ten meters to all paths
-  mutate(distance = distance + 10)
+distance_df <- distances %>%
+  as_tibble(rownames = "geoid") %>%
+  pivot_longer(cols = -geoid, names_to = "park_id", values_to = "distance")
+
+write_rds(distances, "data/distances.rds")
 ```
 
-Now we can calculate the utility specification. The first specification uses the
-distance and size terms from the Alameda County study. The second specification
-adds the amenities with the utilities found by the Kinnell et al. study.
+## Logsums
 
-```{r logsums}
-logsums <- distances %>%
-  left_join(open_spaces %>% st_set_geometry(NULL), by = c("park_id" = "id")) %>%
+Here's the function we use to calculate the logsums. 
+```{r calculate_park_logsums}
+source("R/logsums.R")
+print(calculate_park_logsums)
+```
+
+We use this function with asserted beta values of -1.768 and 0.373 to calculate the
+accessibility logsum.
+
+```{r logsum_vars}
+logsums <- distance_df %>%
+  left_join(
+    open_spaces %>% 
+      transmute(
+        park_id = id, acres,
+        tweet_count, trails, playgrounds, courts,
+      ) %>% 
+      st_set_geometry(NULL),  
+    by = "park_id"
+  ) %>%
   mutate(
-    distance_miles = (distance + 10) * 0.000621371,
-    u_access = -1.768 * log(distance_miles) + 0.373 * log(as.numeric(acres)),
+    u_access = log(distance)*-1.768 + log(acres) * 0.373,
     u_multi  = u_access + 
-      open_spaces$trails * 0.99 + 
-      open_spaces$playgrounds * 0.26 + 
-      open_spaces$courts * 0.43
+      trails * 0.99 +  
+      playgrounds * 0.26 +  
+      courts * 0.43,
+    u_tweets = u_access + 0.1 * yeo.johnson(tweet_count, lambda = 0),
   ) %>%
@@
   summarise(
-    access_ls = log(sum(exp(u_access), na.rm = TRUE)),
-    multi_ls = log(sum(exp(u_multi), na.rm = TRUE))
+    access_ls = log(sum(exp(u_access))),
+    multi_ls = log(sum(exp(u_multi))),
+    tweets_ls = log(sum(exp(u_tweets)))
   ) %>%
-  mutate_at(
-    vars(ends_with("_ls")),
-    list(~ (. - mean(., na.rm = TRUE)) / sd(., na.rm = TRUE))
-  )
+  mutate_at(.vars = c("access_ls", "multi_ls", "tweets_ls"),  ~ (. - mean(.)) / sd(.))
 
-bg_access <- bg_poly %>%
+logsum_vars <- tracts %>%
   left_join(logsums, by = "geoid")
@@
 
-## 10-minute buffer
-
 We are also interested in looking at what happens when the tracts are within a 
 10-minute walk of a park, the threshold established by the Trust for Public Lands.
-This is interesting because whereas a limited number of tract centroids failed
-to overlap with the 10-minute buffer, all of the block group centroids intersect.
+```{r nyc10mw}
+access_10mw <- st_read("data/nyc_10mw.geojson") %>%
+  summarise(d = 1)
 
-## Accessibility Map
-Here's a map of the values. Note that there is also a shiny app in this project
-that allows the user to set different values for the logsum parameters.
+inside_access <- pop_weighted_centroids %>%
+  st_transform(4326) %>%
+  st_join(access_10mw, st_intersects) %>%
+  filter(!is.na(d))
 
+tracts_access <- tracts %>%
+  left_join(logsum_vars, by = "geoid") %>%
+  mutate(walk_10 = ifelse(geoid %in% inside_access$geoid, TRUE, FALSE)) %>%
+  write_rds("data/tracts_access.rds")
+```
+
+Here's a map of the values. Note that there is also a shiny app in this project that
+allows the user to set different values for the logsum parameters.
 ```{r access_map}
 # this interactive map is much easier to create and explore
-pal <- colorQuantile("GnBu", c(bg_access$access_ls, bg_access$multi_ls), n = 5)
-leaflet(bg_access %>% st_transform(4326)) %>%
+pal <- colorQuantile("GnBu", c(tracts_access$access_ls, tracts_access$multi_ls), n = 5)
+bin <- colorFactor("Dark2", tracts_access$walk_10)
+leaflet(tracts_access) %>%
   addProviderTiles(providers$Esri.WorldGrayCanvas) %>%
-  addPolygons(group = "access", color = ~ pal(access_ls), stroke = 1,
+  addPolygons(group = "access", color = ~ pal(access_ls),
               label = ~as.character(round(access_ls, 2))) %>%
-  addPolygons(group = "Kinner", color = ~ pal(multi_ls), stroke = 1,
+  addPolygons(group = "tweets", color = ~ pal(tweets_ls),
+              label = ~as.character(round(tweets_ls, 2))) %>%
+  addPolygons(group = "Kinner", color = ~ pal(multi_ls),
               label = ~as.character(round(multi_ls, 2))) %>%
-  addLayersControl(overlayGroups = c("access", "Kinner"))
+  addPolygons(group = "10-minute walk", color = ~ bin(walk_10)) %>%
+  addLayersControl(baseGroups = c("access", "tweets", "Kinner", "10-minute walk"))
 ```

### 2020-05-08 03_distances.Rmd
Repair park points creator, and rewrite points files

@@
 compute shortest paths using Python's other network libraries. We retrieve
-a walk network for New York City, and re-project it to UTM zone 18N
+a walk network for New York City, and re-project it to UTM zone 18N.
 
@@
 ```{r park_points, eval = FALSE}
-open_spaces <- open_spaces %>%
-  filter(id == "M010") %>%
+# get park boundary polygon
+park_boundaries <- open_spaces %>%
   select(id)  %>%
+
   # some polygons are way too detailed, so we want to simplify to 100 foot resolution
-  st_simplify(dTolerance = 100, preserveTopology = TRUE)
-# some parks have multiple polygons. We need these to be simpler individual features 
-poly_from_multi <- open_spaces %>%
-  filter(st_geometry_type(geometry) == "MULTIPOLYGON") %>%
-  st_cast("POLYGON")
-linestrings <- open_spaces %>%
-  # join the original polygons back with the simplified multipolygons
-  filter(st_geometry_type(geometry) != "MULTIPOLYGON") %>%
-  rbind(poly_from_multi) %>%
+  st_simplify(dTolerance = 100, preserveTopology = TRUE) %>%
+
+  # need to convert everything to multipolygons to get multiple rows per shape
+  st_cast("MULTIPOLYGON") %>%
+
+  st_cast("POLYGON") %>%
+
   # cast the polygons to a linestring of the park perimeter
   st_cast("LINESTRING", group_or_split = TRUE)
-point_samples <- linestrings %>%
-  # sample points along the line, one point per 1000 feet.
+
+point_samples <- park_boundaries %>%
+  # sample points along the line, one point per 500 feet.
   st_line_sample(density = 1/500)
-# append open space id
-open_space_points <- tibble(id = linestrings$id, geometry = point_samples) %>%
+
+# append open space id and coerce to single point per row
+park_points <- st_sf(id = park_boundaries$id, geometry = point_samples)  %>%
   st_as_sf() %>%
   st_cast(to = "POINT")
-```
-
-```{r open_space_points, echo = FALSE}
-park_points <- read_csv("data/park_points.csv") %>%
-  st_as_sf(coords = c("LONGITUDE", "LATITUDE"), crs = 32618)
 ```
@@
 Calculated this way, the path is calculated in meters.
+
+```{r write_python_files}
+
+write_points_file <- function(points, file){
+  points %>% 
+    st_transform(4326) %>%
+    mutate(
+      LATITUDE = st_coordinates(.)[, 2],
+      LONGITUDE = st_coordinates(.)[, 1]
+    ) %>%
+    st_transform(32618) %>%
+    mutate(
+      Y = st_coordinates(.)[, 2],
+      X = st_coordinates(.)[, 1]
+    ) %>%
+    st_set_geometry(NULL) %>%
+    write_csv(file)
+}
+
+park_points     %>% write_points_file("data/park_points.csv")
+bg_centroids    %>% write_points_file("data/bg_centroids.csv")
+tract_centroids %>% write_points_file("data/tract_centroids.csv")
+
+```

### 2020-05-08 py/park_distances.py
Revise shortest path calculator
Apparently we need to do a few different things to make the osmnx package do what we need it to do. First, the euclidean calculation needs to happen with projected coordinates, and the route needs to happen on a projected network. BUT.... the nearest node lookup has to happen on the lat/long network with lat/long coordinates. Very confusing. 

I did take this opportunity, however, to successfully implement multicore processing in the script. You need about 1.5 GB per thread to store the network information, but Beast shouldn't have any issues running that.

@@ -19,16 +19,16 @@ def get_shortest_paths(df):
     """
     park_points = pd.read_csv("data/park_points.csv")
     # TODO: remove sampling
+    #park_sample_ids = "M010"
     #park_sample_ids = park_points.sample(20).id
     park_points.set_index('id', inplace=True)
     #park_points = park_points.loc[park_sample_ids]
-
     park_ids = park_points.index.unique()
 
     # get graph information
     print("Getting graph information")
-    with open("data/graph_proj.file", "rb") as f:
-        graph = pickle.load(f)
+    graph = ox.graph_from_place('New York City, New York, USA', network_type='walk')
+    G = ox.project_graph(graph)
 
     # output file
     write_file = "data/shortest_paths_" + str(os.getpid()) + ".csv"
@@ -38,28 +38,31 @@ def get_shortest_paths(df):
     i = 1
     for bg in df.itertuples():
         # update progress
-        location = i / len(df) * 100
+        location = (i - 1) / len(df) * 100
         sys.stdout.write("Getting block group %d, %d%% completed \r" % (i, location))
         sys.stdout.flush()
         i += 1
 
+        source = ox.get_nearest_node(graph, (bg.LATITUDE, bg.LONGITUDE))
         # loop through parks
         for park in park_ids:
             these_points = park_points.loc[[park]]
             min_euc = float("inf")
 
             for point in these_points.itertuples():
-                # find closest park point by Euclidean distance
-                dx = point.LONGITUDE - bg.LONGITUDE
-                dy = point.LATITUDE - bg.LATITUDE
+                # find closest park point by Euclidean distance in projected coordinates
+                dx = point.X - bg.X
+                dy = point.Y - bg.Y
                 euc_dist = math.sqrt(dx**2 + dy**2)
 
                 if euc_dist < min_euc:
                     min_euc = euc_dist
-                    closest_point = point.node
+                    closest_lat = point.LATITUDE
+                    closest_lon = point.LONGITUDE
 
             try:
-                length = nx.shortest_path_length(graph, source=bg.node, target=closest_point, weight='length')
+                target = ox.get_nearest_node(graph, (closest_lat, closest_lon))
[…]

### 2020-05-11 04_accessibility.Rmd
Restructure accessibility calculation
This makes better use of the tidyverse, simplifying the logsum code. Also, discusses Euclidean vs network distance in more detail.

--- 2020-04-22 04_accessibility.Rmd
@@
 
-In this document we calculate the utility-based measure of accessibility, as well
-as the 10-minute walk buffer.
+In this document we calculate the accessiblity logsums based on the Euclidean
+and network distances from the tract and block group centroids to the tract,
+combined with park attributes.
 
-## Distances
-We cleaned and gathered the data parks data and data for tracts in the previous
-two pages, as well as computed the network-based distance between each block
-group and the nearest edge point of each park.
-
-```{r load, message=FALSE}
+```{r load}
+tracts <- read_rds("data/tracts.rds")
 open_spaces <- read_rds("data/open_spaces.rds")
-blockgroups <- read_csv("data/blockgroups.csv")
-
-# tigris not working, manual download
-#bg_poly <- tigris::block_groups("New York", county =  c("081", "047", "061", "005", "085"))
-bg_poly <- st_read("/Users/gregmacfarlane/Library/Caches/tigris/tl_2019_36_bg.shp") %>%
-  transmute(geoid = GEOID, p_water = AWATER / (AWATER + ALAND)) %>%
-  filter(p_water < 1) %>%
-  filter(geoid %in% blockgroups$GEOID) %>%
-  st_transform(32618)
 ```
 
-In calculating the distances, two things could happen. First, it is possible that
-no path is found between the park and the block group centroid; this could be the
-result of network miscodings or other errors in the network algorithm. We'll have
-to take the results as they come, and we simply remove the park from that block
-group's accessibility calculation. The other issue is when a block group centroid
-and the park edge point match to the *same* node, resulting in a distance of zero.
-Because we are going to log-transform the distance, we add ten meters to all paths.
+## Distance Examination
+The distances were computed according to the code presented in the [Distances](03_distances.html)
+page. But we want to evaluate the difference between the various distance measurements
+and visualize what they mean in terms of our analysis.
 
-```{r distance_adjust}
-distance_files <- list.files("data/nyc_shortest_paths_3500m/", full.names = TRUE)
+```{r read_distances}
+blockgroup_files <- list.files("data/blockgroups", "*.csv", full.names = TRUE)
+tract_files <- list.files("data/tracts", "*.csv", full.names = TRUE)
 
-read_all_files <- function(pattern = pattern, path = "./"){
-  map_df(list.files(path = path, pattern = pattern, full.names = TRUE), read_csv,
-         col_types = list(geoid = col_character(), park_id = col_character()))
+read_dist_csv <- function(x){
+  # warnings are from `inf` strings, which become converted to NA, which is okay.
+  read_csv(x, col_types = "ccnn") %>% as_tibble()
 }
-distances <- read_all_files(".csv", "data/nyc_shortest_paths_5000m/") %>%
-  # filter out infinite paths
-  filter(!is.infinite(distance)) %>%
-  # add ten meters to all paths
-  mutate(distance = distance + 10)
+
+blockgroup_distances <- lapply(blockgroup_files, read_dist_csv) %>% bind_rows()
+tract_distances      <- lapply(tract_files,      read_dist_csv) %>% bind_rows()
 ```
 
-Now we can calculate the utility specification. The first specification uses the
-distance and size terms from the Alameda County study. The second specification
-adds the amenities with the utilities found by the Kinnell et al. study.
+First, let's compare the difference between the Euclidean and network
+distance at the block group level. Well, this is troubling; it appears as though
+there is no relationship between the two methods of measurement.
+
+```{r bg_dist_comparison}
+ggplot(blockgroup_distances %>% sample_n(1e4), aes(x = euc_dist, y = distance)) +
+  geom_point(alpha = 0.3) + geom_smooth()
+```
+
+Let's look at the same plot for tracts. This is much better, though there
+are still some curious issues.
+
+```{r tr_dist_comparison}
+ggplot(tract_distances %>% sample_n(1e4), aes(x = euc_dist, y = distance)) +
+  geom_point(alpha = 0.3) + geom_smooth()
+```
+
+In particular, how is it possible for the
+Euclidean distance to be *longer* than the network distance? Let's look at this
+by distance. It seems that everything is doing okay except for tracts and parks in Staten 
+Island (prefix '085' and "R"). Obviously the shortest path isn't handling Staten
+Island very well. The Verrazzano-Narrows Bridge is in the network, but I-78 and
+the Bayonne Bridge route to Manhattan through New Jersey is not in the network.
+
+```{r tr_dist_comparison_borough}
+ggplot(tract_distances %>% sample_n(1e4) %>% 
+         mutate(borough = substr(geoid, 3, 5),
+                park_borough = substr(park_id, 0, 1),
+                park_borough = ifelse(!park_borough %in% c("B", "M", "Q", "R", "X"), "C", park_borough)), 
+       aes(x = euc_dist, y = distance)) +
+  geom_abline(slope = 1, intercept = 0, lty = "dotted", color = "grey") + 
+  geom_point(alpha = 0.3) + geom_smooth() +
+  xlab("Euclidean Distance") + ylab("Network Distance") +
+  facet_grid(borough ~ park_borough) +
+  theme_bw()
+```
+
+All of this is to say we probably need to eliminate Staten Island for our 
+analysis, or else adjust the network distances we calculate.
+
+Is there a relation between the tract distance and the distances for block
+groups within the tract?
+
+```{r comparison}
+comparison <- blockgroup_distances %>%
+  sample_n(1e5) %>%
+  rename(bg_net = distance, bg_euc = euc_dist) %>%
+  mutate(tract = substr(geoid, 1, 11)) %>%
+  left_join(tract_distances %>% rename(tr_net = distance, tr_euc = euc_dist), 
+            by = c("tract" = "geoid", "park_id" = "park_id"))
+```
+
+Let's look first at the network distances. Yikes!
+```{r comparison-net}
+ggplot(comparison, aes(x = bg_net, y = tr_net)) +
+  geom_point(alpha = 0.1) + geom_smooth() + 
+  xlab("Blockgroup Network Distance") + ylab("Tract Network Distance")
+```
+
+The Euclidean distances make *loads* more sense, with some aggregation error
+but it's obvious the numbers aren't stupid.
+
+```{r comparison-net}
+ggplot(comparison, aes(x = bg_euc, y = tr_euc)) +
+  geom_point(alpha = 0.1) + geom_smooth() + 
+  xlab("Blockgroup Euclidean Distance") + ylab("Tract Euclidean Distance")
+```
+
+Let's make a map of tracts colored by how far the two methods think they are
+from Central Park. In general this seems fine, except again, Staten Island does
+not look that great. Something is definitely happening there.
+
+```{r distance-map}
+pal <- colorQuantile(palette = "magma", log(tract_distances$distance), n = 7)
+tracts %>%
+  select(geoid) %>%
+  left_join(tract_distances %>% filter(park_id == "M010"), by = "geoid") %>%
+  st_transform(4326) %>%
+  leaflet() %>%
+  addProviderTiles(providers$Esri.WorldGrayCanvas) %>%
+  addPolygons(color = ~pal(log(distance)), group = "Network") %>%
+  addPolygons(color = ~pal(log(euc_dist)), group = "Euclidean") %>%
+  addLayersControl(overlayGroups = c("Network", "Euclidean"))
+```
+
+## Logsums
+
+Now that we have the distances between parks and block groups / tracts, we can 
+calculate the logsums.
 
 ```{r logsums}
-logsums <- distances %>%
+logsum <- function(x) { log(sum(exp(x))) }
+
+compute_logsums <- function(df) {
+  df %>%
     left_join(open_spaces %>% st_set_geometry(NULL), by = c("park_id" = "id")) %>%
+    # use euc_distance for impossible distances.
+    mutate( distance = ifelse(distance < euc_dist, euc_dist, distance) ) %>%
+    # convert distances to miles
+    mutate_at(c("distance", "euc_dist"), ~ . * 0.000621371) %>%
+    # must be at least 1/10 miles
+    mutate_at(c("distance", "euc_dist"), ~ ifelse(. < 0.1, 0.1, .)) %>%
+
+    # compute utility
     mutate(
-    distance_miles = (distance + 10) * 0.000621371,
-    u_access = -1.768 * log(distance_miles) + 0.373 * log(as.numeric(acres)),
-    u_multi = u_access + 
-      open_spaces$trails * 0.99 + 
-      open_spaces$playgrounds * 0.26 + 
-      open_spaces$courts * 0.43
+      euc_access = -1.768 * log(euc_dist) + 0.373 * log(as.numeric(acres)),
+      euc_multi  = euc_access + trails * 0.99 +  playgrounds * 0.26 + courts * 0.43,
+      net_access = -1.768 * log(distance) + 0.373 * log(as.numeric(acres)),
+      net_multi  = net_access + trails * 0.99 +  playgrounds * 0.26 + courts * 0.43
     ) %>%
+
+    # group by origin and compute access logsum
     group_by(geoid) %>%
-  summarise(
-    access_ls = log(sum(exp(u_access), na.rm = TRUE)),
-    multi_ls = log(sum(exp(u_multi), na.rm = TRUE))
-  ) %>%
-  mutate_at(
-    vars(ends_with("_ls")),
-    list(~ (. - mean(., na.rm = TRUE)) / sd(., na.rm = TRUE))
-  )
+    summarize_at(vars(euc_access:net_multi), logsum) %>%
 
-bg_access <- bg_poly %>%
-  left_join(logsums, by = "geoid") %>%
-  write_rds("data/bg_access.rds")
+    # standardize
+    mutate_at(vars(euc_access:net_multi), ~(. - mean(.)) / sd(.))
+
+}
+
+tract_logsums <- compute_logsums(tract_distances) %>% write_rds("data/tract_logsums.rds")
+bg_logsums    <- compute_logsums(blockgroup_distances) %>% write_rds("data/bg_logsums.rds")
 ```
 
-## 10-minute buffer
+Let's visualize the access logsums calculated for each graph in this method.
 
-We are also interested in looking at what happens when the tracts are within a 
-10-minute walk of a park, the threshold established by the Trust for Public Lands.
-This is interesting because whereas a limited number of tract centroids failed
-to overlap with the 10-minute buffer, all of the block group centroids intersect.
-
-## Accessibility Map
-Here's a map of the values. Note that there is also a shiny app in this project
-that allows the user to set different values for the logsum parameters.
-
-```{r access_map}
+```{r tracts_access}
+tracts_access <- tracts %>% left_join(tract_logsums, by = "geoid")
 # this interactive map is much easier to create and explore
-pal <- colorQuantile("GnBu", c(bg_access$access_ls, bg_access$multi_ls), n = 5)
-leaflet(bg_access %>% st_transform(4326)) %>%
+pal <- colorQuantile("GnBu", c(tracts_access$euc_access, tracts_access$net_multi), n = 7)
+leaflet(tracts_access %>% st_transform(4326)) %>%
   addProviderTiles(providers$Esri.WorldGrayCanvas) %>%
-  addPolygons(group = "access", color = ~ pal(access_ls), stroke = 1,
-              label = ~as.character(round(access_ls, 2))) %>%
-  addPolygons(group = "Kinner", color = ~ pal(multi_ls), stroke = 1,
-              label = ~as.character(round(multi_ls, 2))) %>%
-  addLayersControl(overlayGroups = c("access", "Kinner"))
+  addPolygons(group = "Network", color = ~ pal(net_access),
+              label = ~as.character(round(net_access, 2))) %>%
+  addPolygons(group = "Network-Multi", color = ~ pal(net_multi),
+              label = ~as.character(round(net_multi, 2))) %>%
+  addPolygons(group = "Euclidean", color = ~ pal(euc_access),
+              label = ~as.character(round(euc_access, 2))) %>%
+  addPolygons(group = "Euclidean-Multi", color = ~ pal(euc_multi),
+              label = ~as.character(round(euc_multi, 2))) %>%
+  addLayersControl(baseGroups = c("Network", "Euclidean", "Network-Multi", "Euclidean-Multi"))
 ```

### 2020-05-11 04_accessibility.Rmd
Calculate 10-minute walk accessibility

@@
 ```
+
+## 10-minute walk buffer
+
+We are also interested in looking at what happens when the tracts are within a 
+10-minute walk of a park, the threshold established by the Trust for Public Lands.
+
+```{r nyc10mw}
+access_10mw <- st_read("data/nyc_10mw.geojson") %>%
+  st_cast("MULTIPOLYGON") %>%
+  lwgeom::st_make_valid() %>%
+  summarise(d = 1)
+
+read_csv("data/tract_centroids.csv", col_types = "cnnnn") %>%
+  st_as_sf(coords = c("LONGITUDE", "LATITUDE"), crs = 4326) %>%
+  mutate(walk10 = st_intersects(., access_10mw, sparse = FALSE)) %>%
+  st_set_geometry(NULL) %>%
+  dplyr::select(geoid, walk10) %>%
+  write_rds("data/walk10.rds")
+```

### 2020-05-11 05_estimation.Rmd
Clean up file names and headers
Re-estimate models and update discussion
Includes analysis of alternative distance calculations, addressing #5.

@@
 ---
-title: "Model "
-author: "Greg Macfarlane"
-date: "6/17/2019"
-output: html_document
+title: "Model Estimation"
 ---
@@
 
-```{r bg_access}
-bg_access <- read_rds("data/bg_access.rds")
+```{r tracts}
+est_data <- read_rds("data/tracts.rds") %>%
+  left_join(read_rds("data/tract_logsums.rds"), by = "geoid") %>%
+  left_join(read_rds("data/walk10.rds"), by = "geoid")
 ```
-
-The accessibility is calculated at the block group level, but the other information
-(health, demographics) is available only at the tract level.
-
-```{r tracts}
-mydata <- bg_access %>% 
-  dplyr::mutate(tract = substr(geoid, 0, 11)) %>%
-  left_join(
-    read_rds("data/tracts.rds") %>%
-      st_set_geometry(NULL),
-    by = c("tract" = "geoid")
-  ) %>%
-  filter(!is.na(households))
-```
-
-### Contiguity weights
 
@@
 
-```{r Wcontig}
-areas_adj <- poly2nb(mydata)
-Wcontig <- nb2listw(areas_adj, style = "W", zero.policy = TRUE)
-print(Wcontig, zero.policy = TRUE)
+```{r W}
+Wtr <- nb2listw(poly2nb(est_data), style = "W", zero.policy = TRUE)
+print(Wtr, zero.policy = TRUE)
 ```
@@
 $$PhysAct = X\beta + \beta_{access}*access + u; u = \lambda W u + \epsilon$$
-We will consider both spatial weights matrices.
 
 ```{r ols_vs_sem}
-access_ols <- lm(update(base_formula, physact ~ . + access_ls), data = mydata)
-access_sem_wc <- errorsarlm(update(base_formula, physact ~ . + access_ls),
-                            data = mydata, listw = Wcontig, zero.policy = TRUE)
+access_ols <- lm(update(base_formula, physact ~ . + euc_access), data = est_data)
+access_sem <- errorsarlm(update(base_formula, physact ~ . + euc_access),
+                            data = est_data, listw = Wtr, zero.policy = TRUE)
 
-ols_vs_sem <- list("OLS" = access_ols, "SEM" = access_sem_wc)
+ols_vs_sem <- list("OLS" = access_ols,  "SEM" = access_sem)
 ```
@@
 
-sp_hausman(access_ols, access_sem_wc)
+sp_hausman(access_ols, access_sem)
 ```
@@
 
-I'm curious what happens when we remove density from the base model.
-
-```{r nodensity}
-# take log(density) out of the bare access model
-nodensity <- lapply(ols_vs_sem, function(model) {
-  update(model, . ~ . - log(density))
-})
-lapply(nodensity, tidy) %>%
-  bind_rows(.id = "model") %>%
-  dwplot() + scale_x_continuous(limits = c(-0.3, 1))
-```
-
-Basically the same thing. It's worth looking at whether the same thing is happening
-in the obesity model.
-
-```{r obesity_sem}
-obesity_sem <- lapply(ols_vs_sem, function(model) {
-  update(model, obesity ~ . + physact)
-})
-lapply(obesity_sem, tidy) %>%
-  bind_rows(.id = "model") %>%
-  dwplot() 
-```
-
-Yup. Okay, given that, the question is whether adding lagged
+Okay, given that, the question is whether adding lagged
 variables $\gamma W X$ to the model will resolve the discrepancy.
@@
 The same basic logic applies to the SLX and SDEM models; if there is no dependence
-relationship among the $y$ variables, then the SLX and SDEM will have unbiased
+relationship among the $y$ variables, then the SLX and SDEM will both have unbiased
 estimates of $\beta$ and $\gamma$.
@@
 ```{r access_slx}
-access_slx_wc <- lmSLX(update(base_formula, physact ~ . + access_ls), 
-                       data = mydata, listw = Wcontig, zero.policy = TRUE)
-access_sdem_wc <- errorsarlm(update(base_formula, physact ~ . + access_ls),
-                            data = mydata, listw = Wcontig, zero.policy = TRUE, 
+access_slx <- lmSLX(update(base_formula, physact ~ . + euc_access), 
+                   data = est_data, listw = Wtr, zero.policy = TRUE)
+access_sdem <- errorsarlm(update(base_formula, physact ~ . + euc_access),
+                          data = est_data, listw = Wtr, zero.policy = TRUE, 
                           Durbin = TRUE)
 slx_vs_sdem <- list(
-  "SDEM" = access_sdem_wc,
-  "SLX" = access_slx_wc
+  "SDEM" = access_sdem, 
+  "SLX" = access_slx
 )
@@
 
-As before, we can try a Hausman-style test.
+As before, we can try a Hausman-style test. In this case the test still suggests
+rejecting the null hypothesis, but the parameter esimates are very close to each
+other. Additionally, rejecting the null hypothesis would suggest the SDM, which
+we rejected on intuitive grounds.
+
 ```{r slx_hausman}
@@
 }
-slx_hausman(access_slx_wc, access_sdem_wc)
+slx_hausman(access_slx, access_sdem)
 ```
@@
 ```{r lagged_vars}
-contiglagged_vars <- mydata %>%
+tr_lagged <- est_data %>%
+  st_set_geometry(NULL) %>%
   as_tibble() %>%
@@
     vars(density, income, fulltime, college, single, youth, young_adults, seniors, black, asian, hispanic, other, physact),
-    ~lag.listw(Wcontig, .)
+    ~lag.listw(Wtr, .)
   ) %>%
-  mutate(geoid = mydata$geoid) %>%
+  mutate(geoid = est_data$geoid) %>%
   dplyr::select(geoid, everything())
 
-names(contiglagged_vars)[-1] <- str_c("lag.", names(contiglagged_vars)[-1])
-contiglagged_data <- mydata %>% left_join(contiglagged_vars, by = "geoid")
+names(tr_lagged)[-1] <- str_c("lag.", names(tr_lagged)[-1])
+est_data_lagged <- est_data %>% left_join(tr_lagged, by = "geoid")
 ```
@@
 ```{r nolag_access}
-access_slx_wc <- lm(update(
+access_slx <- lm(update(
   base_formula, physact ~ . +  log(lag.density) + log(lag.income) + 
     lag.fulltime + lag.college + lag.single + lag.youth +  lag.young_adults + 
-    lag.seniors + lag.black + lag.asian + lag.hispanic + lag.other + access_ls),
-  data = contiglagged_data)
-
-access_sdem_wc <- errorsarlm(update(
+    lag.seniors + lag.black + lag.asian + lag.hispanic + lag.other + euc_access), 
+  data = est_data_lagged)
+access_sdem <- errorsarlm(update(
   base_formula, physact ~ . +  log(lag.density) + log(lag.income) + 
     lag.fulltime + lag.college + lag.single + lag.youth +  lag.young_adults + 
-    lag.seniors + lag.black + lag.asian + lag.hispanic + lag.other + access_ls), 
-  data = contiglagged_data, listw = Wcontig, zero.policy = TRUE)
+    lag.seniors + lag.black + lag.asian + lag.hispanic + lag.other + euc_access), 
+  data = est_data_lagged, listw = Wtr, zero.policy = TRUE)
 ```
@@
 ```{r nolag_access_tests}
-slx_hausman(access_slx_wc, access_sdem_wc)
-slx1_vs_sdem1 <- list("SLX" = access_slx_wc, "SDEM" = access_sdem_wc)
+slx_hausman(access_slx, access_sdem)
+slx1_vs_sdem1 <- list("SLX" = access_slx, "SDEM" = access_sdem)
 
-screenreg(slx1_vs_sdem1, ci.force = TRUE)
+screenreg(slx1_vs_sdem1, ci.force = TRUE, digits = 4)
+```
+
+## Alternative Distances and Aggregations
+
+As discussed on the [Distance](03_distances.html) page, there are four options for
+distance in this study:
+
+  - Euclidean distance between tracts and parks
+  - Network distance between tracts and parks
+  - Euclidean distance between block groups and parks
+  - Network distance between block groups and parks
+
+In this section we are going to examine the predictions of our model were we to
+change the distance calculation.
+
+### Network vs Euclidean Distance
+
+```{r tr_euc_v_net}
+access_sdem_tr_euc <- access_sdem
+access_sdem_tr_net <- errorsarlm(update(
+  access_sdem, . ~ . - euc_access + net_access), 
+  data = est_data_lagged, listw = Wtr, zero.policy = TRUE)
+
+multi_sdem_tr_net <- errorsarlm(update(
+  access_sdem, . ~ . - euc_access + net_multi), 
+  data = est_data_lagged, listw = Wtr, zero.policy = TRUE)
+multi_sdem_tr_euc <- errorsarlm(update(
+  access_sdem, . ~ . - euc_access + euc_multi), 
+  data = est_data_lagged, listw = Wtr, zero.policy = TRUE)
+
+tr_euc_v_net <- list(
+  "Access Euclidean" = access_sdem_tr_euc,
+  "Access Network"   = access_sdem_tr_net,
+  "Multi Euclidean"  = multi_sdem_tr_euc,
+  "Multi Network"    = multi_sdem_tr_net
+)
+```
+
+The chart below shows a comparison of spatial models of physical activity rates
+calculated with Euclidean and network distances. As you can see, the two distance
+calculations show virtually the same coefficients and significance across all
+borders. The access variable is also virutally identical; the network-based distances
+show a slightly smaller mean effect but also a slightly smaller standard 
+deviation. The confidence intervals overlap almost entirely.
+
+```{r show_tr_euc_v_net}
+texreg::screenreg(tr_euc_v_net, digits = 4)
+write_rds(tr_euc_v_net, "data/tr_euc_v_net.rds")
+```
+
+Given the challenges in getting network distances for Staten Island --- and the 
+immateriality of the effect ---  we would prefer to use a consistent distance
+metric across all models.
+
+### Block Group vs Tract
+
+The data available for the study is only available at the tract level. However,
+we could down-project the data to the block group to see if that changes any
+results.
+
+```{r bg_est_data}
+blockgroups <- tigris::block_groups("New York", c("081", "047", "061", "005", "085"), 
+                                    class = "sf")
+
+bg_est_data <- blockgroups %>%
+  transmute(geoid = GEOID, tract = substr(geoid, 1, 11)) %>%
+  left_join(read_rds("data/tracts.rds") %>% st_set_geometry(NULL), by = c("tract" = "geoid") ) %>%
+  filter(!is.na(borough)) %>%
+  left_join(read_rds("data/bg_logsums.rds"))
+
+Wbg <- nb2listw(poly2nb(bg_est_data), style = "W", zero.policy = TRUE)
+
+bg_lagged <- bg_est_data %>%
+  st_set_geometry(NULL) %>%
+  transmute_at(
+    vars(density, income, fulltime, college, single, youth, young_adults, seniors, black, asian, hispanic, other, physact),
+    ~lag.listw(Wbg, ., zero.policy = TRUE)
+  ) %>%
+  mutate(geoid = bg_est_data$geoid) %>%
+  dplyr::select(geoid, everything())
+
+names(bg_lagged)[-1] <- str_c("lag.", names(bg_lagged)[-1])
+bg_est_data_lagged <- bg_est_data %>% left_join(bg_lagged, by = "geoid")
+```
+
+We are unable to estimate some of the models because of collinearity issues;
+this is a problem in the spatially lagged predictor variables especially.
+But we can look at what happens when we make block groups the unit of analysis
+in the SEM.
+
+```{r bg_models}
+access_sem_bg <- errorsarlm(update(base_formula, physact ~ . + euc_access), 
+  data = bg_est_data_lagged, listw = Wbg, zero.policy = TRUE)
+bg_models <- list("Tracts" = access_sem, "BG" = access_sem_bg) %>% write_rds("data/bg_models.rds")
+texreg::screenreg(bg_models, digits = 4)
 ```
@@
 ```{r estimate_sdems}
-base_sdem <- update(access_sdem_wc, formula = . ~ . - access_ls,
-                    data = contiglagged_data, listw = Wcontig, zero.policy = TRUE)
+base_sdem <- update(access_sdem, formula = . ~ . - euc_access,
+                    data = est_data_lagged, listw = Wtr, zero.policy = TRUE)
 
 # estimate models
-pa_access_sdm <- access_sdem_wc
-pa_multi_sdm   <- update(base_sdem, .~ . + multi_ls)
+pa_access_sdem <- access_sdem
+pa_multi_sdem  <- update(base_sdem, .~ . + euc_multi)
+pa_walk10_sdem <- update(base_sdem, .~ . + walk10)
 ```
@@
 pa_models <- list("Base"        = base_sdem,
-                  "Logsum"      = pa_access_sdm,
-                  "Attributes"  = pa_multi_sdm)
+                  "Logsum"      = pa_access_sdem,
+                  "Attributes"  = pa_multi_sdem,
+                  "10-min walk" = pa_walk10_sdem)
 ```

### 2020-05-13 05_estimation.Rmd
Rely on updated (custom) tidiers for sdpdep functions

@@
 ```{r tidy.sarlm}
-tidy.sarlm <- function(x){
-  s <- summary(x)
-  df <- length(s$residuals) - length(s$coefficients) - 1
-  tibble(
-    term = gsub("[\\(\\)]", "\\.", rownames(s$Coef)),
-    estimate = s$Coef[,1],
-    std.error = s$Coef[,2],
-    statistic = estimate / std.error,
-    p.value = 2*(pt(abs(statistic), Inf, lower.tail = FALSE))
-  )
-}
 lapply(ols_vs_sem, tidy) %>%

### 2020-05-13 manuscript/manuscript.Rmd
Rebuild table 2 with xtable
This helps make the table more readable, with
columns that align with each other. Some other edits to tables in the primary paper body. Addresses #7

@@
 library(tidyverse)
+library(broom)
 library(geojsonio)
@@
 library(here)
+library(xtable)
 
@@
 ```{r tracts}
-# built in 01_health_data.Rmd and 03_logsums.Rmd
-tracts <- read_rds(here("data/tracts_access.rds"))
+# built in 01_health_data.Rmd and 04_accessibility.Rmd
+tracts <- est_data <- read_rds(here("data/tracts.rds")) %>%
+  left_join(read_rds(here("data/tract_logsums.rds")), by = "geoid") %>%
+  left_join(read_rds(here("data/walk10.rds")), by = "geoid")
 ```
@@
 intersection with the 10-minute walk buffer; as it is, only 
-`r sum(!tracts$walk_10)` of the `r nrow(tracts)` tract centroids are not located 
+`r sum(!tracts$walk10)` of the `r nrow(tracts)` tract centroids are not located 
 within this buffer.
@@
   geom_sf(data = tracts, inherit.aes=FALSE,
-          aes(fill = cut(multi_ls, breaks = c(-Inf, -3, -2, -1, 0, 1, 2, 3, Inf))),
+          aes(fill = cut(euc_multi, breaks = c(-Inf, -3, -2, -1, 0, 1, 2, 3, Inf))),
           alpha = 0.9, color = NA) +
@@
 ```{r weights, warning = FALSE}
-# This are developed in 03_logsums.Rmd
-distances <- read_rds(here("data/distances.rds"))
-W <- read_rds(here("data/W.rds"))
+W <- read_rds(here("data/Wtr.rds"))
 trMC <- trW(as(W, "CsparseMatrix"), type="MC")
@@
 
-names_for_terms <- c(
-  base_termnames, str_c("$\\gamma$: ", base_termnames[-1])
+termnames <- c(
+  base_termnames, str_c("$\\gamma$: ", base_termnames[-1]), 
+  "Accessibility", "$\\lambda$: spatial correlation"
 )
 
-lambda <- "$\\lambda$: spatial correlation"
-access_terms <- c("Logsum", "Tweets",  "Attributes", "10-min walk")
+#coefficient map
+cm <- as.list(termnames)
+names(cm) <- c(names(slx_vs_sdem$SDEM$coefficients), "$\\lambda$")
 ```
@@
 produces $p$-value of only $`r slx_sdem_htest[2]`$. Though this statistic is
-technically beneath a common hypothesis test threshold of $\alpha = 0.05$, we
-fail to reject the null hypothesis that the coefficients are equivalent, as 
+well beneath a common hypothesis test threshold of $\alpha = 0.05$, we
+elect retain the null hypothesis that the coefficients are equivalent, as 
 the differences are at no point practically different from each other. The consequences
@@
 \label{tab:slx-sdem}
+\begin{tabular}{l d{2.4} d{2.4} d{2.4} c d{2.4} d{2.4} d{2.4} }
+\toprule
+ & \multicolumn{3}{c}{SLX} & & \multicolumn{3}{c}{SDEM} \\
+\cmidrule{2-4}\cmidrule{6-8}
+ & \multicolumn{1}{c}{Estimate} & \multicolumn{2}{c}{95\% Conf.Int.} & 
+ & \multicolumn{1}{c}{Estimate} & \multicolumn{2}{c}{95\% Conf.Int.}\\
+\midrule
 ```{r slx-sdem, results = "asis"}
-texreg(slx_vs_sdem, single.row = TRUE, ci.force = TRUE,  digits = 4,
-       custom.coef.names = c(names_for_terms, "Accessibility", lambda), 
-       # Goodness of fit (LM and SP are different)
-       custom.gof.rows = list(
-         "Log Likelihood" = lapply(slx_vs_sdem, logLik) %>% unlist(),
-         "Num. Obs." = lapply(slx_vs_sdem, function(s) length(s$residuals))
-       ),
-       include.rsquared = F, include.adjrs = F, include.aic = F, include.loglik = F,
-       include.parameters = F, include.nobs = F,
-       use.packages = FALSE, booktabs = TRUE,
-       caption = "Comparison of SLX and SDEM Coefficients",
-       label = "tab:slx-sdem",table = FALSE,
-       custom.note = "%stars $y = $ tract-level physical activity rate.",
-       caption.above = TRUE)
+slx_coefs <- lapply(slx_vs_sdem, function(x) tidy(x, conf.int = TRUE))
+slx_stats <- lapply(slx_vs_sdem, glance)
+tab <- right_join(slx_coefs$SLX, slx_coefs$SDEM, by = "term") %>%
+  transmute(term, estimate.x, conf.low.x, conf.high.x, space = " ",
+                  estimate.y, conf.low.y, conf.high.y) %>%
+  mutate(term = unlist(cm))
+
+xtab <- xtable(tab, digits = 4)
+print(xtab, include.rownames = FALSE, include.colnames = F,
+      sanitize.text.function = identity, floating = F, only.contents = T, hline.after = NULL)
 ```
+\midrule
+Log Likelihood & \multicolumn{3}{c}{$-4831.974$} & & \multicolumn{3}{c}{$-4435.507$}\\
+Num.Obs.       & \multicolumn{3}{c}{$2099$}   & & \multicolumn{3}{c}{$2099$}\\
+\bottomrule
+\end{tabular}
 \end{table*}
@@
 interval, we could suggest that the true effect of excellent versus poor park access
-is anywhere between `r 6 * .02` and `r 6 * .3` percentage points.
+is anywhere between `r 6 * .01` and `r 6 * .3` percentage points.
 
@@
 ```{r pa-models, results = "asis"}
-texreg(pa_models[c(2, 4:5)], digits = 4, ci.force = TRUE,
+texreg(pa_models[c(2:4)], digits = 4, ci.force = TRUE,
        booktabs = TRUE, use.packages = FALSE, 
@@
          "lambda" = "$\\lambda$: spatial correlation", 
-         "access_ls" = "Size and Distance", 
-         "multi_ls" = "Amenities", 
-         "walk_10TRUE" = "10-minute walk"),
+         "euc_access" = "Accessibility", 
+         "euc_multi" = "Accessibility", 
+         "walk10TRUE" = "Accessibility"),
        caption = "Estimated Effect of Accessibility on Physical Activity Rates",
@@
        caption.above = TRUE, include.aic = F, include.lr = F,
-       custom.note = "%stars 95\\% confidence interval in brackets.")
+       custom.note = "%stars 95\\% confidence interval in brackets.  $y = $ tract-level physical activity rate.")
 ```
@@
 error terms, obesity rates in tracts with excellent park accessibility are expected 
-to be between `r 6 * 0.15` percentage points lower and `r 6 * .0053` percentage 
+to be between `r 6 * 0.113` percentage points lower and `r 6 * .0425` percentage 
 points higher than tracts with poor park accessibility. This range of values 
@@
 ```{r obesity-models, results="asis"}
-texreg(obesity_models[c(2, 4:5)], digits = 4, ci.force = TRUE, 
+texreg(obesity_models[c(2:4)], digits = 4, ci.force = TRUE, 
        booktabs = TRUE, use.packages = FALSE, 
@@
          "lambda" = "$\\lambda$: spatial correlation", 
-         "access_ls" = "Size and Distance", 
-         "multi_ls" = "Amenities", 
-         "walk_10TRUE" = "10-minute walk"),
+         "euc_access" = "Accessibility", 
+         "euc_multi" = "Accessibility", 
+         "walk10TRUE" = "Accessibility"),
        caption = "Estimated Effect of Accessibility on Obesity Rates",
@@
        caption.above = TRUE, include.aic = F, include.lr = F,
-       custom.note = "%stars 95\\% confidence interval in brackets.")
+       custom.note = "%stars 95\\% confidence interval in brackets.  $y = $ tract-level obesity rate.")
 ```
@@
 mental health, or any number of potential beneficial outcomes hypothesized
-or explored in the existing literature. Exploring these connections and their
-underlying mechanisms should be a priority as city planners and urban architects
-attempt to improve the quality of life of urban residents in the future.
+or explored in the existing literature. The COVID-19 pandemic and its associated
+social distancing behaviors in many regions of the world has also drawn
+attention to problems of park access, use, and equity. Exploring these
+connections and their underlying mechanisms should be a priority as city
+planners and urban architects attempt to improve the quality of life of urban
+residents in the future.
 
@@
 where the least park-accessible tracts have an expected physical activity
-participation rate between `r 6 * .05` and `r 6 * .35` percentage points lower than the most
+participation rate between `r 6 * .01` and `r 6 * .3` percentage points lower than the most
 accessible tracts. We also found a suggestive though not sigificant relationship

### 2020-05-13 manuscript/appendix.Rmd
Rebuild appendix tables with accessibility measures all on one line
Addresses #7

@@
 pa_models <- read_rds(here("data/pa_models.rds"))
-pa_models$Tweets <- NULL
 obesity_models <- read_rds(here("data/obesity_models.rds"))
-obesity_models$Tweets <- NULL
 ```
@@
 
-names_for_terms <- c(
-  base_termnames, str_c("$\\gamma$: ", base_termnames[-1])
+cmnames <- c(
+  base_termnames, str_c("$\\gamma$: ", base_termnames[-1]), 
+  rep("Accessibility", 3), "$\\lambda$: spatial correlation"
 )
 
-lambda <- "$\\lambda$: spatial correlation"
-access_terms <- c("Size and Distance", "Attributes", "10-min walk")
+#coefficient map
+cm <- as.list(cmnames)
+names(cm) <- c(names(pa_models$Logsum$coefficients), "euc_multi", "walk10TRUE", "$\\lambda$")
 
-ob_names <- c(base_termnames, "Physical Activity Rate")
-ob_names <- c(
-  ob_names, str_c("$\\gamma$: ", ob_names[-1])
+# obesity coefficient map
+cmonames <- c(
+  base_termnames, str_c("$\\gamma$: ", base_termnames[-1]), 
+  "Physical Activity", "$\\gamma$: Physical Activity",
+  rep("Accessibility", 3),
+  "$\\lambda$: spatial correlation"
 )
-
+cmo <- as.list(cmonames)
+names(cmo) <- c(names(obesity_models$Base$coefficients), 
+                "euc_access", "euc_multi", "walk10TRUE",  "$\\lambda$")
 ```
@@
   \begin{center}
-  \scalebox{0.7}{
+  \scalebox{0.8}{
 ```{r pa-fullmodels, results = "asis"}
-texreg(pa_models, digits = 4, ci.force = TRUE,
+texreg(
+  pa_models, digits = 4, ci.force = TRUE,
   booktabs = TRUE, use.packages = FALSE, 
-       custom.coef.names = c(names_for_terms, lambda, access_terms),
-       custom.model.names = c("No Access", access_terms), table = F,
-       caption.above = TRUE, include.aic = F, include.lr = F,
+  custom.coef.map = cm,
+  custom.model.names = c("No Access", "Size and Distance", "Amenities", "10-minute Walk"), 
+  table = F,
+  include.aic = F, include.lr = F,
   custom.note = "%stars 95\\% confidence interval in brackets.")
@@
   \begin{center}
-  \scalebox{0.7}{
+  \scalebox{0.8}{
 ```{r ob-fullmodels, results="asis"}
-texreg(obesity_models, digits = 4, ci.force = TRUE,
+texreg(
+  obesity_models, digits = 4, ci.force = TRUE,
   booktabs = TRUE, use.packages = FALSE, 
-       custom.coef.names = c(ob_names, lambda, access_terms),
-       custom.model.names = c("No Access", access_terms), table = F,
-       caption.above = TRUE, include.aic = F, include.lr = F, 
+  custom.coef.map = cmo,
+  custom.model.names = c("No Access", "Size and Distance", "Amenities", "10-minute Walk"), 
+  table = F,
+  include.aic = F, include.lr = F,
   custom.note = "%stars 95\\% confidence interval in brackets.")

### 2020-05-13 manuscript/manuscript.Rmd
Initial responses to some reviewer comments

@@
 in New York City. The most basic utility specification includes only the
-park size in acres and the distance from the population-weighted tract centroid
-to the boundary of the park in miles,
+park size in acres and the Euclidean distance from the population-weighted tract
+centroid to the nearest boundary of the park in miles,
 \begin{equation}\label{eq:u_access}
@@
 \end{equation}
+There are a few cases where the population-weighted tract centroid lies on or
+within the boundary of a park; for these cases we assert that the minimum
+possible distance is one tenth of a mile.
 The logarithmic transform allows for diminishing marginal utility of distance
@@
 tract as a linear function of the tract's sociodemographic characteristics $X$
-and accessibility to parks $A$,
+and accessibility to parks $\boldsymbol{A}$,
 \begin{equation}\label{eq:themodel}
@@
 \end{equation}
+where $X$ is a matrix of dimension $n\times p$ where $n$ is the number of observations and $p$ is the number of predictor
+variables, and $\boldsymbol{\beta}$ is a $p\times 1$ vector of estimated parameters.
+The accessibility vector $\boldsymbol{A}$ influences physical activity or obesity rates by the
+single estimated parameter $\beta_a$, and a vector $\boldsymbol{\varepsilon}$ 
+represents the model residual as a random variable.
 
@@
 Note that in the lag-$X$ specifications (SLX and SDEM) we exclude the accessiblity 
-component $A$, that is we do *not* consider that the accessibility
+component $\boldsymbol{A}$, that is we do *not* consider that the accessibility
 in a neighboring zone will have an effect on physical activity or obesity rates.
-In a practical sense, this is because the accessibility term $A$ is itself spatially
+In a practical sense, this is because the accessibility term $\boldsymbol{A}$ is itself spatially
 determined.
@@
 error terms, obesity rates in tracts with excellent park accessibility are expected 
-to be between `r 6 * 0.113` percentage points lower and `r 6 * .0425` percentage 
+to be between `r 6 * 0.12` percentage points lower and `r 6 * .035` percentage 
 points higher than tracts with poor park accessibility. This range of values 
@@
 a neighborhood's accessibility to park features that its residents most care
-about. In this paper, we proceed only incrementally towards this by adding some
-selected park amenities as an element of each park's
-attractiveness above and beyond its size. Exploring detailed definitions of
-an increased number of amenities on one hand, and market segmentation strategies
-on the other, could provide a more nuanced understanding of the relationship
-between park accessibility and health outcomes.
+about. In this paper, we proceed only incrementally towards
+this by adding some selected park amenities as an element of each park's
+attractiveness above and beyond its size. The set of amenities we included in
+the utility calculation --- and the contribution of each amenity to the overall
+utility --- was dictated by the availability of data on the park amenities in New
+York City and our ability to find comparable prior studies with transferrable
+utility parameters. We can envision a study where mobile device data
+revealing the home locations of park users would be paired with more detailed
+park amenities and use data (e.g. geolocated Twitter data *a la*
+@roberts2017using) to estimate the utility contribution of these features. This
+could in turn provide a more nuanced understanding of the relationship between
+park accessibility, use, and health outcomes.
 
@@
 exacerbated when the non-highway mode share is high, as is likely when considering
-access to parks. A better metric of travel impedance may be a mode choice model
-logsum, which weights all alternative travel alternatives against each other. 
-We leave this as a recommendation for future research.
+access to parks. We examined replacing the Euclidean distance with a network-based
+distance; the choice of distance metric appeared inconsequential to our larger
+findings in this case. We retained the Euclidean distance for computational simplicity. A
+better metric of travel impedance may be a mode choice model logsum, which
+weights all alternative travel alternatives against each other. We leave this as
+a recommendation for future research.
 

### 2020-05-17 manuscript/manuscript.Rmd
Revise literature review and introduction
Addresses #3 and #5

@@
 After all, it does little to educate individuals on the importance of exercise
-if their community is built in such a way that such exercise is expensive,
-unenjoyable, or unsafe.
+if their community is designed and built in such a way that such exercise is
+expensive, unenjoyable, or unsafe. It is similarly necessary for urban planners
+to identify which neighborhoods have access to quality green space, and which
+neighborhoods need intervention in the form of new or rehabilitated green space,
+or improved transportation access to existing quality green space.
 
-In spite of the potential for green spaces to influence public health outcomes 
+But in spite of the potential for green spaces to influence public health outcomes 
 and numerous studies attempting to empirically estimate the strength of these
@@
 faced is a proliferation of techniques for measuring access to green spaces, of
-which many are plausible but lack robust theoretical bases. In this
-paper, we apply a holistic and flexible measurement for park accessibility
-based in activity location choice theory. This utility-based accessibility measure
-compares the continuous distance to all parks in the region, weighted against
-the sizes of each park and its other assorted amenities.
+which many are plausible but lack robust theoretical bases.
 
-We apply this measurement to study the link between park accessibility and
-attractiveness and census tract-level aggregate physical activity participation
-and obesity rates in New York City, controlling for spatially correlated
-unobserved effects, spatial spillovers of covariates, and tract-level
+In this paper, we apply a holistic and flexible measurement for park
+accessibility based in activity location choice theory. This utility-based
+accessibility measure compares the continuous distance to all parks in the
+region, weighted against the sizes of each park and its other assorted
+amenities. We apply this measure to study the link between park accessibility
+and attractiveness and census tract-level aggregate physical activity
+participation and obesity rates in New York City, controlling for spatially
+correlated unobserved effects, spatial spillovers of covariates, and tract-level
 socioeconomic characteristics. We also demonstrate how the utility-based
 accessibility metric can potentially be expanded to account for other measures
-of a park's attractiveness including its observed social media activity and the
-presence of various park amenities. The paper concludes with a discussion of
-opportunities for future research.
+of a park's attractiveness in the form of various park amenities. The paper
+concludes with a discussion of opportunities for future research.
 
@@
 \label{sec:litreview}
-
-The large majority of extant research on the topic of park access and public health
-outcomes has been focused on comparing metropolitan regions against each other.
-For example, @West2012 used park data from
-the Trust for Public Land’s 2010 "City Park Facts" and public health data from the
-Behavioral Risk Factor Surveillance System (BRFSS) to examine the relationship
-between the density of park land and physical activity and obesity rates for 67
-metropolitan statistical areas in the U.S. The findings in this case conformed to 
-expectation; that is, the study found a significant positive association
-between park density and physical activity and a significant negative
-association between park density and obesity.
-@Larson2016 similarly used self-reported scores on the Gallup-Healthways
-Wellbeing Index to evaluate the relationship between physical health and park
-quantity, quality, and accessibility in 44 U.S. cities. While the authors found
-positive associations between wellbeing and park quality and accessibility,
-these relationships were not statistically significant.
-Conversely, @Richardson2012 examined the relationship between total urban
-greenspace and mortality rates for selected maladies; though the authors did not
-find a statistically significant relationship between the quantity of urban
-greenspace and mortality caused by lung cancer, diabetes, heart disease or car
-accidents, they did find that all-cause mortality was --- oddly --- *higher* in greener
-cities. Finally, in a meta-analysis of 20 peer reviewed journal articles exploring the
-relationship between parks and objectively measured physical activity,
+The question of how green space in the urban environment affects the physical,
+emotional, and mental well-being of urban residents is not new to the academic
+literature. Comprehensive reviews and analysis of this literature up to 2007
+can be had from @tzoulas2007promoting, and for the subsequent decade from
+@kabisch2015human. In spite of the depth of this research arena --- or perhaps
+because of it --- quantitative approaches for assessing both health outcomes and
+access to green space vary widely. It is therefore not surprising that in a
+meta-analysis of 20 recent peer reviewed journal articles exploring the
+relationship between access to parks and objectively measured physical activity,
 @Bancroft2015 found that five studies reported a significant positive
-association between the two, six studies produced mixed results, and nine
-studies found no association at all.
-
-Metropolitan-level analyses such as those described above do not capture the
-within-city variation in accessibility to parks that exist in many cities. Some
-cities with large amounts of total greenspace may nevertheless unequally
-distribute this space throughout the city, leading to areas with poor access.
-Conversely, a city with a smaller overall proportion of greenspace may give all
-of its citizens better access to sufficient greenspace to meet their needs or
-desires for physical activity. Considering access at the neighborhood level within
-a single city may also eliminate some regional or cultural fixed effects
-affecting metropolitan-level analyses.
-
-## Park Accessibility Measures
+association, six studies produced mixed results, and nine studies found no
+association at all.
 
@@
 with which people can accomplish activities there.  Accessibility is an abstract
-concept with tempting quantifiability [@Handy1997], perhaps explaining the proliferation of
-calculation mechanisms. @Dong2006 present a helpful mathematical heirarchy of
-common mechanisms, which we follow here. Consider a person residing at
+concept with tempting quantifiability [@Handy1997], but objective quantification 
+may not be strictly necessary. For example, takano2002urban showed improved 
+survival rates among senior citizens in Japan who self-reported having access
+to qualitatively good walking spaces. Though encouraging, this result could
+simply reveal self-selection: Those seniors who felt the walking space was good
+were those who chose to enjoy it. Urban planners seeking to evaluate which
+residents have good access to quality green space may desire objective and
+therefore comparable measures.
+
+@Dong2006 present a helpful mathematical heirarchy of
+common quantitative mechanisms for calculating access, which we follow here.
+Consider a person residing at
 point $i$ in a city with parks $j \in 1 \ldots J$. An analyst might consider
@@
 
-Variations of this isochrone-based framework are easily derived and relatively
+Applications of this isochrone-based framework are easily derived and relatively
 common. 
@@
 carefully calculated 10-minute network-bound walk, paired with a demographic analysis of
-areas within and outside of this threshold. In other applications $D$ might be more
-variably defined, such as the presence or percent of green space within a
-political or statistical boundary [@Mitchell2008; @Stark2014] or within a specific distance
-threshold [@Kaczynski2014]. It is also possible to attenuate an isochrone with 
+areas within and outside of this threshold. @devries2003natural
+showed the amount of greenspace within a 3-kilometer radius was positively associated
+with a suite of self-reported health outcomes. Similarly, @devries2013streetscape
+showed that streetscape greenery within 500 meters of a residence was associated with
+perceived general health. Conversely, @carlson2012interactions found no relationship
+between the health of senior citizens and the number of parks within 500 meters.
+
+Another common access measure fits in this category, where distance-based
+isochrones are replaced with political, geographical, or statistical boundaries.
+These are especially common in comparative macroscopic studies, such as the
+positive relationships found by @West2012 between density of park land in a
+metropolitan area and self-reported population health indicators derived from
+the Behavioral Risk Factor Surveillance System (BRFSS). On the other hand,
+@Larson2016 found no relationship between physical health and park
+quantity, quality, and accessibility in 44 U.S. cities and self-reported scores
+on the Gallup-Healthways Wellbeing Index. At the sub-metropolitan level, 
+the @Stark2014 found a significant relationship in New York City between the percent
+of a residential ZIP code that is park space and objectively measured body
+mass index (BMI). It is also possible to attenuate an isochrone with 
 various factors; for instance, @Dias2019 considered road safety perception as an
@@
 behavior; that is, the attributes of a park influence walking more than
-merely the distance to it. @Zhang2011 develop a population-weighted,
+merely the distance to it. @hillsdon2006relationship found no relationship between
+a gravity-based accessibility term and self-reported physical activity among middle-aged individuals in Norwich, England. @Zhang2011 developed a population-weighted,
 gravity-based accessibility to parks metric with a national scope, though they
@@
 statistics based on revealed behavioral preferences rather than calibrated or
-asserted values [@Handy1997]. @Kaczynski2016 present what is effectively a 
-utility-based accessibility score they call "ParkIndex", with the explicit
-motivation of developing a uniformly applicable park accessibility statistic,
-though they limit this statistic as a way to add heterogeneity within an
-isochrone analysis.
+asserted values [@Handy1997]. @Kinnell2006 collected a choice-based survey 
+sufficient to construct a utility-based measure, though they do not do so.
+Similarly, @Kaczynski2016 present what is effectively a utility-based score called
+"ParkIndex", with the explicit motivation of developing a uniformly applicable
+park accessibility statistic, though they limit this statistic as a way to add
+heterogeneity within an isochrone analysis.
 
@@
 fallacy, where aggregate statistics mask or contradict disaggregated or
-individual-level trends. A large-sample survey of individuals in New York City,
+individual-level trends. The socioeconomic and public health data used in this
+study are only available at the tract level; projecting the tract-level data to the block
+group level and computing more spatially precise accessibility logsums proved infeasible 
+as the spatial lags of the independent variables introduced substantial collinearity
+in the model equations. A large-sample survey of individuals in New York City,
 including measured physical activities and obesity would always be preferable
@@
 analyses, and to separate the definition of access from the study of its effects.
-This will in turn enable planners to consider how multiple attributes
-of a park --- from its location to its size to its amenities and beyond ---
-benefit the health of the community the park serves.
+This will in turn enhance the ability of planners to consider how multiple
+attributes of a park --- from its location to its size to its amenities and
+beyond --- benefit the health of the community the park serves.
 

### 2020-06-04 manuscript/submission/manuscript.tex
Fix affiliations and update title page

@@
-\documentclass[Afour,sageh.bst]{sagej}
+\documentclass[shortAfour,sageh.bst]{sagej}
 
@@
   	 \def\Corr{{\rm Corr}\,}
-\newcommand{\vect}[1]{\boldsymbol{#1}}
+
+\usepackage{xcolor}
 
@@
 \usepackage{makecell}
+\usepackage{dcolumn}
+\newcolumntype{d}[1]{D{.}{.}{#1}}
+\usepackage{booktabs}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+\usepackage{xcolor}
 
@@
 
-\runninghead{XXXX \emph{et al}.}
-
-\author{XXXX \affilnum{1}, XXXX \affilnum{2}, XXXX\affilnum{3}, XXXX\affilnum{3}}
-
-\affiliation{
-\affilnum{1}{XXXX}\\
-\affilnum{2}{XXXX}\\
-\affilnum{3}{XXXX}}
-
-\corrauth{XXXX}
-
-\email{\href{XXXX}{\nolinkurl{XXXX}}}
+\runninghead{Macfarlane \emph{et al}.}
+
+\author{Gregory Macfarlane\affilnum{1}, Nico Boyd\affilnum{2}, John E. Taylor\affilnum{3}, Kari Watkins\affilnum{3}}
+
+\affiliation{\affilnum{1}{Department of Civil \& Environmental Engineering, Brigham Young University}\\\affilnum{2}{Fehr \& Peers, Los Angeles California}\\\affilnum{3}{School of Civil \& Environmental Engineering, Georgia Institute of Technology}}
+
+\corrauth{Gregory Macfarlane, 430 Engineering Building, Provo UT 84663}
+
+\email{\href{mailto:gregmacfarlane@byu.edu}{\nolinkurl{gregmacfarlane@byu.edu}}}
 
@@
 
-\keywords{Accessibility; Green Space; Public Health}
+\keywords{Accessibility; Green Space}
 
 \maketitle
-
 \clearpage
-\newpage
 \hypertarget{introduction}{%
@@
 it does little to educate individuals on the importance of exercise if
-their community is built in such a way that such exercise is expensive,
-unenjoyable, or unsafe.
-
-In spite of the potential for green spaces to influence public health
-outcomes and numerous studies attempting to empirically estimate the
-strength of these outcomes, evidence to date has been mixed. A major
+their community is designed and built in such a way that such exercise
+is expensive, unenjoyable, or unsafe. It is similarly necessary for
+urban planners to identify which neighborhoods have access to quality
+green space, and which neighborhoods need intervention in the form of
+new or rehabilitated green space, or improved transportation access to
+existing quality green space.
+
+But in spite of the potential for green spaces to influence public
+health outcomes and numerous studies attempting to empirically estimate
+the strength of these outcomes, evidence to date has been mixed. A major
 challenge researchers have faced is a proliferation of techniques for
 measuring access to green spaces, of which many are plausible but lack
-robust theoretical bases. In this paper, we apply a holistic and
-flexible measurement for park accessibility based in activity location
-choice theory. This utility-based accessibility measure compares the
-continuous distance to all parks in the region, weighted against the
-sizes of each park and its other assorted amenities.
-
-We apply this measurement to study the link between park accessibility
-and attractiveness and census tract-level aggregate physical activity
-participation and obesity rates in New York City, controlling for
-spatially correlated unobserved effects, spatial spillovers of
-covariates, and tract-level socioeconomic characteristics. We also
-demonstrate how the utility-based accessibility metric can potentially
-be expanded to account for other measures of a park's attractiveness
-including its observed social media activity and the presence of various
-park amenities. The paper concludes with a discussion of opportunities
-for future research.
+robust theoretical bases.
+
+In this paper, we apply a holistic and flexible measurement for park
+accessibility based in activity location choice theory. This
+utility-based accessibility measure compares the continuous distance to
+all parks in the region, weighted against the sizes of each park and its
+other assorted amenities. We apply this measure to study the link
+between park accessibility and attractiveness and census tract-level
+aggregate physical activity participation and obesity rates in New York
+City, controlling for spatially correlated unobserved effects, spatial
+spillovers of covariates, and tract-level socioeconomic characteristics.
+We also demonstrate how the utility-based accessibility metric can
+potentially be expanded to account for other measures of a park's
+attractiveness in the form of various park amenities. The paper
+concludes with a discussion of opportunities for future research.
 
@@
 
-\label{sec:litreview}
-
-The large majority of extant research on the topic of park access and
-public health outcomes has been focused on comparing metropolitan
-regions against each other. For example, \citet{West2012} used park data
-from the Trust for Public Land's 2010 ``City Park Facts'' and public
-health data from the Behavioral Risk Factor Surveillance System (BRFSS)
-to examine the relationship between the density of park land and
-physical activity and obesity rates for 67 metropolitan statistical
-areas in the U.S. The findings in this case conformed to expectation;
-that is, the study found a significant positive association between park
-density and physical activity and a significant negative association
-between park density and obesity. \citet{Larson2016} similarly used
-self-reported scores on the Gallup-Healthways Wellbeing Index to
-evaluate the relationship between physical health and park quantity,
-quality, and accessibility in 44 U.S. cities. While the authors found
-positive associations between wellbeing and park quality and
-accessibility, these relationships were not statistically significant.
-Conversely, \citet{Richardson2012} examined the relationship between
-total urban greenspace and mortality rates for selected maladies; though
-the authors did not find a statistically significant relationship
-between the quantity of urban greenspace and mortality caused by lung
-cancer, diabetes, heart disease or car accidents, they did find that
-all-cause mortality was --- oddly --- \emph{higher} in greener cities.
-Finally, in a meta-analysis of 20 peer reviewed journal articles
-exploring the relationship between parks and objectively measured
-physical activity, \citet{Bancroft2015} found that five studies reported
-a significant positive association between the two, six studies produced
-mixed results, and nine studies found no association at all.
-
-Metropolitan-level analyses such as those described above do not capture
-the within-city variation in accessibility to parks that exist in many
-cities. Some cities with large amounts of total greenspace may
-nevertheless unequally distribute this space throughout the city,
-leading to areas with poor access. Conversely, a city with a smaller
-overall proportion of greenspace may give all of its citizens better
-access to sufficient greenspace to meet their needs or desires for
-physical activity. Considering access at the neighborhood level within a
-single city may also eliminate some regional or cultural fixed effects
-affecting metropolitan-level analyses.
-
-\hypertarget{park-accessibility-measures}{%
-\subsection{Park Accessibility
-Measures}\label{park-accessibility-measures}}
+\label{sec:litreview} The question of how green space in the urban
+environment affects the physical, emotional, and mental well-being of
+urban residents is not new to the academic literature. Comprehensive
+reviews and analysis of this literature up to 2007 can be had from
+\citet{tzoulas2007promoting}, and for the subsequent decade from
+\citet{kabisch2015human}. In spite of the depth of this research arena
+--- or perhaps because of it --- quantitative approaches for assessing
+both health outcomes and access to green space vary widely. It is
+therefore not surprising that in a meta-analysis of 20 recent peer
+reviewed journal articles exploring the relationship between access to
+parks and objectively measured physical activity, \citet{Bancroft2015}
+found that five studies reported a significant positive association, six
+studies produced mixed results, and nine studies found no association at
+all.
 
@@
 Accessibility is an abstract concept with tempting quantifiability
-\citep{Handy1997}, perhaps explaining the proliferation of calculation
-mechanisms. \citet{Dong2006} present a helpful mathematical heirarchy of
-common mechanisms, which we follow here. Consider a person residing at
-point \(i\) in a city with parks \(j \in 1 \ldots J\). An analyst might
-consider point \(i\) as ``having access'' to a park if the distance to
-the park \(d_{ij}\) is within an ``isochrone,'' or a geometric buffer
-defined by some threshold \(D\),
+\citep{Handy1997}, but objective quantification may not be strictly
+necessary. For example, \citet{takano2002urban} showed improved survival
+rates among senior citizens in Japan who self-reported having access to
+qualitatively good walking spaces. Though encouraging, this result could
+simply reveal self-selection: Those seniors who felt the walking space
+was good were those who chose to enjoy it. Urban planners seeking to
+evaluate which residents have good access to quality green space may
+desire objective and therefore comparable measures.
+
+\citet{Dong2006} present a helpful mathematical hierarchy of common
+quantitative mechanisms for calculating access, which we follow here.
+Consider a person residing at point \(i\) in a city with parks
+\(j \in 1 \ldots J\). An analyst might consider point \(i\) as ``having
+access'' to a park if the distance to the park \(d_{ij}\) is within an
+``isochrone,'' or a geometric buffer defined by some threshold \(D\),
 
@@
 
-Variations of this isochrone-based framework are easily derived and
+Applications of this isochrone-based framework are easily derived and
 relatively common. ParkScore \citep{parkscore2019} is a sophisticated
@@
 10-minute network-bound walk, paired with a demographic analysis of
-areas within and outside of this threshold. In other applications \(D\)
-might be more variably defined, such as the presence or percent of green
-space within a political or statistical boundary
-\citep{Mitchell2008, Stark2014} or within a specific distance threshold
-\citep{Kaczynski2014}. It is also possible to attenuate an isochrone
-with various factors; for instance, \citet{Dias2019} considered road
-safety perception as an extenuating factor in the effective distance to
-a park.
+areas within and outside of this threshold. \citet{devries2003natural}
+showed the amount of greenspace within a 3-kilometer radius was
+positively associated with a suite of self-reported health outcomes.
+Similarly, \citet{devries2013streetscape} showed that streetscape
+greenery within 500 meters of a residence was associated with perceived
+general health. Conversely, \citet{carlson2012interactions} found no
+relationship between the health of senior citizens and the number of
+parks within 500 meters.
+
+Another common access measure fits in this category, where
+distance-based isochrones are replaced with political, geographical, or
+statistical boundaries. For example, \citet{Mitchell2008} find that
+inequalities in health outcomes attributable to income are mitigated in
+statistical areas with a greater percentage of green space. These are
+especially common in comparative macroscopic studies, such as the
+positive relationships found by \citet{West2012} between density of park
+land in a metropolitan area and self-reported population health
+indicators derived from the Behavioral Risk Factor Surveillance System
+(BRFSS). On the other hand, \citet{Larson2016} found no relationship
+between physical health and park quantity, quality, and accessibility in
+44 U.S. cities and self-reported scores on the Gallup-Healthways
+Wellbeing Index. At the sub-metropolitan level, \citet{Stark2014} found
+a significant relationship in New York City between the percent of a
+residential ZIP code that is park space and objectively measured body
+mass index (BMI). It is also possible to attenuate an isochrone with
+various factors; for instance, \citet{Dias2019} considered road safety
+perception as an extenuating factor in the effective distance to a park.
 
 In spite of the flexibility of adapted isochrone techniques, the
-arbritrary definitions necessarily imposed by researchers in its
+arbitrary definitions necessarily imposed by researchers in its
 application can inhibit holistic analysis \citep{Logan2017}. A somewhat
@@
 the attributes of a park influence walking more than merely the distance
-to it. \citet{Zhang2011} develop a population-weighted, gravity-based
-accessibility to parks metric with a national scope, though they do not
-examine its correlation with health outcomes.
+to it. \citet{hillsdon2006relationship} found no relationship between a
+gravity-based accessibility term and self-reported physical activity
+among middle-aged individuals in Norwich, England. \citet{Zhang2011}
+developed a population-weighted, gravity-based accessibility to parks
+metric with a national scope, though they do not examine its correlation
+with health outcomes.
 
@@
 \begin{equation}\label{eq:utilityV}
-V_{ij} = X_j\beta + \beta_d * d_{ij}
-\end{equation} The coefficients \(\vect{\beta}\) are frequently
+V_{ij} = X_j\boldsymbol{\beta} + \beta_d * d_{ij}
+\end{equation} The coefficients \(\boldsymbol{\beta}\) are frequently
 estimated from household surveys, though in the absence of a survey we
@@
 utility-based specification where
-\(\exp(X_j\beta + \beta_d d_{ij}) = X_j f(d_{ij})\) \citep{Daly1982}.
-The distinction between gravity and utility-based specification is
-meaningful, however. Primarily, it becomes possible to construct
-accessibility statistics based on revealed behavioral preferences rather
-than calibrated or asserted values \citep{Handy1997}.
-\citet{Kaczynski2016} present what is effectively a utility-based
-accessibility score they call ``ParkIndex'', with the explicit
-motivation of developing a uniformly applicable park accessibility
-statistic, though they limit this statistic as a way to add
-heterogeneity within an isochrone analysis.
+\(\exp(X_j\boldsymbol{\beta} + \beta_d d_{ij}) = X_j f(d_{ij})\)
+\citep{Daly1982}. The distinction between gravity and utility-based
+specification is meaningful, however. Primarily, it becomes possible to
+construct accessibility statistics based on revealed behavioral
+preferences rather than calibrated or asserted values \citep{Handy1997}.
+\citet{Kinnell2006} collected a choice-based survey sufficient to
+construct a utility-based measure, though they do not do so. Similarly,
+\citet{Kaczynski2016} present what is effectively a utility-based score
+called ``ParkIndex'', with the explicit motivation of developing a
+uniformly applicable park accessibility statistic, though they limit
+this statistic as a way to add heterogeneity within an isochrone
+analysis.
 
@@
 going forward. For each park, we calculate the size of the park in
-acres. Finally, using a Twitter application programming interface (API)
-implemented with the Python package Tweepy, we also collected and stored
-tweets containing geotags of precise geographic coordinates located
-within the boundaries of the parks; from this information, we were able
-to segregate tweets that were generated within a park in September 2014.
-This geolocated twitter activity could provide an additional point of
-information on the degree to which individual parks are actually used
-\citep{Wang2016}.
+acres.
 
@@
 \multicolumn{6}{l}{\textbf{Tract Variables, N = 2102}}\\
-\hspace{1em}Obesity & Share of adults over 18 who are obese & 10.20 & \makecell{24.90\\ (19.83, 30.80)} & 45.40 & CDC 500 Cities\\
-\hspace{1em}Physical Activity & Share of adults over 18 who engage in some leisure-time physical activity & 45.90 & \makecell{72.10\\ (66.60, 76.77)} & 90.70 & CDC 500 Cities\\
+\hspace{1em}Obesity & Share of adults over 18 who are obese & 9.60 & \makecell{24.50\\ (19.60, 30.50)} & 44.20 & CDC 500 Cities\\
+\hspace{1em}Physical Activity & Share of adults over 18 who engage in some leisure-time physical activity & 48.10 & \makecell{69.50\\ (64.70, 74.60)} & 89.10 & CDC 500 Cities\\
 \hspace{1em}Income & Median tract income & 9053.00 & \makecell{59,592.50\\ (41,928.25, 79,092.75)} & 250001.00 & ACS\\
@@
 \hspace{1em}Trails & Presence of trails & 0.00 & \makecell{0.00\\ (0.00, 0.00)} & 1.00 & NYC\\
-\hspace{1em}Tweets & Tweets emanating from park in September 2014 & 0.00 & \makecell{0.00\\ (0.00, 2.00)} & 1593.00 & Twitter API\\
 \bottomrule
@@
 
-We calculate a set of utility-based accessibility statistics for each
+We calculate a pair of utility-based accessibility statistics for each
 tract in New York City. The most basic utility specification includes
-only the park size in acres and the distance from the
-population-weighted tract centroid to the boundary of the park in miles,
-\begin{equation}\label{eq:u_access}
+only the park size in acres and the Euclidean distance from the
+population-weighted tract centroid to the nearest boundary of the park
+in miles, \begin{equation}\label{eq:u_access}
 V_{ij} = \lambda_s * \log(size_j) + \lambda_d * \log(distance_{ij})
-\end{equation} The logarithmic transform allows for diminishing marginal
-utility of distance and park size: A 1-mile increase to a trip matters
-more for a 1-mile trip than a 10-mile trip. \citet{Macfarlane2019}
-estimated destination choice parameters for park trips in Alameda County
+\end{equation} There are a few cases where the population-weighted tract
+centroid lies on or within the boundary of a park; for these cases we
+assert that the minimum possible distance is one tenth of a mile. The
+logarithmic transform allows for diminishing marginal utility of
+distance and park size: A 1-mile increase to a trip matters more for a
+1-mile trip than a 10-mile trip. \citet{Macfarlane2019} estimated
+destination choice parameters for park trips in Alameda County
 (Oakland), California by applying this utility specification to
@@
 
-The third utility specification includes the number of geolocated tweets
-emanating from within the park in September of 2014 in addition to the
-size and distance terms in Equation \ref{eq:u_access},
-\begin{equation}\label{eq:u_tweets}
-\begin{split}
-V_{ij} &= \lambda_s * \log(size_j) + \lambda_d * \log(distance_{ij}) + \\ 
-  &\quad \lambda_{tw} * YJ(tweets)
-\end{split}
-\end{equation} with \(YJ(x)\) being a Yeo-Johnson transformation that
-implements a diminishing marginal return similar to \(log(x)\), but
-where \(YJ(0) = 0\) \citep{Yeo2000}. In this case we have no external
-information describing how destination choice to parks may be affected
-by the twitter activity in the park, so we assert a value of
-\(\lambda_{tw} = 0.1\)
-
 We then calculate the utility-based accessibility of each tract \(A_i\)
@@
 census tract as a linear function of the tract's sociodemographic
-characteristics \(X\) and accessibility to parks \(A\),
+characteristics \(X\) and accessibility to parks \(\boldsymbol{A}\),
 \begin{equation}\label{eq:themodel}
- y = X\beta + \beta_{a}A + \varepsilon
-\end{equation}
+ \boldsymbol{y} = X\boldsymbol{\beta} + \beta_{a}\boldsymbol{A} + \boldsymbol{\varepsilon}
+\end{equation} where \(X\) is a matrix of dimension \(n\times p\) where
+\(n\) is the number of observations and \(p\) is the number of predictor
+variables, and \(\boldsymbol{\beta}\) is a \(p\times 1\) vector of
+estimated parameters. The accessibility vector \(\boldsymbol{A}\)
+influences physical activity or obesity rates by the single estimated
+parameter \(\beta_a\), and a vector \(\boldsymbol{\varepsilon}\)
+represents the model residual as a random variable.
 
@@
 \begin{equation}\label{eq:autoregression}
- x = \rho W x + \varepsilon
+ \boldsymbol{x} = \rho W \boldsymbol{x} + \boldsymbol{\varepsilon}
 \end{equation} with the strength of dependence an estimated parameter
@@
 the autodependence relationship on the dependent variable
-\(y = \rho W y + \ldots\) has \(\rho = 0\) in the current case.
+\(\boldsymbol{y} = \rho W \boldsymbol{y} + \ldots\) has \(\rho = 0\) in
+the current case.
 
@@
 model residuals are spatially dependent, \begin{equation}\label{eq:SEM}
- y = X\beta + \beta_a A + u; u = \lambda W u + \varepsilon
+ \boldsymbol{y} = X\boldsymbol{\beta} + \beta_a \boldsymbol{A} + \boldsymbol{u}; \boldsymbol{u} = \lambda W \boldsymbol{u} + \boldsymbol{\varepsilon}
 \end{equation} that the outcome is partially dependent on the
@@
 \begin{equation}\label{eq:SLX}
- y = X\beta + \beta_a A + W X \gamma + \varepsilon
+ \boldsymbol{y} = X\boldsymbol{\beta} + \beta_a \boldsymbol{A} + W X \boldsymbol{\gamma} + \boldsymbol{\varepsilon}
 \end{equation} or a linear combination of both.
 \begin{equation}\label{eq:SDEM}
- y = X\beta + \beta_a A + W X \gamma + u; u = \lambda W u + \varepsilon 
+ \boldsymbol{y} = X\boldsymbol{\beta} + \beta_a \boldsymbol{A} + W X \boldsymbol{\gamma} + \boldsymbol{u}; \boldsymbol{u} = \lambda W \boldsymbol{u} + \boldsymbol{\varepsilon}
 \end{equation} These models are referred as the spatial error model
@@
 error model (SDEM). \citet{Pace2008} suggest that a Hausman-style test
-of the estimates of \(\beta\) derived from the OLS (Equation
-\ref{eq:themodel}) and SEM (Equation \ref{eq:SEM}) can identify whether
-the estimates are consistent. If the \(\beta\) estimates are dissimilar,
-both specifications are inappropriate as they contain untreated omitted
-variables. Similarly, if the SLX and SDEM estimates are dissimilar it is
-an indication of missing variables in that specification. On the other
-hand if the estimates of both pairs of models are similar and the
-residual correlation parameter \(\lambda\) is non-zero, the model
-accounting for spatially dependent residuals will produce proper
-estimates of the model standard errors.
+of the estimates of \(\boldsymbol{\beta}\) derived from the OLS
+(Equation \ref{eq:themodel}) and SEM (Equation \ref{eq:SEM}) can
+identify whether the estimates are consistent. If the
+\(\boldsymbol{\beta}\) estimates are dissimilar, both specifications are
+inappropriate as they contain untreated omitted variables. Similarly, if
+the SLX and SDEM estimates are dissimilar it is an indication of missing
+variables in that specification. On the other hand if the estimates of
+both pairs of models are similar and the residual correlation parameter
+\(\lambda\) is non-zero, the model accounting for spatially dependent
+residuals will produce proper estimates of the model standard errors.
 
 Note that in the lag-\(X\) specifications (SLX and SDEM) we exclude the
-accessiblity component \(A\), that is we do \emph{not} consider that the
-accessibility in a neighboring zone will have an effect on physical
-activity or obesity rates. In a practical sense, this is because the
-accessibility term \(A\) is itself spatially determined.
+accessiblity component \(\boldsymbol{A}\), that is we do \emph{not}
+consider that the accessibility in a neighboring zone will have an
+effect on physical activity or obesity rates. In a practical sense, this
+is because the accessibility term \(\boldsymbol{A}\) is itself spatially
+determined.
 
@@
 the coefficients are equivalent; this test produces \(p\)-value of only
-\(0.03057\). Though this statistic is technically beneath a common
-hypothesis test threshold of \(\alpha = 0.05\), we fail to reject the
-null hypothesis that the coefficients are equivalent, as the differences
-are at no point practically different from each other. The consequences
-of rejecting the null hypothesis in this case would be to suggest a
-model with spatial dependence of the dependent variable; as stated
-above, we feel that such a relationship is unreasonable. As a
-consequence of these analyses, we adopt the SDEM specification moving
-forward as the spatial lag of the errors is significant and the overal
-log likelihood of the SDEM is higher than the SLX specification.
+\(1.307e-23\). Though this statistic is well beneath a common hypothesis
+test threshold of \(\alpha = 0.05\), we elect retain the null hypothesis
+that the coefficients are equivalent, as the differences are at no point
+practically different from each other. The consequences of rejecting the
+null hypothesis in this case would be to suggest a model with spatial
+dependence of the dependent variable; as stated above, we feel that such
+a relationship is unreasonable. As a consequence of these analyses, we
+adopt the SDEM specification moving forward as the spatial lag of the
+errors is significant and the overal log likelihood of the SDEM is
+higher than the SLX specification.
 
@@
 \label{tab:slx-sdem}
-
-\begin{tabular}{l c c}
+\begin{tabular}{l d{2.4} d{2.4} d{2.4} c d{2.4} d{2.4} d{2.4} }
 \toprule
- & SLX & SDEM \\
+ & \multicolumn{3}{c}{SLX} & & \multicolumn{3}{c}{SDEM} \\
+\cmidrule{2-4}\cmidrule{6-8}
+ & \multicolumn{1}{c}{Estimate} & \multicolumn{2}{c}{95\% Conf.Int.} &
+ & \multicolumn{1}{c}{Estimate} & \multicolumn{2}{c}{95\% Conf.Int.}\\
 \midrule
-(Intercept)                         & $-35.3520 \; [-47.4781; -23.2260]^{*}$ & $-27.2048 \; [-45.0525; -9.3571]^{*}$ \\
-log(Density)                        & $0.1057 \; [ -0.0920;   0.3034]$       & $0.2301 \; [  0.0646;  0.3956]^{*}$   \\
-log(Income)                         & $6.4092 \; [  5.8339;   6.9845]^{*}$   & $6.2664 \; [  5.7721;  6.7607]^{*}$   \\
-Fulltime                            & $0.1365 \; [  0.1130;   0.1601]^{*}$   & $0.1434 \; [  0.1221;  0.1647]^{*}$   \\
-College-educated                    & $0.0371 \; [  0.0058;   0.0683]^{*}$   & $0.0313 \; [  0.0042;  0.0583]^{*}$   \\
-Single Adults                       & $-0.0488 \; [ -0.0696;  -0.0279]^{*}$  & $-0.0472 \; [ -0.0659; -0.0284]^{*}$  \\
-Youth (0-17)                        & $-0.1292 \; [ -0.1643;  -0.0941]^{*}$  & $-0.1300 \; [ -0.1608; -0.0992]^{*}$  \\
-Young adults (18-34)                & $0.0395 \; [  0.0122;   0.0669]^{*}$   & $0.0387 \; [  0.0153;  0.0622]^{*}$   \\
-Seniors (65+)                       & $0.0301 \; [ -0.0053;   0.0655]$       & $0.0354 \; [  0.0038;  0.0671]^{*}$   \\
-Black population share              & $-0.0522 \; [ -0.0653;  -0.0391]^{*}$  & $-0.0536 \; [ -0.0641; -0.0432]^{*}$  \\
-Asian population share              & $-0.0941 \; [ -0.1101;  -0.0781]^{*}$  & $-0.0954 \; [ -0.1081; -0.0827]^{*}$  \\
-Hispanic population share           & $-0.1134 \; [ -0.1270;  -0.0998]^{*}$  & $-0.1152 \; [ -0.1261; -0.1044]^{*}$  \\
-Other Minorities                    & $0.0154 \; [ -0.0957;   0.1265]$       & $-0.0119 \; [ -0.1145;  0.0906]$      \\
-$\gamma$: log(Density)              & $1.6773 \; [  1.3277;   2.0269]^{*}$   & $1.1617 \; [  0.7470;  1.5764]^{*}$   \\
-$\gamma$: log(Income)               & $1.9854 \; [  1.0562;   2.9146]^{*}$   & $1.6505 \; [  0.5414;  2.7597]^{*}$   \\
-$\gamma$: Fulltime                  & $-0.0309 \; [ -0.0756;   0.0138]$      & $-0.0006 \; [ -0.0530;  0.0517]$      \\
-$\gamma$: College-educated          & $-0.0002 \; [ -0.0545;   0.0541]$      & $-0.0174 \; [ -0.0819;  0.0471]$      \\
-$\gamma$: Single Adults             & $-0.0390 \; [ -0.0764;  -0.0016]^{*}$  & $-0.0210 \; [ -0.0667;  0.0247]$      \\
-$\gamma$: Youth (0-17)              & $0.0297 \; [ -0.0348;   0.0941]$       & $0.0205 \; [ -0.0552;  0.0962]$       \\
-$\gamma$: Young adults (18-34)      & $0.1318 \; [  0.0847;   0.1789]^{*}$   & $0.0872 \; [  0.0319;  0.1424]^{*}$   \\
-$\gamma$: Seniors (65+)             & $0.1505 \; [  0.0860;   0.2151]^{*}$   & $0.1181 \; [  0.0420;  0.1941]^{*}$   \\
-$\gamma$: Black population share    & $0.0156 \; [ -0.0010;   0.0321]$       & $0.0102 \; [ -0.0073;  0.0278]$       \\
-$\gamma$: Asian population share    & $-0.0325 \; [ -0.0521;  -0.0129]^{*}$  & $-0.0399 \; [ -0.0601; -0.0197]^{*}$  \\
-$\gamma$: Hispanic population share & $-0.0028 \; [ -0.0201;   0.0144]$      & $0.0003 \; [ -0.0182;  0.0187]$       \\
-$\gamma$: Other Minorities          & $0.2827 \; [  0.0215;   0.5438]^{*}$   & $0.1799 \; [ -0.1104;  0.4703]$       \\
-Accessibility                       & $0.4522 \; [  0.3218;   0.5825]^{*}$   & $0.2076 \; [  0.0554;  0.3597]^{*}$   \\
-$\lambda$: spatial correlation      &                                        & $0.5813 \; [  0.5344;  0.6282]^{*}$   \\
+% latex table generated in R 4.0.0 by xtable 1.8-4 package
+% Thu Jun  4 16:31:52 2020
+ (Intercept) & -15.8424 & -26.8735 & -4.8112 &   & -24.9740 & -41.8930 & -8.0549 \\
+  log(Density) & 0.0484 & -0.1314 & 0.2282 &   & 0.1775 & 0.0384 & 0.3166 \\
+  log(Income) & 5.8210 & 5.2977 & 6.3443 &   & 5.9985 & 5.5746 & 6.4224 \\
+  Fulltime & 0.1150 & 0.0936 & 0.1365 &   & 0.1275 & 0.1090 & 0.1460 \\
+  College-educated & 0.0012 & -0.0272 & 0.0297 &   & 0.0076 & -0.0158 & 0.0309 \\
+  Single Adults & -0.0433 & -0.0623 & -0.0244 &   & -0.0362 & -0.0526 & -0.0198 \\
+  Youth (0-17) & -0.1511 & -0.1830 & -0.1192 &   & -0.1310 & -0.1576 & -0.1045 \\
+  Young adults (18-34) & 0.0257 & 0.0008 & 0.0505 &   & 0.0295 & 0.0094 & 0.0496 \\
+  Seniors (65+) & 0.0137 & -0.0185 & 0.0459 &   & 0.0403 & 0.0130 & 0.0677 \\
+  Black population share & -0.0465 & -0.0584 & -0.0346 &   & -0.0499 & -0.0586 & -0.0411 \\
+  Asian population share & -0.0686 & -0.0832 & -0.0541 &   & -0.0767 & -0.0873 & -0.0662 \\
+  Hispanic population share & -0.1017 & -0.1140 & -0.0894 &   & -0.1025 & -0.1116 & -0.0934 \\
+  Other Minorities & 0.0368 & -0.0643 & 0.1378 &   & 0.0037 & -0.0849 & 0.0923 \\
+  $\gamma$: log(Density) & 1.2594 & 0.9413 & 1.5774 &   & 1.0985 & 0.7155 & 1.4815 \\
+  $\gamma$: log(Income) & 2.3930 & 1.5476 & 3.2383 &   & 1.9742 & 0.9465 & 3.0020 \\
+  $\gamma$: Fulltime & -0.1398 & -0.1804 & -0.0991 &   & -0.0397 & -0.0869 & 0.0076 \\
+  $\gamma$: College-educated & -0.1312 & -0.1806 & -0.0818 &   & -0.0710 & -0.1305 & -0.0115 \\
+  $\gamma$: Single Adults & -0.0480 & -0.0821 & -0.0140 &   & -0.0082 & -0.0504 & 0.0339 \\
+  $\gamma$: Youth (0-17) & -0.1031 & -0.1618 & -0.0445 &   & -0.0108 & -0.0798 & 0.0583 \\
+  $\gamma$: Young adults (18-34) & 0.1191 & 0.0762 & 0.1619 &   & 0.0842 & 0.0335 & 0.1349 \\
+  $\gamma$: Seniors (65+) & 0.0108 & -0.0479 & 0.0695 &   & 0.0590 & -0.0102 & 0.1282 \\
+  $\gamma$: Black population share & 0.0096 & -0.0054 & 0.0247 &   & 0.0010 & -0.0151 & 0.0172 \\
+  $\gamma$: Asian population share & -0.0661 & -0.0840 & -0.0483 &   & -0.0397 & -0.0583 & -0.0210 \\
+  $\gamma$: Hispanic population share & -0.0060 & -0.0216 & 0.0097 &   & -0.0010 & -0.0182 & 0.0162 \\
+  $\gamma$: Other Minorities & 0.1868 & -0.0508 & 0.4244 &   & 0.0726 & -0.1845 & 0.3297 \\
+  Accessibility & 0.5430 & 0.4195 & 0.6666 &   & 0.1663 & 0.0277 & 0.3048 \\
+  $\lambda$: spatial correlation &  &  &  &   & 0.6905 & 0.6513 & 0.7296 \\
+
 \midrule
-Log Likelihood                      & $-5032.2042$                           & $-4786.9274$                          \\
-Num. Obs.                           & $2099$                                 & $2099$                                \\
-LR test: statistic                  & $$                                     & $490.5536$                            \\
-LR test: p-value                    & $$                                     & $0.0000$                              \\
+Log Likelihood & \multicolumn{3}{c}{$-4831.974$} & & \multicolumn{3}{c}{$-4435.507$}\\
+Num.Obs.       & \multicolumn{3}{c}{$2099$}   & & \multicolumn{3}{c}{$2099$}\\
 \bottomrule
-\multicolumn{3}{l}{\scriptsize{$^*$ 0 outside the confidence interval. $y = $ tract-level physical activity rate.}}
 \end{tabular}
@@
 effect resulting from a tract's own attributes and the indirect effect
-(\(\gamma\)) resulting from the spatially-weighted attributes of its
-neighbors. For example, a percentage point increase in the share of
-young adults in a tract increases the expected physical activity rate in
-a tract by 0.03872 percentage points, and a percentage point increase in
-the share of young adults \emph{in neighboring tracts} increases the
-expected physical activity rate by an \emph{additional} 0.08718
-percentage points. This opportunity to examine spatial spillovers of
-attributes is a key benefit of using a spatial model.
+(\(\boldsymbol{\gamma}\)) resulting from the spatially-weighted
+attributes of its neighbors. For example, a percentage point increase in
+the share of young adults in a tract increases the expected physical
+activity rate in a tract by 0.02947 percentage points, and a percentage
+point increase in the share of young adults \emph{in neighboring tracts}
+increases the expected physical activity rate by an \emph{additional}
+0.08417 percentage points. This opportunity to examine spatial
+spillovers of attributes is a key benefit of using a spatial model.
 
@@
 utility-based accessiblity to green spaces show a significantly higher
-physical activity participation rate. Taking the rough mean of the three
+physical activity participation rate. Taking the rough mean of the 2
 estimated utility-based coefficients, moving from the least-accessible
 tract (\(A_i = -3\)) to the most-accessible tract (\(A_i = 3\)) is
-expected to raise the physical activity rate by 1.2 percentage points.
+expected to raise the physical activity rate by 0.9 percentage points.
 With the understanding of the full 95\% confidence interval, we could
 suggest that the true effect of excellent versus poor park access is
-anywhere between 0.3 and 2.1 percentage points.
+anywhere between 0.06 and 1.8 percentage points.
 
@@
 effect is large and implies an effect on activity rates anywhere from a
-loss of 2.22 percentage points to a gain of 9.
+loss of 1.08 percentage points to a gain of 8.1.
 
@@
 
-\begin{tabular}{l c c c c}
+\begin{tabular}{l c c c }
 \toprule
- & Size and Distance & Twitter & Amenities & 10-Minute Walk \\
+ & Size and Distance & Amenities & 10-Minute Walk \\
 \midrule
-Size and Distance & $0.2076^{*}$        &                     &                     &                      \\
-                  & $ [0.0554; 0.3597]$ &                     &                     &                      \\
-Amenities         &                     &                     & $0.1975^{*}$        &                      \\
-                  &                     &                     & $ [0.0428; 0.3522]$ &                      \\
-Twitter Activity  &                     & $0.2229^{*}$        &                     &                      \\
-                  &                     & $ [0.0659; 0.3799]$ &                     &                      \\
-10-minute walk    &                     &                     &                     & $0.5682$             \\
-                  &                     &                     &                     & $ [-0.3638; 1.5001]$ \\
+Accessibility  & $0.1663^{*}$        & $0.1493^{*}$        & $0.5865$             \\
+               & $[0.0277;\ 0.3048]$ & $[0.0073;\ 0.2914]$ & $[-0.1778;\ 1.3508]$ \\
 \midrule
-Num. obs.         & $2099$              & $2099$              & $2099$              & $2099$               \\
-Parameters        & $28$                & $28$                & $28$                & $28$                 \\
-Log Likelihood    & $-4786.9274$        & $-4786.6411$        & $-4787.3677$        & $-4789.6660$         \\
+Num. obs.      & 2099                & 2099                & 2099                 \\
+Parameters     & 28                  & 28                  & 28                   \\
+Log Likelihood & -4435.3869          & -4436.0034          & -4436.9264           \\
 \bottomrule
-\multicolumn{5}{l}{\scriptsize{$^*$ 0 outside the confidence interval. 95\% confidence interval in brackets.}}
+\multicolumn{4}{l}{\scriptsize{$^*$ 0 outside the confidence interval 95\% confidence interval in brackets.  $y = $ tract-level physical activity rate.}}
 \end{tabular}
@@
 rates in tracts with excellent park accessibility are expected to be
-between 0.9 percentage points lower and 0.0318 percentage points higher
+between 0.72 percentage points lower and 0.21 percentage points higher
 than tracts with poor park accessibility. This range of values suggests
@@
 
-\begin{tabular}{l c c c c}
+\begin{tabular}{l c c c }
 \toprule
- & Size and Distance & Twitter & Amenities & 10-Minute Walk \\
+ & Size and Distance & Amenities & 10-Minute Walk \\
 \midrule
-Physical Activity           & $-0.4251^{*}$         & $-0.4250^{*}$         & $-0.4251^{*}$         & $-0.4256^{*}$         \\
-                            & $ [-0.4463; -0.4039]$ & $ [-0.4462; -0.4038]$ & $ [-0.4463; -0.4039]$ & $ [-0.4468; -0.4045]$ \\
-$\gamma$: Physical Activity & $-0.0321$             & $-0.0317$             & $-0.0318$             & $-0.0362$             \\
-                            & $ [-0.0841;  0.0199]$ & $ [-0.0838;  0.0203]$ & $ [-0.0839;  0.0203]$ & $ [-0.0882;  0.0158]$ \\
-Size and Distance           & $-0.0688$             &                       &                       &                       \\
-                            & $ [-0.1440;  0.0064]$ &                       &                       &                       \\
-Amenities                   &                       &                       & $-0.0695$             &                       \\
-                            &                       &                       & $ [-0.1472;  0.0083]$ &                       \\
-Twitter Activity            &                       & $-0.0731$             &                       &                       \\
-                            &                       & $ [-0.1516;  0.0053]$ &                       &                       \\
-10-minute walk              &                       &                       &                       & $-0.3573$             \\
-                            &                       &                       &                       & $ [-0.7650;  0.0505]$ \\
+Physical Activity           & $-0.4802^{*}$         & $-0.4802^{*}$         & $-0.4803^{*}$         \\
+                            & $[-0.5043;\ -0.4561]$ & $[-0.5043;\ -0.4561]$ & $[-0.5044;\ -0.4562]$ \\
+$\gamma$: Physical Activity & $0.0197$              & $0.0198$              & $0.0173$              \\
+                            & $[-0.0380;\ 0.0775]$  & $[-0.0380;\ 0.0775]$  & $[-0.0404;\ 0.0750]$  \\
+Accessibility               & $-0.0403$             & $-0.0429$             & $-0.2630$             \\
+                            & $[-0.1158;\ 0.0351]$  & $[-0.1210;\ 0.0352]$  & $[-0.6491;\ 0.1232]$  \\
 \midrule
-Num. obs.                   & $2099$                & $2099$                & $2099$                & $2099$                \\
-Parameters                  & $30$                  & $30$                  & $30$                  & $30$                  \\
-Log Likelihood              & $-3194.8851$          & $-3194.8268$          & $-3194.9556$          & $-3195.0152$          \\
+Num. obs.                   & 2099                  & 2099                  & 2099                  \\
+Parameters                  & 30                    & 30                    & 30                    \\
+Log Likelihood              & -3113.8451            & -3113.8136            & -3113.5028            \\
 \bottomrule
-\multicolumn{5}{l}{\scriptsize{$^*$ 0 outside the confidence interval. 95\% confidence interval in brackets.}}
+\multicolumn{4}{l}{\scriptsize{$^*$ 0 outside the confidence interval 95\% confidence interval in brackets.  $y = $ tract-level obesity rate.}}
 \end{tabular}
@@
 ecological inference fallacy, where aggregate statistics mask or
-contradict disaggregated or individual-level trends. A large-sample
-survey of individuals in New York City, including measured physical
-activities and obesity would always be preferable to the tract-level
-data used in this study. An ideal survey to address the question would
-incorporate both sets of questions: physical activity and health data on
-one hand and park use (including which parks were used and how
-frequently) on the other. As no such dataset exists to our knowledge,
-this tract-level aggregate analysis with asserted and transferred
-utility coefficients is the possibility that remains.
+contradict disaggregated or individual-level trends. The socioeconomic
+and public health data used in this study are only available at the
+tract level; projecting the tract-level data to the block group level
+and computing more spatially precise accessibility logsums proved
+infeasible as the spatial lags of the independent variables introduced
+substantial collinearity in the model equations. A large-sample survey
+of individuals in New York City, including measured physical activities
+and obesity would always be preferable to the tract-level data used in
+this study. An ideal survey to address the question would incorporate
+both sets of questions: physical activity and health data on one hand
+and park use (including which parks were used and how frequently) on the
+other. As no such dataset exists to our knowledge, this tract-level
+aggregate analysis with asserted and transferred utility coefficients is
+the possibility that remains.
 
@@
 its residents most care about. In this paper, we proceed only
-incrementally towards this by adding Twitter activity and some selected
-park amenities as an element of each park's attractiveness above and
-beyond its size. Exploring detailed definitions of an increased number
-of amenities on one hand, and market segmentation strategies on the
-other, could provide a more nuanced understanding of the relationship
-between park accessibility and health outcomes.
+incrementally towards this by adding some selected park amenities as an
+element of each park's attractiveness above and beyond its size. The set
+of amenities we included in the utility calculation --- and the
+contribution of each amenity to the overall utility --- was dictated by
+the availability of data on the park amenities in New York City and our
+ability to find comparable prior studies with transferrable utility
+parameters. We can envision a study where mobile device data revealing
+the home locations of park users would be paired with more detailed park
+amenities and use data (e.g.~geolocated Twitter data \emph{a la}
+\citet{roberts2017using}) to estimate the utility contribution of these
+features. This could in turn provide a more nuanced understanding of the
+relationship between park accessibility, use, and health outcomes.
 
@@
 when the non-highway mode share is high, as is likely when considering
-access to parks. A better metric of travel impedance may be a mode
-choice model logsum, which weights all alternative travel alternatives
-against each other. We leave this as a recommendation for future
-research.
+access to parks. We examined replacing the Euclidean distance with a
+network-based distance; the choice of distance metric appeared
+inconsequential to our larger findings in this case while substantially
+increasing the computational load required. Additionally, we could not
+verify the accuracy of the underlying network data at the scale of this
+analysis. We therefore retain the Euclidean distance for simplicity. A
+better metric of travel impedance may be a mode choice model logsum,
+which weights all alternative travel alternatives against each other. We
+leave this as a recommendation for future research.
 
@@
 health, or any number of potential beneficial outcomes hypothesized or
-explored in the existing literature. Exploring these connections and
-their underlying mechanisms should be a priority as city planners and
-urban architects attempt to improve the quality of life of urban
-residents in the future.
+explored in the existing literature. The COVID-19 pandemic and its
+associated social distancing behaviors in many regions of the world has
+also drawn attention to problems of park access, use, and equity.
+Exploring these connections and their underlying mechanisms should be a
+priority as city planners and urban architects attempt to improve the
+quality of life of urban residents in the future.
 
@@
 relationship where the least park-accessible tracts have an expected
-physical activity participation rate between 0.3 and 2.1 percentage
+physical activity participation rate between 0.06 and 1.8 percentage
 points lower than the most accessible tracts. We also found a suggestive
@@
 separate the definition of access from the study of its effects. This
-will in turn enable planners to consider how multiple attributes of a
-park --- from its location to its size to its amenities and beyond ---
-benefit the health of the community the park serves.
+will in turn enhance the ability of planners to consider how multiple
+attributes of a park --- from its location to its size to its amenities
+and beyond --- benefit the health of the community the park serves.
+
+\begin{acks}
+This project was funded by the Speedwell Foundation. We are grateful to Rachel
+Samuels and Neda Madi for helping to assemble the data.
+\end{acks}
 
 \bibliographystyle{sageh.bst}
-\bibliography{manuscript.bbl}
-
-\appendix
-\section{Appendix}
-
-In this appendix we present the complete estimation results for the models 
-relating different definitions of access to physical activity (in Table
-\ref{tab:pa-fullmodels}) and to obesity (in Table \ref{tab:ob-fullmodels}). In
-each case we also present a base model with no accessibility statistics for
-comparison.
+\bibliography{library.bib}
+
+\hypertarget{appendix}{%
+\subsection{Appendix}\label{appendix}}
+
+In this appendix we present the complete estimation results for the
+models relating different definitions of access to physical activity (in
+Table \ref{tab:pa-fullmodels}) and to obesity (in Table
+\ref{tab:ob-fullmodels}). In each case we also present a base model with
+no accessibility statistics for comparison.
 
 \begin{table*}
-\caption{Estimated Effects of Accessibility and Controls on Physical Activity Rates}
+  \caption{\label{tab:pa-fullmodels} Estimated Effect of Accessibility on Physical Activity Rates}
   \begin{center}
-\scalebox{0.7}{
-\begin{tabular}{l c c c c c}
+  \scalebox{0.8}{
+
+\begin{tabular}{l c c c c}
 \toprule
- & No Access & Size and Distance & Tweets & Attributes & 10-min walk \\
+ & No Access & Size and Distance & Amenities & 10-minute Walk \\
 \midrule
-(Intercept)                         & $-25.9256^{*}$         & $-27.2048^{*}$         & $-26.5608^{*}$         & $-27.2431^{*}$         & $-26.1786^{*}$         \\
-                                    & $ [-43.9792; -7.8720]$ & $ [-45.0525; -9.3571]$ & $ [-44.3812; -8.7404]$ & $ [-45.1016; -9.3846]$ & $ [-44.2194; -8.1378]$ \\
-log(Density)                        & $0.2249^{*}$           & $0.2301^{*}$           & $0.2280^{*}$           & $0.2281^{*}$           & $0.2201^{*}$           \\
-                                    & $ [  0.0594;  0.3905]$ & $ [  0.0646;  0.3956]$ & $ [  0.0626;  0.3934]$ & $ [  0.0626;  0.3936]$ & $ [  0.0544;  0.3858]$ \\
-log(Income)                         & $6.2290^{*}$           & $6.2664^{*}$           & $6.2575^{*}$           & $6.2632^{*}$           & $6.2277^{*}$           \\
-                                    & $ [  5.7342;  6.7239]$ & $ [  5.7721;  6.7607]$ & $ [  5.7636;  6.7513]$ & $ [  5.7688;  6.7575]$ & $ [  5.7331;  6.7224]$ \\
-Fulltime                            & $0.1442^{*}$           & $0.1434^{*}$           & $0.1434^{*}$           & $0.1433^{*}$           & $0.1444^{*}$           \\
-                                    & $ [  0.1228;  0.1656]$ & $ [  0.1221;  0.1647]$ & $ [  0.1220;  0.1647]$ & $ [  0.1220;  0.1646]$ & $ [  0.1230;  0.1658]$ \\
-College-educated                    & $0.0307^{*}$           & $0.0313^{*}$           & $0.0316^{*}$           & $0.0307^{*}$           & $0.0315^{*}$           \\
-                                    & $ [  0.0036;  0.0578]$ & $ [  0.0042;  0.0583]$ & $ [  0.0046;  0.0586]$ & $ [  0.0036;  0.0577]$ & $ [  0.0043;  0.0586]$ \\
-Single Adults                       & $-0.0475^{*}$          & $-0.0472^{*}$          & $-0.0474^{*}$          & $-0.0469^{*}$          & $-0.0478^{*}$          \\
-                                    & $ [ -0.0663; -0.0287]$ & $ [ -0.0659; -0.0284]$ & $ [ -0.0661; -0.0286]$ & $ [ -0.0657; -0.0282]$ & $ [ -0.0667; -0.0290]$ \\
-Youth (0-17)                        & $-0.1302^{*}$          & $-0.1300^{*}$          & $-0.1304^{*}$          & $-0.1300^{*}$          & $-0.1307^{*}$          \\
-                                    & $ [ -0.1611; -0.0993]$ & $ [ -0.1608; -0.0992]$ & $ [ -0.1611; -0.0996]$ & $ [ -0.1608; -0.0992]$ & $ [ -0.1615; -0.0998]$ \\
-Young adults (18-34)                & $0.0372^{*}$           & $0.0387^{*}$           & $0.0387^{*}$           & $0.0388^{*}$           & $0.0370^{*}$           \\
-                                    & $ [  0.0137;  0.0606]$ & $ [  0.0153;  0.0622]$ & $ [  0.0153;  0.0621]$ & $ [  0.0153;  0.0622]$ & $ [  0.0135;  0.0605]$ \\
-Seniors (65+)                       & $0.0384^{*}$           & $0.0354^{*}$           & $0.0348^{*}$           & $0.0359^{*}$           & $0.0380^{*}$           \\
-                                    & $ [  0.0068;  0.0701]$ & $ [  0.0038;  0.0671]$ & $ [  0.0032;  0.0664]$ & $ [  0.0043;  0.0675]$ & $ [  0.0064;  0.0697]$ \\
-Black population share              & $-0.0537^{*}$          & $-0.0536^{*}$          & $-0.0536^{*}$          & $-0.0535^{*}$          & $-0.0535^{*}$          \\
-                                    & $ [ -0.0642; -0.0433]$ & $ [ -0.0641; -0.0432]$ & $ [ -0.0640; -0.0432]$ & $ [ -0.0639; -0.0431]$ & $ [ -0.0639; -0.0430]$ \\
-Asian population share              & $-0.0961^{*}$          & $-0.0954^{*}$          & $-0.0954^{*}$          & $-0.0955^{*}$          & $-0.0963^{*}$          \\
-                                    & $ [ -0.1088; -0.0834]$ & $ [ -0.1081; -0.0827]$ & $ [ -0.1081; -0.0827]$ & $ [ -0.1082; -0.0829]$ & $ [ -0.1090; -0.0837]$ \\
-Hispanic population share           & $-0.1148^{*}$          & $-0.1152^{*}$          & $-0.1153^{*}$          & $-0.1153^{*}$          & $-0.1147^{*}$          \\
-                                    & $ [ -0.1256; -0.1039]$ & $ [ -0.1261; -0.1044]$ & $ [ -0.1261; -0.1044]$ & $ [ -0.1261; -0.1044]$ & $ [ -0.1255; -0.1038]$ \\
-Other Minorities                    & $-0.0161$              & $-0.0119$              & $-0.0126$              & $-0.0115$              & $-0.0170$              \\
-                                    & $ [ -0.1190;  0.0867]$ & $ [ -0.1145;  0.0906]$ & $ [ -0.1151;  0.0899]$ & $ [ -0.1141;  0.0910]$ & $ [ -0.1199;  0.0858]$ \\
-$\gamma$: log(Density)              & $1.1804^{*}$           & $1.1617^{*}$           & $1.1491^{*}$           & $1.1685^{*}$           & $1.1668^{*}$           \\
-                                    & $ [  0.7624;  1.5984]$ & $ [  0.7470;  1.5764]$ & $ [  0.7341;  1.5642]$ & $ [  0.7539;  1.5831]$ & $ [  0.7484;  1.5851]$ \\
-$\gamma$: log(Income)               & $1.5660^{*}$           & $1.6505^{*}$           & $1.6211^{*}$           & $1.6398^{*}$           & $1.5611^{*}$           \\
-                                    & $ [  0.4473;  2.6848]$ & $ [  0.5414;  2.7597]$ & $ [  0.5135;  2.7288]$ & $ [  0.5305;  2.7491]$ & $ [  0.4433;  2.6790]$ \\
-$\gamma$: Fulltime                  & $0.0029$               & $-0.0006$              & $-0.0009$              & $0.0002$               & $0.0025$               \\
-                                    & $ [ -0.0498;  0.0556]$ & $ [ -0.0530;  0.0517]$ & $ [ -0.0532;  0.0514]$ & $ [ -0.0521;  0.0525]$ & $ [ -0.0502;  0.0551]$ \\
-$\gamma$: College-educated          & $-0.0190$              & $-0.0174$              & $-0.0163$              & $-0.0193$              & $-0.0212$              \\
-                                    & $ [ -0.0842;  0.0461]$ & $ [ -0.0819;  0.0471]$ & $ [ -0.0808;  0.0482]$ & $ [ -0.0839;  0.0452]$ & $ [ -0.0863;  0.0440]$ \\
-$\gamma$: Single Adults             & $-0.0218$              & $-0.0210$              & $-0.0218$              & $-0.0198$              & $-0.0215$              \\
-                                    & $ [ -0.0680;  0.0243]$ & $ [ -0.0667;  0.0247]$ & $ [ -0.0674;  0.0239]$ & $ [ -0.0655;  0.0259]$ & $ [ -0.0676;  0.0246]$ \\
-$\gamma$: Youth (0-17)              & $0.0169$               & $0.0205$               & $0.0200$               & $0.0217$               & $0.0161$               \\
-                                    & $ [ -0.0594;  0.0932]$ & $ [ -0.0552;  0.0962]$ & $ [ -0.0557;  0.0956]$ & $ [ -0.0540;  0.0975]$ & $ [ -0.0602;  0.0923]$ \\
-$\gamma$: Young adults (18-34)      & $0.0827^{*}$           & $0.0872^{*}$           & $0.0872^{*}$           & $0.0884^{*}$           & $0.0823^{*}$           \\
-                                    & $ [  0.0270;  0.1384]$ & $ [  0.0319;  0.1424]$ & $ [  0.0320;  0.1425]$ & $ [  0.0331;  0.1437]$ & $ [  0.0267;  0.1380]$ \\
-$\gamma$: Seniors (65+)             & $0.1207^{*}$           & $0.1181^{*}$           & $0.1161^{*}$           & $0.1198^{*}$           & $0.1204^{*}$           \\
-                                    & $ [  0.0440;  0.1974]$ & $ [  0.0420;  0.1941]$ & $ [  0.0400;  0.1921]$ & $ [  0.0437;  0.1958]$ & $ [  0.0438;  0.1971]$ \\
-$\gamma$: Black population share    & $0.0096$               & $0.0102$               & $0.0104$               & $0.0099$               & $0.0096$               \\
-                                    & $ [ -0.0081;  0.0273]$ & $ [ -0.0073;  0.0278]$ & $ [ -0.0071;  0.0279]$ & $ [ -0.0077;  0.0274]$ & $ [ -0.0081;  0.0273]$ \\
-$\gamma$: Asian population share    & $-0.0429^{*}$          & $-0.0399^{*}$          & $-0.0398^{*}$          & $-0.0405^{*}$          & $-0.0428^{*}$          \\
-                                    & $ [ -0.0631; -0.0226]$ & $ [ -0.0601; -0.0197]$ & $ [ -0.0599; -0.0196]$ & $ [ -0.0606; -0.0203]$ & $ [ -0.0630; -0.0225]$ \\
-$\gamma$: Hispanic population share & $0.0026$               & $0.0003$               & $0.0001$               & $0.0002$               & $0.0025$               \\
-                                    & $ [ -0.0160;  0.0212]$ & $ [ -0.0182;  0.0187]$ & $ [ -0.0184;  0.0185]$ & $ [ -0.0183;  0.0186]$ & $ [ -0.0161;  0.0210]$ \\
-$\gamma$: Other Minorities          & $0.1695$               & $0.1799$               & $0.1770$               & $0.1798$               & $0.1756$               \\
-                                    & $ [ -0.1225;  0.4616]$ & $ [ -0.1104;  0.4703]$ & $ [ -0.1132;  0.4672]$ & $ [ -0.1106;  0.4702]$ & $ [ -0.1165;  0.4677]$ \\
-$\lambda$: spatial correlation      & $0.5920^{*}$           & $0.5813^{*}$           & $0.5809^{*}$           & $0.5815^{*}$           & $0.5914^{*}$           \\
-                                    & $ [  0.5458;  0.6382]$ & $ [  0.5344;  0.6282]$ & $ [  0.5339;  0.6278]$ & $ [  0.5346;  0.6284]$ & $ [  0.5451;  0.6376]$ \\
-Size and Distance                   &                        & $0.2076^{*}$           &                        &                        &                        \\
-                                    &                        & $ [  0.0554;  0.3597]$ &                        &                        &                        \\
-Tweets                              &                        &                        & $0.2229^{*}$           &                        &                        \\
-                                    &                        &                        & $ [  0.0659;  0.3799]$ &                        &                        \\
-Attributes                          &                        &                        &                        & $0.1975^{*}$           &                        \\
-                                    &                        &                        &                        & $ [  0.0428;  0.3522]$ &                        \\
-10-min walk                         &                        &                        &                        &                        & $0.5682$               \\
-                                    &                        &                        &                        &                        & $ [ -0.3638;  1.5001]$ \\
+(Intercept)                         & $-24.5190^{*}$         & $-24.8266^{*}$         & $-24.8920^{*}$         & $-24.7176^{*}$         \\
+                                    & $ [-41.5947; -7.4433]$ & $ [-41.7445; -7.9087]$ & $ [-41.8372; -7.9468]$ & $ [-41.7891; -7.6461]$ \\
+log(Density)                        & $0.1740^{*}$           & $0.1766^{*}$           & $0.1757^{*}$           & $0.1686^{*}$           \\
+                                    & $ [  0.0348;  0.3132]$ & $ [  0.0375;  0.3156]$ & $ [  0.0366;  0.3148]$ & $ [  0.0293;  0.3079]$ \\
+log(Income)                         & $5.9786^{*}$           & $5.9976^{*}$           & $5.9964^{*}$           & $5.9767^{*}$           \\
+                                    & $ [  5.5540;  6.4032]$ & $ [  5.5737;  6.4215]$ & $ [  5.5723;  6.4205]$ & $ [  5.5523;  6.4011]$ \\
+Fulltime                            & $0.1283^{*}$           & $0.1275^{*}$           & $0.1275^{*}$           & $0.1285^{*}$           \\
+                                    & $ [  0.1098;  0.1468]$ & $ [  0.1090;  0.1460]$ & $ [  0.1090;  0.1460]$ & $ [  0.1100;  0.1470]$ \\
+College-educated                    & $0.0075$               & $0.0076$               & $0.0073$               & $0.0083$               \\
+                                    & $ [ -0.0159;  0.0310]$ & $ [ -0.0158;  0.0309]$ & $ [ -0.0161;  0.0306]$ & $ [ -0.0152;  0.0317]$ \\
+Single Adults                       & $-0.0363^{*}$          & $-0.0362^{*}$          & $-0.0360^{*}$          & $-0.0366^{*}$          \\
+                                    & $ [ -0.0527; -0.0198]$ & $ [ -0.0526; -0.0198]$ & $ [ -0.0524; -0.0196]$ & $ [ -0.0530; -0.0201]$ \\
+Youth (0-17)                        & $-0.1306^{*}$          & $-0.1311^{*}$          & $-0.1310^{*}$          & $-0.1311^{*}$          \\
+                                    & $ [ -0.1572; -0.1040]$ & $ [ -0.1576; -0.1046]$ & $ [ -0.1576; -0.1045]$ & $ [ -0.1577; -0.1045]$ \\
+Young adults (18-34)                & $0.0283^{*}$           & $0.0293^{*}$           & $0.0294^{*}$           & $0.0281^{*}$           \\
+                                    & $ [  0.0081;  0.0484]$ & $ [  0.0092;  0.0495]$ & $ [  0.0092;  0.0495]$ & $ [  0.0079;  0.0482]$ \\
+Seniors (65+)                       & $0.0430^{*}$           & $0.0403^{*}$           & $0.0408^{*}$           & $0.0427^{*}$           \\
+                                    & $ [  0.0157;  0.0704]$ & $ [  0.0130;  0.0677]$ & $ [  0.0135;  0.0682]$ & $ [  0.0153;  0.0700]$ \\
+Black population share              & $-0.0499^{*}$          & $-0.0499^{*}$          & $-0.0498^{*}$          & $-0.0497^{*}$          \\
+                                    & $ [ -0.0587; -0.0412]$ & $ [ -0.0586; -0.0412]$ & $ [ -0.0585; -0.0411]$ & $ [ -0.0584; -0.0409]$ \\
+Asian population share              & $-0.0772^{*}$          & $-0.0767^{*}$          & $-0.0768^{*}$          & $-0.0774^{*}$          \\
+                                    & $ [ -0.0877; -0.0666]$ & $ [ -0.0873; -0.0662]$ & $ [ -0.0874; -0.0663]$ & $ [ -0.0879; -0.0669]$ \\
+Hispanic population share           & $-0.1021^{*}$          & $-0.1025^{*}$          & $-0.1025^{*}$          & $-0.1020^{*}$          \\
+                                    & $ [ -0.1112; -0.0929]$ & $ [ -0.1116; -0.0934]$ & $ [ -0.1116; -0.0934]$ & $ [ -0.1111; -0.0928]$ \\
+Other Minorities                    & $0.0006$               & $0.0035$               & $0.0037$               & $-0.0005$              \\
+                                    & $ [ -0.0882;  0.0894]$ & $ [ -0.0851;  0.0921]$ & $ [ -0.0850;  0.0923]$ & $ [ -0.0893;  0.0883]$ \\
+$\gamma$: log(Density)              & $1.1105^{*}$           & $1.0987^{*}$           & $1.1030^{*}$           & $1.0928^{*}$           \\
+                                    & $ [  0.7245;  1.4964]$ & $ [  0.7156;  1.4817]$ & $ [  0.7196;  1.4865]$ & $ [  0.7063;  1.4793]$ \\
+$\gamma$: log(Income)               & $1.9269^{*}$           & $1.9646^{*}$           & $1.9570^{*}$           & $1.9189^{*}$           \\
+                                    & $ [  0.8913;  2.9625]$ & $ [  0.9370;  2.9922]$ & $ [  0.9282;  2.9857]$ & $ [  0.8836;  2.9541]$ \\
+$\gamma$: Fulltime                  & $-0.0360$              & $-0.0396$              & $-0.0388$              & $-0.0363$              \\
+                                    & $ [ -0.0835;  0.0115]$ & $ [ -0.0869;  0.0076]$ & $ [ -0.0861;  0.0085]$ & $ [ -0.0837;  0.0112]$ \\
+$\gamma$: College-educated          & $-0.0707^{*}$          & $-0.0711^{*}$          & $-0.0721^{*}$          & $-0.0731^{*}$          \\
+                                    & $ [ -0.1307; -0.0107]$ & $ [ -0.1306; -0.0116]$ & $ [ -0.1317; -0.0125]$ & $ [ -0.1332; -0.0131]$ \\
+$\gamma$: Single Adults             & $-0.0081$              & $-0.0085$              & $-0.0077$              & $-0.0076$              \\
+                                    & $ [ -0.0506;  0.0344]$ & $ [ -0.0507;  0.0336]$ & $ [ -0.0499;  0.0345]$ & $ [ -0.0501;  0.0348]$ \\
+$\gamma$: Youth (0-17)              & $-0.0111$              & $-0.0111$              & $-0.0101$              & $-0.0120$              \\
+                                    & $ [ -0.0806;  0.0585]$ & $ [ -0.0802;  0.0579]$ & $ [ -0.0793;  0.0591]$ & $ [ -0.0815;  0.0575]$ \\
+$\gamma$: Young adults (18-34)      & $0.0806^{*}$           & $0.0842^{*}$           & $0.0848^{*}$           & $0.0801^{*}$           \\
+                                    & $ [  0.0296;  0.1317]$ & $ [  0.0335;  0.1349]$ & $ [  0.0339;  0.1356]$ & $ [  0.0291;  0.1311]$ \\
+$\gamma$: Seniors (65+)             & $0.0625$               & $0.0589$               & $0.0603$               & $0.0623$               \\
+                                    & $ [ -0.0071;  0.1322]$ & $ [ -0.0103;  0.1282]$ & $ [ -0.0090;  0.1296]$ & $ [ -0.0073;  0.1319]$ \\
+$\gamma$: Black population share    & $0.0006$               & $0.0011$               & $0.0008$               & $0.0006$               \\
+                                    & $ [ -0.0157;  0.0168]$ & $ [ -0.0151;  0.0172]$ & $ [ -0.0153;  0.0170]$ & $ [ -0.0157;  0.0168]$ \\
+$\gamma$: Asian population share    & $-0.0410^{*}$          & $-0.0398^{*}$          & $-0.0401^{*}$          & $-0.0409^{*}$          \\
+                                    & $ [ -0.0597; -0.0223]$ & $ [ -0.0584; -0.0212]$ & $ [ -0.0587; -0.0215]$ & $ [ -0.0596; -0.0222]$ \\
+$\gamma$: Hispanic population share & $0.0009$               & $-0.0009$              & $-0.0008$              & $0.0008$               \\
+                                    & $ [ -0.0164;  0.0182]$ & $ [ -0.0181;  0.0163]$ & $ [ -0.0181;  0.0164]$ & $ [ -0.0165;  0.0181]$ \\
+$\gamma$: Other Minorities          & $0.0656$               & $0.0715$               & $0.0710$               & $0.0716$               \\
+                                    & $ [ -0.1926;  0.3239]$ & $ [ -0.1856;  0.3287]$ & $ [ -0.1863;  0.3284]$ & $ [ -0.1866;  0.3299]$ \\
+Accessibility                       &                        & $0.1610^{*}$           & $0.1472^{*}$           & $0.5865$               \\
+                                    &                        & $ [  0.0238;  0.2982]$ & $ [  0.0058;  0.2886]$ & $ [ -0.1778;  1.3508]$ \\
+$\lambda$: spatial correlation      & $0.6985^{*}$           & $0.6906^{*}$           & $0.6917^{*}$           & $0.6987^{*}$           \\
+                                    & $ [  0.6600;  0.7370]$ & $ [  0.6514;  0.7297]$ & $ [  0.6526;  0.7307]$ & $ [  0.6602;  0.7372]$ \\
 \midrule
-Num. obs.                           & $2099$                 & $2099$                 & $2099$                 & $2099$                 & $2099$                 \\
-Parameters                          & $27$                   & $28$                   & $28$                   & $28$                   & $28$                   \\
-Log Likelihood                      & $-4790.3792$           & $-4786.9274$           & $-4786.6411$           & $-4787.3677$           & $-4789.6660$           \\
+Num. obs.                           & $2099$                 & $2099$                 & $2099$                 & $2099$                 \\
+Parameters                          & $27$                   & $28$                   & $28$                   & $28$                   \\
+Log Likelihood                      & $-4438.0569$           & $-4435.5066$           & $-4436.0465$           & $-4436.9264$           \\
 \bottomrule
-\multicolumn{6}{l}{\scriptsize{$^*$ 0 outside the confidence interval. 95\% confidence interval in brackets.}}
+\multicolumn{5}{l}{\scriptsize{$^*$ 0 outside the confidence interval. 95\% confidence interval in brackets.}}
 \end{tabular}
-}
-\label{tab:pa-fullmodels}
-\end{center}
+}\end{center}
 \end{table*}
@@
 \begin{table*}
-\caption{Estimated Effects of Accessibility and Controls on Obesity Rates}
+  \caption{\label{tab:ob-fullmodels} Estimated Effect of Accessibility on Obesity Rates}
   \begin{center}
-\scalebox{0.7}{
-\begin{tabular}{l c c c c c}
+  \scalebox{0.8}{
+
+\begin{tabular}{l c c c c}
 \toprule
- & No Access & Size and Distance & Twitter & Amenities & 10-Minute Walk \\
+ & No Access & Size and Distance & Amenities & 10-minute Walk \\
 \midrule
-(Intercept)                         & $69.6657^{*}$         & $69.9773^{*}$         & $69.8388^{*}$         & $69.9833^{*}$         & $69.7516^{*}$         \\
-                                    & $ [59.1228; 80.2086]$ & $ [59.4547; 80.4999]$ & $ [59.3196; 80.3579]$ & $ [59.4480; 80.5185]$ & $ [59.2183; 80.2850]$ \\
-log(Density)                        & $-0.0343$             & $-0.0370$             & $-0.0366$             & $-0.0367$             & $-0.0305$             \\
-                                    & $ [-0.1115;  0.0429]$ & $ [-0.1141;  0.0402]$ & $ [-0.1137;  0.0406]$ & $ [-0.1139;  0.0404]$ & $ [-0.1078;  0.0467]$ \\
-log(Income)                         & $-0.3886^{*}$         & $-0.4015^{*}$         & $-0.4001^{*}$         & $-0.4021^{*}$         & $-0.3882^{*}$         \\
-                                    & $ [-0.6649; -0.1122]$ & $ [-0.6780; -0.1251]$ & $ [-0.6765; -0.1238]$ & $ [-0.6786; -0.1256]$ & $ [-0.6643; -0.1121]$ \\
-Fulltime                            & $-0.0117^{*}$         & $-0.0116^{*}$         & $-0.0116^{*}$         & $-0.0116^{*}$         & $-0.0119^{*}$         \\
-                                    & $ [-0.0227; -0.0007]$ & $ [-0.0226; -0.0006]$ & $ [-0.0226; -0.0006]$ & $ [-0.0225; -0.0006]$ & $ [-0.0229; -0.0009]$ \\
-College-educated                    & $0.0372^{*}$          & $0.0371^{*}$          & $0.0370^{*}$          & $0.0372^{*}$          & $0.0367^{*}$          \\
-                                    & $ [ 0.0237;  0.0506]$ & $ [ 0.0236;  0.0505]$ & $ [ 0.0235;  0.0504]$ & $ [ 0.0237;  0.0506]$ & $ [ 0.0233;  0.0502]$ \\
-Single Adults                       & $0.0017$              & $0.0017$              & $0.0018$              & $0.0017$              & $0.0019$              \\
-                                    & $ [-0.0078;  0.0112]$ & $ [-0.0078;  0.0112]$ & $ [-0.0077;  0.0113]$ & $ [-0.0078;  0.0112]$ & $ [-0.0076;  0.0114]$ \\
-Youth (0-17)                        & $0.0074$              & $0.0075$              & $0.0076$              & $0.0075$              & $0.0077$              \\
-                                    & $ [-0.0080;  0.0227]$ & $ [-0.0078;  0.0228]$ & $ [-0.0077;  0.0230]$ & $ [-0.0078;  0.0229]$ & $ [-0.0076;  0.0231]$ \\
-Young adults (18-34)                & $-0.0119^{*}$         & $-0.0125^{*}$         & $-0.0125^{*}$         & $-0.0125^{*}$         & $-0.0118^{*}$         \\
-                                    & $ [-0.0234; -0.0005]$ & $ [-0.0239; -0.0010]$ & $ [-0.0239; -0.0010]$ & $ [-0.0240; -0.0011]$ & $ [-0.0232; -0.0004]$ \\
-Seniors (65+)                       & $-0.0896^{*}$         & $-0.0886^{*}$         & $-0.0884^{*}$         & $-0.0887^{*}$         & $-0.0894^{*}$         \\
-                                    & $ [-0.1052; -0.0740]$ & $ [-0.1042; -0.0730]$ & $ [-0.1040; -0.0728]$ & $ [-0.1043; -0.0731]$ & $ [-0.1050; -0.0738]$ \\
-Black population share              & $0.0533^{*}$          & $0.0533^{*}$          & $0.0533^{*}$          & $0.0533^{*}$          & $0.0532^{*}$          \\
-                                    & $ [ 0.0483;  0.0583]$ & $ [ 0.0484;  0.0583]$ & $ [ 0.0483;  0.0583]$ & $ [ 0.0483;  0.0582]$ & $ [ 0.0482;  0.0581]$ \\
-Asian population share              & $-0.1043^{*}$         & $-0.1044^{*}$         & $-0.1044^{*}$         & $-0.1044^{*}$         & $-0.1042^{*}$         \\
-                                    & $ [-0.1106; -0.0981]$ & $ [-0.1107; -0.0982]$ & $ [-0.1107; -0.0982]$ & $ [-0.1106; -0.0982]$ & $ [-0.1104; -0.0979]$ \\
-Hispanic population share           & $-0.0042$             & $-0.0039$             & $-0.0039$             & $-0.0039$             & $-0.0042$             \\
-                                    & $ [-0.0098;  0.0014]$ & $ [-0.0095;  0.0017]$ & $ [-0.0095;  0.0018]$ & $ [-0.0096;  0.0017]$ & $ [-0.0098;  0.0014]$ \\
-Other Minorities                    & $-0.0639^{*}$         & $-0.0650^{*}$         & $-0.0650^{*}$         & $-0.0652^{*}$         & $-0.0632^{*}$         \\
-                                    & $ [-0.1141; -0.0137]$ & $ [-0.1152; -0.0149]$ & $ [-0.1152; -0.0149]$ & $ [-0.1153; -0.0150]$ & $ [-0.1134; -0.0131]$ \\
-Physical Activity Rate              & $-0.5805^{*}$         & $-0.5825^{*}$         & $-0.5808^{*}$         & $-0.5834^{*}$         & $-0.5674^{*}$         \\
-                                    & $ [-0.8179; -0.3431]$ & $ [-0.8193; -0.3456]$ & $ [-0.8176; -0.3439]$ & $ [-0.8205; -0.3463]$ & $ [-0.8050; -0.3298]$ \\
-$\gamma$: log(Density)              & $0.0755$              & $0.0372$              & $0.0407$              & $0.0388$              & $0.0880$              \\
-                                    & $ [-0.6347;  0.7857]$ & $ [-0.6728;  0.7473]$ & $ [-0.6691;  0.7504]$ & $ [-0.6718;  0.7494]$ & $ [-0.6217;  0.7976]$ \\
-$\gamma$: log(Income)               & $-0.0010$             & $-0.0005$             & $-0.0004$             & $-0.0007$             & $-0.0007$             \\
-                                    & $ [-0.0302;  0.0282]$ & $ [-0.0296;  0.0287]$ & $ [-0.0295;  0.0288]$ & $ [-0.0299;  0.0284]$ & $ [-0.0299;  0.0285]$ \\
-$\gamma$: Fulltime                  & $0.0869^{*}$          & $0.0867^{*}$          & $0.0864^{*}$          & $0.0870^{*}$          & $0.0885^{*}$          \\
-                                    & $ [ 0.0505;  0.1233]$ & $ [ 0.0504;  0.1230]$ & $ [ 0.0501;  0.1228]$ & $ [ 0.0506;  0.1233]$ & $ [ 0.0521;  0.1250]$ \\
-$\gamma$: College-educated          & $-0.0108$             & $-0.0107$             & $-0.0106$             & $-0.0109$             & $-0.0112$             \\
-                                    & $ [-0.0365;  0.0150]$ & $ [-0.0364;  0.0149]$ & $ [-0.0363;  0.0151]$ & $ [-0.0367;  0.0148]$ & $ [-0.0369;  0.0146]$ \\
-$\gamma$: Single Adults             & $-0.0356$             & $-0.0359$             & $-0.0356$             & $-0.0362$             & $-0.0351$             \\
-                                    & $ [-0.0777;  0.0065]$ & $ [-0.0779;  0.0061]$ & $ [-0.0776;  0.0064]$ & $ [-0.0782;  0.0059]$ & $ [-0.0772;  0.0070]$ \\
-$\gamma$: Youth (0-17)              & $-0.0296$             & $-0.0312^{*}$         & $-0.0312^{*}$         & $-0.0315^{*}$         & $-0.0291$             \\
-                                    & $ [-0.0605;  0.0014]$ & $ [-0.0622; -0.0002]$ & $ [-0.0622; -0.0002]$ & $ [-0.0626; -0.0005]$ & $ [-0.0601;  0.0018]$ \\
-$\gamma$: Young adults (18-34)      & $-0.0276$             & $-0.0266$             & $-0.0260$             & $-0.0270$             & $-0.0275$             \\
-                                    & $ [-0.0690;  0.0138]$ & $ [-0.0680;  0.0147]$ & $ [-0.0674;  0.0154]$ & $ [-0.0684;  0.0144]$ & $ [-0.0689;  0.0139]$ \\
-$\gamma$: Seniors (65+)             & $0.0155^{*}$          & $0.0154^{*}$          & $0.0154^{*}$          & $0.0155^{*}$          & $0.0153^{*}$          \\
-                                    & $ [ 0.0050;  0.0259]$ & $ [ 0.0051;  0.0258]$ & $ [ 0.0050;  0.0258]$ & $ [ 0.0051;  0.0259]$ & $ [ 0.0049;  0.0258]$ \\
-$\gamma$: Black population share    & $-0.0504^{*}$         & $-0.0509^{*}$         & $-0.0509^{*}$         & $-0.0507^{*}$         & $-0.0506^{*}$         \\
-                                    & $ [-0.0640; -0.0368]$ & $ [-0.0645; -0.0373]$ & $ [-0.0645; -0.0373]$ & $ [-0.0643; -0.0371]$ & $ [-0.0642; -0.0371]$ \\
-$\gamma$: Asian population share    & $0.0214^{*}$          & $0.0226^{*}$          & $0.0227^{*}$          & $0.0226^{*}$          & $0.0215^{*}$          \\
-                                    & $ [ 0.0088;  0.0341]$ & $ [ 0.0099;  0.0353]$ & $ [ 0.0100;  0.0354]$ & $ [ 0.0099;  0.0354]$ & $ [ 0.0088;  0.0342]$ \\
-$\gamma$: Hispanic population share & $0.0707$              & $0.0691$              & $0.0693$              & $0.0692$              & $0.0670$              \\
-                                    & $ [-0.0777;  0.2190]$ & $ [-0.0791;  0.2173]$ & $ [-0.0789;  0.2175]$ & $ [-0.0790;  0.2174]$ & $ [-0.0813;  0.2153]$ \\
-$\gamma$: Other Minorities          & $-0.4259^{*}$         & $-0.4251^{*}$         & $-0.4250^{*}$         & $-0.4251^{*}$         & $-0.4256^{*}$         \\
-                                    & $ [-0.4471; -0.4047]$ & $ [-0.4463; -0.4039]$ & $ [-0.4462; -0.4038]$ & $ [-0.4463; -0.4039]$ & $ [-0.4468; -0.4045]$ \\
-$\gamma$: Physical Activity Rate    & $-0.0351$             & $-0.0321$             & $-0.0317$             & $-0.0318$             & $-0.0362$             \\
-                                    & $ [-0.0872;  0.0169]$ & $ [-0.0841;  0.0199]$ & $ [-0.0838;  0.0203]$ & $ [-0.0839;  0.0203]$ & $ [-0.0882;  0.0158]$ \\
-$\lambda$: spatial correlation      & $0.8003^{*}$          & $0.7988^{*}$          & $0.7988^{*}$          & $0.7998^{*}$          & $0.8001^{*}$          \\
-                                    & $ [ 0.7706;  0.8301]$ & $ [ 0.7689;  0.8287]$ & $ [ 0.7689;  0.8287]$ & $ [ 0.7700;  0.8296]$ & $ [ 0.7703;  0.8299]$ \\
-Size and Distance                   &                       & $-0.0688$             &                       &                       &                       \\
-                                    &                       & $ [-0.1440;  0.0064]$ &                       &                       &                       \\
-Tweets                              &                       &                       & $-0.0731$             &                       &                       \\
-                                    &                       &                       & $ [-0.1516;  0.0053]$ &                       &                       \\
-Attributes                          &                       &                       &                       & $-0.0695$             &                       \\
-                                    &                       &                       &                       & $ [-0.1472;  0.0083]$ &                       \\
-10-min walk                         &                       &                       &                       &                       & $-0.3573$             \\
-                                    &                       &                       &                       &                       & $ [-0.7650;  0.0505]$ \\
+(Intercept)                         & $71.6539^{*}$         & $71.7489^{*}$         & $71.7525^{*}$         & $71.7182^{*}$         \\
+                                    & $ [61.1144; 82.1933]$ & $ [61.2170; 82.2809]$ & $ [61.2164; 82.2887]$ & $ [61.1846; 82.2518]$ \\
+log(Density)                        & $-0.0294$             & $-0.0307$             & $-0.0306$             & $-0.0266$             \\
+                                    & $ [-0.1037;  0.0448]$ & $ [-0.1050;  0.0436]$ & $ [-0.1049;  0.0437]$ & $ [-0.1009;  0.0478]$ \\
+log(Income)                         & $-0.4849^{*}$         & $-0.4907^{*}$         & $-0.4908^{*}$         & $-0.4861^{*}$         \\
+                                    & $ [-0.7612; -0.2085]$ & $ [-0.7672; -0.2141]$ & $ [-0.7674; -0.2142]$ & $ [-0.7623; -0.2098]$ \\
+Fulltime                            & $-0.0137^{*}$         & $-0.0137^{*}$         & $-0.0137^{*}$         & $-0.0139^{*}$         \\
+                                    & $ [-0.0244; -0.0031]$ & $ [-0.0244; -0.0030]$ & $ [-0.0244; -0.0030]$ & $ [-0.0246; -0.0032]$ \\
+College-educated                    & $0.0343^{*}$          & $0.0343^{*}$          & $0.0343^{*}$          & $0.0340^{*}$          \\
+                                    & $ [ 0.0211;  0.0474]$ & $ [ 0.0211;  0.0474]$ & $ [ 0.0211;  0.0474]$ & $ [ 0.0208;  0.0471]$ \\
+Single Adults                       & $0.0010$              & $0.0010$              & $0.0010$              & $0.0012$              \\
+                                    & $ [-0.0082;  0.0103]$ & $ [-0.0083;  0.0103]$ & $ [-0.0083;  0.0102]$ & $ [-0.0081;  0.0104]$ \\
+Youth (0-17)                        & $0.0051$              & $0.0052$              & $0.0052$              & $0.0054$              \\
+                                    & $ [-0.0099;  0.0201]$ & $ [-0.0098;  0.0202]$ & $ [-0.0098;  0.0202]$ & $ [-0.0096;  0.0204]$ \\
+Young adults (18-34)                & $-0.0095$             & $-0.0097$             & $-0.0098$             & $-0.0094$             \\
+                                    & $ [-0.0206;  0.0016]$ & $ [-0.0209;  0.0014]$ & $ [-0.0209;  0.0014]$ & $ [-0.0205;  0.0017]$ \\
+Seniors (65+)                       & $-0.0826^{*}$         & $-0.0821^{*}$         & $-0.0821^{*}$         & $-0.0825^{*}$         \\
+                                    & $ [-0.0977; -0.0675]$ & $ [-0.0973; -0.0669]$ & $ [-0.0973; -0.0670]$ & $ [-0.0976; -0.0673]$ \\
+Black population share              & $0.0462^{*}$          & $0.0462^{*}$          & $0.0462^{*}$          & $0.0461^{*}$          \\
+                                    & $ [ 0.0414;  0.0511]$ & $ [ 0.0414;  0.0511]$ & $ [ 0.0414;  0.0510]$ & $ [ 0.0413;  0.0510]$ \\
+Asian population share              & $-0.1010^{*}$         & $-0.1010^{*}$         & $-0.1010^{*}$         & $-0.1009^{*}$         \\
+                                    & $ [-0.1069; -0.0950]$ & $ [-0.1070; -0.0951]$ & $ [-0.1070; -0.0951]$ & $ [-0.1068; -0.0949]$ \\
+Hispanic population share           & $-0.0062^{*}$         & $-0.0061^{*}$         & $-0.0061^{*}$         & $-0.0062^{*}$         \\
+                                    & $ [-0.0118; -0.0007]$ & $ [-0.0116; -0.0006]$ & $ [-0.0116; -0.0006]$ & $ [-0.0117; -0.0007]$ \\
+Other Minorities                    & $-0.0642^{*}$         & $-0.0646^{*}$         & $-0.0647^{*}$         & $-0.0637^{*}$         \\
+                                    & $ [-0.1127; -0.0156]$ & $ [-0.1132; -0.0161]$ & $ [-0.1133; -0.0162]$ & $ [-0.1122; -0.0151]$ \\
+$\gamma$: log(Density)              & $-0.5545^{*}$         & $-0.5565^{*}$         & $-0.5567^{*}$         & $-0.5445^{*}$         \\
+                                    & $ [-0.7908; -0.3182]$ & $ [-0.7927; -0.3203]$ & $ [-0.7929; -0.3204]$ & $ [-0.7812; -0.3079]$ \\
+$\gamma$: log(Income)               & $-0.0863$             & $-0.1004$             & $-0.0987$             & $-0.0783$             \\
+                                    & $ [-0.7966;  0.6240]$ & $ [-0.8108;  0.6100]$ & $ [-0.8091;  0.6118]$ & $ [-0.7883;  0.6317]$ \\
+$\gamma$: Fulltime                  & $-0.0118$             & $-0.0115$             & $-0.0116$             & $-0.0116$             \\
+                                    & $ [-0.0404;  0.0169]$ & $ [-0.0402;  0.0172]$ & $ [-0.0402;  0.0171]$ & $ [-0.0402;  0.0171]$ \\
+$\gamma$: College-educated          & $0.0698^{*}$          & $0.0698^{*}$          & $0.0699^{*}$          & $0.0710^{*}$          \\
+                                    & $ [ 0.0334;  0.1062]$ & $ [ 0.0334;  0.1062]$ & $ [ 0.0335;  0.1063]$ & $ [ 0.0346;  0.1075]$ \\
+$\gamma$: Single Adults             & $-0.0114$             & $-0.0113$             & $-0.0114$             & $-0.0117$             \\
+                                    & $ [-0.0368;  0.0140]$ & $ [-0.0367;  0.0140]$ & $ [-0.0368;  0.0140]$ & $ [-0.0371;  0.0137]$ \\
+$\gamma$: Youth (0-17)              & $-0.0330$             & $-0.0330$             & $-0.0332$             & $-0.0326$             \\
+                                    & $ [-0.0748;  0.0088]$ & $ [-0.0748;  0.0088]$ & $ [-0.0750;  0.0086]$ & $ [-0.0744;  0.0092]$ \\
+$\gamma$: Young adults (18-34)      & $-0.0238$             & $-0.0247$             & $-0.0248$             & $-0.0235$             \\
+                                    & $ [-0.0545;  0.0069]$ & $ [-0.0554;  0.0060]$ & $ [-0.0555;  0.0059]$ & $ [-0.0542;  0.0071]$ \\
+$\gamma$: Seniors (65+)             & $-0.0222$             & $-0.0217$             & $-0.0218$             & $-0.0222$             \\
+                                    & $ [-0.0629;  0.0185]$ & $ [-0.0624;  0.0190]$ & $ [-0.0625;  0.0189]$ & $ [-0.0628;  0.0185]$ \\
+$\gamma$: Black population share    & $0.0186^{*}$          & $0.0186^{*}$          & $0.0186^{*}$          & $0.0185^{*}$          \\
+                                    & $ [ 0.0080;  0.0292]$ & $ [ 0.0080;  0.0292]$ & $ [ 0.0080;  0.0292]$ & $ [ 0.0079;  0.0291]$ \\
+$\gamma$: Asian population share    & $-0.0460^{*}$         & $-0.0462^{*}$         & $-0.0461^{*}$         & $-0.0461^{*}$         \\
+                                    & $ [-0.0594; -0.0325]$ & $ [-0.0596; -0.0327]$ & $ [-0.0596; -0.0327]$ & $ [-0.0595; -0.0327]$ \\
+$\gamma$: Hispanic population share & $0.0257^{*}$          & $0.0263^{*}$          & $0.0263^{*}$          & $0.0258^{*}$          \\
+                                    & $ [ 0.0129;  0.0386]$ & $ [ 0.0134;  0.0392]$ & $ [ 0.0134;  0.0391]$ & $ [ 0.0130;  0.0386]$ \\
+$\gamma$: Other Minorities          & $0.0794$              & $0.0789$              & $0.0790$              & $0.0767$              \\
+                                    & $ [-0.0648;  0.2236]$ & $ [-0.0652;  0.2230]$ & $ [-0.0652;  0.2231]$ & $ [-0.0674;  0.2209]$ \\
+Physical Activity                   & $-0.4807^{*}$         & $-0.4803^{*}$         & $-0.4803^{*}$         & $-0.4803^{*}$         \\
+                                    & $ [-0.5048; -0.4566]$ & $ [-0.5044; -0.4561]$ & $ [-0.5044; -0.4562]$ & $ [-0.5044; -0.4562]$ \\
+$\gamma$: Physical Activity         & $0.0180$              & $0.0195$              & $0.0194$              & $0.0173$              \\
+                                    & $ [-0.0397;  0.0757]$ & $ [-0.0383;  0.0772]$ & $ [-0.0383;  0.0772]$ & $ [-0.0404;  0.0750]$ \\
+Accessibility                       &                       & $-0.0349$             & $-0.0352$             & $-0.2630$             \\
+                                    &                       & $ [-0.1095;  0.0397]$ & $ [-0.1129;  0.0425]$ & $ [-0.6491;  0.1232]$ \\
+$\lambda$: spatial correlation      & $0.8363^{*}$          & $0.8357^{*}$          & $0.8360^{*}$          & $0.8361^{*}$          \\
+                                    & $ [ 0.8101;  0.8625]$ & $ [ 0.8094;  0.8620]$ & $ [ 0.8098;  0.8622]$ & $ [ 0.8099;  0.8624]$ \\
 \midrule
-Num. obs.                           & $2099$                & $2099$                & $2099$                & $2099$                & $2099$                \\
-Parameters                          & $29$                  & $30$                  & $30$                  & $30$                  & $30$                  \\
-Log Likelihood                      & $-3196.4885$          & $-3194.8851$          & $-3194.8268$          & $-3194.9556$          & $-3195.0152$          \\
+Num. obs.                           & $2099$                & $2099$                & $2099$                & $2099$                \\
+Parameters                          & $29$                  & $30$                  & $30$                  & $30$                  \\
+Log Likelihood                      & $-3114.3931$          & $-3113.9742$          & $-3113.9998$          & $-3113.5028$          \\
 \bottomrule
-\multicolumn{6}{l}{\scriptsize{$^*$ 0 outside the confidence interval. 95\% confidence interval in brackets.}}
+\multicolumn{5}{l}{\scriptsize{$^*$ 0 outside the confidence interval. 95\% confidence interval in brackets.}}
 \end{tabular}
-}
-\label{tab:ob-fullmodels}
-\end{center}
+}\end{center}
 \end{table*}

### 2020-06-05 manuscript/submission/manuscript.tex
De-identify manuscript and write modified text in blue
Also include response to reviewers document

@@
 
-\author{Gregory Macfarlane\affilnum{1}, Nico Boyd\affilnum{2}, John E. Taylor\affilnum{3}, Kari Watkins\affilnum{3}}
-
-\affiliation{\affilnum{1}{Department of Civil \& Environmental Engineering, Brigham Young University}\\\affilnum{2}{Fehr \& Peers, Los Angeles California}\\\affilnum{3}{School of Civil \& Environmental Engineering, Georgia Institute of Technology}}
-
-\corrauth{Gregory Macfarlane, 430 Engineering Building, Provo UT 84663}
-
-\email{\href{mailto:gregmacfarlane@byu.edu}{\nolinkurl{gregmacfarlane@byu.edu}}}
+\author{XXXX\affilnum{1}, XXXX\affilnum{2}, XXXX\affilnum{3}, XXXXX \affilnum{3}}
+
+\affiliation{\affilnum{1}{XXXX}\\\affilnum{2}{XXXX}\\\affilnum{3}{XXXX}}
+
+\corrauth{XXXXX}
+
+\email{XXXX}
 
@@
 their community is designed and built in such a way that such exercise
-is expensive, unenjoyable, or unsafe. It is similarly necessary for
+is expensive, unenjoyable, or unsafe. \textcolor{blue}{It is similarly necessary for
 urban planners to identify which neighborhoods have access to quality
@@
 new or rehabilitated green space, or improved transportation access to
-existing quality green space.
+existing quality green space.}
 
@@
 
-\label{sec:litreview} The question of how green space in the urban
+\label{sec:litreview}
+
+\textcolor{blue}{
+The question of how green space in the urban
 environment affects the physical, emotional, and mental well-being of
@@
 studies produced mixed results, and nine studies found no association at
-all.
-
+all.}
+
+\textcolor{blue}{
 Loosely defined, the \emph{accessibility} of an arbitrary place
@@
 evaluate which residents have good access to quality green space may
-desire objective and therefore comparable measures.
+desire objective and therefore comparable measures.}
 
@@
 10-minute network-bound walk, paired with a demographic analysis of
-areas within and outside of this threshold. \citet{devries2003natural}
+areas within and outside of this threshold. \textcolor{blue}{\citet{devries2003natural}
 showed the amount of greenspace within a 3-kilometer radius was
@@
 relationship between the health of senior citizens and the number of
-parks within 500 meters.
+parks within 500 meters.}
 
@@
 distance-based isochrones are replaced with political, geographical, or
-statistical boundaries. For example, \citet{Mitchell2008} find that
-inequalities in health outcomes attributable to income are mitigated in
-statistical areas with a greater percentage of green space. These are
+statistical boundaries. \textcolor{blue}{For example, \citet{Mitchell2008} find that inequalities
+in health outcomes attributable to income are mitigated in statistical areas
+with a greater percentage of green space. \citet{Stark2014} found a significant
+relationship in New York City between the percent of a residential ZIP code that
+is park space and objectively measured body mass index (BMI).} Political or
+regional boundaries are
 especially common in comparative macroscopic studies, such as the
@@
 44 U.S. cities and self-reported scores on the Gallup-Healthways
-Wellbeing Index. At the sub-metropolitan level, \citet{Stark2014} found
-a significant relationship in New York City between the percent of a
-residential ZIP code that is park space and objectively measured body
-mass index (BMI). It is also possible to attenuate an isochrone with
+Wellbeing Index. It is also possible to attenuate an isochrone with
 various factors; for instance, \citet{Dias2019} considered road safety
@@
 the attributes of a park influence walking more than merely the distance
-to it. \citet{hillsdon2006relationship} found no relationship between a
+to it. \textcolor{blue}{\citet{hillsdon2006relationship} found no relationship between a
 gravity-based accessibility term and self-reported physical activity
-among middle-aged individuals in Norwich, England. \citet{Zhang2011}
+among middle-aged individuals in Norwich, England.} \citet{Zhang2011}
 developed a population-weighted, gravity-based accessibility to parks
@@
  \boldsymbol{y} = X\boldsymbol{\beta} + \beta_{a}\boldsymbol{A} + \boldsymbol{\varepsilon}
-\end{equation} where \(X\) is a matrix of dimension \(n\times p\) where
+\end{equation}
+\textcolor{blue}{where \(X\) is a matrix of dimension \(n\times p\) where
 \(n\) is the number of observations and \(p\) is the number of predictor
@@
 parameter \(\beta_a\), and a vector \(\boldsymbol{\varepsilon}\)
-represents the model residual as a random variable.
+represents the model residual as a random variable.}
 
@@
 \(1.307e-23\). Though this statistic is well beneath a common hypothesis
-test threshold of \(\alpha = 0.05\), we elect retain the null hypothesis
+test threshold of \(\alpha = 0.05\), we elect to retain the null hypothesis
 that the coefficients are equivalent, as the differences are at no point
@@
 ecological inference fallacy, where aggregate statistics mask or
-contradict disaggregated or individual-level trends. The socioeconomic
+contradict disaggregated or individual-level trends. \textcolor{blue}{The socioeconomic
 and public health data used in this study are only available at the
@@
 infeasible as the spatial lags of the independent variables introduced
-substantial collinearity in the model equations. A large-sample survey
+substantial collinearity in the model equations.} A large-sample survey
 of individuals in New York City, including measured physical activities
@@
 incrementally towards this by adding some selected park amenities as an
-element of each park's attractiveness above and beyond its size. The set
+element of each park's attractiveness above and beyond its size. \textcolor{blue}{The set
 of amenities we included in the utility calculation --- and the
@@
 \citet{roberts2017using}) to estimate the utility contribution of these
-features. This could in turn provide a more nuanced understanding of the
-relationship between park accessibility, use, and health outcomes.
+features.} This could in turn provide a more nuanced understanding of the
+relationship between park accessibility, \textcolor{blue}{use,} and health outcomes.
 
@@
 when the non-highway mode share is high, as is likely when considering
-access to parks. We examined replacing the Euclidean distance with a
+access to parks. \textcolor{blue}{We examined replacing the Euclidean distance with a
 network-based distance; the choice of distance metric appeared
@@
 verify the accuracy of the underlying network data at the scale of this
-analysis. We therefore retain the Euclidean distance for simplicity. A
+analysis. We therefore retain the Euclidean distance for simplicity.} A
 better metric of travel impedance may be a mode choice model logsum,
@@
 health, or any number of potential beneficial outcomes hypothesized or
-explored in the existing literature. The COVID-19 pandemic and its
+explored in the existing literature. \textcolor{blue}{The COVID-19 pandemic and its
 associated social distancing behaviors in many regions of the world has
-also drawn attention to problems of park access, use, and equity.
+also drawn attention to problems of park access, use, and equity.}
 Exploring these connections and their underlying mechanisms should be a
@@
 \begin{acks}
-This project was funded by the Speedwell Foundation. We are grateful to Rachel
-Samuels and Neda Madi for helping to assemble the data.
 \end{acks}

### 2020-06-05 02_parks_data.Rmd
Repo cleanup
This includes a number of edits to the data elements related to switching the unit of analysis from tracts to block groups
Clean up file names and headers

@@
 title: "Parks Data"
-author: "Greg Macfarlane"
-date: "6/6/2019"
-output: html_document
-editor_options: 
-  chunk_output_type: console
 ---
 
-```{r setup}
+```{r setup, cache = FALSE}
+knitr::opts_chunk$set(cache = TRUE)
 library(leaflet)

### 2020-06-05 03_distances.Rmd

@@
 
-With `r nrow(open_space_points)` and `r nrow(bg_centroids)`, that suggests we
-need to compute `r nrow(open_space_points) * nrow(bg_centroids)` shortest
+With `r nrow(park_points)` and `r nrow(tract_centroids)`, that suggests we
+need to compute `r nrow(park_points) * nrow(bg_centroids)` shortest
 paths. Even on a 20+ core process, this would take several weeks.  As a result,

### 2020-06-05 04_accessibility.Rmd

@@
 open_spaces <- read_rds("data/open_spaces.rds")
+distances <- read_rds("data/distances.rds")
 ```
@@
   # warnings are from `inf` strings, which become converted to NA, which is okay.
-  read_csv(x, col_types = "ccnn") %>% as_tibble()
+  suppressWarnings(read_csv(x, col_types = "ccnn") %>% as_tibble())
 }
 
-blockgroup_distances <- lapply(blockgroup_files, read_dist_csv) %>% bind_rows()
-tract_distances      <- lapply(tract_files,      read_dist_csv) %>% bind_rows()
+blockgroup_distances <- lapply(blockgroup_files, read_dist_csv) %>% 
+  bind_rows() %>% 
+  left_join(distances$blockgroups %>% rename(euc_old = distance), 
+            by = c("geoid", "park_id"))
+tract_distances <- lapply(tract_files, read_dist_csv) %>% 
+  bind_rows() %>% 
+  left_join(distances$tracts %>% rename(euc_old = distance), 
+            by = c("geoid", "park_id"))
 ```
@@
     mutate(
-      euc_access = -1.768 * log(euc_dist) + 0.373 * log(as.numeric(acres)),
+      euc_access = -1.768 * log(euc_old) + 0.373 * log(as.numeric(acres)),
       euc_multi  = euc_access + trails * 0.99 +  playgrounds * 0.26 + courts * 0.43,

### 2020-06-05 manuscript/manuscript.Rmd

@@
 concept with tempting quantifiability [@Handy1997], but objective quantification 
-may not be strictly necessary. For example, takano2002urban showed improved 
+may not be strictly necessary. For example, @takano2002urban showed improved 
 survival rates among senior citizens in Japan who self-reported having access
@@
 
-@Dong2006 present a helpful mathematical heirarchy of
+@Dong2006 present a helpful mathematical hierarchy of
 common quantitative mechanisms for calculating access, which we follow here.
@@
 isochrones are replaced with political, geographical, or statistical boundaries.
+For example, @Mitchell2008 find that inequalities in health outcomes attributable to 
+income are mitigated in statistical areas with a greater percentage of green space.
 These are especially common in comparative macroscopic studies, such as the
@@
 on the Gallup-Healthways Wellbeing Index. At the sub-metropolitan level, 
-the @Stark2014 found a significant relationship in New York City between the percent
+@Stark2014 found a significant relationship in New York City between the percent
 of a residential ZIP code that is park space and objectively measured body
@@
 
-In spite of the flexibility of adapted isochrone techniques, the arbritrary
+In spite of the flexibility of adapted isochrone techniques, the arbitrary
 definitions necessarily imposed by researchers in its application can inhibit
@@
 distance; the choice of distance metric appeared inconsequential to our larger
-findings in this case. We retained the Euclidean distance for computational simplicity. A
+findings in this case while substantially increasing the computational load required.
+Additionally, we could not verify the accuracy of the underlying network data at 
+the scale of this analysis. We therefore retain the Euclidean distance for
+simplicity. A
 better metric of travel impedance may be a mode choice model logsum, which

### 2020-06-05 manuscript/submission/coverletter/coverletter.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Professional Formal Letter
% LaTeX Template
% Version 2.0 (12/2/17)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Brian Moses
% Vel (vel@LaTeXTemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt]{letter} % Set the font size (10pt, 11pt and 12pt) and paper size (letterpaper, a4paper, etc)

\input{structure.tex} % Include the file that specifies the document structure

%\longindentation=0pt % Un-commenting this line will push the closing "Sincerely," and date to the left of the page
\setlength\parindent{0pt}

\usepackage{fontspec}

% Classic
\setmainfont[BoldFont={Roboto Bold}]{Roboto Light}

%----------------------------------------------------------------------------------------
%	YOUR INFORMATION
%----------------------------------------------------------------------------------------

\Who{Gregory S. Macfarlane} % Your name

\Title{, PhD, PE} % Your title, leave blank for no title

\authordetails{
	%Civil \& Environmental Engineering\\ % Your department/institution
	430 Engineering Building \\ % Your address
	Provo, UT 84602\\ % Your city, zip code, country, etc
	Email: gregmacfarlane@byu.edu\\ % Your email address
	Phone: (801) 422-8505\\ % Your phone number
}

%----------------------------------------------------------------------------------------
%	HEADER CONTENTS
%----------------------------------------------------------------------------------------

\logo{logo.png} % Logo filename, your logo should have square dimensions (i.e. roughly the same width and height), if it does not, you will need to adjust spacing within the HEADER STRUCTURE block in structure.tex (read the comments carefully!)

\headerlineone{} % Top header line, leave blank if you only want the bottom line

\headerlinetwo{} % Bottom header line

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	TO ADDRESS
%----------------------------------------------------------------------------------------

\begin{letter}{
}

%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------

\opening{Dear Professor See,}

We would like to thank both reviewers for their thoughtful and helpful comments. We are delighted that they found our submission a “well-written paper that makes a useful contribution to the accessibility literature regarding quantifying accessibility” as well as “a nice added-value to the extensive literature on the subject.”

We feel we have addressed each comment raised by the reviewers, both major and minor. In particular, we re-executed our analysis using network distances in place of the Euclidean distances used in the original manuscript; the findings of this analysis were inconsequential, and our decision to retain the Euclidean specification is detailed in the attached response to reviewers.

We are grateful for the opportunity to submit this revised manuscript for further review and consideration in {\em Environment and Planning B: Urban Analytics and City Science}.

\closing{Regards,}

%----------------------------------------------------------------------------------------
%	OPTIONAL FOOTNOTE
%----------------------------------------------------------------------------------------

% Uncomment the 4 lines below to print a footnote with custom text
%\def\thefootnote{}
%\def\footnoterule{\hrule}
%\footnotetext{\hspace*{\fill}{\footnotesize\em Footnote text}}
%\def\thefootnote{\arabic{footnote}}

%----------------------------------------------------------------------------------------

\end{letter}

\end{document}

### 2020-06-05 manuscript/submission/coverletter/structure.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Professional Formal Letter
% Structure Specification File
% Version 1.0 (12/2/17)
%
% This file originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Brian Moses
% Vel (vel@LaTeXTemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\usepackage{graphicx} % Required for including pictures

\usepackage[T1]{fontenc} % Output font encoding for international characters
\usepackage[utf8]{inputenc} % Required for inputting international characters
\usepackage{gfsdidot} % Use the GFS Didot font: http://www.tug.dk/FontCatalogue/gfsdidot/
\usepackage{microtype} % Improves typography

\pagestyle{empty} % Suppress headers and footers

\setlength\parindent{1cm} % Paragraph indentation

% Create a new command for the horizontal rule in the document which allows thickness specification
\makeatletter
\newcommand{\vhrulefill}[1]{\leavevmode\leaders\hrule\@height#1\hfill \kern\z@}
\makeatother

%----------------------------------------------------------------------------------------
%	DOCUMENT MARGINS
%----------------------------------------------------------------------------------------

\usepackage{geometry} % Required for adjusting page dimensions

\geometry{
	top=1cm, % Top margin
	bottom=1.5cm, % Bottom margin
	left=3cm, % Left margin
	right=3cm, % Right margin
	%showframe, % Uncomment to show how the type block is set on the page
}

%----------------------------------------------------------------------------------------
%	DEFINE CUSTOM COMMANDS
%----------------------------------------------------------------------------------------

\newcommand{\logo}[1]{\renewcommand{\logo}{#1}}

\newcommand{\Who}[1]{\renewcommand{\Who}{#1}}
\newcommand{\Title}[1]{\renewcommand{\Title}{#1}}

\newcommand{\headerlineone}[1]{\renewcommand{\headerlineone}{#1}}
\newcommand{\headerlinetwo}[1]{\renewcommand{\headerlinetwo}{#1}}

\newcommand{\authordetails}[1]{\renewcommand{\authordetails}{#1}}

%----------------------------------------------------------------------------------------
%	AUTHOR DETAILS STRUCTURE
%----------------------------------------------------------------------------------------

\newcommand{\authordetailsblock}{
	\hspace{\fill} % Move the author details to the far right
	\parbox[t]{0.48\textwidth}{ % Box holding the author details; width value specifies where it starts and ends, increase to move details left
		\footnotesize % Use a smaller font size for the details
		\textbf{\Who\Title}\\ % Author name
		\authordetails % The author details text, all italicised
	}
}

%----------------------------------------------------------------------------------------
%	HEADER STRUCTURE
%----------------------------------------------------------------------------------------

\address{
	\includegraphics[width=2.8in]{\logo} % Include the logo of author institution
	\hspace{.52\textwidth} % Position of the institution logo, increase to move left, decrease to move right
	\vskip -0.18\textheight~\\ % Position of the large header text in relation to the institution logo, increase to move down, decrease to move up
	\Large\hspace{0.2\textwidth}\headerlineone\hfill ~\\[0.05\textheight] % First line of institution name, adjust hspace if your logo is wide
	\hspace{0.2\textwidth}\headerlinetwo\hfill \normalsize % Second line of institution name, adjust hspace if your logo is wide
	%\makebox[0ex][r]{\textbf{\Who\Title}}\hspace{0.01\textwidth} % Print author name and title with a little whitespace to the right
	~\\[-0.01\textheight] % Reduce the whitespace above the horizontal rule
	%\hspace{0.0\textwidth}\vhrulefill{1pt} \\ % Horizontal rule, adjust hspace if your logo is wide and \vhrulefill for the thickness of the rule
	\authordetailsblock % Include the letter author's details on the right side of the page under the horizontal rule
	\hspace{-0.15\textwidth} % Horizontal position of the author details block, increase to move left, decrease to move right
	\vspace{.0\textheight} % Move the date and letter content up for a more compact look
}

%----------------------------------------------------------------------------------------
%	COMPOSE THE ENTIRE HEADER
%----------------------------------------------------------------------------------------

\renewcommand{\opening}[1]{
	{\centering\fromaddress\vspace{0.05\textheight} \\ % Print the header and from address here, add whitespace to move date down
	\hspace*{\longindentation}\today\hspace*{\fill}\par} % Print today's date, remove \today to not display it
	{\raggedright \toname \\ \toaddress \par} % Print the to name and address
	\vspace{1cm} % White space after the to address
	\noindent #1 % Print the opening line
}

%----------------------------------------------------------------------------------------
%	SIGNATURE STRUCTURE
%----------------------------------------------------------------------------------------

\signature{\Who\Title} % The signature is a combination of the author's name and title

\renewcommand{\closing}[1]{
	\vspace{2.5mm} % Some whitespace after the letter content and before the signature
	\noindent % Stop paragraph indentation
	\hspace*{\longindentation} % Move the signature right to the value of \longindentation
	\parbox{\indentedwidth}{
		\raggedright
		#1 % Print the signature text
		\vskip 1.65cm % Whitespace between the closing text and author's name for a physical signature
		\fromsig % Prints the value of \signature{}, i.e. author name and title
	}
}

### 2020-06-19 manuscript/manuscript.tex
Add tex file in case RMD changes

--- 2020-06-04 manuscript/submission/manuscript.tex
@@
 
-\affiliation{\affilnum{1}{Department of Civil \& Environmental Engineering, Brigham Young University}\\\affilnum{2}{Fehr \& Peers, Los Angeles California}\\\affilnum{3}{School of Civil \& Environmental Engineering, Georgia Institute of Technology}}
+\affiliation{\affilnum{}{}\\\affilnum{}{}\\\affilnum{}{}}
 
@@
 
-\email{\href{mailto:gregmacfarlane@byu.edu}{\nolinkurl{gregmacfarlane@byu.edu}}}
+\email{\href{mailto:gregmacfarlane@gmail.com}{\nolinkurl{gregmacfarlane@gmail.com}}}
 
@@
 \maketitle
-\clearpage
+
 \hypertarget{introduction}{%
@@
 \begin{figure*}
-\includegraphics{map-1} \caption{Normalized utility-based park accessibility values in New York City.}\label{fig:map}
+\includegraphics{manuscript_files/figure-latex/map-1} \caption{Normalized utility-based park accessibility values in New York City.}\label{fig:map}
 \end{figure*}

### 2020-09-22 manuscript/manuscript.Rmd
Submit first revisions

@@
 author:
-  - name: Gregory Macfarlane
+  - name: Gregory S. Macfarlane
     num: 1
@@
 areas within and outside of this threshold. @devries2003natural
-showed the amount of greenspace within a 3-kilometer radius was positively associated
+showed the amount of green space within a 3-kilometer radius was positively associated
 with a suite of self-reported health outcomes. Similarly, @devries2013streetscape
@@
 "destinations" are parks and green spaces in New York City.
-We retrieved a polygons layer of public parks and greenspaces within New York City’s
+We retrieved a polygons layer of public parks and green spaces within New York City’s
 municipal boundaries and checked it for accuracy and relevance [@nycparks].
@@
 
-Note that in the lag-$X$ specifications (SLX and SDEM) we exclude the accessiblity 
+Note that in the lag-$X$ specifications (SLX and SDEM) we exclude the accessibility 
 component $\boldsymbol{A}$, that is we do *not* consider that the accessibility
@@
 SDEM specification moving forward as the spatial lag of the errors is 
-significant and the overal log likelihood of the SDEM is higher than the SLX 
+significant and the overall log likelihood of the SDEM is higher than the SLX 
 specification.
@@
 suppressed for clarity but do not change meaningfully across the four specifications.
-Complete model estimates are available in the Appendix. Each of the three
+Complete model estimates are available in Table \ref{tab:pa-fullmodels} of the Supplementary Material. Each of the three
 utility-based specifications is significant at the $\alpha = 0.05$ level or lower,
 and is of the hypothesized directionality. That is, residents living in tracts 
-with increased utility-based accessiblity to green spaces show a significantly
+with increased utility-based accessibility to green spaces show a significantly
 higher physical activity participation rate. Taking the rough mean of the 2
@@
 utility-based accessibility measures as well as the 10-minute walk buffer. 
-As before, the estimates of the other variables are available in the Appendix.
+As before, the estimates of the other variables are available in Table 
+\ref{tab:ob-fullmodels} of the Supplementary Material.
 The correlation between physical activity rates and obesity is clear; for every
 percentage point increase in physical activity rate, the expected obesity rate
-drops by $0.43$ percentage points in all four accessiblity specifications.
+drops by $0.43$ percentage points in all four accessibility specifications.
 The indirect effect of physical activity rates on obesity in neighboring zones
@@
 participation rate between `r 6 * .01` and `r 6 * .3` percentage points lower than the most
-accessible tracts. We also found a suggestive though not sigificant relationship
-between park accessiblity and expected obesity rates *in addition to* the effect
+accessible tracts. We also found a suggestive though not significant relationship
+between park accessibility and expected obesity rates *in addition to* the effect
 of physical activity participation.

### 2020-09-22 manuscript/manuscript_complete_source.tex
Submit first revisions

--- 2020-06-19 manuscript/manuscript.tex
@@
 \usepackage{xcolor}
+
+\renewcommand{\appendixname}{Supplementary Material}
 
@@
 
-\author{Gregory Macfarlane\affilnum{1}, Nico Boyd\affilnum{2}, John E. Taylor\affilnum{3}, Kari Watkins\affilnum{3}}
+\author{Gregory S. Macfarlane\affilnum{1}, Nico Boyd\affilnum{2}, John E. Taylor\affilnum{3}, Kari Watkins\affilnum{3}}
 
@@
 areas within and outside of this threshold. \citet{devries2003natural}
-showed the amount of greenspace within a 3-kilometer radius was
+showed the amount of green space within a 3-kilometer radius was
 positively associated with a suite of self-reported health outcomes.
@@
 and the ``destinations'' are parks and green spaces in New York City. We
-retrieved a polygons layer of public parks and greenspaces within New
+retrieved a polygons layer of public parks and green spaces within New
 York City's municipal boundaries and checked it for accuracy and
@@
 Note that in the lag-\(X\) specifications (SLX and SDEM) we exclude the
-accessiblity component \(\boldsymbol{A}\), that is we do \emph{not}
+accessibility component \(\boldsymbol{A}\), that is we do \emph{not}
 consider that the accessibility in a neighboring zone will have an
@@
 adopt the SDEM specification moving forward as the spatial lag of the
-errors is significant and the overal log likelihood of the SDEM is
+errors is significant and the overall log likelihood of the SDEM is
 higher than the SLX specification.
@@
 % latex table generated in R 4.0.0 by xtable 1.8-4 package
-% Thu Jun  4 16:31:52 2020
+% Tue Jul  7 09:56:24 2020
  (Intercept) & -15.8424 & -26.8735 & -4.8112 &   & -24.9740 & -41.8930 & -8.0549 \\ 
@@
 clarity but do not change meaningfully across the four specifications.
-Complete model estimates are available in the Appendix. Each of the
-three utility-based specifications is significant at the
-\(\alpha = 0.05\) level or lower, and is of the hypothesized
-directionality. That is, residents living in tracts with increased
-utility-based accessiblity to green spaces show a significantly higher
-physical activity participation rate. Taking the rough mean of the 2
-estimated utility-based coefficients, moving from the least-accessible
-tract (\(A_i = -3\)) to the most-accessible tract (\(A_i = 3\)) is
-expected to raise the physical activity rate by 0.9 percentage points.
-With the understanding of the full 95\% confidence interval, we could
-suggest that the true effect of excellent versus poor park access is
-anywhere between 0.06 and 1.8 percentage points.
+Complete model estimates are available in Table \ref{tab:pa-fullmodels}
+of the Supplementary Material. Each of the three utility-based
+specifications is significant at the \(\alpha = 0.05\) level or lower,
+and is of the hypothesized directionality. That is, residents living in
+tracts with increased utility-based accessibility to green spaces show a
+significantly higher physical activity participation rate. Taking the
+rough mean of the 2 estimated utility-based coefficients, moving from
+the least-accessible tract (\(A_i = -3\)) to the most-accessible tract
+(\(A_i = 3\)) is expected to raise the physical activity rate by 0.9
+percentage points. With the understanding of the full 95\% confidence
+interval, we could suggest that the true effect of excellent versus poor
+park access is anywhere between 0.06 and 1.8 percentage points.
 
@@
 as the 10-minute walk buffer. As before, the estimates of the other
-variables are available in the Appendix. The correlation between
-physical activity rates and obesity is clear; for every percentage point
-increase in physical activity rate, the expected obesity rate drops by
-\(0.43\) percentage points in all four accessiblity specifications. The
-indirect effect of physical activity rates on obesity in neighboring
-zones is inconsequential, supporting our methodological assertion that
-public health variables are not spatially dependent, though the factors
-leading to them may be.
+variables are available in Table \ref{tab:ob-fullmodels} of the
+Supplementary Material. The correlation between physical activity rates
+and obesity is clear; for every percentage point increase in physical
+activity rate, the expected obesity rate drops by \(0.43\) percentage
+points in all four accessibility specifications. The indirect effect of
+physical activity rates on obesity in neighboring zones is
+inconsequential, supporting our methodological assertion that public
+health variables are not spatially dependent, though the factors leading
+to them may be.
 
@@
 points lower than the most accessible tracts. We also found a suggestive
-though not sigificant relationship between park accessiblity and
+though not significant relationship between park accessibility and
 expected obesity rates \emph{in addition to} the effect of physical
@@
 \hypertarget{appendix}{%
-\subsection{Appendix}\label{appendix}}
-
-In this appendix we present the complete estimation results for the
+\subsection{Supplementary Material}\label{appendix}}
+\setcounter{table}{0}
+\renewcommand{\thetable}{S\arabic{table}}
+
+In this supplementary material we present the complete estimation results for the
 models relating different definitions of access to physical activity (in

### 2020-09-22 manuscript/submission/manuscript.tex
Submit first revisions

@@
 \usepackage[colorlinks,bookmarksopen,bookmarksnumbered,citecolor=red,urlcolor=red]{hyperref}
+\renewcommand{\appendixname}{Supplementary Material}
 
@@
 
-\runninghead{Macfarlane \emph{et al}.}
+\runninghead{XXXX \emph{et al}.}
 
@@
   code, are available on GitHub at
-  \url{https://github.com/gregmacfarlane/parks_access}.}. The Centers
+  \url{https://github.com/XXXX}.}. The Centers
 for Disease Control and Prevention makes small-area estimates on key
@@
 clarity but do not change meaningfully across the four specifications.
-Complete model estimates are available in the Appendix. Each of the
+Complete model estimates are available in Table \ref{tab:pa-fullmodels}. Each of the
 three utility-based specifications is significant at the
@@
 directionality. That is, residents living in tracts with increased
-utility-based accessiblity to green spaces show a significantly higher
+utility-based accessibility to green spaces show a significantly higher
 physical activity participation rate. Taking the rough mean of the 2
@@
 as the 10-minute walk buffer. As before, the estimates of the other
-variables are available in the Appendix. The correlation between
+variables are available in Table \ref{tab:ob-fullmodel} in the Supplementary Material. The correlation between
 physical activity rates and obesity is clear; for every percentage point
 increase in physical activity rate, the expected obesity rate drops by
-\(0.43\) percentage points in all four accessiblity specifications. The
+\(0.43\) percentage points in all four accessibility specifications. The
 indirect effect of physical activity rates on obesity in neighboring
@@
 \bibliographystyle{sageh.bst}
-\bibliography{library.bib}
+\bibliography{manuscript.bbl}
 
 \hypertarget{appendix}{%
-\subsection{Appendix}\label{appendix}}
-
-In this appendix we present the complete estimation results for the
+\subsection{Supplementary Material}\label{appendix}}
+\setcounter{table}{0}
+\renewcommand{\thetable}{S\arabic{table}}
+
+In this supplementary material we present the complete estimation results for the
 models relating different definitions of access to physical activity (in

### 2020-09-22 02_parks_data.Rmd
Build website

@@
 
-```{r fm1}
+```{r fm1, cache = FALSE}
 leaflet(st_buffer(parks %>% filter(grepl("Flushing Meadows", park_name)), dist = 0.000001)) %>%
@@
 
-```{r fm3}
+```{r fm3, cache=FALSE}
 leaflet(st_transform(dissolved, 4326) ) %>%

### 2020-09-22 manuscript/manuscript.Rmd
Remove discussion of cemeteries from data assembly

@@
 variables for each containing park indicating the presence of sports courts,
-playgrounds, and trails.
-
-To this dataset of parks and regularized green spaces, we add a polygons layer of
-cemeteries in New York that are open to the public. Cemeteries are important
-green spaces that can be used for many types of physical activity. These
-operations leave us with `r nrow(parks)` distinct green spaces; for simplicity 
-we will refer to both parks and cemeteries as "parks" going forward. 
-For each park, we calculate the size of the park in acres.
+playgrounds, and trails. These operations leave us with `r nrow(parks)` distinct
+green spaces; For each park, we calculate the size of the park in acres.
 

### 2020-09-22 manuscript/manuscript.Rmd
Make graphic with tikz

@@
 
-```{r map, fig.env="figure*", echo=FALSE, message=FALSE, warning=FALSE, fig.height=4, fig.cap="Normalized utility-based park accessibility values in New York City."}
+```{r map, fig.env="figure*", echo=FALSE, message=FALSE, warning=FALSE, fig.height=4, fig.cap="Normalized utility-based park accessibility values in New York City.", dev='tikz'}
 library(ggmap)

### 2020-09-22 manuscript/manuscript.Rmd
Various typos

@@
 corrauth: "Gregory Macfarlane, 430 Engineering Building, Provo UT 84663"
-email: gregmacfarlane@gmail.com
+email: gregmacfarlane@byu.edu
 abstract: >
@@
 well beneath a common hypothesis test threshold of $\alpha = 0.05$, we
-elect retain the null hypothesis that the coefficients are equivalent, as 
+elect to retain the null hypothesis that the coefficients are equivalent, as 
 the differences are at no point practically different from each other. The consequences
@@
 This project was funded by the Speedwell Foundation. We are grateful to Rachel
-Samuels and Neda Madi for helping to assemble the data.
+Samuels and Neda Madi for helping to assemble the data. We are also grateful for
+the three anonymous reviewers, whose comments significantly strengthened the 
+manuscript.
 \end{acks}

### 2020-09-24 02_parks_data.Rmd

@@
 ```{r write}
-open_spaces <- rbind(
-  dissolved %>% 
+open_spaces <-  dissolved %>% 
   transmute(id = parknum, name = park_name, acres, courts, playgrounds, trails, 
-              type = "park"),
-  dissolved_cemeteries %>% 
-    transmute(id = source_id, name, acres, courts = FALSE, playgrounds = FALSE, 
-              trails = FALSE, type = "cemetery")
-  ) %>%
+            type = "park") %>%
   filter(as.numeric(acres) > 0.5) %>%

### 2020-09-24 04_accessibility.Rmd

@@
   df %>%
+    filter(!is.na(euc_old)) %>%
     left_join(open_spaces %>% st_set_geometry(NULL), by = c("park_id" = "id")) %>%
@@
   st_cast("MULTIPOLYGON") %>%
-  lwgeom::st_make_valid() %>%
+  st_make_valid() %>%
   summarise(d = 1)

### 2020-09-24 05_estimation.Rmd
Write matrix to file
Restore model estimation code
Don't know where this went in the interim, but we're back now.

@@
 Wtr <- nb2listw(poly2nb(est_data), style = "W", zero.policy = TRUE)
+Wtr %>% write_rds("data/Wtr.rds")
 print(Wtr, zero.policy = TRUE)
@@
                    data = est_data, listw = Wtr, zero.policy = TRUE)
+class(access_slx) <- "lm"
 access_sdem <- errorsarlm(update(base_formula, physact ~ . + euc_access),
@@
   htmlreg(obesity_models, digits = 3, table = FALSE, single.row = TRUE, 
-                   caption.above = TRUE, caption = "Spatial Error Model ",
+                   caption.above = TRUE, caption = "Spatial Error Model ", ci.force = TRUE,
+
           stars = c(0.001, 0.01, 0.05, 0.1) )

### 2020-09-24 manuscript/manuscript.tex

@@
 
-\email{\href{mailto:gregmacfarlane@gmail.com}{\nolinkurl{gregmacfarlane@gmail.com}}}
+\email{\href{mailto:gregmacfarlane@byu.edu}{\nolinkurl{gregmacfarlane@byu.edu}}}
 
@@
 sub-facilities, we created variables for each containing park indicating
-the presence of sports courts, playgrounds, and trails.
-
-To this dataset of parks and regularized green spaces, we add a polygons
-layer of cemeteries in New York that are open to the public. Cemeteries
-are important green spaces that can be used for many types of physical
-activity. These operations leave us with 1,277 distinct green spaces;
-for simplicity we will refer to both parks and cemeteries as ``parks''
-going forward. For each park, we calculate the size of the park in
-acres.
+the presence of sports courts, playgrounds, and trails. These operations
+leave us with 1,191 distinct green spaces; For each park, we calculate
+the size of the park in acres.
 
@@
 \addlinespace[0.3em]
-\multicolumn{6}{l}{\textbf{Park Variables, N = 1277}}\\
-\hspace{1em}Size & Park size in acres & 0.50 & \makecell{1.66\\ (0.95, 5.62)} & 1961.00 & NYC\\
+\multicolumn{6}{l}{\textbf{Park Variables, N = 1191}}\\
+\hspace{1em}Size & Park size in acres & 0.50 & \makecell{1.57\\ (0.94, 4.45)} & 1961.00 & NYC\\
 \hspace{1em}Courts & Presence of sport courts / ball fields & 0.00 & \makecell{0.00\\ (0.00, 0.00)} & 1.00 & NYC\\
@@
 the coefficients are equivalent; this test produces \(p\)-value of only
-\(1.307e-23\). Though this statistic is well beneath a common hypothesis
+\(1.318e-23\). Though this statistic is well beneath a common hypothesis
 test threshold of \(\alpha = 0.05\), we elect retain the null hypothesis
@@
 % latex table generated in R 4.0.0 by xtable 1.8-4 package
-% Thu Jun  4 16:31:52 2020
- (Intercept) & -15.8424 & -26.8735 & -4.8112 &   & -24.9740 & -41.8930 & -8.0549 \\ 
-  log(Density) & 0.0484 & -0.1314 & 0.2282 &   & 0.1775 & 0.0384 & 0.3166 \\ 
-  log(Income) & 5.8210 & 5.2977 & 6.3443 &   & 5.9985 & 5.5746 & 6.4224 \\ 
-  Fulltime & 0.1150 & 0.0936 & 0.1365 &   & 0.1275 & 0.1090 & 0.1460 \\ 
-  College-educated & 0.0012 & -0.0272 & 0.0297 &   & 0.0076 & -0.0158 & 0.0309 \\ 
-  Single Adults & -0.0433 & -0.0623 & -0.0244 &   & -0.0362 & -0.0526 & -0.0198 \\ 
-  Youth (0-17) & -0.1511 & -0.1830 & -0.1192 &   & -0.1310 & -0.1576 & -0.1045 \\ 
-  Young adults (18-34) & 0.0257 & 0.0008 & 0.0505 &   & 0.0295 & 0.0094 & 0.0496 \\ 
-  Seniors (65+) & 0.0137 & -0.0185 & 0.0459 &   & 0.0403 & 0.0130 & 0.0677 \\ 
-  Black population share & -0.0465 & -0.0584 & -0.0346 &   & -0.0499 & -0.0586 & -0.0411 \\ 
-  Asian population share & -0.0686 & -0.0832 & -0.0541 &   & -0.0767 & -0.0873 & -0.0662 \\ 
-  Hispanic population share & -0.1017 & -0.1140 & -0.0894 &   & -0.1025 & -0.1116 & -0.0934 \\ 
-  Other Minorities & 0.0368 & -0.0643 & 0.1378 &   & 0.0037 & -0.0849 & 0.0923 \\ 
-  $\gamma$: log(Density) & 1.2594 & 0.9413 & 1.5774 &   & 1.0985 & 0.7155 & 1.4815 \\ 
-  $\gamma$: log(Income) & 2.3930 & 1.5476 & 3.2383 &   & 1.9742 & 0.9465 & 3.0020 \\ 
-  $\gamma$: Fulltime & -0.1398 & -0.1804 & -0.0991 &   & -0.0397 & -0.0869 & 0.0076 \\ 
-  $\gamma$: College-educated & -0.1312 & -0.1806 & -0.0818 &   & -0.0710 & -0.1305 & -0.0115 \\ 
-  $\gamma$: Single Adults & -0.0480 & -0.0821 & -0.0140 &   & -0.0082 & -0.0504 & 0.0339 \\ 
-  $\gamma$: Youth (0-17) & -0.1031 & -0.1618 & -0.0445 &   & -0.0108 & -0.0798 & 0.0583 \\ 
-  $\gamma$: Young adults (18-34) & 0.1191 & 0.0762 & 0.1619 &   & 0.0842 & 0.0335 & 0.1349 \\ 
-  $\gamma$: Seniors (65+) & 0.0108 & -0.0479 & 0.0695 &   & 0.0590 & -0.0102 & 0.1282 \\ 
-  $\gamma$: Black population share & 0.0096 & -0.0054 & 0.0247 &   & 0.0010 & -0.0151 & 0.0172 \\ 
-  $\gamma$: Asian population share & -0.0661 & -0.0840 & -0.0483 &   & -0.0397 & -0.0583 & -0.0210 \\ 
-  $\gamma$: Hispanic population share & -0.0060 & -0.0216 & 0.0097 &   & -0.0010 & -0.0182 & 0.0162 \\ 
-  $\gamma$: Other Minorities & 0.1868 & -0.0508 & 0.4244 &   & 0.0726 & -0.1845 & 0.3297 \\ 
-  Accessibility & 0.5430 & 0.4195 & 0.6666 &   & 0.1663 & 0.0277 & 0.3048 \\ 
-  $\lambda$: spatial correlation &  &  &  &   & 0.6905 & 0.6513 & 0.7296 \\
+% Tue Sep 22 16:54:49 2020
+ (Intercept) & -15.8791 & -26.8066 & -4.9515 &   & -24.7352 & -41.5391 & -7.9312 \\ 
+  log(Density) & 0.0502 & -0.1280 & 0.2284 &   & 0.1760 & 0.0371 & 0.3150 \\ 
+  log(Income) & 5.8667 & 5.3476 & 6.3859 &   & 6.0134 & 5.5901 & 6.4368 \\ 
+  Fulltime & 0.1157 & 0.0944 & 0.1369 &   & 0.1271 & 0.1086 & 0.1455 \\ 
+  College-educated & 0.0029 & -0.0253 & 0.0311 &   & 0.0077 & -0.0156 & 0.0310 \\ 
+  Single Adults & -0.0435 & -0.0623 & -0.0247 &   & -0.0365 & -0.0528 & -0.0201 \\ 
+  Youth (0-17) & -0.1528 & -0.1844 & -0.1211 &   & -0.1320 & -0.1585 & -0.1055 \\ 
+  Young adults (18-34) & 0.0245 & -0.0001 & 0.0492 &   & 0.0292 & 0.0092 & 0.0493 \\ 
+  Seniors (65+) & 0.0108 & -0.0212 & 0.0427 &   & 0.0386 & 0.0112 & 0.0659 \\ 
+  Black population share & -0.0471 & -0.0589 & -0.0353 &   & -0.0499 & -0.0586 & -0.0412 \\ 
+  Asian population share & -0.0684 & -0.0828 & -0.0540 &   & -0.0764 & -0.0870 & -0.0659 \\ 
+  Hispanic population share & -0.1003 & -0.1126 & -0.0881 &   & -0.1023 & -0.1114 & -0.0932 \\ 
+  Other Minorities & 0.0341 & -0.0661 & 0.1343 &   & 0.0047 & -0.0837 & 0.0931 \\ 
+  $\gamma$: log(Density) & 1.2513 & 0.9367 & 1.5659 &   & 1.0873 & 0.7062 & 1.4684 \\ 
+  $\gamma$: log(Income) & 2.3641 & 1.5266 & 3.2016 &   & 1.9780 & 0.9563 & 2.9997 \\ 
+  $\gamma$: Fulltime & -0.1346 & -0.1749 & -0.0943 &   & -0.0411 & -0.0882 & 0.0059 \\ 
+  $\gamma$: College-educated & -0.1201 & -0.1692 & -0.0711 &   & -0.0704 & -0.1296 & -0.0112 \\ 
+  $\gamma$: Single Adults & -0.0520 & -0.0857 & -0.0183 &   & -0.0094 & -0.0514 & 0.0325 \\ 
+  $\gamma$: Youth (0-17) & -0.1013 & -0.1594 & -0.0432 &   & -0.0128 & -0.0815 & 0.0559 \\ 
+  $\gamma$: Young adults (18-34) & 0.1131 & 0.0706 & 0.1555 &   & 0.0838 & 0.0334 & 0.1342 \\ 
+  $\gamma$: Seniors (65+) & 0.0015 & -0.0568 & 0.0598 &   & 0.0545 & -0.0145 & 0.1235 \\ 
+  $\gamma$: Black population share & 0.0099 & -0.0051 & 0.0248 &   & 0.0011 & -0.0149 & 0.0172 \\ 
+  $\gamma$: Asian population share & -0.0644 & -0.0821 & -0.0467 &   & -0.0397 & -0.0582 & -0.0212 \\ 
+  $\gamma$: Hispanic population share & -0.0074 & -0.0229 & 0.0081 &   & -0.0015 & -0.0185 & 0.0156 \\ 
+  $\gamma$: Other Minorities & 0.1629 & -0.0725 & 0.3983 &   & 0.0723 & -0.1840 & 0.3286 \\ 
+  Accessibility & 0.6575 & 0.5348 & 0.7801 &   & 0.2306 & 0.0907 & 0.3705 \\ 
+  $\lambda$: spatial correlation &  &  &  &   & 0.6854 & 0.6459 & 0.7249 \\
 
@@
 the share of young adults in a tract increases the expected physical
-activity rate in a tract by 0.02947 percentage points, and a percentage
+activity rate in a tract by 0.02922 percentage points, and a percentage
 point increase in the share of young adults \emph{in neighboring tracts}
 increases the expected physical activity rate by an \emph{additional}
-0.08417 percentage points. This opportunity to examine spatial
+0.08378 percentage points. This opportunity to examine spatial
 spillovers of attributes is a key benefit of using a spatial model.
@@
 
-\begin{tabular}{l c c c }
+\begin{tabular}{l c c c}
 \toprule
@@
 \midrule
-Accessibility  & $0.1663^{*}$        & $0.1493^{*}$        & $0.5865$             \\
-               & $[0.0277;\ 0.3048]$ & $[0.0073;\ 0.2914]$ & $[-0.1778;\ 1.3508]$ \\
+Accessibility  & $0.2306^{*}$        & $0.1923^{*}$        & $0.5865$             \\
+               & $ [0.0907; 0.3705]$ & $ [0.0498; 0.3347]$ & $ [-0.1778; 1.3508]$ \\
 \midrule
-Num. obs.      & 2099                & 2099                & 2099                 \\
-Parameters     & 28                  & 28                  & 28                   \\
-Log Likelihood & -4435.3869          & -4436.0034          & -4436.9264           \\
+Num. obs.      & $2099$              & $2099$              & $2099$               \\
+Parameters     & $28$                & $28$                & $28$                 \\
+Log Likelihood & $-4433.0965$        & $-4434.7087$        & $-4436.9264$         \\
 \bottomrule
-\multicolumn{4}{l}{\scriptsize{$^*$ 0 outside the confidence interval 95\% confidence interval in brackets.  $y = $ tract-level physical activity rate.}}
+\multicolumn{4}{l}{\scriptsize{$^*$ Null hypothesis value outside the confidence interval. 95\% confidence interval in brackets.  $y = $ tract-level physical activity rate.}}
 \end{tabular}
@@
 \midrule
-Physical Activity           & $-0.4802^{*}$         & $-0.4802^{*}$         & $-0.4803^{*}$         \\
-                            & $[-0.5043;\ -0.4561]$ & $[-0.5043;\ -0.4561]$ & $[-0.5044;\ -0.4562]$ \\
-$\gamma$: Physical Activity & $0.0197$              & $0.0198$              & $0.0173$              \\
-                            & $[-0.0380;\ 0.0775]$  & $[-0.0380;\ 0.0775]$  & $[-0.0404;\ 0.0750]$  \\
-Accessibility               & $-0.0403$             & $-0.0429$             & $-0.2630$             \\
-                            & $[-0.1158;\ 0.0351]$  & $[-0.1210;\ 0.0352]$  & $[-0.6491;\ 0.1232]$  \\
+Physical Activity           & $-0.4798^{*}$         & $-0.4800^{*}$         & $-0.4803^{*}$         \\
+                            & $ [-0.5039; -0.4556]$ & $ [-0.5041; -0.4558]$ & $ [-0.5044; -0.4562]$ \\
+$\gamma$: Physical Activity & $0.0207$              & $0.0204$              & $0.0173$              \\
+                            & $ [-0.0371;  0.0785]$ & $ [-0.0375;  0.0782]$ & $ [-0.0404;  0.0750]$ \\
+Accessibility               & $-0.0495$             & $-0.0471$             & $-0.2630$             \\
+                            & $ [-0.1260;  0.0270]$ & $ [-0.1259;  0.0316]$ & $ [-0.6491;  0.1232]$ \\
 \midrule
-Num. obs.                   & 2099                  & 2099                  & 2099                  \\
-Parameters                  & 30                    & 30                    & 30                    \\
-Log Likelihood              & -3113.8451            & -3113.8136            & -3113.5028            \\
+Num. obs.                   & $2099$                & $2099$                & $2099$                \\
+Parameters                  & $30$                  & $30$                  & $30$                  \\
+Log Likelihood              & $-3113.5891$          & $-3113.7048$          & $-3113.5028$          \\
 \bottomrule
-\multicolumn{4}{l}{\scriptsize{$^*$ 0 outside the confidence interval 95\% confidence interval in brackets.  $y = $ tract-level obesity rate.}}
+\multicolumn{4}{l}{\scriptsize{$^*$ Null hypothesis value outside the confidence interval. 95\% confidence interval in brackets.  $y = $ tract-level obesity rate.}}
 \end{tabular}

### 2020-09-24 manuscript/manuscript.Rmd
Address contributions more fully, close #9

@@
 In spite of its flexibility and basis in choice theory, utility-based
-accessibility measures have not received much application in the accessibility
+accessibility measures have not received much application in the park accessibility
 literature compared with distance-based or even gravity-based measures.
 @Vale2016 present a descriptive classification of active accessibility techniques, and
-explicitly dismiss utility-based metrics for incorporating randomness. The
-accessibility formula presented in Equation \ref{eq:utility} is the expectation of a
-random utility process, and is not in and of itself random any more than the
-gravity model is random.
+explicitly dismiss utility-based metrics for incorporating randomness. This is 
+a curious decision: The accessibility formula presented in Equation
+\ref{eq:utility} is the expectation of a random utility process, but the measure
+is not in and of itself random any more than the gravity model is random.
 Utility-based accessibility metrics are commonly used, however, in alternatives
@@
 making calibrated and multimodal logsums readily available [@Geurs2010].
+
+To our knowledge, there has been no previous attempt to examine
+access to parks in a metropolitan area using a utility-based definition as the
+primary indicator of access. Consequently, there has also been no previous
+effort to examine the effect of park access on health outcomes using this
+theoretically attractive technique. In this study, we first develop a utility-based
+measure of park access in New York City, and then apply this measure to study the
+effect of access to public parks on aggregate health outcomes.
 

### 2020-09-24 manuscript/manuscript.Rmd
Clean up model estimates, with cemeteries eliminated
This closes #10

@@
 ```{r slx-sdem, results = "asis"}
+class(slx_vs_sdem$SLX) <- "lm"
 slx_coefs <- lapply(slx_vs_sdem, function(x) tidy(x, conf.int = TRUE))
@@
 \midrule
-Log Likelihood & \multicolumn{3}{c}{$-4831.974$} & & \multicolumn{3}{c}{$-4435.507$}\\
-Num.Obs.       & \multicolumn{3}{c}{$2099$}   & & \multicolumn{3}{c}{$2099$}\\
+Log Likelihood & \multicolumn{3}{c}{$`r logLik(slx_vs_sdem$SLX)`$} & & \multicolumn{3}{c}{$`r logLik(slx_vs_sdem$SDEM)`$}\\
+Num.Obs.       & \multicolumn{3}{c}{$`r nobs(slx_vs_sdem$SLX)`$}   & & \multicolumn{3}{c}{$`r nrow(slx_vs_sdem$SDEM$X)`$}\\
 \bottomrule
@@
 Table \ref{tab:pa-models} presents the estimated spatial lag and accessibility
-coefficients for three models using different specifications of the utility
+coefficients for two models using different specifications of the utility
 equation, as well as the ten-minute walk buffer calculated by ParkScore. 
@@
 suppressed for clarity but do not change meaningfully across the four specifications.
-Complete model estimates are available in Table \ref{tab:pa-fullmodels} of the Supplementary Material. Each of the three
+Complete model estimates are available in Table \ref{tab:pa-fullmodels} of the Supplementary Material. Each of the two
 utility-based specifications is significant at the $\alpha = 0.05$ level or lower,
-and is of the hypothesized directionality. That is, residents living in tracts 
+and is of the hypothesized direction That is, residents living in tracts 
 with increased utility-based accessibility to green spaces show a significantly
-higher physical activity participation rate. Taking the rough mean of the 2
+higher physical activity participation rate. Taking the rough mean of the two
 estimated utility-based coefficients, moving from the least-accessible tract
@@
 most-accessible tract ($A_i = 3$) is expected to raise the physical activity rate
-by `r 6 * .15` percentage points. With the understanding of the full 95\% confidence
+by `r 6 * .22` percentage points. With the understanding of the full 95\% confidence
 interval, we could suggest that the true effect of excellent versus poor park access
-is anywhere between `r 6 * .01` and `r 6 * .3` percentage points.
+is anywhere between `r 6 * .05` and `r 6 * .35` percentage points.
 
-The 10-minute walk buffer is considerably less useful at isolating the effects
+In contrast, 10-minute walk buffer is considerably less useful at isolating the effects
 of park "access" on physical activity rates. As so few tracts are located
 outside of the buffer, the standard error of the estimated effect is large and implies
-an effect on activity rates anywhere from a loss of `r 6 * .18` percentage points
-to a gain of `r 6 * 1.35`.
+an effect on activity rates anywhere from a loss of `r .18` percentage points
+to a gain of `r 1.35`.
 

### 2020-09-24 manuscript/manuscript.Rmd
Clarify applicability strategy close #13

@@
 observation however reinforces our suggestion that a measure explicitly based in
-the utility of access is warranted.
+the utility of access is warranted.  We acknowledge that a utility-based
+framework for access may be more technically difficult for some practitioners to
+independently construct for their analyses than an isochrone or even a
+gravity-based measure. That said, it may not be necessary for practicing
+planners to construct this measure themselves: web-based tools such as ParkIndex
+[@Kaczynski2016] and even WalkScore (https://www.walkscore.com) abstract complex
+methodologies into tools that planners can and do readily apply.
 
@@
 a more comprehensive and flexible approach
-for measuring the impact of park access on health outcomes. Adopting
-utility-based accessibilities of the kind used in this study will allow
+for measuring the impact of park access on health outcomes.
+
+Adopting utility-based accessibilities of the kind used in this study will allow
 researchers to encompass the full range of park amenities in their accessibility
-analyses, and to separate the definition of access from the study of its effects.
-This will in turn enhance the ability of planners to consider how multiple
-attributes of a park --- from its location to its size to its amenities and
-beyond --- benefit the health of the community the park serves.
+analyses, and to separate the definition of access from the study of its
+effects. This will in turn enhance the ability of planners to consider how
+multiple attributes of a park --- from its location to its size to its amenities
+and beyond --- benefit the health of the community the park serves.
 

### 2020-09-24 manuscript/manuscript.Rmd
Clarify discussion of limitations, close #11

@@
 a neighborhood's accessibility to park features that its residents most care
-about. In this paper, we proceed only incrementally towards
-this by adding some selected park amenities as an element of each park's
-attractiveness above and beyond its size. The set of amenities we included in
+about. The set of amenities we included in
 the utility calculation --- and the contribution of each amenity to the overall
-utility --- was dictated by the availability of data on the park amenities in New
-York City and our ability to find comparable prior studies with transferrable
-utility parameters. We can envision a study where mobile device data
+utility --- was dictated by the availability of open data on the park amenities in New
+York City and our ability to find comparable prior studies with transferable
+utility parameters. It is remarkable that our two utility specifications --- one
+with size and distance, and one with size and distance plus amenities --- result
+in such similar model estimates. This may indicate that the utility is driven
+largely by size and distance, or that the additional park amenities we included
+in the utility specification are spatially distributed in a way that correlates
+with the health outcomes. Either way, further analysis examining more amenity
+variables is warranted.
+ We can envision a study where mobile device data
 revealing the home locations of park users would be paired with more detailed

### 2020-09-24 manuscript/manuscript.Rmd
Minor edits

@@
 
-This paper applies a previously-presented but little-used accessibility
+This paper applies a previously presented but seldom applied accessibility
 statistic that could, in theory, accommodate many attributes of the destination
@@
 improvement in public health. Although many have theorized the link between park
-accessibility and these metrics, previous literature has produced mixed
-findings, perhaps owing to the range of variables modeled and the coarse spatial
-scale of the analyses. Using New York City as a case study, we presented a
+access and public, previous literature has produced mixed
+findings, perhaps owing to the wide range of accessibility definitions. 
+Using New York City as a case study, we presented a
 holistic and flexible measurement for park accessibility that compares the

### 2020-09-24 manuscript/manuscript.tex
Build document with revisions

@@
 In spite of its flexibility and basis in choice theory, utility-based
-accessibility measures have not received much application in the
+accessibility measures have not received much application in the park
 accessibility literature compared with distance-based or even
@@
 classification of active accessibility techniques, and explicitly
-dismiss utility-based metrics for incorporating randomness. The
-accessibility formula presented in Equation \ref{eq:utility} is the
-expectation of a random utility process, and is not in and of itself
-random any more than the gravity model is random. Utility-based
-accessibility metrics are commonly used, however, in alternatives
-analyses of transit infrastructure improvements \citep{DeJong2007}. A
-reason for this is likely that a regional travel demand model is
-available to the analysts, thus making calibrated and multimodal logsums
-readily available \citep{Geurs2010}.
+dismiss utility-based metrics for incorporating randomness. This is a
+curious decision: The accessibility formula presented in Equation
+\ref{eq:utility} is the expectation of a random utility process, but the
+measure is not in and of itself random any more than the gravity model
+is random. Utility-based accessibility metrics are commonly used,
+however, in alternatives analyses of transit infrastructure improvements
+\citep{DeJong2007}. A reason for this is likely that a regional travel
+demand model is available to the analysts, thus making calibrated and
+multimodal logsums readily available \citep{Geurs2010}.
+
+To our knowledge, there has been no previous attempt to examine access
+to parks in a metropolitan area using a utility-based definition as the
+primary indicator of access. Consequently, there has also been no
+previous effort to examine the effect of park access on health outcomes
+using this theoretically attractive technique. In this study, we first
+develop a utility-based measure of park access in New York City, and
+then apply this measure to study the effect of access to public parks on
+aggregate health outcomes.
 
@@
 \(1.318e-23\). Though this statistic is well beneath a common hypothesis
-test threshold of \(\alpha = 0.05\), we elect retain the null hypothesis
-that the coefficients are equivalent, as the differences are at no point
-practically different from each other. The consequences of rejecting the
-null hypothesis in this case would be to suggest a model with spatial
-dependence of the dependent variable; as stated above, we feel that such
-a relationship is unreasonable. As a consequence of these analyses, we
-adopt the SDEM specification moving forward as the spatial lag of the
-errors is significant and the overall log likelihood of the SDEM is
-higher than the SLX specification.
+test threshold of \(\alpha = 0.05\), we elect to retain the null
+hypothesis that the coefficients are equivalent, as the differences are
+at no point practically different from each other. The consequences of
+rejecting the null hypothesis in this case would be to suggest a model
+with spatial dependence of the dependent variable; as stated above, we
+feel that such a relationship is unreasonable. As a consequence of these
+analyses, we adopt the SDEM specification moving forward as the spatial
+lag of the errors is significant and the overall log likelihood of the
+SDEM is higher than the SLX specification.
 
@@
 % latex table generated in R 4.0.0 by xtable 1.8-4 package
-% Tue Sep 22 16:54:49 2020
+% Thu Sep 24 13:27:59 2020
  (Intercept) & -15.8791 & -26.8066 & -4.9515 &   & -24.7352 & -41.5391 & -7.9312 \\ 
@@
 \midrule
-Log Likelihood & \multicolumn{3}{c}{$-4831.974$} & & \multicolumn{3}{c}{$-4435.507$}\\
-Num.Obs.       & \multicolumn{3}{c}{$2099$}   & & \multicolumn{3}{c}{$2099$}\\
+Log Likelihood & \multicolumn{3}{c}{$-4,815$} & & \multicolumn{3}{c}{$-4,433$}\\
+Num.Obs.       & \multicolumn{3}{c}{$2,099$}   & & \multicolumn{3}{c}{$2,099$}\\
 \bottomrule
@@
 Table \ref{tab:pa-models} presents the estimated spatial lag and
-accessibility coefficients for three models using different
-specifications of the utility equation, as well as the ten-minute walk
-buffer calculated by ParkScore. Note that the model called ``Size and
+accessibility coefficients for two models using different specifications
+of the utility equation, as well as the ten-minute walk buffer
+calculated by ParkScore. Note that the model called ``Size and
 Distance'' is precisely the model labeled ``SDEM'' in Table
@@
 Complete model estimates are available in Table \ref{tab:pa-fullmodels}
-of the Supplementary Material. Each of the three utility-based
+of the Supplementary Material. Each of the two utility-based
 specifications is significant at the \(\alpha = 0.05\) level or lower,
-and is of the hypothesized directionality. That is, residents living in
-tracts with increased utility-based accessibility to green spaces show a
+and is of the hypothesized direction That is, residents living in tracts
+with increased utility-based accessibility to green spaces show a
 significantly higher physical activity participation rate. Taking the
-rough mean of the 2 estimated utility-based coefficients, moving from
+rough mean of the two estimated utility-based coefficients, moving from
 the least-accessible tract (\(A_i = -3\)) to the most-accessible tract
-(\(A_i = 3\)) is expected to raise the physical activity rate by 0.9
+(\(A_i = 3\)) is expected to raise the physical activity rate by 1.32
 percentage points. With the understanding of the full 95\% confidence
 interval, we could suggest that the true effect of excellent versus poor
-park access is anywhere between 0.06 and 1.8 percentage points.
-
-The 10-minute walk buffer is considerably less useful at isolating the
-effects of park ``access'' on physical activity rates. As so few tracts
-are located outside of the buffer, the standard error of the estimated
-effect is large and implies an effect on activity rates anywhere from a
-loss of 1.08 percentage points to a gain of 8.1.
+park access is anywhere between 0.3 and 2.1 percentage points.
+
+In contrast, 10-minute walk buffer is considerably less useful at
+isolating the effects of park ``access'' on physical activity rates. As
+so few tracts are located outside of the buffer, the standard error of
+the estimated effect is large and implies an effect on activity rates
+anywhere from a loss of 0.18 percentage points to a gain of 1.35.
 
@@
 
-This paper applies a previously-presented but little-used accessibility
-statistic that could, in theory, accommodate many attributes of the
-destination parks as well as the people who might use them. As an
-illustration: the park-going population could be separated into at least
-four delineated clusters, each preferring different amenities of a park:
+This paper applies a previously presented but seldom applied
+accessibility statistic that could, in theory, accommodate many
+attributes of the destination parks as well as the people who might use
+them. As an illustration: the park-going population could be separated
+into at least four delineated clusters, each preferring different
+amenities of a park:
 
@@
 obtain a measure of a neighborhood's accessibility to park features that
-its residents most care about. In this paper, we proceed only
-incrementally towards this by adding some selected park amenities as an
-element of each park's attractiveness above and beyond its size. The set
-of amenities we included in the utility calculation --- and the
-contribution of each amenity to the overall utility --- was dictated by
-the availability of data on the park amenities in New York City and our
-ability to find comparable prior studies with transferrable utility
-parameters. We can envision a study where mobile device data revealing
-the home locations of park users would be paired with more detailed park
-amenities and use data (e.g.~geolocated Twitter data \emph{a la}
-\citet{roberts2017using}) to estimate the utility contribution of these
-features. This could in turn provide a more nuanced understanding of the
-relationship between park accessibility, use, and health outcomes.
+its residents most care about. The set of amenities we included in the
+utility calculation --- and the contribution of each amenity to the
+overall utility --- was dictated by the availability of open data on the
+park amenities in New York City and our ability to find comparable prior
+studies with transferable utility parameters. It is remarkable that our
+two utility specifications --- one with size and distance, and one with
+size and distance plus amenities --- result in such similar model
+estimates. This may indicate that the utility is driven largely by size
+and distance, or that the additional park amenities we included in the
+utility specification are spatially distributed in a way that correlates
+with the health outcomes. Either way, further analysis examining more
+amenity variables is warranted. We can envision a study where mobile
+device data revealing the home locations of park users would be paired
+with more detailed park amenities and use data (e.g.~geolocated Twitter
+data \emph{a la} \citet{roberts2017using}) to estimate the utility
+contribution of these features. This could in turn provide a more
+nuanced understanding of the relationship between park accessibility,
+use, and health outcomes.
 
@@
 reinforces our suggestion that a measure explicitly based in the utility
-of access is warranted.
+of access is warranted. We acknowledge that a utility-based framework
+for access may be more technically difficult for some practitioners to
+independently construct for their analyses than an isochrone or even a
+gravity-based measure. That said, it may not be necessary for practicing
+planners to construct this measure themselves: web-based tools such as
+ParkIndex \citep{Kaczynski2016} and even WalkScore
+(\url{https://www.walkscore.com}) abstract complex methodologies into
+tools that planners can and do readily apply.
 
@@
 measures of improvement in public health. Although many have theorized
-the link between park accessibility and these metrics, previous
-literature has produced mixed findings, perhaps owing to the range of
-variables modeled and the coarse spatial scale of the analyses. Using
-New York City as a case study, we presented a holistic and flexible
-measurement for park accessibility that compares the continuous distance
-to all parks in the region, weighted against the size of the park and
-its other amenities, with weights determinable through revealed
-preferences. In terms of physical activity, we found a positive
-relationship where the least park-accessible tracts have an expected
-physical activity participation rate between 0.06 and 1.8 percentage
-points lower than the most accessible tracts. We also found a suggestive
-though not significant relationship between park accessibility and
-expected obesity rates \emph{in addition to} the effect of physical
-activity participation.
+the link between park access and public, previous literature has
+produced mixed findings, perhaps owing to the wide range of
+accessibility definitions. Using New York City as a case study, we
+presented a holistic and flexible measurement for park accessibility
+that compares the continuous distance to all parks in the region,
+weighted against the size of the park and its other amenities, with
+weights determinable through revealed preferences. In terms of physical
+activity, we found a positive relationship where the least
+park-accessible tracts have an expected physical activity participation
+rate between 0.06 and 1.8 percentage points lower than the most
+accessible tracts. We also found a suggestive though not significant
+relationship between park accessibility and expected obesity rates
+\emph{in addition to} the effect of physical activity participation.
 
@@
 more comprehensive and flexible approach for measuring the impact of
-park access on health outcomes. Adopting utility-based accessibilities
-of the kind used in this study will allow researchers to encompass the
-full range of park amenities in their accessibility analyses, and to
-separate the definition of access from the study of its effects. This
-will in turn enhance the ability of planners to consider how multiple
-attributes of a park --- from its location to its size to its amenities
-and beyond --- benefit the health of the community the park serves.
+park access on health outcomes.
+
+Adopting utility-based accessibilities of the kind used in this study
+will allow researchers to encompass the full range of park amenities in
+their accessibility analyses, and to separate the definition of access
+from the study of its effects. This will in turn enhance the ability of
+planners to consider how multiple attributes of a park --- from its
+location to its size to its amenities and beyond --- benefit the health
+of the community the park serves.
 
@@
 \hypertarget{appendix}{%
-\subsection{Supplementary Material}\label{appendix}}
-\setcounter{table}{0}
-\renewcommand{\thetable}{S\arabic{table}}
-
-In this supplementary material we present the complete estimation results for the
+\subsection{Appendix}\label{appendix}}
+
+In this appendix we present the complete estimation results for the
 models relating different definitions of access to physical activity (in
@@
 \midrule
-(Intercept)                         & $-24.5190^{*}$         & $-24.8266^{*}$         & $-24.8920^{*}$         & $-24.7176^{*}$         \\
-                                    & $ [-41.5947; -7.4433]$ & $ [-41.7445; -7.9087]$ & $ [-41.8372; -7.9468]$ & $ [-41.7891; -7.6461]$ \\
-log(Density)                        & $0.1740^{*}$           & $0.1766^{*}$           & $0.1757^{*}$           & $0.1686^{*}$           \\
-                                    & $ [  0.0348;  0.3132]$ & $ [  0.0375;  0.3156]$ & $ [  0.0366;  0.3148]$ & $ [  0.0293;  0.3079]$ \\
-log(Income)                         & $5.9786^{*}$           & $5.9976^{*}$           & $5.9964^{*}$           & $5.9767^{*}$           \\
-                                    & $ [  5.5540;  6.4032]$ & $ [  5.5737;  6.4215]$ & $ [  5.5723;  6.4205]$ & $ [  5.5523;  6.4011]$ \\
-Fulltime                            & $0.1283^{*}$           & $0.1275^{*}$           & $0.1275^{*}$           & $0.1285^{*}$           \\
-                                    & $ [  0.1098;  0.1468]$ & $ [  0.1090;  0.1460]$ & $ [  0.1090;  0.1460]$ & $ [  0.1100;  0.1470]$ \\
-College-educated                    & $0.0075$               & $0.0076$               & $0.0073$               & $0.0083$               \\
-                                    & $ [ -0.0159;  0.0310]$ & $ [ -0.0158;  0.0309]$ & $ [ -0.0161;  0.0306]$ & $ [ -0.0152;  0.0317]$ \\
-Single Adults                       & $-0.0363^{*}$          & $-0.0362^{*}$          & $-0.0360^{*}$          & $-0.0366^{*}$          \\
-                                    & $ [ -0.0527; -0.0198]$ & $ [ -0.0526; -0.0198]$ & $ [ -0.0524; -0.0196]$ & $ [ -0.0530; -0.0201]$ \\
-Youth (0-17)                        & $-0.1306^{*}$          & $-0.1311^{*}$          & $-0.1310^{*}$          & $-0.1311^{*}$          \\
-                                    & $ [ -0.1572; -0.1040]$ & $ [ -0.1576; -0.1046]$ & $ [ -0.1576; -0.1045]$ & $ [ -0.1577; -0.1045]$ \\
-Young adults (18-34)                & $0.0283^{*}$           & $0.0293^{*}$           & $0.0294^{*}$           & $0.0281^{*}$           \\
-                                    & $ [  0.0081;  0.0484]$ & $ [  0.0092;  0.0495]$ & $ [  0.0092;  0.0495]$ & $ [  0.0079;  0.0482]$ \\
-Seniors (65+)                       & $0.0430^{*}$           & $0.0403^{*}$           & $0.0408^{*}$           & $0.0427^{*}$           \\
-                                    & $ [  0.0157;  0.0704]$ & $ [  0.0130;  0.0677]$ & $ [  0.0135;  0.0682]$ & $ [  0.0153;  0.0700]$ \\
-Black population share              & $-0.0499^{*}$          & $-0.0499^{*}$          & $-0.0498^{*}$          & $-0.0497^{*}$          \\
-                                    & $ [ -0.0587; -0.0412]$ & $ [ -0.0586; -0.0412]$ & $ [ -0.0585; -0.0411]$ & $ [ -0.0584; -0.0409]$ \\
-Asian population share              & $-0.0772^{*}$          & $-0.0767^{*}$          & $-0.0768^{*}$          & $-0.0774^{*}$          \\
-                                    & $ [ -0.0877; -0.0666]$ & $ [ -0.0873; -0.0662]$ & $ [ -0.0874; -0.0663]$ & $ [ -0.0879; -0.0669]$ \\
-Hispanic population share           & $-0.1021^{*}$          & $-0.1025^{*}$          & $-0.1025^{*}$          & $-0.1020^{*}$          \\
-                                    & $ [ -0.1112; -0.0929]$ & $ [ -0.1116; -0.0934]$ & $ [ -0.1116; -0.0934]$ & $ [ -0.1111; -0.0928]$ \\
-Other Minorities                    & $0.0006$               & $0.0035$               & $0.0037$               & $-0.0005$              \\
-                                    & $ [ -0.0882;  0.0894]$ & $ [ -0.0851;  0.0921]$ & $ [ -0.0850;  0.0923]$ & $ [ -0.0893;  0.0883]$ \\
-$\gamma$: log(Density)              & $1.1105^{*}$           & $1.0987^{*}$           & $1.1030^{*}$           & $1.0928^{*}$           \\
-                                    & $ [  0.7245;  1.4964]$ & $ [  0.7156;  1.4817]$ & $ [  0.7196;  1.4865]$ & $ [  0.7063;  1.4793]$ \\
-$\gamma$: log(Income)               & $1.9269^{*}$           & $1.9646^{*}$           & $1.9570^{*}$           & $1.9189^{*}$           \\
-                                    & $ [  0.8913;  2.9625]$ & $ [  0.9370;  2.9922]$ & $ [  0.9282;  2.9857]$ & $ [  0.8836;  2.9541]$ \\
-$\gamma$: Fulltime                  & $-0.0360$              & $-0.0396$              & $-0.0388$              & $-0.0363$              \\
-                                    & $ [ -0.0835;  0.0115]$ & $ [ -0.0869;  0.0076]$ & $ [ -0.0861;  0.0085]$ & $ [ -0.0837;  0.0112]$ \\
-$\gamma$: College-educated          & $-0.0707^{*}$          & $-0.0711^{*}$          & $-0.0721^{*}$          & $-0.0731^{*}$          \\
-                                    & $ [ -0.1307; -0.0107]$ & $ [ -0.1306; -0.0116]$ & $ [ -0.1317; -0.0125]$ & $ [ -0.1332; -0.0131]$ \\
-$\gamma$: Single Adults             & $-0.0081$              & $-0.0085$              & $-0.0077$              & $-0.0076$              \\
-                                    & $ [ -0.0506;  0.0344]$ & $ [ -0.0507;  0.0336]$ & $ [ -0.0499;  0.0345]$ & $ [ -0.0501;  0.0348]$ \\
-$\gamma$: Youth (0-17)              & $-0.0111$              & $-0.0111$              & $-0.0101$              & $-0.0120$              \\
-                                    & $ [ -0.0806;  0.0585]$ & $ [ -0.0802;  0.0579]$ & $ [ -0.0793;  0.0591]$ & $ [ -0.0815;  0.0575]$ \\
-$\gamma$: Young adults (18-34)      & $0.0806^{*}$           & $0.0842^{*}$           & $0.0848^{*}$           & $0.0801^{*}$           \\
-                                    & $ [  0.0296;  0.1317]$ & $ [  0.0335;  0.1349]$ & $ [  0.0339;  0.1356]$ & $ [  0.0291;  0.1311]$ \\
-$\gamma$: Seniors (65+)             & $0.0625$               & $0.0589$               & $0.0603$               & $0.0623$               \\
-                                    & $ [ -0.0071;  0.1322]$ & $ [ -0.0103;  0.1282]$ & $ [ -0.0090;  0.1296]$ & $ [ -0.0073;  0.1319]$ \\
+(Intercept)                         & $-24.5190^{*}$         & $-24.7352^{*}$         & $-24.8758^{*}$         & $-24.7176^{*}$         \\
+                                    & $ [-41.5947; -7.4433]$ & $ [-41.5391; -7.9312]$ & $ [-41.7511; -8.0005]$ & $ [-41.7891; -7.6461]$ \\
+log(Density)                        & $0.1740^{*}$           & $0.1760^{*}$           & $0.1753^{*}$           & $0.1686^{*}$           \\
+                                    & $ [  0.0348;  0.3132]$ & $ [  0.0371;  0.3150]$ & $ [  0.0362;  0.3143]$ & $ [  0.0293;  0.3079]$ \\
+log(Income)                         & $5.9786^{*}$           & $6.0134^{*}$           & $6.0060^{*}$           & $5.9767^{*}$           \\
+                                    & $ [  5.5540;  6.4032]$ & $ [  5.5901;  6.4368]$ & $ [  5.5822;  6.4298]$ & $ [  5.5523;  6.4011]$ \\
+Fulltime                            & $0.1283^{*}$           & $0.1271^{*}$           & $0.1272^{*}$           & $0.1285^{*}$           \\
+                                    & $ [  0.1098;  0.1468]$ & $ [  0.1086;  0.1455]$ & $ [  0.1087;  0.1457]$ & $ [  0.1100;  0.1470]$ \\
+College-educated                    & $0.0075$               & $0.0077$               & $0.0071$               & $0.0083$               \\
+                                    & $ [ -0.0159;  0.0310]$ & $ [ -0.0156;  0.0310]$ & $ [ -0.0162;  0.0305]$ & $ [ -0.0152;  0.0317]$ \\
+Single Adults                       & $-0.0363^{*}$          & $-0.0365^{*}$          & $-0.0362^{*}$          & $-0.0366^{*}$          \\
+                                    & $ [ -0.0527; -0.0198]$ & $ [ -0.0528; -0.0201]$ & $ [ -0.0526; -0.0198]$ & $ [ -0.0530; -0.0201]$ \\
+Youth (0-17)                        & $-0.1306^{*}$          & $-0.1320^{*}$          & $-0.1316^{*}$          & $-0.1311^{*}$          \\
+                                    & $ [ -0.1572; -0.1040]$ & $ [ -0.1585; -0.1055]$ & $ [ -0.1581; -0.1050]$ & $ [ -0.1577; -0.1045]$ \\
+Young adults (18-34)                & $0.0283^{*}$           & $0.0292^{*}$           & $0.0293^{*}$           & $0.0281^{*}$           \\
+                                    & $ [  0.0081;  0.0484]$ & $ [  0.0092;  0.0493]$ & $ [  0.0092;  0.0494]$ & $ [  0.0079;  0.0482]$ \\
+Seniors (65+)                       & $0.0430^{*}$           & $0.0386^{*}$           & $0.0398^{*}$           & $0.0427^{*}$           \\
+                                    & $ [  0.0157;  0.0704]$ & $ [  0.0112;  0.0659]$ & $ [  0.0125;  0.0671]$ & $ [  0.0153;  0.0700]$ \\
+Black population share              & $-0.0499^{*}$          & $-0.0499^{*}$          & $-0.0497^{*}$          & $-0.0497^{*}$          \\
+                                    & $ [ -0.0587; -0.0412]$ & $ [ -0.0586; -0.0412]$ & $ [ -0.0585; -0.0410]$ & $ [ -0.0584; -0.0409]$ \\
+Asian population share              & $-0.0772^{*}$          & $-0.0764^{*}$          & $-0.0766^{*}$          & $-0.0774^{*}$          \\
+                                    & $ [ -0.0877; -0.0666]$ & $ [ -0.0870; -0.0659]$ & $ [ -0.0872; -0.0661]$ & $ [ -0.0879; -0.0669]$ \\
+Hispanic population share           & $-0.1021^{*}$          & $-0.1023^{*}$          & $-0.1024^{*}$          & $-0.1020^{*}$          \\
+                                    & $ [ -0.1112; -0.0929]$ & $ [ -0.1114; -0.0932]$ & $ [ -0.1115; -0.0933]$ & $ [ -0.1111; -0.0928]$ \\
+Other Minorities                    & $0.0006$               & $0.0047$               & $0.0043$               & $-0.0005$              \\
+                                    & $ [ -0.0882;  0.0894]$ & $ [ -0.0837;  0.0931]$ & $ [ -0.0842;  0.0929]$ & $ [ -0.0893;  0.0883]$ \\
+$\gamma$: log(Density)              & $1.1105^{*}$           & $1.0873^{*}$           & $1.0967^{*}$           & $1.0928^{*}$           \\
+                                    & $ [  0.7245;  1.4964]$ & $ [  0.7062;  1.4684]$ & $ [  0.7145;  1.4789]$ & $ [  0.7063;  1.4793]$ \\
+$\gamma$: log(Income)               & $1.9269^{*}$           & $1.9780^{*}$           & $1.9650^{*}$           & $1.9189^{*}$           \\
+                                    & $ [  0.8913;  2.9625]$ & $ [  0.9563;  2.9997]$ & $ [  0.9397;  2.9902]$ & $ [  0.8836;  2.9541]$ \\
+$\gamma$: Fulltime                  & $-0.0360$              & $-0.0411$              & $-0.0394$              & $-0.0363$              \\
+                                    & $ [ -0.0835;  0.0115]$ & $ [ -0.0882;  0.0059]$ & $ [ -0.0865;  0.0078]$ & $ [ -0.0837;  0.0112]$ \\
+$\gamma$: College-educated          & $-0.0707^{*}$          & $-0.0704^{*}$          & $-0.0718^{*}$          & $-0.0731^{*}$          \\
+                                    & $ [ -0.1307; -0.0107]$ & $ [ -0.1296; -0.0112]$ & $ [ -0.1312; -0.0125]$ & $ [ -0.1332; -0.0131]$ \\
+$\gamma$: Single Adults             & $-0.0081$              & $-0.0094$              & $-0.0080$              & $-0.0076$              \\
+                                    & $ [ -0.0506;  0.0344]$ & $ [ -0.0514;  0.0325]$ & $ [ -0.0501;  0.0341]$ & $ [ -0.0501;  0.0348]$ \\
+$\gamma$: Youth (0-17)              & $-0.0111$              & $-0.0128$              & $-0.0108$              & $-0.0120$              \\
+                                    & $ [ -0.0806;  0.0585]$ & $ [ -0.0815;  0.0559]$ & $ [ -0.0797;  0.0582]$ & $ [ -0.0815;  0.0575]$ \\
+$\gamma$: Young adults (18-34)      & $0.0806^{*}$           & $0.0838^{*}$           & $0.0846^{*}$           & $0.0801^{*}$           \\
+                                    & $ [  0.0296;  0.1317]$ & $ [  0.0334;  0.1342]$ & $ [  0.0340;  0.1352]$ & $ [  0.0291;  0.1311]$ \\
+$\gamma$: Seniors (65+)             & $0.0625$               & $0.0545$               & $0.0579$               & $0.0623$               \\
+                                    & $ [ -0.0071;  0.1322]$ & $ [ -0.0145;  0.1235]$ & $ [ -0.0112;  0.1270]$ & $ [ -0.0073;  0.1319]$ \\
 $\gamma$: Black population share    & $0.0006$               & $0.0011$               & $0.0008$               & $0.0006$               \\
-                                    & $ [ -0.0157;  0.0168]$ & $ [ -0.0151;  0.0172]$ & $ [ -0.0153;  0.0170]$ & $ [ -0.0157;  0.0168]$ \\
-$\gamma$: Asian population share    & $-0.0410^{*}$          & $-0.0398^{*}$          & $-0.0401^{*}$          & $-0.0409^{*}$          \\
-                                    & $ [ -0.0597; -0.0223]$ & $ [ -0.0584; -0.0212]$ & $ [ -0.0587; -0.0215]$ & $ [ -0.0596; -0.0222]$ \\
-$\gamma$: Hispanic population share & $0.0009$               & $-0.0009$              & $-0.0008$              & $0.0008$               \\
-                                    & $ [ -0.0164;  0.0182]$ & $ [ -0.0181;  0.0163]$ & $ [ -0.0181;  0.0164]$ & $ [ -0.0165;  0.0181]$ \\
-$\gamma$: Other Minorities          & $0.0656$               & $0.0715$               & $0.0710$               & $0.0716$               \\
-                                    & $ [ -0.1926;  0.3239]$ & $ [ -0.1856;  0.3287]$ & $ [ -0.1863;  0.3284]$ & $ [ -0.1866;  0.3299]$ \\
-Accessibility                       &                        & $0.1610^{*}$           & $0.1472^{*}$           & $0.5865$               \\
-                                    &                        & $ [  0.0238;  0.2982]$ & $ [  0.0058;  0.2886]$ & $ [ -0.1778;  1.3508]$ \\
-$\lambda$: spatial correlation      & $0.6985^{*}$           & $0.6906^{*}$           & $0.6917^{*}$           & $0.6987^{*}$           \\
-                                    & $ [  0.6600;  0.7370]$ & $ [  0.6514;  0.7297]$ & $ [  0.6526;  0.7307]$ & $ [  0.6602;  0.7372]$ \\
+                                    & $ [ -0.0157;  0.0168]$ & $ [ -0.0149;  0.0172]$ & $ [ -0.0153;  0.0169]$ & $ [ -0.0157;  0.0168]$ \\
+$\gamma$: Asian population share    & $-0.0410^{*}$          & $-0.0397^{*}$          & $-0.0401^{*}$          & $-0.0409^{*}$          \\
+                                    & $ [ -0.0597; -0.0223]$ & $ [ -0.0582; -0.0212]$ & $ [ -0.0587; -0.0216]$ & $ [ -0.0596; -0.0222]$ \\
+$\gamma$: Hispanic population share & $0.0009$               & $-0.0015$              & $-0.0012$              & $0.0008$               \\
+                                    & $ [ -0.0164;  0.0182]$ & $ [ -0.0185;  0.0156]$ & $ [ -0.0184;  0.0159]$ & $ [ -0.0165;  0.0181]$ \\
+$\gamma$: Other Minorities          & $0.0656$               & $0.0723$               & $0.0719$               & $0.0716$               \\
+                                    & $ [ -0.1926;  0.3239]$ & $ [ -0.1840;  0.3286]$ & $ [ -0.1849;  0.3287]$ & $ [ -0.1866;  0.3299]$ \\
+Accessibility                       &                        & $0.2306^{*}$           & $0.1923^{*}$           & $0.5865$               \\
+                                    &                        & $ [  0.0907;  0.3705]$ & $ [  0.0498;  0.3347]$ & $ [ -0.1778;  1.3508]$ \\
+$\lambda$: spatial correlation      & $0.6985^{*}$           & $0.6854^{*}$           & $0.6885^{*}$           & $0.6987^{*}$           \\
+                                    & $ [  0.6600;  0.7370]$ & $ [  0.6459;  0.7249]$ & $ [  0.6492;  0.7278]$ & $ [  0.6602;  0.7372]$ \\
 \midrule
@@
 Parameters                          & $27$                   & $28$                   & $28$                   & $28$                   \\
-Log Likelihood                      & $-4438.0569$           & $-4435.5066$           & $-4436.0465$           & $-4436.9264$           \\
+Log Likelihood                      & $-4438.0569$           & $-4433.0965$           & $-4434.7087$           & $-4436.9264$           \\
 \bottomrule
-\multicolumn{5}{l}{\scriptsize{$^*$ 0 outside the confidence interval. 95\% confidence interval in brackets.}}
+\multicolumn{5}{l}{\scriptsize{$^*$ Null hypothesis value outside the confidence interval. 95\% confidence interval in brackets.}}
 \end{tabular}
@@
 \midrule
-(Intercept)                         & $71.6539^{*}$         & $71.7489^{*}$         & $71.7525^{*}$         & $71.7182^{*}$         \\
-                                    & $ [61.1144; 82.1933]$ & $ [61.2170; 82.2809]$ & $ [61.2164; 82.2887]$ & $ [61.1846; 82.2518]$ \\
-log(Density)                        & $-0.0294$             & $-0.0307$             & $-0.0306$             & $-0.0266$             \\
-                                    & $ [-0.1037;  0.0448]$ & $ [-0.1050;  0.0436]$ & $ [-0.1049;  0.0437]$ & $ [-0.1009;  0.0478]$ \\
-log(Income)                         & $-0.4849^{*}$         & $-0.4907^{*}$         & $-0.4908^{*}$         & $-0.4861^{*}$         \\
-                                    & $ [-0.7612; -0.2085]$ & $ [-0.7672; -0.2141]$ & $ [-0.7674; -0.2142]$ & $ [-0.7623; -0.2098]$ \\
-Fulltime                            & $-0.0137^{*}$         & $-0.0137^{*}$         & $-0.0137^{*}$         & $-0.0139^{*}$         \\
-                                    & $ [-0.0244; -0.0031]$ & $ [-0.0244; -0.0030]$ & $ [-0.0244; -0.0030]$ & $ [-0.0246; -0.0032]$ \\
+(Intercept)                         & $71.6539^{*}$         & $71.7483^{*}$         & $71.7551^{*}$         & $71.7182^{*}$         \\
+                                    & $ [61.1144; 82.1933]$ & $ [61.2129; 82.2836]$ & $ [61.2150; 82.2951]$ & $ [61.1846; 82.2518]$ \\
+log(Density)                        & $-0.0294$             & $-0.0308$             & $-0.0307$             & $-0.0266$             \\
+                                    & $ [-0.1037;  0.0448]$ & $ [-0.1051;  0.0435]$ & $ [-0.1050;  0.0436]$ & $ [-0.1009;  0.0478]$ \\
+log(Income)                         & $-0.4849^{*}$         & $-0.4974^{*}$         & $-0.4956^{*}$         & $-0.4861^{*}$         \\
+                                    & $ [-0.7612; -0.2085]$ & $ [-0.7743; -0.2205]$ & $ [-0.7724; -0.2187]$ & $ [-0.7623; -0.2098]$ \\
+Fulltime                            & $-0.0137^{*}$         & $-0.0137^{*}$         & $-0.0136^{*}$         & $-0.0139^{*}$         \\
+                                    & $ [-0.0244; -0.0031]$ & $ [-0.0244; -0.0030]$ & $ [-0.0243; -0.0029]$ & $ [-0.0246; -0.0032]$ \\
 College-educated                    & $0.0343^{*}$          & $0.0343^{*}$          & $0.0343^{*}$          & $0.0340^{*}$          \\
-                                    & $ [ 0.0211;  0.0474]$ & $ [ 0.0211;  0.0474]$ & $ [ 0.0211;  0.0474]$ & $ [ 0.0208;  0.0471]$ \\
+                                    & $ [ 0.0211;  0.0474]$ & $ [ 0.0211;  0.0474]$ & $ [ 0.0212;  0.0475]$ & $ [ 0.0208;  0.0471]$ \\
 Single Adults                       & $0.0010$              & $0.0010$              & $0.0010$              & $0.0012$              \\
-                                    & $ [-0.0082;  0.0103]$ & $ [-0.0083;  0.0103]$ & $ [-0.0083;  0.0102]$ & $ [-0.0081;  0.0104]$ \\
-Youth (0-17)                        & $0.0051$              & $0.0052$              & $0.0052$              & $0.0054$              \\
-                                    & $ [-0.0099;  0.0201]$ & $ [-0.0098;  0.0202]$ & $ [-0.0098;  0.0202]$ & $ [-0.0096;  0.0204]$ \\
+                                    & $ [-0.0082;  0.0103]$ & $ [-0.0082;  0.0103]$ & $ [-0.0082;  0.0103]$ & $ [-0.0081;  0.0104]$ \\
+Youth (0-17)                        & $0.0051$              & $0.0054$              & $0.0054$              & $0.0054$              \\
+                                    & $ [-0.0099;  0.0201]$ & $ [-0.0095;  0.0204]$ & $ [-0.0096;  0.0204]$ & $ [-0.0096;  0.0204]$ \\
 Young adults (18-34)                & $-0.0095$             & $-0.0097$             & $-0.0098$             & $-0.0094$             \\
                                     & $ [-0.0206;  0.0016]$ & $ [-0.0209;  0.0014]$ & $ [-0.0209;  0.0014]$ & $ [-0.0205;  0.0017]$ \\
-Seniors (65+)                       & $-0.0826^{*}$         & $-0.0821^{*}$         & $-0.0821^{*}$         & $-0.0825^{*}$         \\
-                                    & $ [-0.0977; -0.0675]$ & $ [-0.0973; -0.0669]$ & $ [-0.0973; -0.0670]$ & $ [-0.0976; -0.0673]$ \\
-Black population share              & $0.0462^{*}$          & $0.0462^{*}$          & $0.0462^{*}$          & $0.0461^{*}$          \\
+Seniors (65+)                       & $-0.0826^{*}$         & $-0.0818^{*}$         & $-0.0819^{*}$         & $-0.0825^{*}$         \\
+                                    & $ [-0.0977; -0.0675]$ & $ [-0.0969; -0.0666]$ & $ [-0.0970; -0.0667]$ & $ [-0.0976; -0.0673]$ \\
+Black population share              & $0.0462^{*}$          & $0.0463^{*}$          & $0.0462^{*}$          & $0.0461^{*}$          \\
                                     & $ [ 0.0414;  0.0511]$ & $ [ 0.0414;  0.0511]$ & $ [ 0.0414;  0.0510]$ & $ [ 0.0413;  0.0510]$ \\
-Asian population share              & $-0.1010^{*}$         & $-0.1010^{*}$         & $-0.1010^{*}$         & $-0.1009^{*}$         \\
+Asian population share              & $-0.1010^{*}$         & $-0.1011^{*}$         & $-0.1010^{*}$         & $-0.1009^{*}$         \\
                                     & $ [-0.1069; -0.0950]$ & $ [-0.1070; -0.0951]$ & $ [-0.1070; -0.0951]$ & $ [-0.1068; -0.0949]$ \\
@@
                                     & $ [-0.0118; -0.0007]$ & $ [-0.0116; -0.0006]$ & $ [-0.0116; -0.0006]$ & $ [-0.0117; -0.0007]$ \\
-Other Minorities                    & $-0.0642^{*}$         & $-0.0646^{*}$         & $-0.0647^{*}$         & $-0.0637^{*}$         \\
-                                    & $ [-0.1127; -0.0156]$ & $ [-0.1132; -0.0161]$ & $ [-0.1133; -0.0162]$ & $ [-0.1122; -0.0151]$ \\
-$\gamma$: log(Density)              & $-0.5545^{*}$         & $-0.5565^{*}$         & $-0.5567^{*}$         & $-0.5445^{*}$         \\
-                                    & $ [-0.7908; -0.3182]$ & $ [-0.7927; -0.3203]$ & $ [-0.7929; -0.3204]$ & $ [-0.7812; -0.3079]$ \\
-$\gamma$: log(Income)               & $-0.0863$             & $-0.1004$             & $-0.0987$             & $-0.0783$             \\
-                                    & $ [-0.7966;  0.6240]$ & $ [-0.8108;  0.6100]$ & $ [-0.8091;  0.6118]$ & $ [-0.7883;  0.6317]$ \\
+Other Minorities                    & $-0.0642^{*}$         & $-0.0649^{*}$         & $-0.0649^{*}$         & $-0.0637^{*}$         \\
+                                    & $ [-0.1127; -0.0156]$ & $ [-0.1135; -0.0164]$ & $ [-0.1135; -0.0164]$ & $ [-0.1122; -0.0151]$ \\
+$\gamma$: log(Density)              & $-0.5545^{*}$         & $-0.5544^{*}$         & $-0.5550^{*}$         & $-0.5445^{*}$         \\
+                                    & $ [-0.7908; -0.3182]$ & $ [-0.7907; -0.3182]$ & $ [-0.7913; -0.3187]$ & $ [-0.7812; -0.3079]$ \\
+$\gamma$: log(Income)               & $-0.0863$             & $-0.1110$             & $-0.1063$             & $-0.0783$             \\
+                                    & $ [-0.7966;  0.6240]$ & $ [-0.8220;  0.6000]$ & $ [-0.8173;  0.6047]$ & $ [-0.7883;  0.6317]$ \\
 $\gamma$: Fulltime                  & $-0.0118$             & $-0.0115$             & $-0.0116$             & $-0.0116$             \\
-                                    & $ [-0.0404;  0.0169]$ & $ [-0.0402;  0.0172]$ & $ [-0.0402;  0.0171]$ & $ [-0.0402;  0.0171]$ \\
+                                    & $ [-0.0404;  0.0169]$ & $ [-0.0401;  0.0172]$ & $ [-0.0403;  0.0171]$ & $ [-0.0402;  0.0171]$ \\
 $\gamma$: College-educated          & $0.0698^{*}$          & $0.0698^{*}$          & $0.0699^{*}$          & $0.0710^{*}$          \\
                                     & $ [ 0.0334;  0.1062]$ & $ [ 0.0334;  0.1062]$ & $ [ 0.0335;  0.1063]$ & $ [ 0.0346;  0.1075]$ \\
-$\gamma$: Single Adults             & $-0.0114$             & $-0.0113$             & $-0.0114$             & $-0.0117$             \\
-                                    & $ [-0.0368;  0.0140]$ & $ [-0.0367;  0.0140]$ & $ [-0.0368;  0.0140]$ & $ [-0.0371;  0.0137]$ \\
-$\gamma$: Youth (0-17)              & $-0.0330$             & $-0.0330$             & $-0.0332$             & $-0.0326$             \\
-                                    & $ [-0.0748;  0.0088]$ & $ [-0.0748;  0.0088]$ & $ [-0.0750;  0.0086]$ & $ [-0.0744;  0.0092]$ \\
-$\gamma$: Young adults (18-34)      & $-0.0238$             & $-0.0247$             & $-0.0248$             & $-0.0235$             \\
-                                    & $ [-0.0545;  0.0069]$ & $ [-0.0554;  0.0060]$ & $ [-0.0555;  0.0059]$ & $ [-0.0542;  0.0071]$ \\
-$\gamma$: Seniors (65+)             & $-0.0222$             & $-0.0217$             & $-0.0218$             & $-0.0222$             \\
-                                    & $ [-0.0629;  0.0185]$ & $ [-0.0624;  0.0190]$ & $ [-0.0625;  0.0189]$ & $ [-0.0628;  0.0185]$ \\
-$\gamma$: Black population share    & $0.0186^{*}$          & $0.0186^{*}$          & $0.0186^{*}$          & $0.0185^{*}$          \\
-                                    & $ [ 0.0080;  0.0292]$ & $ [ 0.0080;  0.0292]$ & $ [ 0.0080;  0.0292]$ & $ [ 0.0079;  0.0291]$ \\
-$\gamma$: Asian population share    & $-0.0460^{*}$         & $-0.0462^{*}$         & $-0.0461^{*}$         & $-0.0461^{*}$         \\
-                                    & $ [-0.0594; -0.0325]$ & $ [-0.0596; -0.0327]$ & $ [-0.0596; -0.0327]$ & $ [-0.0595; -0.0327]$ \\
-$\gamma$: Hispanic population share & $0.0257^{*}$          & $0.0263^{*}$          & $0.0263^{*}$          & $0.0258^{*}$          \\
-                                    & $ [ 0.0129;  0.0386]$ & $ [ 0.0134;  0.0392]$ & $ [ 0.0134;  0.0391]$ & $ [ 0.0130;  0.0386]$ \\
-$\gamma$: Other Minorities          & $0.0794$              & $0.0789$              & $0.0790$              & $0.0767$              \\
-                                    & $ [-0.0648;  0.2236]$ & $ [-0.0652;  0.2230]$ & $ [-0.0652;  0.2231]$ & $ [-0.0674;  0.2209]$ \\
-Physical Activity                   & $-0.4807^{*}$         & $-0.4803^{*}$         & $-0.4803^{*}$         & $-0.4803^{*}$         \\
-                                    & $ [-0.5048; -0.4566]$ & $ [-0.5044; -0.4561]$ & $ [-0.5044; -0.4562]$ & $ [-0.5044; -0.4562]$ \\
-$\gamma$: Physical Activity         & $0.0180$              & $0.0195$              & $0.0194$              & $0.0173$              \\
-                                    & $ [-0.0397;  0.0757]$ & $ [-0.0383;  0.0772]$ & $ [-0.0383;  0.0772]$ & $ [-0.0404;  0.0750]$ \\
-Accessibility                       &                       & $-0.0349$             & $-0.0352$             & $-0.2630$             \\
-                                    &                       & $ [-0.1095;  0.0397]$ & $ [-0.1129;  0.0425]$ & $ [-0.6491;  0.1232]$ \\
-$\lambda$: spatial correlation      & $0.8363^{*}$          & $0.8357^{*}$          & $0.8360^{*}$          & $0.8361^{*}$          \\
-                                    & $ [ 0.8101;  0.8625]$ & $ [ 0.8094;  0.8620]$ & $ [ 0.8098;  0.8622]$ & $ [ 0.8099;  0.8624]$ \\
+$\gamma$: Single Adults             & $-0.0114$             & $-0.0112$             & $-0.0114$             & $-0.0117$             \\
+                                    & $ [-0.0368;  0.0140]$ & $ [-0.0366;  0.0141]$ & $ [-0.0368;  0.0140]$ & $ [-0.0371;  0.0137]$ \\
+$\gamma$: Youth (0-17)              & $-0.0330$             & $-0.0325$             & $-0.0328$             & $-0.0326$             \\
+                                    & $ [-0.0748;  0.0088]$ & $ [-0.0743;  0.0093]$ & $ [-0.0746;  0.0090]$ & $ [-0.0744;  0.0092]$ \\
+$\gamma$: Young adults (18-34)      & $-0.0238$             & $-0.0246$             & $-0.0248$             & $-0.0235$             \\
+                                    & $ [-0.0545;  0.0069]$ & $ [-0.0553;  0.0060]$ & $ [-0.0555;  0.0059]$ & $ [-0.0542;  0.0071]$ \\
+$\gamma$: Seniors (65+)             & $-0.0222$             & $-0.0208$             & $-0.0212$             & $-0.0222$             \\
+                                    & $ [-0.0629;  0.0185]$ & $ [-0.0616;  0.0199]$ & $ [-0.0620;  0.0195]$ & $ [-0.0628;  0.0185]$ \\
+$\gamma$: Black population share    & $0.0186^{*}$          & $0.0187^{*}$          & $0.0187^{*}$          & $0.0185^{*}$          \\
+                                    & $ [ 0.0080;  0.0292]$ & $ [ 0.0081;  0.0293]$ & $ [ 0.0081;  0.0293]$ & $ [ 0.0079;  0.0291]$ \\
+$\gamma$: Asian population share    & $-0.0460^{*}$         & $-0.0461^{*}$         & $-0.0460^{*}$         & $-0.0461^{*}$         \\
+                                    & $ [-0.0594; -0.0325]$ & $ [-0.0595; -0.0326]$ & $ [-0.0595; -0.0326]$ & $ [-0.0595; -0.0327]$ \\
+$\gamma$: Hispanic population share & $0.0257^{*}$          & $0.0264^{*}$          & $0.0264^{*}$          & $0.0258^{*}$          \\
+                                    & $ [ 0.0129;  0.0386]$ & $ [ 0.0136;  0.0393]$ & $ [ 0.0135;  0.0393]$ & $ [ 0.0130;  0.0386]$ \\
+$\gamma$: Other Minorities          & $0.0794$              & $0.0786$              & $0.0786$              & $0.0767$              \\
+                                    & $ [-0.0648;  0.2236]$ & $ [-0.0655;  0.2227]$ & $ [-0.0655;  0.2228]$ & $ [-0.0674;  0.2209]$ \\
+Physical Activity                   & $-0.4807^{*}$         & $-0.4798^{*}$         & $-0.4800^{*}$         & $-0.4803^{*}$         \\
+                                    & $ [-0.5048; -0.4566]$ & $ [-0.5039; -0.4556]$ & $ [-0.5041; -0.4558]$ & $ [-0.5044; -0.4562]$ \\
+$\gamma$: Physical Activity         & $0.0180$              & $0.0207$              & $0.0204$              & $0.0173$              \\
+                                    & $ [-0.0397;  0.0757]$ & $ [-0.0371;  0.0785]$ & $ [-0.0375;  0.0782]$ & $ [-0.0404;  0.0750]$ \\
+Accessibility                       &                       & $-0.0495$             & $-0.0471$             & $-0.2630$             \\
+                                    &                       & $ [-0.1260;  0.0270]$ & $ [-0.1259;  0.0316]$ & $ [-0.6491;  0.1232]$ \\
+$\lambda$: spatial correlation      & $0.8363^{*}$          & $0.8362^{*}$          & $0.8365^{*}$          & $0.8361^{*}$          \\
+                                    & $ [ 0.8101;  0.8625]$ & $ [ 0.8100;  0.8624]$ & $ [ 0.8103;  0.8627]$ & $ [ 0.8099;  0.8624]$ \\
 \midrule
@@
 Parameters                          & $29$                  & $30$                  & $30$                  & $30$                  \\
-Log Likelihood                      & $-3114.3931$          & $-3113.9742$          & $-3113.9998$          & $-3113.5028$          \\
+Log Likelihood                      & $-3114.3931$          & $-3113.5891$          & $-3113.7048$          & $-3113.5028$          \\
 \bottomrule
-\multicolumn{5}{l}{\scriptsize{$^*$ 0 outside the confidence interval. 95\% confidence interval in brackets.}}
+\multicolumn{5}{l}{\scriptsize{$^*$ Null hypothesis value outside the confidence interval. 95\% confidence interval in brackets.}}
 \end{tabular}

### 2020-09-25 manuscript/submission/manuscript.tex
Update manuscript for reviewers

@@
 \usepackage[colorlinks,bookmarksopen,bookmarksnumbered,citecolor=red,urlcolor=red]{hyperref}
-\renewcommand{\appendixname}{Supplementary Material}
 
@@
 the coefficients are equivalent; this test produces \(p\)-value of only
-\(1.307e-23\). Though this statistic is well beneath a common hypothesis
-test threshold of \(\alpha = 0.05\), we elect to retain the null hypothesis
-that the coefficients are equivalent, as the differences are at no point
-practically different from each other. The consequences of rejecting the
-null hypothesis in this case would be to suggest a model with spatial
-dependence of the dependent variable; as stated above, we feel that such
-a relationship is unreasonable. As a consequence of these analyses, we
-adopt the SDEM specification moving forward as the spatial lag of the
-errors is significant and the overall log likelihood of the SDEM is
-higher than the SLX specification.
+\(1.318e-23\). Though this statistic is well beneath a common hypothesis
+test threshold of \(\alpha = 0.05\), we elect to retain the null
+hypothesis that the coefficients are equivalent, as the differences are
+at no point practically different from each other. The consequences of
+rejecting the null hypothesis in this case would be to suggest a model
+with spatial dependence of the dependent variable; as stated above, we
+feel that such a relationship is unreasonable. As a consequence of these
+analyses, we adopt the SDEM specification moving forward as the spatial
+lag of the errors is significant and the overall log likelihood of the
+SDEM is higher than the SLX specification.
 
@@
 % latex table generated in R 4.0.0 by xtable 1.8-4 package
-% Thu Jun  4 16:31:52 2020
- (Intercept) & -15.8424 & -26.8735 & -4.8112 &   & -24.9740 & -41.8930 & -8.0549 \\
-  log(Density) & 0.0484 & -0.1314 & 0.2282 &   & 0.1775 & 0.0384 & 0.3166 \\
-  log(Income) & 5.8210 & 5.2977 & 6.3443 &   & 5.9985 & 5.5746 & 6.4224 \\
-  Fulltime & 0.1150 & 0.0936 & 0.1365 &   & 0.1275 & 0.1090 & 0.1460 \\
-  College-educated & 0.0012 & -0.0272 & 0.0297 &   & 0.0076 & -0.0158 & 0.0309 \\
-  Single Adults & -0.0433 & -0.0623 & -0.0244 &   & -0.0362 & -0.0526 & -0.0198 \\
-  Youth (0-17) & -0.1511 & -0.1830 & -0.1192 &   & -0.1310 & -0.1576 & -0.1045 \\
-  Young adults (18-34) & 0.0257 & 0.0008 & 0.0505 &   & 0.0295 & 0.0094 & 0.0496 \\
-  Seniors (65+) & 0.0137 & -0.0185 & 0.0459 &   & 0.0403 & 0.0130 & 0.0677 \\
-  Black population share & -0.0465 & -0.0584 & -0.0346 &   & -0.0499 & -0.0586 & -0.0411 \\
-  Asian population share & -0.0686 & -0.0832 & -0.0541 &   & -0.0767 & -0.0873 & -0.0662 \\
-  Hispanic population share & -0.1017 & -0.1140 & -0.0894 &   & -0.1025 & -0.1116 & -0.0934 \\
-  Other Minorities & 0.0368 & -0.0643 & 0.1378 &   & 0.0037 & -0.0849 & 0.0923 \\
-  $\gamma$: log(Density) & 1.2594 & 0.9413 & 1.5774 &   & 1.0985 & 0.7155 & 1.4815 \\
-  $\gamma$: log(Income) & 2.3930 & 1.5476 & 3.2383 &   & 1.9742 & 0.9465 & 3.0020 \\
-  $\gamma$: Fulltime & -0.1398 & -0.1804 & -0.0991 &   & -0.0397 & -0.0869 & 0.0076 \\
-  $\gamma$: College-educated & -0.1312 & -0.1806 & -0.0818 &   & -0.0710 & -0.1305 & -0.0115 \\
-  $\gamma$: Single Adults & -0.0480 & -0.0821 & -0.0140 &   & -0.0082 & -0.0504 & 0.0339 \\
-  $\gamma$: Youth (0-17) & -0.1031 & -0.1618 & -0.0445 &   & -0.0108 & -0.0798 & 0.0583 \\
-  $\gamma$: Young adults (18-34) & 0.1191 & 0.0762 & 0.1619 &   & 0.0842 & 0.0335 & 0.1349 \\
-  $\gamma$: Seniors (65+) & 0.0108 & -0.0479 & 0.0695 &   & 0.0590 & -0.0102 & 0.1282 \\
-  $\gamma$: Black population share & 0.0096 & -0.0054 & 0.0247 &   & 0.0010 & -0.0151 & 0.0172 \\
-  $\gamma$: Asian population share & -0.0661 & -0.0840 & -0.0483 &   & -0.0397 & -0.0583 & -0.0210 \\
-  $\gamma$: Hispanic population share & -0.0060 & -0.0216 & 0.0097 &   & -0.0010 & -0.0182 & 0.0162 \\
-  $\gamma$: Other Minorities & 0.1868 & -0.0508 & 0.4244 &   & 0.0726 & -0.1845 & 0.3297 \\
-  Accessibility & 0.5430 & 0.4195 & 0.6666 &   & 0.1663 & 0.0277 & 0.3048 \\
-  $\lambda$: spatial correlation &  &  &  &   & 0.6905 & 0.6513 & 0.7296 \\
+% Thu Sep 24 13:41:03 2020
+ (Intercept) & -15.8791 & -26.8066 & -4.9515 &   & -24.7352 & -41.5391 & -7.9312 \\ 
+  log(Density) & 0.0502 & -0.1280 & 0.2284 &   & 0.1760 & 0.0371 & 0.3150 \\ 
+  log(Income) & 5.8667 & 5.3476 & 6.3859 &   & 6.0134 & 5.5901 & 6.4368 \\ 
+  Fulltime & 0.1157 & 0.0944 & 0.1369 &   & 0.1271 & 0.1086 & 0.1455 \\ 
+  College-educated & 0.0029 & -0.0253 & 0.0311 &   & 0.0077 & -0.0156 & 0.0310 \\ 
+  Single Adults & -0.0435 & -0.0623 & -0.0247 &   & -0.0365 & -0.0528 & -0.0201 \\ 
+  Youth (0-17) & -0.1528 & -0.1844 & -0.1211 &   & -0.1320 & -0.1585 & -0.1055 \\ 
+  Young adults (18-34) & 0.0245 & -0.0001 & 0.0492 &   & 0.0292 & 0.0092 & 0.0493 \\ 
+  Seniors (65+) & 0.0108 & -0.0212 & 0.0427 &   & 0.0386 & 0.0112 & 0.0659 \\ 
+  Black population share & -0.0471 & -0.0589 & -0.0353 &   & -0.0499 & -0.0586 & -0.0412 \\ 
+  Asian population share & -0.0684 & -0.0828 & -0.0540 &   & -0.0764 & -0.0870 & -0.0659 \\ 
+  Hispanic population share & -0.1003 & -0.1126 & -0.0881 &   & -0.1023 & -0.1114 & -0.0932 \\ 
+  Other Minorities & 0.0341 & -0.0661 & 0.1343 &   & 0.0047 & -0.0837 & 0.0931 \\ 
+  $\gamma$: log(Density) & 1.2513 & 0.9367 & 1.5659 &   & 1.0873 & 0.7062 & 1.4684 \\ 
+  $\gamma$: log(Income) & 2.3641 & 1.5266 & 3.2016 &   & 1.9780 & 0.9563 & 2.9997 \\ 
+  $\gamma$: Fulltime & -0.1346 & -0.1749 & -0.0943 &   & -0.0411 & -0.0882 & 0.0059 \\ 
+  $\gamma$: College-educated & -0.1201 & -0.1692 & -0.0711 &   & -0.0704 & -0.1296 & -0.0112 \\ 
+  $\gamma$: Single Adults & -0.0520 & -0.0857 & -0.0183 &   & -0.0094 & -0.0514 & 0.0325 \\ 
+  $\gamma$: Youth (0-17) & -0.1013 & -0.1594 & -0.0432 &   & -0.0128 & -0.0815 & 0.0559 \\ 
+  $\gamma$: Young adults (18-34) & 0.1131 & 0.0706 & 0.1555 &   & 0.0838 & 0.0334 & 0.1342 \\ 
+  $\gamma$: Seniors (65+) & 0.0015 & -0.0568 & 0.0598 &   & 0.0545 & -0.0145 & 0.1235 \\ 
+  $\gamma$: Black population share & 0.0099 & -0.0051 & 0.0248 &   & 0.0011 & -0.0149 & 0.0172 \\ 
+  $\gamma$: Asian population share & -0.0644 & -0.0821 & -0.0467 &   & -0.0397 & -0.0582 & -0.0212 \\ 
+  $\gamma$: Hispanic population share & -0.0074 & -0.0229 & 0.0081 &   & -0.0015 & -0.0185 & 0.0156 \\ 
+  $\gamma$: Other Minorities & 0.1629 & -0.0725 & 0.3983 &   & 0.0723 & -0.1840 & 0.3286 \\ 
+  Accessibility & 0.6575 & 0.5348 & 0.7801 &   & 0.2306 & 0.0907 & 0.3705 \\ 
+  $\lambda$: spatial correlation &  &  &  &   & 0.6854 & 0.6459 & 0.7249 \\
 
 \midrule
-Log Likelihood & \multicolumn{3}{c}{$-4831.974$} & & \multicolumn{3}{c}{$-4435.507$}\\
-Num.Obs.       & \multicolumn{3}{c}{$2099$}   & & \multicolumn{3}{c}{$2099$}\\
+Log Likelihood & \multicolumn{3}{c}{$-4,815$} & & \multicolumn{3}{c}{$-4,433$}\\
+Num.Obs.       & \multicolumn{3}{c}{$2,099$}   & & \multicolumn{3}{c}{$2,099$}\\
 \bottomrule
@@
 clarity but do not change meaningfully across the four specifications.
-Complete model estimates are available in Table \ref{tab:pa-fullmodels}. Each of the
-three utility-based specifications is significant at the
-\(\alpha = 0.05\) level or lower, and is of the hypothesized
-directionality. That is, residents living in tracts with increased
-utility-based accessibility to green spaces show a significantly higher
-physical activity participation rate. Taking the rough mean of the 2
-estimated utility-based coefficients, moving from the least-accessible
-tract (\(A_i = -3\)) to the most-accessible tract (\(A_i = 3\)) is
-expected to raise the physical activity rate by 0.9 percentage points.
-With the understanding of the full 95\% confidence interval, we could
-suggest that the true effect of excellent versus poor park access is
-anywhere between 0.06 and 1.8 percentage points.
-
-The 10-minute walk buffer is considerably less useful at isolating the
-effects of park ``access'' on physical activity rates. As so few tracts
-are located outside of the buffer, the standard error of the estimated
-effect is large and implies an effect on activity rates anywhere from a
-loss of 1.08 percentage points to a gain of 8.1.
+Complete model estimates are available in Table \ref{tab:pa-fullmodels}
+of the Supplementary Material. Each of the two utility-based
+specifications is significant at the \(\alpha = 0.05\) level or lower,
+and is of the hypothesized direction That is, residents living in tracts
+with increased utility-based accessibility to green spaces show a
+significantly higher physical activity participation rate. Taking the
+rough mean of the two estimated utility-based coefficients, moving from
+the least-accessible tract (\(A_i = -3\)) to the most-accessible tract
+(\(A_i = 3\)) is expected to raise the physical activity rate by 1.32
+percentage points. With the understanding of the full 95\% confidence
+interval, we could suggest that the true effect of excellent versus poor
+park access is anywhere between 0.3 and 2.1 percentage points.
+
+In contrast, 10-minute walk buffer is considerably less useful at
+isolating the effects of park ``access'' on physical activity rates. As
+so few tracts are located outside of the buffer, the standard error of
+the estimated effect is large and implies an effect on activity rates
+anywhere from a loss of 0.18 percentage points to a gain of 1.35.
 
@@
 as the 10-minute walk buffer. As before, the estimates of the other
-variables are available in Table \ref{tab:ob-fullmodel} in the Supplementary Material. The correlation between
-physical activity rates and obesity is clear; for every percentage point
-increase in physical activity rate, the expected obesity rate drops by
-\(0.43\) percentage points in all four accessibility specifications. The
-indirect effect of physical activity rates on obesity in neighboring
-zones is inconsequential, supporting our methodological assertion that
-public health variables are not spatially dependent, though the factors
-leading to them may be.
+variables are available in Table \ref{tab:ob-fullmodels} of the
+Supplementary Material. The correlation between physical activity rates
+and obesity is clear; for every percentage point increase in physical
+activity rate, the expected obesity rate drops by \(0.43\) percentage
+points in all four accessibility specifications. The indirect effect of
+physical activity rates on obesity in neighboring zones is
+inconsequential, supporting our methodological assertion that public
+health variables are not spatially dependent, though the factors leading
+to them may be.
 
@@
 ecological inference fallacy, where aggregate statistics mask or
-contradict disaggregated or individual-level trends. \textcolor{blue}{The socioeconomic
+contradict disaggregated or individual-level trends. The socioeconomic
 and public health data used in this study are only available at the
@@
 infeasible as the spatial lags of the independent variables introduced
-substantial collinearity in the model equations.} A large-sample survey
+substantial collinearity in the model equations. A large-sample survey
 of individuals in New York City, including measured physical activities
@@
 obtain a measure of a neighborhood's accessibility to park features that
-its residents most care about. In this paper, we proceed only
-incrementally towards this by adding some selected park amenities as an
-element of each park's attractiveness above and beyond its size. \textcolor{blue}{The set
-of amenities we included in the utility calculation --- and the
-contribution of each amenity to the overall utility --- was dictated by
-the availability of data on the park amenities in New York City and our
-ability to find comparable prior studies with transferrable utility
-parameters. We can envision a study where mobile device data revealing
-the home locations of park users would be paired with more detailed park
-amenities and use data (e.g.~geolocated Twitter data \emph{a la}
-\citet{roberts2017using}) to estimate the utility contribution of these
-features.} This could in turn provide a more nuanced understanding of the
-relationship between park accessibility, \textcolor{blue}{use,} and health outcomes.
+its residents most care about. The set of amenities we included in the
+utility calculation --- and the contribution of each amenity to the
+overall utility --- was dictated by the availability of open data on the
+park amenities in New York City and our ability to find comparable prior
+studies with transferable utility parameters. It is remarkable that our
+two utility specifications --- one with size and distance, and one with
+size and distance plus amenities --- result in such similar model
+estimates. This may indicate that the utility is driven largely by size
+and distance, or that the additional park amenities we included in the
+utility specification are spatially distributed in a way that correlates
+with the health outcomes. Either way, further analysis examining more
+amenity variables is warranted. We can envision a study where mobile
+device data revealing the home locations of park users would be paired
+with more detailed park amenities and use data (e.g.~geolocated Twitter
+data \emph{a la} \citet{roberts2017using}) to estimate the utility
+contribution of these features. This could in turn provide a more
+nuanced understanding of the relationship between park accessibility,
+use, and health outcomes.
 
@@
 when the non-highway mode share is high, as is likely when considering
-access to parks. \textcolor{blue}{We examined replacing the Euclidean distance with a
+access to parks. We examined replacing the Euclidean distance with a
 network-based distance; the choice of distance metric appeared
@@
 verify the accuracy of the underlying network data at the scale of this
-analysis. We therefore retain the Euclidean distance for simplicity.} A
+analysis. We therefore retain the Euclidean distance for simplicity. A
 better metric of travel impedance may be a mode choice model logsum,
@@
 health, or any number of potential beneficial outcomes hypothesized or
-explored in the existing literature. \textcolor{blue}{The COVID-19 pandemic and its
+explored in the existing literature. The COVID-19 pandemic and its
 associated social distancing behaviors in many regions of the world has
-also drawn attention to problems of park access, use, and equity.}
+also drawn attention to problems of park access, use, and equity.
 Exploring these connections and their underlying mechanisms should be a
@@
 measures of improvement in public health. Although many have theorized
-the link between park accessibility and these metrics, previous
-literature has produced mixed findings, perhaps owing to the range of
-variables modeled and the coarse spatial scale of the analyses. Using
-New York City as a case study, we presented a holistic and flexible
-measurement for park accessibility that compares the continuous distance
-to all parks in the region, weighted against the size of the park and
-its other amenities, with weights determinable through revealed
-preferences. In terms of physical activity, we found a positive
-relationship where the least park-accessible tracts have an expected
-physical activity participation rate between 0.06 and 1.8 percentage
-points lower than the most accessible tracts. We also found a suggestive
-though not significant relationship between park accessibility and
-expected obesity rates \emph{in addition to} the effect of physical
-activity participation.
+the link between park access and public health, previous literature has
+produced mixed findings, perhaps owing to the wide range of
+accessibility definitions. Using New York City as a case study, we
+presented a holistic and flexible measurement for park accessibility
+that compares the continuous distance to all parks in the region,
+weighted against the size of the park and its other amenities, with
+weights determinable through revealed preferences. In terms of physical
+activity, we found a positive relationship where the least
+park-accessible tracts have an expected physical activity participation
+rate between 0.06 and 1.8 percentage points lower than the most
+accessible tracts. We also found a suggestive though not significant
+relationship between park accessibility and expected obesity rates
+\emph{in addition to} the effect of physical activity participation.
 

### 2020-09-25 manuscript/manuscript.Rmd
Correct color palette in access map

@@
           alpha = 0.9, color = NA) +
-  scale_fill_brewer("Accessibility", palette = "RdYlBu")
+  scale_fill_manual("Accessibility", 
+                    values =   c("#F46D43", "#FDAE61", "#FEE090", "#E0F3F8", "#ABD9E9", 
+                                 "#74ADD1", "#4575B4"))
 ```

### 2020-09-25 manuscript/manuscript.Rmd
Minor edits to manuscript, rebuild

@@
 improvement in public health. Although many have theorized the link between park
-access and public, previous literature has produced mixed
+access and public health, previous literature has produced mixed
 findings, perhaps owing to the wide range of accessibility definitions. 

### 2020-09-25 manuscript/manuscript.tex
Update appendix labels and copy complete source tex file
Minor edits to manuscript, rebuild

@@
 % latex table generated in R 4.0.0 by xtable 1.8-4 package
-% Thu Sep 24 13:27:59 2020
+% Thu Sep 24 14:12:00 2020
  (Intercept) & -15.8791 & -26.8066 & -4.9515 &   & -24.7352 & -41.5391 & -7.9312 \\ 
@@
 measures of improvement in public health. Although many have theorized
-the link between park access and public, previous literature has
+the link between park access and public health, previous literature has
 produced mixed findings, perhaps owing to the wide range of
@@
 \hypertarget{appendix}{%
-\subsection{Appendix}\label{appendix}}
+\subsection{Supplementary Material}\label{appendix}}
+\setcounter{table}{0}
+\renewcommand{\thetable}{S\arabic{table}}
 

### 2020-09-25 manuscript/submission/manuscript.tex
Minor edits to manuscript, rebuild

@@
 their community is designed and built in such a way that such exercise
-is expensive, unenjoyable, or unsafe. \textcolor{blue}{It is similarly necessary for
+is expensive, unenjoyable, or unsafe. It is similarly necessary for
 urban planners to identify which neighborhoods have access to quality
@@
 new or rehabilitated green space, or improved transportation access to
-existing quality green space.}
+existing quality green space.
 
@@
 
-\textcolor{blue}{
 The question of how green space in the urban
@@
 studies produced mixed results, and nine studies found no association at
-all.}
-
-\textcolor{blue}{
+all.
+
 Loosely defined, the \emph{accessibility} of an arbitrary place
@@
 evaluate which residents have good access to quality green space may
-desire objective and therefore comparable measures.}
+desire objective and therefore comparable measures.
 
@@
 10-minute network-bound walk, paired with a demographic analysis of
-areas within and outside of this threshold. \textcolor{blue}{\citet{devries2003natural}
+areas within and outside of this threshold. \citet{devries2003natural}
 showed the amount of greenspace within a 3-kilometer radius was
@@
 relationship between the health of senior citizens and the number of
-parks within 500 meters.}
+parks within 500 meters.
 
@@
 distance-based isochrones are replaced with political, geographical, or
-statistical boundaries. \textcolor{blue}{For example, \citet{Mitchell2008} find that inequalities
+statistical boundaries. For example, \citet{Mitchell2008} find that inequalities
 in health outcomes attributable to income are mitigated in statistical areas
@@
 relationship in New York City between the percent of a residential ZIP code that
-is park space and objectively measured body mass index (BMI).} Political or
+is park space and objectively measured body mass index (BMI). Political or
 regional boundaries are
@@
 the attributes of a park influence walking more than merely the distance
-to it. \textcolor{blue}{\citet{hillsdon2006relationship} found no relationship between a
+to it. \citet{hillsdon2006relationship} found no relationship between a
 gravity-based accessibility term and self-reported physical activity
-among middle-aged individuals in Norwich, England.} \citet{Zhang2011}
+among middle-aged individuals in Norwich, England. \citet{Zhang2011}
 developed a population-weighted, gravity-based accessibility to parks
@@
 
-To our knowledge, there has been no previous attempt to examine access
+\textcolor{blue}{To our knowledge, there has been no previous attempt to examine access
 to parks in a metropolitan area using a utility-based definition as the
@@
 then apply this measure to study the effect of access to public parks on
-aggregate health outcomes.
+aggregate health outcomes.}
 
@@
 \end{equation}
-\textcolor{blue}{where \(X\) is a matrix of dimension \(n\times p\) where
+where \(X\) is a matrix of dimension \(n\times p\) where
 \(n\) is the number of observations and \(p\) is the number of predictor
@@
 parameter \(\beta_a\), and a vector \(\boldsymbol{\varepsilon}\)
-represents the model residual as a random variable.}
+represents the model residual as a random variable.
 
@@
 obtain a measure of a neighborhood's accessibility to park features that
-its residents most care about. The set of amenities we included in the
+its residents most care about. \textcolor{blue}{The set of amenities we included in the
 utility calculation --- and the contribution of each amenity to the
@@
 with the health outcomes. Either way, further analysis examining more
-amenity variables is warranted. We can envision a study where mobile
+amenity variables is warranted.} We can envision a study where mobile
 device data revealing the home locations of park users would be paired
@@
 reinforces our suggestion that a measure explicitly based in the utility
-of access is warranted. We acknowledge that a utility-based framework
+of access is warranted. \textcolor{blue}{We acknowledge that a utility-based framework
 for access may be more technically difficult for some practitioners to
@@
 (\url{https://www.walkscore.com}) abstract complex methodologies into
-tools that planners can and do readily apply.
+tools that planners can and do readily apply.}
 

### 2020-09-25 manuscript/submission/coverletter/coverletter.tex
New cover letter to editor

@@
 
-We would like to thank both reviewers for their thoughtful and helpful comments.
-We are delighted that they found our submission a “well-written paper that makes a useful contribution to the accessibility literature regarding quantifying accessibility” as well as “a nice added-value to the extensive literature on the subject.”
+Please find attached the second revision of our manuscript, \emph{Modeling the
+impacts of park access on health outcomes: a utility-based accessibility
+approach.}  We are pleased that one of the original referees appears wholly
+satisfied by  our revisions. Though we are disappointed that the other original
+referee could not provide comment, we are grateful to have received additional
+comments from a third referee.
 
-We feel we have addressed each comment raised by the reviewers, both major and minor.
-In particular, we re-executed our analysis using network distances in place of the Euclidean distances used in the original manuscript; the findings of this analysis were inconsequential, and our decision to retain the Euclidean specification is detailed in the attached response to reviewers.
+Many of the comments from this new referee were extraordinarily helpful to us as
+we seek to clarify the specific contribution of our work, and to ensure that it
+reaches the broadest possible audience. In particular, the recommendation to remove
+cemeteries from consideration modestly strengthened our econometric findings.
+At the same time, we feel that the new referee made some comments that we
+exhaustively addressed in our previous response to Referee 1 (using Euclidean
+distances, spatial resolution), or that contradict the recommendations of the
+original referee that did not re-review the manuscript (including data on park use).
 
-We are grateful for the opportunity to submit this revised manuscript for further review and consideration in {\em Environment and Planning B: Urban Analytics and City Science}.
+An attached document provides a more detailed response to each of the new
+referee's comments. We reiterate our willingness to supply more explanatory detail
+on our distance and spatial resolution investigations in a supplemental file at
+your invitation.
+
+Lastly, we are grateful for the opportunity to submit this revised manuscript for
+further review and consideration in {\em Environment and Planning B: Urban
+Analytics and City Science}.
 

### 2020-09-25 manuscript/manuscript.Rmd
Add sentence about putting amenities into utility in contribution
Also, minor typo correction

@@
 measure of park access in New York City, and then apply this measure to study the
-effect of access to public parks on aggregate health outcomes.
+effect of access to public parks on aggregate health outcomes. In this
+application, we demonstrate how additional park amenities including park size,
+sport facilities, playgrounds, and trails can be incorporated in a more complete
+and informative measure of access beyond simple proximity.
 
@@
 where the least park-accessible tracts have an expected physical activity
-participation rate between `r 6 * .01` and `r 6 * .3` percentage points lower than the most
+participation rate between $0.3$ and $2.1$ percentage points lower than the most
 accessible tracts. We also found a suggestive though not significant relationship

### 2020-09-25 manuscript/manuscript.tex
Add sentence about putting amenities into utility in contribution
Also, minor typo correction

@@
 then apply this measure to study the effect of access to public parks on
-aggregate health outcomes.
+aggregate health outcomes. In this application, we demonstrate how
+additional park amenities including park size, sport facilities,
+playgrounds, and trails can be incorporated in a more complete and
+informative measure of access beyond simple proximity.
 
@@
 % latex table generated in R 4.0.0 by xtable 1.8-4 package
-% Thu Sep 24 14:12:00 2020
+% Fri Sep 25 10:52:15 2020
  (Intercept) & -15.8791 & -26.8066 & -4.9515 &   & -24.7352 & -41.5391 & -7.9312 \\ 
@@
 park-accessible tracts have an expected physical activity participation
-rate between 0.06 and 1.8 percentage points lower than the most
+rate between \(0.3\) and \(2.1\) percentage points lower than the most
 accessible tracts. We also found a suggestive though not significant

### 2020-09-25 manuscript/submission/manuscript.tex
Add sentence about putting amenities into utility in contribution
Also, minor typo correction

@@
 then apply this measure to study the effect of access to public parks on
-aggregate health outcomes.}
+aggregate health outcomes. In this application, we demonstrate how additional
+park amenities including park size, sport facilities, playgrounds, and trails 
+can be incorporated in a more complete and informative measure of access beyond simple proximity.}
 
@@
 park-accessible tracts have an expected physical activity participation
-rate between 0.06 and 1.8 percentage points lower than the most
+rate between $0.3$ and $2.1$ percentage points lower than the most
 accessible tracts. We also found a suggestive though not significant

### 2020-11-11 manuscript/manuscript.Rmd
Final submission

@@
 classoption:
-  - shortAfour
+  - Crown
 output: 

### 2020-11-11 manuscript/manuscript.tex
Submit manuscript to editorial office
Final submission

@@
-\documentclass[shortAfour,sageh.bst]{sagej}
+\documentclass[Crown,sageh.bst]{sagej}
 
@@
 \renewcommand{\appendixname}{Supplementary Material}
-
+\renewcommand{\journalname}{Environment and Planning B: Urban Analytics and City Science}
 \usepackage{hyperref}
@@
 \usepackage{makecell}
-\usepackage{xcolor}
 
@@
 
-\affiliation{\affilnum{}{}\\\affilnum{}{}\\\affilnum{}{}}
+\affiliation{\affilnum{1}{Civil and Environmental Engineering Department, Brigham Young University}\\\affilnum{2}{Fehr and Peers, Los Angeles, California}\\\affilnum{3}{School of Civil and Environmental Engineering, Georgia Institute of Technology}}
 
@@
 % latex table generated in R 4.0.0 by xtable 1.8-4 package
-% Fri Sep 25 10:52:15 2020
+% Fri Oct  9 11:22:00 2020
  (Intercept) & -15.8791 & -26.8066 & -4.9515 &   & -24.7352 & -41.5391 & -7.9312 \\ 
